\documentstyle[11pt,twoside,manpage]{report}
\begin{document}

\begin{titlepage}
    \vspace*{1.0in}
    \begin{flushleft}
          {\huge\bf Marion Sutaken} \\[.25cm]
          {\huge\bf Roger Hagencamp} \\[.25cm]
          {\huge\bf LUPE} \\[.25cm]
          {\rule[.1in]{4.5in}{.02in}}\\[.25cm]
          {\bf Jim Mochel}\\
    \end{flushleft}
\end{titlepage}

\raggedbottom
\pagenumbering{arabic}
\pagestyle{headings}
\chapter*{Basic Stats}

\begin{manpage}{Basic Stats}{Lupe}{Version 1.1}

\subtitle{Name}
	Marion Sutaken, Lupe

\subtitle{Race}
	Human

\subtitle{Gender}
	Male, obviously

\subtitle{Lifestyle}
	See Elsewhere

\subtitle{Stats}

\begin{verbatim}
	Body			6(r)
	Quickness		6
	Strength		6
	Charisma		3(r)
	Intelligence	6
	Willpower		6(r)
	Essence			6
	Magick			0
	Reaction		6
\end{verbatim}

\begin{verbatim}
	Astral			6
	Defense			6
	Dodge			6
	KI				
\end{verbatim}

\begin{verbatim}
	Karma			11
\end{verbatim}

\end{manpage}

\newpage

\begin{manpage}{Skills}{Lupe}{Version 1.1}

\subtitle{Languages} 

	English--8, Japanese--4, German--7, Salish--1

\subtitle{Combat Skills}

(5)---Unarmed Cmbt--4,U. Cmbt(Martial)--6 \\
(3)---Unarmed Cmbt--2,U. Cmbt(Grappling)--5 \\
(4)---Ranged Cmbt--2,R. Cmbt(Pistol)--4,R. Cmbt(Spetsdod)--6 \\
(4)---Armed Cmbt--2,A. Cmbt(Swords)--4,A. Cmbt(Katana)--7 \\
(3)---Vehicle--3,Vehicle(Scorpion)--5 \\

Armed Cmbt(Staff)--1 \\

Running--2,Climbing--2,Jumping--2,Body Control--2,Stealth--3 \\
Acrobatics--5,Tumbling--4 \\

Psychology--2,Military Science--2 \\

Helicopter--1,Grenades--2 \\

\end{manpage}

\begin{manpage}{People We Know}{Lupe}{Version 1.1}

\subtitle{Thistle Morning}
	AKA Slither, Simone Kike, run by Donna.
	Late Teens , native american. Dark skin and Hair. Brown eyes.
	about 5'8''.

\subtitle{Trickster}
	AKA Trixy, run by Katherine

\subtitle{Lovecraft}
	AKA Carl Dallon, Randolph Carter \\
	Tall thin, Black Hair, Pale Complexion

\subtitle{Ferret}
	AKA Weasel, Frederick Valsius \\
	5'9'', Thin, Moussed Up Suicide Blond. Fashionable.
	Mirror Shades, Fair Skinned.

\subtitle{Roger Wolf}
	Ex Captain Wolfs Wabbits.

\subtitle{Paul Pierson Smith}
	``Butch'', Supply Sargent

\subtitle{Tozo Kensai}
	Mentor, Ex Criminal Psych.

\end{manpage}	

\begin{manpage}{Things We Have}{Lupe}{Version 1.1}
\subtitle{Current Funds}
	As Marion Sutaken : 32K, As Cover  4K

\subtitle{Stocks}
	Atlantis 6,280 (bought at 59) on June 1st.

\subtitle{Other Identities}
	Rger Hagencamp. Complete with driver's licsence and ID.

\end{manpage}

\begin{manpage}{General Equipment}{Lupe}{Version 1.1}
\subtitle{weaponry}
5 Spetsdods  Damage:3L1 \\
140 Darts for above \\

Smoke Grenades OOOOOOOOOOOO \\
Mini Grenades OOOOOOOOOO \\
Concussion Grenades OOOOOOOOOOOOOOO (4m3) \\
Gas Grenades OOOOOOOOOOOOO \\

9mm Broom Handle Mauser rebored for .45 cal. Laser Sighted with 
vindicator ratshot load. Has flasher embedded in sight base.

Nekode (high Tungsten Steel)

Flasher OO \\

Katana (High Tech)

Aug-CSL Weapon System \\
Assualt Rifle conceal:2 Ammo:40 Damage:5M3 Wt:4 \\
LMG conceal:NA Ammo:40 Damage:6M3 WT:5.5 \\

Throwing Knives OOOOOOO

Staff Made of 2 Defiance AZ-150 stun batons \\

APDS Ammo. \\

\subtitle{Armour}

Leather 0/2/1 \\
Armour Jacket 5/3/2 \\
ForeArm Guards \\
Helm for above \\

\subtitle{Security}
	Retinal Scanner \\
	Jammer (5) \\

\subtitle{Communication and Other}
	Wrist Model w/flip \\
 	Pocket Secretary \\

\subtitle{Disguise}
	Drop Tacs OO, Hair Wash, Cyper Eyes (reflective), Suits, Metal Ear Improvements
		
\subtitle{Vehicle}
	Harly Skorpion : Handling:3 Speed:50/160 Body:3 Armour:1 Signature:3 
	Pilot:2 Firmpoints:2 HardPoints:1 \\
	Grenade Launchers:2 armed with candy cane loads gas and concussion \\
	
\subtitle{Medical}
	Antidote Patches OO, Stim Patches(6) OO, Platinum Card med insurance \\

\subtitle{Other}
	Microflares OOOO, Stealth Grapple Line \\

\end{manpage}

\section{History}

{\bf Our second mission} We are hired by Joesph Mendela of Farad. They have
hired a special decker to do some very complex programming. 
He seems to be trapped in his programmin project. He is in an environment 
suit and his project is overdue. 

As a result of our skilled investigations we discover that Bryan
MacDonald, head of the project, is in the employ of MicroTek. He is
exposed and then dissappears from the face of the earth.

Marion and Thistle are approached by some rent-a-thugs. Lupe removes
them from the theater of operations. We sell the rent-a-thug's vehicle.
Marion and Thistle visit Thistle's lodge. Lupe talks to a small sprite.
We head back.

\end{document}


