h29630
s 00048/00000/00000
d D 1.1 99/12/02 16:06:50 jmochel 2 1
cC
cK55065
cO-rw-rw-rw-
e
s 00000/00000/00000
d D 1.0 99/12/02 16:06:46 jmochel 1 0
c BitKeeper file G:/SpaceHybrid/worlds/tanah/history/history.tex
cBjmochel@devilmountain.bedford.foliage.com|ChangeSet|19991202203126|52994|e2968a7f5cb68f67
cHdevilmountain.bedford.foliage.com
cK45041
cPworlds/tanah/history/history.tex
cReb4787ac5cb68f68
cZ-05:00
c______________________________________________________________________
e
u
U
f e 0
f x 33
t
T
I 2
\font\title=cmssdc10 scaled 2488 
\rightline{\title History of Tanah}
\vskip 1.5 true in

There are many waves of colonization that are a part of Tanah's
history. At the beginning there were only a few native races, known collectively
as the ``Tor''. The first wave consisted of the ``Lordim-Tor'' or
Lord-\=em-Tor. This stands for ``Lords-over-all-Earth''. 

Golden haired and red eyed, wielding immense power. They brought with them 
their own human servants. Their humans did not thrive in this new land 
so the Lordimtor bred them to the Tor. The end result was the forerunners 
to the Torgans.

Cities were built, Temples were set up. 
{\narrower\narrower Lordimtorka and Lordimtora eventually 
to be jnown as the Lord and Lady or Lorda and Lorka}

Not a golden age , but it could have been worse. The Tor came to
maintain a very uneasy truce with the Lordim.

The second wave was a mixture of the high and the lo. The Od\=an\=a 
Tall and Slim, and Golden eyed brought with them two races: The Hairoch
and the Drow. The Od\=an\=a were numerous and tried to take the 
land and cities from the Lordimtor. 

The creation of the Badlands. Also known as the hells

At the last, the Lordimtor were the  victors. But the cost was
great. The last of the Lordimtor to survive were the ones now
known as the Lord and the Lady. They bade the Drow to withdraw 
from their sight. The Drow instead waged war against the Lordim and
were almost totally destroyed. The Lordim then bade the Hairoch to 
withdraw and to only raise arms in defense of themselves and others.
Then did the Lord and the Lady dwell for a time with the Torgans. 


The third wave was large and widespread. The Duwan and the Kurrok 
came to one part of the continent and the elves to another.
These races were pursued by a race called the Mergoth. The Lord 
and the Lady batted with the Mergoth and closed the gates to this
world. In doing so they weakened themselves so that they must 
sleep for hundreds of years.

Next came the Human races. Widely spread. Next came the 
Rupa Kechil, unknown to the rest.

\bye
E 2
I 1
E 1
