\title{Cultures of Tanah}

\part{General}

\chapter*{Introduction}

The following are the cultures in the world of Tanah. Many of
these may be known to the world by other
names and some may be almost unknown or mythical in reputation.
Player Characters are unlikely to know much about the other cultures.

\section*{Human Cultures}

The human cultures available are listed below along with 
a smaller than thumbnail description :

\begin{itemize}
        \item [Kalifate(Kal-\={e}-f\={a}t)] Moorish Spain. 
        \item [Safoan(Sa-F\={o}-an)] Island Subgroup of the Kalifate.
        \item [Kothan(K\={o}-Than)] Germanik Viceral.
        \item [Tyronian(T\={i}-R\={o}-N\={e}-an)] Kothan gone over to Horse Nomadic
        \item [Emrik(Em-Rik)] Kothan subgroup
        \item [Vairman(Vair-Man)] Non-Scot Highlander culture
        \item [Dalesman(Dal-Man)] Old-Style Mormon Stereotype.
        \item [Arsa'e(Ar-sa-\={e})] Peublo based culture.
        \item [Tarmane(Tar-M\={a}n)] Masai Hunter Gatherer/Herder Types
        \item [Sarsin(Sar-Sin)] Persian Islamic, Jihads, Fanaticism
        \item [Merovan(Mer-\={O}-Van)] Norman Farmer
        \item [Hightan(H\={i}-Tan)] Scottish Highlander
        \item [Hairochon(Hair-o-K\={o}n)] Giant Dwarves, some similiarities to the
                BloodGuard of the Thomas Covenant series.
        \item [Thanaen(Tha-N\={a}-En)] Venetian culture, Sisterhood of Steel,
                Liaden
        \item [Horeshi] Egyptian Theocracy
\end{itemize}

\part{Cultural Descriptions}

\input duwan.cul
\input kurrock.cul
\input torgan.cul

\input kalifate.cul
\input arsae.cul
\input hightan.cul
\input dales.cul
\input vairman.cul
\input shan.cul
\input Thenaen.cul

\end{document}
