\documentstyle{article}
\title{The Koran Kingdom}
\begin{document}
\maketitle

\section{Overview}

The Koran Kingdom is a collection of city states under under one
ruling family. The kingdom is the end result of annexations of 
two existing cultures into a ordered collection of 
Duchies, Baronies, Earldoms, and Marches. 

The conquerers are a race called the Kylinds. 
The Kingdom is divided up into Fees, Earldoms, Baronies, 
and Duchies. 

Locale                        Annexed        Family

Aligoth             City                     Arlane
Meara               Duchy                    Du Malik
Kerny               Duchy                    Du Savat
Kassan              Duchy                    Ma Tavik
Mark                Duchy                    Lathonell
Longmoor            Duchy                    Bowman
Tolan               Duchy                    Ravenhost
Keldar              Duchy                    Kolin
Breman              Earldom                  NaJerhan
Saviney             Duchy                    Karric
Low Shor            Duchy                    Herosen     
Kart Moor           Duchy                    Sentil
Lankmoor Riding     Mark                     Kinard
Sifean              Earldom                  Arilin
Hoc Hollan          Earldom                  MacLorKre

There are at least seven distict cultures and at least 3 distinct
human races. Their are many subcultures growing out of this blend of
races. 
                    Predominant
Area                Race           Culture

Aligoth             Kylind         Mearan
Meara               Kylind         Mearan
Kerny               Kylind         Mearan
Kassan              Kylind         Kassani
Mark                Kylind         Mearan
Longmoor            Kylind         Mearan
Tolan               Merovan        Keldark
Keldar              Merovan        Keldark
Breman              Kylind         Bremani
Saviney             Merovan        Bremani
Low Shor            Kylind         Kassani
Kart Moor           Kylind         Mearan
Lankmoor Riding     Merovan        Lankmooran
Sifean              Merovan        Elvish
Hoc Hollan          Hightan        Hightan

Aligoth         

The city state of Aligoth has a number of very important resources.
It has two deep, steady, and navigable rivers. It lies in a rich fertile
valley with heavy forests and good farming. There are large deposits of
Iron, and copper as well as some gold.

Meara           

The Duchy of Meara is at a higher altitude than Aligoth but it also
has access to two rivers though these are not navigable at all. Despite
this Meara has a gorgeous seaport called Solana as well as many silver and
Copper deposits. 

Kerny           

Kerny is as high as Meara and without a decent port, however there
are several plants and fruits which seem to grow only in the Kerny soil an
thus there are many wines and luxury goods from the area. There is some
silver mining in the eastern hills of Kerny.

Kassan          

A resource poor region it produces some of the most notable theologians 

Mark            
Longmoor        
Tolan           
Keldar          
Breman          
Saviney         
Low Shor        
Kart Moor       
Lankmoor Riding 
Sifean          
Hoc Hollan      



 
