\title{\large{Hybrid}\thanks{Copyright 1998} \large{: Players Guide} }
\author{Jim Mochel}
\date{\today}

\listof{SHTable}{Tables}

\chapter{Quick and Dirty Intro to the mechanics}

\section{Rolling dice}

There is one main type of roll in \SH\ . The roll is 
made with percentile dice against a Success Chance (SC). If the roll 
is under or equal to the Success Chance, then the roll is successful.
If it is greater than the Success Chance then it is a failure.

The Success Chance is the percentage chance to perform a given task This SC is
determined from the statistics and skill of the character 
and modified based on the difficulty of the task. The most common 
modifier is called a Difficulty Factor (DF). This is a number that typically 
ranges from -10 to +10.

$ {Success Chance} = 3 \times {The\ Stat} + Rank \times 4 + {Difficulty\ of\ Task} \times 5 $

As an example if the player character has a Physical Strength (PST) of 15, a rank in 
weight lifting of 4 and is trying to lift half his weight in mass ( a Difficulty Factor or DF of -5). 
This means the Success Chance (SC) is $ SC = 3 \times PST + Rank \times 4 + DF \times 5 $
In the case of the weightlifting this means $ SC = 3 \times 15 + 4 \times 4 + -5 \times 5  = 36\% $

\subsection{Open-ended Rolls}

The range of die rolls is 1-100. If you roll 00 (a 100) you roll again add
\index{Open-ended Rolls}
the second roll to the first to get our total.

\subsection{Evaluating Success and Failure}

When percentile dice are rolled and the result is under the success chance, that
is a normal success. When the rolled number is significantly lower than the needed 
roll there is a chance the action may have a greater than normal success. This is 
called a ``Critical'' success. Table \ref{Table:CriticalSuccess} on page on
\index{Critical Success}
page~\pageref{Table:CriticalSuccess} describes the rolls needed.

As an example. If a character needed to roll a 40 or under to hit a target 
with a rock and they rolled under $ 1/2 $ of 40 then they will do 1.25
times the damage they would normally do.

In the case of very poor rolls there is a chance that the roll  
may be a critical failure This is caused by rolling 50 above your success chance or 
rolling above by $ 1/2 $ the success chance of the action, whichever is greater.

So someone with a success chance of 90 needs to roll a 140 or higher to
critically miss while someone with a success chance of 120 needs to roll a
180 or higher to critically miss.

To determine the severity of the critical failure roll against the 
amount missed by as a success chance and compare the result to table
\index{Critical Failure}
\ref{Table:CriticalFailure} on page~\pageref{Table:CriticalFailure}.

\input{troll1.tex}
\input{troll2.tex}




\chapter{Tasks and Skills}

A \ndx{task} is an action or a group of actions to be performed. Each task has a 
difficulty associated with it. That combined with the knowledge of the character's 
rank in the skill and their stats allows us to determine the percentile roll needed 
to succeed.

To do a task the character determines the \ndx{Difficulty Factor} {\em DF} of the 
task and what skill(s) may be used to do the task. A base chance to 
{\em \ndx{BC}} is determined and modified by the difficulty factor 
of the task. 

Forcing a locked door is a task that has some difficulty. If the 
character has no skill in forcing doors then they are forcing the 
door based on using just physical strength. Their chance to force the 
door is based on their physical strength and how difficult the door 
is to force. The sum total chance to force the door is called the Success Chance {\em SC}.

If the character has a skill in forcing doors then they will have 
knowledge about how best to apply their physical strength to get the 
door open. 

Most players will not see a task description such as this. The GM may use
it.

\section{Tasks}

\subsection{Description}

\begin{description}
	\item[Name] 
	Self Explanatory
	\item[DF] The difficulty of the task
	\item[SB] The stat basis of the task
	\item[Time]
    How long the task typically takes
    \item[Applicable Skills]
    Any skills that may be applied to the task
\end{description}

\subsection{Difficulty Factors}

The difficulty of a task is described by a number 
referred to as an ``Difficulty Factor'' or DF. Difficulty Factors 
for tasks typically range from -10  to +4. Throughout \SH\ it is 
assumed that the base DF of an action is 0 {\bf unless otherwise 
stated}. 

The modifier for a task is simply 5\% times the Difficulty Factor or:
\[ Modifier = 5 \times {Difficulty\ Factor} \]

If there are a series of actions that can be lumped 
together in a single task the DF for the task is the average of the DFs for all the tasks.

Jogging across the street and leaping a small fence are actions that 
are best lumped together into one task. There is no reason 
to ask the character to roll a task roll for each action. 
But if the character stands the chance of being exposed to
someone looking for him then a roll should be made for the entire set 
of actions. 

There are some common actions and ways of describing actions that have
standard DFs.



\begin{SHTable}[h]
	\begin{tabular}{l|l}
	Subjective						& DF \\
	\hline
    Trivial			& +2 \\
	Simple			&  0 \\
	Non-Trivial	 	&  -2 \\
	Difficult		&  -5 \\
	Very Difficult  & -7 \\ 
	Damned Difficult & -10 \\
   	Nearly Impossible & -20 \\
	\end{tabular}
    \caption{Subjective Difficulty Factors}\label{Table:SubjectiveDFs}
\end{SHTable}


% FILE Generic DFs for Actions
% REF 
\begin{SHTable}
	\begin{tabular}{lr}
	Basic Identification of Actions Needed for a task & +3	\\ 
\hline
	Judgement of Quality                          & +2	\\
	Basic Perception Roll w/in area of Skill      & +1	\\
	Basic Action ( makes up 60\% or more of the   & 0	\\  
	actions made by someone using this skill)     &      \\
	Anyone of basic competence would know this   &      \\
	action well.                                  &      \\
	\end{tabular}
    \caption{Generic DFs for Actions}\label{Table:GenericDFs}
\end{SHTable}



\subsection{Stat Basis}

The task has a \ndx{stat basis} that describes what stat or combination of 
stats can be used to do the task. This is only used if the character 
has none of the skills in the Applicable Skills entry. 

The Base Chance for someone who has no skill is 
\[ (3 \times SB_{skill}) \over {2} \]. 

\subsection{Time}

The task will have time associated with it. This is the average time 
the task typically takes to perform. 

\subsection{Applicable Skills}

This is a list of suggested skills that could be used to do the task. 
It is not exhaustive.

\section{Skills}

\subsection{Description}

\begin{description}
	\item[Name] 
	Self Explanatory
	\item[Stat Basis] 
	The stat, or combination of stats, that is used by the skill. 
	\item[Difficulty Factor] 
	The modifier for doing any action with this skill.
	\item[Generation Cost]
	The character generation cost of a skill or skill package. Skills
	only cost 1 point. Skill packages typically vary from 1
	to 10 points in cost.
	\item[EP Cost] 
	The experience point cost is the amount of experience points it takes to
	buy a roll in a skill. 
\end{description}

\subsection{Ranking}

Proficiency in a skill is described by a number with a range of 0-30.
The higher the number, the greater the character's expertise. Someone
is completely unfamiliar with a skill is considered to be
\ndx{unranked}. Someone who is familiar with the basics of
the skill is rank 0. Other rankings are described in table
\ref{Table:SkillRanks}.

\begin{SHTable}
	\begin{tabular}{ll}
    Rank & Expertise \\
\hline
	0           & Familiar with the skill \\
	1-3         & Beginner \\
	4-6         & Dedicated Amateur \\
	7-10        & Solid Workaday Craftsman \\
	11-14       & Professional \\
	15-18       & Expert \\
	19-25       & Mastery \\
	25+         & Mystical Mastery \\
	\end{tabular}
    \caption{Skill Ranks: What they mean}\label{Table:SkillRanks}
\end{SHTable}



\subsection{Stat Basis}

Each skill has a stat or a combination of stats that is called the
\index{Skills!Stat Basis}
stat basis and is used to calculate the base chance of using the 
skill. 

To use a skill the GM determines what the Base Chance of the skill is 
and adds in the modifiers for the task being performed.
The Base Chance of using a skill is three times the Stat Basis of the skill
or \[ 3 \times SB_{skill} \] For each rank the character has in the skill add 4\%.
The modifiers for the task vary for each situation.

\begin{quote}
A character with rank:0 in Rock Throwing is throwing a rock 
across the street. The character has a Accuracy (ACC) of 12. Their Base Chance 
to hit is \( 3 \times 12 = 36\% \).
\end{quote}

\subsection{Gaining Skills}
\index{Skills!Gaining}

\subsection{Raising Skills}

A character can gain experience points for roleplaying and use those
\index{Skills!Raising}
experience points to buy that skill.

% FILE Costs of Skill Components
% REF 
\begin{SHTable}
	\begin{tabular}{lll}
    BasicType           & Cost          & DF \\
	\hline
	Mental Disciplines      &       3         & -4 \\
	Art                     &       3         & -2 \\
	Science                 &       7         & 0 \\
	Engineering             &       5         & 0 \\
	Crafts                  &       4         & -1 \\
	Technical Study         &       4         & 0 \\
	Physical Disciplines    &       2         & 0 \\
    \hline
    Interaction                    & Cost          & DF \\
	\hline
	Unassisted              &       0         & 0 \\
	Single Assisted         &       1         & -1 \\
	Multiple Assisted       &       2         & -2 \\    \hline
    Tool Use                       & Cost          & DF \\
	\hline
	Non-Tool Based          &       0         & 0 \\
	Simple Tool Based      &        1         & -1 \\
	Complex Tool Based      &       2         & -2 \\    \hline
	\end{tabular}
    \caption{Costs of Skill Components}\label{Table:SkillComponentCosts}
\end{SHTable}






Each skill has a base cost associated with it. This base cost is listed
with the skill or it can be gotten from table
\index{Skills!Base Cost}
\index{Skills!Raising}
\ref{Table:SkillComponentCosts} Included below is a list of some typical types of skills and their costs.

\begin{itemize}
	\item Lore Skills {\small (Mental Discipline, No Assist, No Tools)} Cost is 3
	\item Spoken Language Skills {\small (Mental Discipline, No Assist, No Tools)} Cost is 3
	\item Written Language Skills {\small (Mental Discipline, No Assist, Simple Tools)} Cost is 4
	\item Unarmed Weapon Skills {\small (Physical Discipline, No Assist, No Tools)} Cost is 2
	\item Primitive Weapon Skills {\small (Physical Discipline, No Assist, Simple Tools)} Cost is 3
	\item Complex Weapon Skills {\small (Physical Discipline, No Assist, Complex Tools)} Cost is 4
	\item Basic Science Skills {\small (Science,No Assist, No Tools)} Cost is 7
	\item Basic Engineering Skills {\small (Engineering,No Assist, Complex Tools)} Cost is 7
	\item Basic Technical Skills {\small (Technical, No Assist, Complex Tools)} Cost is 6
\end{itemize}


\begin{SHTable}[h]
   \begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l}
   Rank & 0 &  1 &  2 &  3 &  4 &  5 &  6 &  7 &  8 &  9 & 10&  11&  12&  13&  14&  15&  16&  17&  18&  19&  20&  21&  22&  23&  24&  25&  26&  27&  28&  29&  30 \\
   \hline
B & 2 &  4 &  4 &  4 &  4 &  6 &  6 &  6 &  8 &  8 & 10&  10&  12&  12&  14&  14&  16&  16&  18&  18&  20&  20&  22&  22&  24&  24&  26&  26&  28&  28&  30&  30 \\
a & 3 &  6 &  6 &  6 &  6 &  9 &  9 &  9 & 12&  12&  15&  15&  18&  18&  21&  21&  24&  24&  27&  27&  30&  30&  33&  33&  36&  36&  39&  39&  42&  42&  45&  45 \\
s & 4 &  8 &  8 &  8 &  8 & 12&  12&  12&  16&  16&  20&  20&  24&  24&  28&  28&  32&  32&  36&  36&  40&  40&  44&  44&  48&  48&  52&  52&  56&  56&  60&  60 \\
e & 5 & 10&  10&  10&  10&  15&  15&  15&  20&  20&  25&  25&  30&  30&  35&  35&  40&  40&  45&  45&  50&  50&  55&  55&  60&  60&  65&  65&  70&  70&  75&  75 \\
  & 6 & 12&  12&  12&  12&  18&  18&  18&  24&  24&  30&  30&  36&  36&  42&  42&  48&  48&  54&  54&  60&  60&  66&  66&  72&  72&  78&  78&  84&  84&  90&  90 \\
  & 7 & 14&  14&  14&  14&  21&  21&  21&  28&  28&  35&  35&  42&  42&  49&  49&  56&  56&  63&  63&  70&  70&  77&  77&  84&  84&  91&  91&  98&  98&  105& 105 \\
  & 8 & 16&  16&  16&  16&  24&  24&  24&  32&  32&  40&  40&  48&  48&  56&  56&  64&  64&  72&  72&  80&  80&  88&  88&  96&  96& 104& 104& 112& 112& 120& 120 \\
  \end{tabular}
  \caption{Skill Cost}\label{Table:SkillEEPs}
\end{SHTable}


To determine the cost of raising a skill from one rank to the next rank
up find the row in table \ref{Table:SkillEEPs} that has the base cost of the skill.
Find the column with your current rank in that skill.
The cost in each column to the right is the cost it takes to raise a
skill from the current rank. To go up in Weapon:Fist (base cost 2) from
rank 0 to rank 1 costs 4 EEPs. To go from rank 1 to rank 2 is another 4
EEPs and so on.

\subsection{Training}

For each 10 hours of training with a teacher the character gets 1 EEP.
For each 20 hours of training with a partner the character gets 1 EEP.
For each 30 hours of self-training with a the character gets 1 EEP.
\index{Skills!Training}

There are all sorts of modifiers so ask....

\subsection{Costs of unlisted skills}

When figuring out the cost of previously unlisted skill use table \ref{Table:SkillComponentCosts}
simply add together all of the  costs that appear to apply.

\subsection{Relations Among Skills}


In situations where the character does not have a skill that
\index{Skills!Related}
is directly applicable to the task being performed the character 
may choose to use a related skill.

A typical example would be in using two different types of handguns. The
character has rank 10 in Slug Pistol but is using a Stun Weapon. The stun
weapon is fairly different from the Slug Pistol so the character can only
apply 1/5 of his expertise in Slug Pistol to using this pistol. So he has
an effective rank 2 in the weapon.

As a rule the following relations apply.

\input{tskill5.tex}

\subsection{Unfamiliar Tools}


If the skill requires the use of tools and the tool that the character is
\index{Skills!Unfamiliar Tools}
utilizing is unfamiliar, then the action occurs at a DF -2. This usually
only happens if the differences between the version of the tool the
character normally uses and the current one actual effect how it is
used. A gun with a different mass than the entity is used to is
unfamiliar, whereas a gun of the same model and same manufacturer is
not. To eliminate this unfamiliarity modifier requires that the entity
familiarize himself with the tool with a DF -3 roll against the SB of 
the skill with a gain of 1 DF per roll. 

\section{Types of Skills}

The section on skills describes the basic way that skills are 
handled but there are a variety of special types of skills that are 
used for special circumstances.

\subsection{General Skills}

Skills that are described as general skills cover a wide range of
\index{Skills!General}
\index{Skills!Specific}
tasks with very little depth. A person who has learned a general 
skill such as Throw Object is able to throw just about anything they 
can get their hands on ( knives, spoons, rocks, chairs) with a lesser 
success chance than someone who has a specific skill in throwing a
particular object.

In addition, there are skills known as support skills that are solely
\index{Skills!Support}
designed to increase the success chance when doing one type of action 
with a skill. Someone who uses their sword to parry weapon attacks 
may wish to train specifically in parrying with a sword. So they 
would have a ``Long Sword' skill and a ``Long Sword : Parry'' skill.

General skills only give 1\%/rank to the success chance. Specific 
skills (the \SH\ norm), give 4\%/rank. Support Skills add 2\%/rank.

There is no limit on the number of support skills that may be applied to
a single task.

\subsection{Filter Skills}

There is a category of skills which affects the use of other skills 
in an environment different from the one they were learned in. These skills 
are called filter skills. A Filter skill is any skill that can allow
\index{Skills!Filter}
for the full expression of other skills in an environment other than 
that for which those skills were designed for.

Typical filter skills include the following: 0-g maneuver, Tech 
Level Lore, Culture Lore, Mounted Combat, Vehicular Combat 
skills, Armor Wearing, and Computer operations.

For situations in which the character is attempting to apply a skill 
in a environment he is not familiar with and that skill {\em must }
interact with that environment, then the rank in the filter skill 
becomes the upper limit on the effective rank of the skill being 
used.

As an example, if someone has a mounted combat skill at rank 5, he or she
may use their archery skill up to rank 5 without making any rolls
against their mounted combat. If the character has a higher archery skill
and wants to bring it all to bear on a shot, they must roll against
their mounted combat first in order to get the full use of the archery
skill.

\subsection{Optional Rule:Skill Pools}

$ {Pool\, Bonus} = Rank_{Highest\, Skill}/2 + \sum {Rank_{All\, Other\, Skills}}/10$ with a maximum
of $ Rank_{Highest\, Rank} \cdot 2$
\index{Skills!Pools}
Pools may be grouped according to training style, SB, or character
preference. 



\chapter{General Play}

This chapter discusses various pieces of the game system that effect 
every character. These rules are not specific to either combat or 
non-combat situations.  

The model of tasks and actions in \SH\ is based on a series of 
reactions and actions. When a character first enters a scene
they determine how much they see and understand of the situation {\em
\ndx{perception roll}}. Then they determine how quickly they can react {\em 
\ndx{initiative roll}}. The character will react faster when they know what
\index{Initiative}
is going on and slower when they don't. If a character is expecting 
something to happen they can prepare for that occurrence {\em preset 
reactions} and speed up their response. 

Once the character has reacted they determine what they will do and then 
do the action. 

There are a variety of things that can modify the chance of doing an 
action successfully. The character can mentally prepare for the 
action {\em set-up} to increase their chances. The action can be sped 
up by decreasing the chance of success {\em rushing an action}. 
Actions can be performed simultaneously {\em floretine}. There are 
additional modifiers for doing something while moving or while tired 
and so on\dots

\section{Time Scale}

\index{Time Scale}
Time is referred to by the units we are used to, Hours, minutes, and seconds 
and one that is new: Pulses. A \ndx{pulse} is 1/10th of a second. Pulses are
used in combat and other time critical activities.

\section{Perception}

\index{Perception}
Most of the time a situation is self evident. A character automatically
knows that there is a bar in the room and how many people are in it.
But if something could go unnoticed by the character, such as a suprise 
attack or something hidden, the player should make a \ndx{perception roll}. 
A perception roll is typically SB = PAW, DF=0, with modifiers for 
how alert the character is trying to be. A perception roll takes
8 pulses. A \ndx{Passive Perception Roll} can be made
\index{Perception!Passive}
during any action at 1/4 the success chance of a normal perception roll. A
passive perception roll takes no time and takes no modifiers for 
simultaneous actions.

The critical success and failure effects are fairly straight forward. 

\begin{description}
	\item Amazing Success
        Total Understanding, 300% Detail, +-0% Timing

	\item Very Notable Success
        Total Identification, 200% Detail, +-5% Timing

    \item Notable Success
        Total Identification, 150% Detail, +-10% Timing

	\item Solid Success
        Able to Identify exactly what is happening, 125% Detail, +-25% Timing

	\item Success
        Basic Identification, 100% Detail, +-50% timing

	\item Failure
        Vague Identification, 25% Detail, +-75% timing

	\item Solid Failure
        No real clue, 0 Detail, 0 Timing

	\item Notable Failure
        Inaccurate Identification, +-125% Detail, +-175% Timing

	\item Very Notable Failure
        Inaccurate Identification, +-150% Detail, +-200% Timing

	\item Amazing Failure
        Wildly Inaccurate Identification, +-250% Detail, +-300% Timing
\end{description}

\begin{verbatim}
Task: Active Physical Perception  
DF: 0 
Time: 8 cts. 
Skills: General Perception, Combat Perception
Notes: 
\end{verbatim}

\begin{verbatim}
Task: Passive Physical Perception  
DF: 0 
Time: 0 cts. 
Skills: General Perception, Combat Perception
Notes: Done at 1/4 the normal chance 
\end{verbatim}

\input{tgpm6}

\section{\ndx{Initiative} (Who Goes First)}

When a character first enters a situation where action may be required they must determine
how much they know and how quickly they react.

When a character first becomes involved in a conflict they roll a perception roll. Then the PC rolls an initiative roll. The 
Initiative roll is simply $ 2d6 + 8 - Speed_{Reaction} $ added together. There are modifiers 

$ Speed_{Reaction} = 1/2 {Character's\ Speed } $

\index{Speed!Reaction}
\[{Initiative} = 2d6 + 8 - Speed_{Reaction}\]

If the perception roll is unsuccessful, the character adds a modifier 
to the roll. 

\[{Initiative} = 2d6 + 8 - Speed_{Reaction} + 5\]

There are, of course, modifiers to the perception roll as detailed in table 
~\ref{Table:PerceptionModifiers}

If the initiative roll is lower than 1 the excess speed goes toward speed points 
and can be applied to a number of seperate tasks.

\subsection{Speed Gains Due to Rank in a Skill}

The character may add \( Rank/2 \) points to their speed points when using a
skill. This may only be done once the character has decided to use a
\index{Speed!Gains from Skill Rank}
given skill. 

\subsection{How to avoid the math}

There is a set of tables that the GM can provide that can be used to
simplify this. 

\subsection{\ndx{Preset Reactions}}

When a character is waiting for something specific to happen and intends to react a certain 
way when it does the charcetr is presetting an action. A gunfighter waiting for someone else 
to start drawing their weapon is a preset action. Having a preset action allows the character to increase
the chance of detecting the triggering action and speeds up the preset action. 
Holding a preset action can be fatiguing over long periods of time.

Declaring an action to be preset allows an DF +4 to a perception roll. If the perception roll is successful, the 
character gets to apply their $ 2 \times Speed_{Reaction} $. A Preset reaction may only be held for MST 
in the time scale that the players are working in before a cost of 1 MFT must be expended.

\section{\ndx{Actions}}

Actions normally begin at the count given by the initiative roll. The 
must be made at this point. The speed of the action is determined and 
the character takes this action on a pulse given by Initiative + The speed of the action.  

\section{Speeds of Actions}

Most actions have a speed associated with them. All simple actions
\index{Speed!of Actions}
, unless otherwise noted, have a standard speed of 10 pulse. 


% Speeds of Basic Actions

\input{tgpm7}
\index{Actions!speed of}
Actions can be performed faster. Speeding up an action lowers the
chance of success. Generally half the time to act means you have half the chance to succeed.

For each percentage of time units the action is sped up a corresponding percentage is removed from 
the success chance. Thus an action performed in 1/4 the time has 1/4 the success chance.

Actions can be sped up using speed points. 


\section{Drawing a Tool or Weapon}


This most often applies to drawing a weapon but can also apply to 
other tools. In general, when a weapon is in hand, all normal weapon 
speeds apply. In order to get a weapon into ones hand it takes 
\( 2 \times Speed_{weapon} \) in pulses. 

In order to get a weapon in hand faster than \( 2 \times 
Speed_{weapon} \) requires a fast draw roll against the weapon's 
skill. A successful ready roll brings the tool or weapon to bear at
\index{Speed!of drawing a weapon}
\index{Speed!of draw}
\( Speed_{weapon} \).


\section{Resolving an Action}

Actions usually require only a skill roll to be made. 

\subsection{Results}

The end result of a roll is either a numeric value or a simple 
subjective result. See the table ~\ref{Table:CriticalSuccess}

\section{Modifiers} 

This section describes the common Difficulty Factors for various 
situations. All these modifiers are culmulative.

\subsection{Unranked in the Skill}

A character who has training or experience in an action is
unranked in the required skill. Any character performing an action using 
a skill they have no rank in has 1/2 the normal base chance and adds 2 pulses to 
their initiative. 

\subsection{\ndx{Set-up}}

Waiting and prepping oneself for a task is called Setting-Up. It will generally increase 
the chance to do something at a cost of increased time to get it done.

Setting Up for an action takes as long as it takes to perform the action. The end effect is a
bonus to the Success Chance of \[ 20\% + 2\%/rank\]. 

To set-up an action with a time scale of pulses or seconds (and sometime minutes) the total time taken is \( 1 \times Speed_{Action} \).
To set-up an action with a time scale of many minutes, hours, days, or weeks the total time taken is \( 1/4 \times Speed_{Action} \).  

\subsection{Florentine}

Performing two actions at the same time is called Florentining.
\index{Florentine}
\index{Simultaneous Actions}
\index{Actions!Simultaneous}

One of the two actions is the primary action and it recieves a 
DF -3. The secondary action recieves a DF -6. This is only true 
if the two actions are both physical or both mental. If one 
action is a mental action and the other is a physical one the modifiers
go down to DF -2 and DF -4.

% Include General Modifiers Table
\input{tskill1.tex}

\subsection{Physically Injured or Tired}

A character that is injured or fatigued has DF modifiers to 
their actions. Physical fatigue has the greatest effect on physical actions 
and Mental fatigue has the greatest effect on Mental actions.
\index{Injury}

\input{tskill2.tex}
\input{tskill3.tex}

\subsection{\ndx{Movement}}

When performing an action the character may be affected by 
his rate of movement. If the character is moving faster than a 
walk the DF due to movement applys to any physical action they are 
attempting. ANy mental action they perform is subject to 1/2 
the listed DFs.


\begin{table}[h]
	\begin{tabular}{ll}
	Double Move: jog							  & DF -2 \\
	Triple Move: Run							  & DF -4 \\
	Fast move: Dash							 & DF -6\\
	Vehicular Movement							& DF -10 \\ 
    \end{tabular}
    \caption{Movement Modifiers}
\end{table}

\subsection{Environmental Conditions}

This is a catchall area. Characters generally are at their best 
performance in conditions similiar to the environment in which they 
were raised. Any drastic modifications from that environment in 
terms of light, gravity, humidity, etc\dots can lower the character's 
performance.

\input{tskill4.tex}

\section{\ndx{Fatigue and Exhaustion}}
\index{Fatigue}
\index{Exhaustion}

A character using energy to perform actions draws from two different 
types of reservoirs: Fatigue and Exhaustion. For physical actions the 
stats are Physical Fatigue and Physical Exhaustion (PFT and PEX). For mental
actions the stats are Mental Fatigue and Mental Exhaustion (MFT and MEX).

Fatigue is the quick access pool of energy a character can use.
Exhaustion is the reserve pool of energy a character can use. 

\subsection{Losing Fatigue}

A character loses fatigue as the result of physical activity or combat. 
A character that has lost all their fatigue has no modifiers to their actions.
Fatigue will come back quickly. For each 10 points of fatigue used the character 
also loses 1 point of exhaustion.

\subsection{Losing Exhaustion}
A character loses Exhaustion by performing strenous activity or by losing 
fatigue. There are modifiers for being low in Exhaustion.

\input{tgpm8}

Characters lose MFT and MEX in the same manner.

\input{tgpm9}

\subsection{Restoring Fatigue and Exhaustion}

The restoration of Fatigue is usually very quick. Exhaustion and Fatigue
restore themselves independently of each other.

\input{tgpm10}

\section{Physical Movement}

Each character has a statistic named Physical Movement. This is the character's
movement in meters/second at a dash. There are a total of five different types
of movement that a character may utilize. Each type of movement has its own
movement rate which is derived from the character's movement statistic. 
Ideally the player will have the full range of movements listed on his 
character's sheet. 

\input{tgpm2}

If the movement is being resolved during a time scale of greater than every
pulse one can get the distance traveled by simply multiplying the movement 
of the individual times the time spent moving. The time spent accelerating
is ignored as being negligible.

\begin{quote}
Let us say that Joe Daring spends 15 seconds running down a deserted street.
If he doesn't run out of street he will have covered 4 * 15 = 60 meters. If 
this seems a bit short, keep in mind that a run is not a full dash. At a full
dash Joe would have covered twice the distance and would be slowing down pretty 
drastically due to losing wind.
\end{quote}

\subsection{Acceleration}

\marginpar{It is important to remember that the accelleration rules 
should only be used when the distance travelled by the characters 
over a {\bf short period} of time is important }

In dealing with movement on a pulse by pulse scale we need to actually
deal with acceleration. The sequence is quite simple. Whatever the
final movement  rate is that the character intends to use is considered
the target movement rate. When the character first starts moving he
makes an skill roll in order to start moving at the movement
rate just below the target movement rate. Once the roll is made the
character is now moving at that lower rate. On his next  initiative the
character may attempt to accelerate to the target movement. Note  that
the gain number is the movement rate. If an acceleration roll is failed
the end result is that the character drops to the next lowest available
movement  rate. 

\begin{quotation}
Reed Johnson has a movement of Dash 10, Run 5, Jog 2.5, Walk 1.3, Crawl .6
\end{quotation}

\input{tgpm4}

\section{Mental Movement}
This is a measure of the character's speed of mental travel. It is 
usually only used in Psionics and Computer usage.

\section{Opposing Skill Rolls}

An opposing skill roll in a roll in which the character attempts to 
undo an action done previously by another character. Typically the SN 
of the original action is taken as a negative modifier to the current 
skill roll.

\section{Stealth and Concealment}

Opposing Skill Rolls

\section{Deception and Detection}

Opposing Skill rolls









\chapter{Combat}

The combat section details the types of actions that may be taken
while in combat. The chapter on General Play must be understood before working with the combat details.

\section{Description}

Combat normally occurs on a pulse by pulse basis. The process is
fairly simple: Determine First Reaction. For each of those reactions in
order determine the action or attack, the damage from the attack ( if
any), the secondary effects of that damage ( if any). Take a breath.
Continue.

\section{First Action Determination}

As detailed in the chapter on General Play mechanics. Perception
is rolled, initiative is determined and actions are chosen.

\section{Attack}

\subsection{Closing to Attack}

\index{Attack!Closing to}
\index{Closing to Attack}
When attacking someone with a weapon of greater reach than their own an
attacker must close to get in range to strike. If the defender is aware
of the attack and has a usable initiative the may actively resist the
closing action. To do so they must make an skill roll using a weapon to
fend the attacker off. Fending does not require a re-roll of initiative,
the time taken for the fend (same as block and parry) is simply added to
the defender's current initiative.

A fend is treated as any other attack form and all active defenses can be
performed against it. If the fend is successful and the attacker chooses
to ignore it the fend does normal damage for the weapon.

If a character that has closed with their opponent is unarmed
they may proceed to grapple, to throw, or to overbear.

If the defender wishes to simply retreat they may do so. They
may do so by rolling to fend off the closing action at a DF +6.
Of course, they do end up moving backwards.

If an attacker has been closed upon they may choose to drop their
current weapon and use a shorter one, they may choose to use their
current weapon as if it were a club, or they may attempt to retreat.

\subsection{Calculating Chances to Hit}

\index{Attack!Success chance}
The attack has a chance to hit that comes from the SC of the weapon and
is modified by the DF of the environment and also the defense of the
person being attacked. Melee
weapons base all their attacks on PCA. Missile and thrown weapons
base all their attacks on ACC.

Mental actions performed against inanimate objects is based on FCS
and mental attacks against an entity are based on MCA.

\subsection{All out attack}

An all out attack means that the character is attacking without any attempt to defend themself.

A character may choose to perform an all out attack and thus gain
their MDF or PDF to their attacks and lose his MDF or PDF for defense. This is simply an
extension to the concept of applying Total Concentration as detailed
in the General Play Mechanics chapter.

\subsection{Advance}


A character may choose to press in on an opponent. In doing so
\index{Attacking!Advance}
\index{Attacking!Press}
they gain DF +4 to all offensive actions and DF -4 to all defensive
actions. This is only possible if the attacker has a weapon of greater
or equal length to the defender.

\subsection{Called Shots}

In any physical targeted action there is the potential to specify the
\index{Attacks!Called Shots}
\index{Called Shots}
location of the strike. That of course entails DF modifiers to the
action.
\index{}

\input{tgpm11}

\subsection{Hit Location}

The target number is calculated, the roll is made. If the attack
is a success then the damage is applied against the armour and then
the target.
\index{Attacks!Hit Location}
\index{Hit Location}
All hits are checked against the hit location table.

\input{tgpm12}

If any result on the Hit Location table indicates a target for which there
is a right and a left, the one's value of the die roll determines the side.
If the die is odd, the hit was against the left. If the die is even, the hit
was against the right.

\subsection{Indirect Fire}

Indirect fire (i.e. a Lob) requires an additional DF -2. Range is the
PST in meters.

\section{\ndx{Damage}}

\subsection{General Notes}

All damage is calculated and then applied to the location specified
by the hit location table. If that area is armored the damage is
first applied to that armour. If the damage is great enough to get
past the armour, the damage is then applied against the
appropriate type of Fatigue such as PFT or MFT and then against the
PBD or MBD of the entity.

If the weapon has any secondary effects such as knockback or radiation
they are applied and calculated.

\subsection{Critical Damage}

Any attacks that cause critical damage apply the additional damage to
the PBD or MBD after armour.

\subsection{Types of Damage}

There are several types of damage. There is Crushing, Cutting,
Piercing, Projectile, Laser, Energy, and explosive damage. Each one
is typically associated with a specific weapon type.

\begin{description}
	\item[Crushing Damage]
    \index{Damage!Crushing}
	Crushing damage is damage caused by low speed blunt weapons such as
	a club, a staff, a fist, or a chair.

	\item[Cutting Damage]
    \index{Damage!Cutting}
	Cutting damage is caused by the use of slicing or chopping motions
	with an edge weapon.

	\item[Piercing Damage]
    \index{Damage!Piercing}
	Piercing damage is caused by low speed pointed objects entering the
	body along the axis of the point.

	\item[Projectile Damage]
    \index{Damage!Projectile}
	Projectile damage is caused by objects moving at high speeds. The
	only real difference between piercing or crushing and projectile
	damage is that the weapon moves at a high speed and imparts a
	high amount of kinetic energy to the target.

	\item[Laser Damage]
    \index{Damage!Laser}
	Laser damage is caused by optical lasers. Damage caused by
	non-optical lasing devices such as Masers and X--lasers is classified
	as Energy damage.

	\item[Energy Damage]
    \index{Damage!Energy}
	Energy damage (abbrev. NRG) is typically associated with non-optical
	electromagnetic weapons.

	\item[Explosive Damage]
    \index{Damage!Explosive}
	Explosive damage is, quite logically, caused by explosions. It is
	the result of a expanding wave front of gasses or minute particles.

\end{description}

\subsection{Secondary effects}

There are several types of secondary effects. There is knockback,
bleeding, and Shock.

\subsubsection{\ndx{Knockback}}

When a character has been hit by a something with large amount of kinetic
\index{Damage!Knockback}
energy they can fall down or lose their balance. This is called Knock-Back.
It happens when more than 1/2 of the entities PFT or 1/4 of their PBD is taken
away in a single crushing or projectile strike. It can also happen with {\em any}
explosive attack. The Knockback resistance roll is DF -2. If successful the
character is unaffected. If failed the entity has fallen to the ground.
The stat basis is typically PST or PAG whichever is greater.

\subsubsection{\ndx{Bleeding}}
\index{Damage!Bleeding}
Bleeding is the result of a cutting or piercing attack that has done
actual PBD damage. The Bleeding resistance roll is DF -3. If failed the
end result is 1 point of PFT loss to bleeding per 20 pulses. The stat
basis is PEN.

\subsubsection{\ndx{Shock}}

Shock is the state brought on by massive disruption of the senses or
nervous system of the character. Shock effects range from the minor
(startled) to the major (being unconscious).
\index{Damage!Shock}

A System Shock roll is necessary when an attack does
either PBD or MBD damage or when a successful attack is made with
energy weapons such as Charged particle or TASER weapons.
A System Shock roll is made against PEN or MEN.


\begin{table}
	\begin{tabular}{cll}
	Roll			  & Effect & DF \\
	Normal Failure	  & Jolted/Startled & -2  \\
	Failed by 25+	   & Stunned & -4  \\
	Failed by 50+	   & Badly Stunned & -6 \\
    Failed by 75+     & Unconscious & - \\
	\end{tabular}
    \caption{System Shock Effects}
\end{table}

Recovering from being stunned or shocked means rolling every initiative roll pulses at not speed 
\( 2d6 + 45 \).

\section{\ndx{Defenses}}

\subsection{Rolling with the blow}

OK, you know you are going to get hit, you have no time for any other defense then to 
try and roll with the blow and thus avoid being stunned or knocked out.

The act of rolling with the blow involves an attempt to take the
alloted damage but absorb it in such a way that the normal secondary
effects such as stun or knockback do not take effect. The action
requires no time but does require that the defender be aware of the
attack and declare that he wishes to roll with the attack. The base
roll goes against PAG for physical attacks and MAG for mental
attacks. It adds DF +5 to the System Shock roll if any is made.
The act of rolling with the blow causes a reroll of initiative.

\subsection{\ndx{Normal Defense}}

\index{Defense!Normal}
There are a number of forms of active defense. All entities, if they
are aware of an attack, may apply their normal defense against that
attack. This does not count as an action !

\subsection{\ndx{Retreating}}

\index{Defense!Retreating}
A character may choose to retreat any time they have the initiative to do so.
A retreat may be performed simultaneously with any other action at no mods.
Retreat will add DF +6 to any defensive action and DF -6 to any offensive action.

\subsection{\ndx{Evasion}}

Weaving back and forth and trying to actively avoid attacks is called evading.

\index{Defense!Evading}
For as long as a PC is evading an attack or series of attacks their defense is \( 2
\times PDF or MDF \). The character need only declare that they are evading and it takes effect at
their first action point. Of course the character can perform other actions
at the same time but they will be considered as florentine actions. The
character is at a DF +3 when performing a dodge from an evading state.

\subsection{\ndx{Dodging}}

\index{Defense!Dodging}
OK, just moving out of the way is not enough,  you want to be out of the area ! Dodging is one way
to achieve that. It gives you a better defense then evading but it does require you to pick yourself up 
afterwards.

Dodging is an extension of the normal defensive technique of getting out
of the way. Dodging implies that the PC is actively throwing himself out
of the path of an attack. Dodging takes 5 pulses to start, 10 pulses of movement,
and 5 pulses of deceleration. A Dodge leaves the character in the act of
a controlled fall. A skilled individual may roll to acrobatically recover.
A dodging character has \( 2 \times PDF \) during the first part of the dodge,
\( 3 \times PDF \) during the second part of the dodge and normal PDF for
the recovery portion of the dodge.

\subsection{Dropping Prone}
\index{Defense!Dropping Prone}
A specialized form of Dodge that only works within a strong gravity
field. It is a 5 pulse action that leaves the character in a prone
position. During the action the character has a defense of \( 3 \times PDF \)
Once down the character has 1/2 the normal PDF. 30 pulses are required to
get back up.

\subsection{Crouching}

\index{Defense!Crouching Down}
Crouching down can be used as a one time evasive maneuver against an
incoming attack. It is a five pulse action that gives \( 2 \times PDF \)
against the attack. This is in lieu of full evasion.

\subsection{Parrying}

\index{Defense!Parrying}
Parrying an attack involves redirecting an attacker's weapon with the
character's own. A parry is done with a shield or weapon. DF -3, SB = Wpn SB,
Speed as per 1/2 weapon speed. DF -5 against Thrown, DF -30 against Projectile,
DF -40 against NRG. This is simply a skill opposition roll.

\subsubsection{Binding Weapons}

\index{Defense!Binding}
If a defender succeeds in a parry by less than 5\% the two weapons are assumed
to have become ``Bound'' and the attacker has advanced on the defender. See rules
on advance. The defender may roll at their next initiative to release the weapon.
This is a skill opposition roll.

\subsubsection{Overrunning}

\index{Defense!Overrunning}
If the attacker fails to avoid a parry by more than 25\% then the
attacker is effectively off balance and is subject to DFs just as if
they had failed a system shock roll.

\subsection{Block}

\index{Defense!Blocking}
A block is an attempt to use a weapon or a shield to provide addition
armor against damage. DF -2. If the block is successful the defender rolls
damage with the weapon and can apply that damage as armor. Speed as per
1/2 weapon speed.

\subsection{Disarm}
\index{Defense!Disarml}
DF = -4, Skill opposition roll., Speed as per weapon speed.

\section{Fancy Maneuvers}

\index{Combat!Fancy Maneuvers}
\index{Fancy Maneuvers}

\subsection{Spinning}

\index{Combat!Spinning}
\index{Spinning}

Any action performed while spinning has a DF -2, a damage modifier
of \( 1.5 \times Normal\ Damage \), and is 1.5 times slower than a
normal attack.

\subsection{Jumping}

\index{Combat!Jumping}
\index{Jumping}

A jumping attack is as per spinning with a DF -3.

\begin{table}
	\begin{tabular}{ll}
	Spinning		 &		  DF -2 DAM 1.5* SPD 1.5* \\
	Jumping		&		  DF -3 DAM 1.5* SPD 1.5* \\
	\end{tabular}
    \caption{Melee Combat modifiers}
\end{table}

\subsection{Feint}

A feint is used to distract an opponent or to trigger an opponents
preset actions.

The main thing to remember that a feint is, in effect, a deception
roll. It involves a weapon skill roll to convince the other
individual that an attack is being made. The feint roll takes a DF
-6. All who are within range may roll to save against
being fooled by the feint.

This is considered an opposing skill roll so the amount the feinted makes
their roll by is subtracted from the feintee's perception roll.

\section{Close Conflict}

\index{Combat!Close Conflict}
\index{Close Conflict}
Once someone has closed to within arms reach they may choose to do
any of the following.

\subsection{Overbear}

\index{Combat!Overbear}
\index{Overbear}
An overbear is simply performed by closing with an opponent and then
making a normal attack using SB=PCA. Like any other attack it may be
repulsed or actively countered.

The gain for such an attack is to have the opponent on the ground.
Damage for an overbear attack is simply equal to the attackers PSE.

\subsection{Throw}

\index{Combat!Throw}
\index{Throw}
A throw is simply performed by closing with an opponent and then
making a normal attack using SB=PCA. Like any other attack it may be
repulsed or actively countered.

The gain for such an attack is to have the opponent on the ground.
Damage for a throw attack is simply equal to the attackers \( PSE \times 2\).
DF -5.

\subsection{Grapple}

\index{Combat!Grapple}
\index{Grapple}
A grapple is simply an attempt to get a hand hold on the opponent.
It is like any other attack in that it may be countered normally.

A successful grapple gives a DF +5 modifier to any other close combat
attack such as throw, overbear, and any attempts to increase the hold.

\subsection{Hold}

\index{Combat!Hold}
\index{Hold}
A hold is initiated by a grapple action and the initial strength of a
hold is given by the SN of the grapple. If the attempt to hold or
immobilize someone is the sole aim of the attack then the attacker
may choose to improve the hold by rolling again. For each attempt to
improve the hold the attacker may only add 1/2 of the SN of the roll.
No hold may be greater in strength than 5 * PST of the holder.
The opponent may reduce the strength of a hold by the SN of any
grapple skill rolls he makes.








\chapter{NPC-PC Interaction}

\section{Outline}

This chapter discusses the rules for the various ways that the player 
characters may interact with \index{characters!non-player}
\index{NPCs}
non-player characters.

\section{Reaction Rolls}

A reaction roll is a roll made to determine a Non player character's 
reaction to some action on the part of a PC or NPC. It should never 
be rolled by a PC.

A Reaction Roll upon encountering a PC for the first time has 
horrendous numbers of variables attached to it but as a rule of thumb 
the roll is DF 0, SB=GAW with a gain of getting the NPCs basic respect.

\section{Presence}

Presence is the outward reflection of an person's awareness of his 
environment. It is also known as Aura and Charisma. Presence is 
usually the end result of the player's role playing but it can be 
enhanced by the intentional decision to "make an entrance" or "make an 
impression".

To do so the character must decide whether he wishes to make a
general attempt at establishing a presence or whether he wants to 
establish himself as a physical or mental personality of note.
Remember that Albert Schwietzer had as much of a presence as Darth
Vader.

The actual presence roll is made at an DF-3, SB = GAW or PAW or MAW or
any other statistic depending on the type of presence the character wishes to establish. 

\section{Morale}

Morale rolls are typically made when an NPC realizes that a conflict
\index{Morale}
( physical, Mental, or verbal ) is not going as planned. At that point,
usually after a perception roll, the NPC has to make a morale roll. 
Morale rolls are SB = GAW, MAW, PAW.



\chapter{NPC-PC Interaction}
-
-\section{Outline}
-
-This chapter discusses the rules for the various ways that the player 
-characters may interact with \index{characters!non-player}
-\index{NPCs}
-non-player characters.
-
-\section{Reaction Rolls}
-
-A reaction roll is a roll made to determine a Non player character's 
-reaction to some action on the part of a PC or NPC. It should never 
-be rolled by a PC.
-
-A Reaction Roll upon encountering a PC for the first time has 
-horrendous numbers of variables attached to it but as a rule of thumb 
-the roll is DF 0, SB=GAW with a gain of getting the NPCs basic respect.
-
-\section{Presence}
-
-Presence is the outward reflection of an person's awareness of his 
-environment. It is also known as Aura and Charisma. Presence is 
-usually the end result of the player's role playing but it can be 
-enhanced by the intentional decision to "make an entrance" or "make an 
-impression".
-
-To do so the character must decide whether he wishes to make a
-general attempt at establishing a presence or whether he wants to 
-establish himself as a physical or mental personality of note.
-Remember that Albert Schwietzer had as much of a presence as Darth
-Vader.
-
-The actual presence roll is made at an DF-3, SB = GAW or PAW or MAW or
-any other statistic depending on the type of presence the character wishes to establish. 
-
-\section{Morale}
-
-Morale rolls are typically made when an NPC realizes that a conflict
-\index{Morale}
-( physical, Mental, or verbal ) is not going as planned. At that point,
-usually after a perception roll, the NPC has to make a morale roll. 
-Morale rolls are SB = GAW, MAW, PAW.
-
-
-


