\chapter{Education}

\section{Outline}

The begining character is assumed to have some form of education. The 
education may simply be general life experience or it may be formal 
educational training. 

As a result of education the character gains EDU points in skill
points. Those skill points may be used to buy basic education skills
or other basic skills or skill packages.

The initial skills that can be gained by using these points 
are simple educational and cultural skills\footnote{Describe what 
this means for non-formally educated individuals}.

As a result of education the character automatically gets the 
following skills:

\subsection{Automatically Gained Skills}
\begin{enumerate}
	\item EDU in basic education skills.
	\item EDU in points toward skills in written and spoken language.
	\item EDU in points toward Cultural Lores. Both local and larger 
	scale.
	\item EDU in points toward Lore:[Tech Index] of Culture.
	\item 10 points toward manuevering skills for the native 
	environment.
\end{enumerate}

A limitation to highest rank reachable\footnote{ should this be   
discussed here } is based on a 50\% learning roll in that skill. In
\marginpar{Expand and demystify this} 
other words when spending Experience gained from base education and 
careers the character may not gain any ranks higher than those that 
he has a 50\% chance of getting in an experience roll.\footnote{ ee 
the section describing learning rolls}

A summary of that limitation is presented in table \dots.

% Include the Learning Limitations Table
\input{tcgen3.tex}

\begin{quotation}
As an example. Schlem the Schlump has an education of 9. 
\marginpar{Redo this example}
He automatically gains 9 points in skill rankings due to his 
education and applies them to Basic Science and Basic Social Science. 
He gets 9 points to spend in language and spends it all in his Native 
Language:Spoken. He uses his points toward lore to gain a complete 
knowledge of his planet. And gets an 8 in Lore:Tech Index 4 (The tech 
index of Schlump). He also gets 10 points in maneuvering in grav 
environment 1.0 G. The only points that he needs to worry about a
limit on is the initial 9 points. Those points, unlike the other 
points gained, are the result of simple teaching and should be 
checked to make sure that the character has not overstepped what he 
can learn. In the case of those points he should look at his lowest 
stat ( EDU = 9) and should be careful not to go above rank 4 in any 
skill that requires EDU. 
\end{quotation}

% EOF
