\chapter{Generating Character Statistics}

\section{Outline}

In Space Hybrid a the physical and mental attributes of a character 
are described by a series of numbers called statistics or stats. 
Physical Strength is a typical statistic. Generally the higher a
given statistic is the more the character can do with skills that 
require the use of that stat. 

In describing the statistics you will see both the name of the 
statistic in question followed by its abbreviation and a description of
its origin and usage. 

In generating the statistics of the character the player assigns 13 to
each of the stats and has 9 points thereafter to spread among
the 9 primary statistics. The player has complete freedom in choosing 
how the points are distributed.  

The minimum statistic is 5. The maximum amount that may be placed into
a statistic during the initial point allocation is 25. Racial and 
Gender statistic modifiers are added on later. The final value for a
statistic varies based on race and background of the entity.

The statistics and the ranges they may assume are described in the 
next three sections.

\section{Primary Statistics}
\begin{description}
	\item[Physical Strength		(PST)]
	Physical power of body. This is the overall value for the character's
	raw muscle power and is not tied to some particular set of limbs. 
	Typically, actions such as lifting ae based on PST.
	\item[Physical Endurance		(PEN)]
	Physical resilience and Stamina of body. This is a measure of the
	character's overall endurance and ability to resist hardship as 
	well as the ability to bounce back from hardship.
	\item[Dexterity				(DEX)]
	Eye and hand coordination and speed of hand movement. This is
	specifically tied to the character's manipulatory limbs. 
	\item[Physical Agility		(PAG)]
	Physical agility of body. This affects the overall body actions of the
	character. It is also a measure of how sensitive the character is to
	the relationship between his body and the environment.
	\item[Mental Strength		(MST)]
	Raw mental power. It is a measure of the characters overall
	computational and reasoning strength. It is also associated with 
	the character's strength of will. 
	\item[Mental Endurance		(MEN)]
	Resilience and stamina of mind. It is an overall measurement of the
	minds ability to recover from shock or disorientation. 
	\item[Mental Agility			(MAG)]
	Mental agility. This affects the overall mind actions of the
	character. It is also a measure of how aware the character is of the
	relationship between his mind and the environment. In another day and
	age this might be called ``Cunning''.
	\item[Psi Potential	(PSI)]
	Measure of how much of a character's MST can be used by the 
	character in psionic actions. This is only a potential value.
	The PSI value does not reflect how much training the character 
	has received, only how much power could be available to the 
	character if indeed the character was psionically trained. 
	\item[Education	(EDU)]
	Measure of the base life experience an entity has absorbed. This 
	is not referring to just formal education but also to general
    life experience in his or her culture.
\end{description}

\section{Secondary Statistics}
\begin{description}
	\item[Physical Body              (PBD)]
    The amount of physical damage a character can absorb. Derived from PST
    and PEN.
	\item[Physical Strength Effect   (PSE)]
    The amount of damage a character can inflict by basic use of strength.
    Derived from PST.
	\item[Physical Fatigue           (PFT)]
    The amount of energy a character can expend, either in damage or in
    work. Derived from PEN and PAG.
	\item[Physical Awareness         (PAW)]
    A measure of a chracter's connection and responses to his physical
    senses. 
	\item[Physical Movement           (PMV)]
    A measure of the character's movemnt. Derived from STR and END and
    racial modifiers.
	\item[Mental Body                (MBD)]
    The amount of mental damage a character can absorb. Derived from MEN and MST.
	\item[Mental Strength Effect     (MSE)]
    The amount of mental damage a character can inflict by basic use of
    mental strength. Derived from MST.
	\item[Mental Fatigue             (MFT)]
    The amount of mental energy a character can expend, either in damage
    or in work. Derived from MEN and MAG.
	\item[Mental Awareness           (MAW)]
    A Measure of the character's connection and ability to quickly correalate
    concious and subconcious clues absorbed by his senses. Derived from PSI,MAG.
    \item[Mental Movement (MMV)]
    A measure of the characters rate of movement in the purely mental 
	realms of psionics and computer interfaces.
\end{description}

\section{Tertiary Statistics}
\begin{description}
	\item[Accuracy (ACC)]
    A measure of the character's effectiveness with projectile or missile
    weapons. Derived from STR and DEX. Could also be called Physical
    Accuracy.
	\item[Physical Combat Ability (PCA)]
    A measure of a character's ability to in\-flict 
	dam\-age in Hand-to-Hand combat. Derived from STR,PAG,DEX.
	\item[Physical Defense (PDF)]
    A measure of a character's ability to avoid taking damage in hand to
    hand combat. Derived from PAG,DEX.
	\item[Focus	(FCS)]
    A measure of the character's effectiveness with focused mental
    actions. Derived from MST and MAG. could also be called Mental
    Accuracy.
	\item[Mental Combat Ability (MCA)]
    A measure of a character's ability to inflict damage in Mind to Mind
    combat. Derived from MST,MAG,PSI
	\item[Mental Defense (MDF)]
    A measure of a character's ability to avoid taking damage in mental
    combat or highly stressful situations. Derived from EDU, MAG.
	\item[General Awareness (GAW)]
    A measure of a character's connection and response to his Mental and
    physical senses. Derived from MAW and PAW.
\end{description}

\section{Other Statistics}
\begin{description}
	\item[Race]
    Self explanatory
	\item[Gender]
    If Applicable.
	\item[Height  (HT) ]
    Expressed in Centimeters. If the creature being described is
    quadrapedal, the height given is the height to the shoulder.
    See the section \dots
	\item[Weight  (WT) ]
    Expressed in Kilograms. See section \dots
	\item[Appearence   (APP)]
    A measure of how attractive a character is to others of his race.
\end{description}

% Include Statistic Calculation Tables
\input{tcgen2.tex}

\clearpage

\section{Racial Modifiers}

The player must decide, with the GM's agreement, on the race that the 
character will be. Once that decision is made any racial modifiers 
must be applied to the statistics. From that point on, no statistic 
may be allowed to exceed the racial maxima.

\section{Gender Modifiers}

Some races may have modifiers to the statistics of the PC based on 
\marginpar{{\em GM's Note} Modifiers to statistics based on gender is
often a sensitive topic and the GM should just dump the rule if it 
turns out to contreversial} their gender.

\section{Cultural Modifiers}

It is possible that the GM may have some cultures that are affected 
by modifiers to their statistics. If so, these modifiers should be 
applied at this time rather than later.

\section{Determination of Height and Weight}

If the character has no preference for the height of the characterit 
may be randomly generated usingf the following formula:

\( Height = AverageHeight + {{2d10 - 11} \over {10}} \times 
HeightVariation
\)

\( Weight = AverageWeight + {{2d10 - 11} \over {10}} \times 
WeightVariation
\)

These figures are based on an adult of the given race.
 
