\documentstyle{book}

\begin{document}
\title{{\center Spell and Psionics Design Model}}
\author{JSM}
\maketitle

\chapter{Spell and Psionics Design}

\section{Outline}

For the rest of the document when I refer to ``Spells'', I am 
referring to any type of application of power derived from a
non-physical source. This includes Psionic workings as well as major 
magical works.

The overall idea is that there are a group of independent and 
dependent factors involved in designing applications of power. 
An independent factor is one that is used in the first approach of 
designing the spell or psionic ability, a dependent factor or 
factor is given a value as a result of the initial design but then 
may be altered by other design decisions. 

THere are a number of Factors or independent factors that form the 
framework for a spell's design. 

\section{Factors involved in spell design}	

\subsection{Area of Energies}

This describes the types of energies to be used. In a magical context 
these would be :

\begin{itemize}
	\item Light
	\item Dark
	\item Shadow
	\item Starlight
	\item Fire
	\item Water
	\item Air
	\item Earth
	\item Belief
	\item Stream
	\item Fabric
\end{itemize}

In psionics these are 

\begin{itemize}
	\item Telekinetics
	\item Phanokinetics
	\item Temporokinetics
	\item Energetics
	\item Biokinetics
\end{itemize}

\subsection{Focus Type}
This describes if the energies affect a target, multiple targets, or 
no targets at all. 

\begin{itemize}
	\item Directed,Self
	\item Directed,Single Target
	\item Directed,Multiple Targets
	\item Non-Directed
\end{itemize}

\subsection{Actions}

This is what the energies are to be used for. There are two types. 
The first type is used when you are manipulating the energies without an 
external target. The second type of action assumes that you are 
applying these energies to affect a target. 

The actions that need no target are as follows:

\begin{itemize}
	\item Detection/Concealment
	\item Divination/Anti-Divination?
	\item Summoning/Banishment
	\item Creation/Destruction
	\item Concentration/Dissapation
	\item Transport/Anti-transport?
	\item Binding/Releasing
	\item Transmutation/Stasis
	\item Translocation/Anchoring
	\item Transmutation/Stasis
\end{itemize}

The actions that require a target are as follows

\begin{itemize}
	\item Influence
	\item Control
	\item Damage
	\item Restore
\end{itemize}

\subsection{Target Components Affected}

If the spell is directed, it must be determined what components of 
the target the spell affects. 

\begin{itemize}
	\item Matter(Inanimate)
	\item Body(Animate)
	\item Mana(Inanimate)
	\item Lifeforce(Animate)
	\item Thought
	\item Perception
	\item Essence(spirit or soul)
\end{itemize}


\subsection{Concentration Type}

The combined depth and duration of the concentration involved. This 
generates a multiplier from which may be figured the overall casting 
time of the spell. 

\begin{itemize}
   	\item Talent
	\item Talent,Instinctual
	\item Spell, Simple
	\item Spell, Standard
	\item Spell, Extended
	\item Working, Simple
	\item Working, Standard
	\item Working, Extended
	\item Ritual, Simple
	\item Ritual, Standard
	\item Ritual, Extended
	\item Rite, Simple
	\item Rite, Standard
	\item Rite, Extended
\end{itemize}

\subsection{Spell Components}
Amount of external props and components.

\begin{itemize}
	\item Verbal
	\item Somatic
	\item Material
	\item Preparation
\end{itemize}

\subsection{Spell Components Modifiers}
The additional modifiers that affect the efficacy of Spell 
Components.

\begin{itemize}
	\item Expensive
	\item Cheap
	\item Rare
	\item Common
	\item Renewable
	\item Non-Renewable
	\item Reusable
	\item Non-Reusable
	\item Complex
	\item Loud
	\item Quiet
	\item Long
	\item Short
\end{itemize}

\subsection{Resistance}
How can the energies be resisted. Resistance defaults to some value 
expressed as an EF modifier to the Saving Throw. To raise or lower 
the EF of resistance from the default will have an appropriate effect
on Spell Design Points.

\subsection{Quantitative Effect}
How much damage or restoration can a spell do (If applicable)
This is expressed as a numeric constant. 

\subsection{Ease Factor}
The Ease Factor involved in casting the spell. Expressed as a
standard EF, not as an EF modifier.

\subsection{Energy Cost}
What is its cost in Mental Fatigue.

\subsection{Casting Time}
How long does the action take in counts or any appropriate time unit.

\subsection{Duration}
How long does it last. Instaneous spells last for a very small and 
fleeting duration. Active Concentration duration spells last for as 
long as the caster concenmtrates on the spell. Any other actions the 
caster may partake of will be considered florentine actions. Passive 
Concentration duration spells last for as long as the caster is 
concious and or clear minded. Permanent spells last until dispelled 
or disrupted. If the spell has a default duration derived from 
previous dependent factors, it is typically expressed in 
appropriate time units. 

\begin{itemize}
	\item Instantaneous
	\item Active Concentration
	\item Passive Concentration
	\item Permanant
	\item Default 
\end{itemize}

\subsection{Range}

Touch range spells require the caster to come into physical contact 
with the target. Default range spells are typically expressed as 
multipliers of the mages own Magical Potential. 
 
\begin{itemize}
	\item Touch
	\item Default
\end{itemize}

\subsection{Drain}
Numeric value denoting the Ease Factor of the roll needed to avoid 
paying the Mental Fatigue cost of the casting.



\section{Dependent Factors Tables}

For a given EC=10
For a given EF=7
For a given CT=10
						QE
Light					3
Dark					3
Shadow					2
Starlight				2

Fire					5
Water					5
Air						5
Earth					5

Belief					6

Stream					1
Fabric					2

Telekinetics			1
Phanokinetics			1
Temporokinetics			1	
Energetics				1	
Biokinetics				1	

						
Directed,Self
Directed,Single Target
Directed,Multiple Targets	
Non-Directed

Detection/Concealment
Divination/Anti-Divination?
Summoning/Banishment
Creation/Destruction
Concentration/Dissapation
Transport/Anti-transport?
Binding/Releasing
Transmutation/Stasis
Translocation/Anchoring
Transmutation/Stasis

Influence
Control
Damage
Restore

							EF	COST	CT		DUR	RES	RANGE QE

Matter(Inanimate)
Body(Animate)
Mana(Inanimate)
Lifeforce(Animate)
Thought
Perception
Essence(spirit or soul)

Talent
Talent,Instinctual
Spell, Simple
Spell, Standard
Spell, Extended
Working, Simple
Working, Standard
Working, Extended
Ritual, Simple
Ritual, Standard
Ritual, Extended
Rite, Simple
Rite, Standard
Rite, Extended


							EF	COST	CT		DUR	RES	RANGE QE

Verbal
Somatic
Material
Preparation

Expensive
Cheap
Rare
Common
Renewable
Non-Renewable
Reusable
Non-Reusable
Complex
Loud
Quiet
Long
Short


\section{Examples and Explanation}

A typical design scenario would proceed along these lines .
The PC would detail the Area of Energy to be used, The actions
and, if there is a target, the target components affected.
This generates various defaults for some values and the others are 
set to usable default values as the starting point for the design.

For example these are the dependent facrors that one would 
typically see along with what they derive their default values from.

\begin{verbatim}
CT						Derived from Area of Energy and Actions
COST					Derived from Area of Energy and Actions
RESISTANCE				Defaults to Passive and Active Resistance
QUANTITATIVE EFFECT		Derived from Area of Energy 
COMPONENTS OF TARGET 	Defaults to all components
CONCENTRATION TYPE		Defaults to simple spell
MATERIAL COMPONENTS		Defaults to none
PREPARATION				Defaults to none
RANGE					Defaults to Mental Strength (MST)
DRAIN					Defaults to standard EF=7
\end{verbatim}

Once a spell has been initially laid out the designer can increase or
decrease the spells value by manipulating the factors and a "Spell 
Point Pool". 

If the designer lengthens the Casting Time then points are added to 
the pool and if he Shortens it points are subtracted from the pool. 
And so it goes for each addition or subtraction to the factors of the 
spell.


\section{Examples}

{\large The following example uses bogus numbers. }

The fireball spell has the following basic details. The Area of 
Energy is Fire. The first Action is to Summon the Fire. The second 
Action is to Transport Fire. The third ACtion is to Damage the 
Target. So the spell is directed at multiple targets. 
 
The above things imply the following:

\begin{verbatim}
CAST TIME			5 counts
COST				5 Mental Fatigue
EASE FACTOR			2 
RESISTANCE			Both Passive and Active Resistance
QUANTITATIVE EFFECT	d10-4 (Light)
TARGET COMPONENTS	all
TYPE OF CAST		Simple spell
MATERIAL COMPONENTS	none
PREPARATION			none
RANGE				Mental Strength (MST) in yards or hexes
DRAIN				4
\end{verbatim}

Now the designer can modify each of the elements of the spell
and balance it by adding and subtracting from the pool. 

After this section is a set of {\large VERY ROUGH} values for 
adding/subtracting points to the pool. 

With these default values we can see that the spell is pretty wimpy. 
We would like to make this fairly nasty so lets add to the Spell 
Design Pool by doing the following:

We extend the cast time to 15 counts (3 seconds) from 5 counts (1 
second). This adds two points to the pool. The spell currently 
affects all seven components of the target. Lets cut that down to 2
(Body and Matter). That adds 5 points to the pool. We can add to the 
concentration needed to cast and make it an Extended Spell. That adds 
1 to the pool. 

This makes the spell something like this:

\begin{verbatim}
CAST TIME			15 counts
COST				5 Mental Fatigue
EASE FACTOR			2 
RESISTANCE			Both Passive and Active Resistance
QUANTITATIVE EFFECT	d10-4 (Light)
TARGET COMPONENTS	2 (Matter and Body)
TYPE OF CAST		Extended spell
MATERIAL COMPONENTS	none
PREPARATION			none
RANGE				Mental Strength (MST) in yards or hexes
DRAIN				4
\end{verbatim}

With 8 points in the pool. 

Let us now start to improve key elements of the spell. Lets add to 
the EF of the spell by 2. That costs 4 points of the pool. Lets 
double the range. That cost 1 point of the pool. We still have 3
points in the pool. Lets up the damage. Lets approximately double it 
for the average roll (Very approximate). This costs another point. 
This gives us two points left in the pool and a spell that looks like 
the following:

\begin{verbatim}
CAST TIME			15 counts
COST				5 Mental Fatigue
EASE FACTOR			4 
RESISTANCE			Both Passive and Active Resistance
QUANTITATIVE EFFECT	d10+2 (Light)
TARGET COMPONENTS	2 (Matter and Body)
TYPE OF CAST		Extended spell
MATERIAL COMPONENTS	none
PREPARATION			none
RANGE				2 times Mental Strength (MST) in yards or hexes
DRAIN				4
\end{verbatim}

We can then spend the last two points on EF. That makes an EF = 5. 

A quick explanation of EF for those who have not encountered the 
topic. In Space Hybrid the chance to perform an action is based on the Ease 
Factor of the action times the Stat Basis of the action plus 5\% 
times the Rank of the action. For discussion's sake we will assume an 
average Stat Basis (SB) of 7. So a mage with rank 0 in the fireball 
spell would have an average chance of \( 4 \times 7 + 1 \times 5\% \) 
or 33\%. This is without setup or any spell purification. 

\section{Spell Design Pool transformations}

\subsection{EASE FACTOR (EF)}
\begin{itemize}
	\item Decrease EF				(EF-n)		+2n
	\item Increase EF				(EF+n)		-2n
\end{itemize}

\subsection{CAST TIME (CT)}
\begin{itemize}
	\item Shorten Cast Time		(CT/n)		-(n-1)
	\item Lengthen Cast Time		(CT x n)	+(n-1)
\end{itemize}

\subsection{COST}
\begin{itemize}
	\item Decrease Cost			(Cost/n)	-(n-1)
	\item Increase Cost			(Cost x n)	+(n-1)
\end{itemize}

\subsection{DURATION}
\begin{itemize}
	\item Decrease Duration		(Dur/n)		+(n-1)
	\item Increase Duration		(Dur x n)	-(n-1)
\end{itemize}

\subsection{RESISTANCE}
\begin{itemize}
	\item Passive/Active			+0
	\item Passive					-1
	\item Active					-2
	\item Neither					-3
\end{itemize}

\subsection{QUANTITATIVE EFFECT (QE)}
\begin{itemize}
	\item Increase				(QE x n)	-(n-1)
	\item Decrease				(QE/n)		+(n-1)
\end{itemize}

\subsection{TARGET COMPONENTS}
\begin{itemize}
	\item Decrease 				+1/TargetType
\end{itemize}

\subsection{TYPE OF CAST}
\begin{itemize}
	\item Instinctual Talent  -3
	\item Talent				-2
	\item Standard Spell		+0
	\item Extended Spell		+1
	\item Ritual				+3
\end{itemize}

\subsection{MATERIAL COMPONENTS}
\begin{itemize}
	\item Cheap/Common		+1
	\item Rare/Expensive		+2
	\item Reusable			+0
	\item Non-Reusable		+1	
\end{itemize}

\subsection{PREPARATION}
\begin{itemize}
	\item Simple				+0.5
	\item Short				+0.5
	\item Complex				+1
	\item Long				+1
\end{itemize}

\section{Other Notes that are of interest}

Investment Rituals are specific to the energy being used. Normally,
invested items can resist. With sufficient preparation the 
resistance can be dropped to 0. 

Warding rituals are similiar.

Knowing True Names acts to lower the resistance of the target.

Remember that this spell design process is simply intended to speed
the actual creation of spells. Once a spell has had its values determined
it may be manipulated by putting more power into it in order to
"turbo-charge" the spell. 


\end{document}





