
Bitadara (Elves)


	Elven culture is entirely connected and interwoven with their
life cycles. Elves speak of distinct "Life Ages" or Kii. These are
physiologically distinct forms. These forms are named and have almost
no correalation to the chronological ages of the entity. They are in
name : Chawara (infancy), Iquira (EE-KWER-A) (Childhood), Anatathan
(AN-A-TA-THAN) (Young Adult), Laenya (LAA-EE-NYA) (Time of Passing),
Sheerahnen (SHE-EE-RAH-NEEN) (Fullness), Eya (EE-YA) (Inward Turning).


Chawara (infancy)

  A path is decided by the first step, and no sooner. - Elven Proverb.

	An elven child is born without hair or nails. Almost no real
vision is developed until a month after birth. Empathy, for many, is at
the strongest it will be ever be. The environment empathically
influences the future forms of the Elf. It is conceivable that the
first hint of mage talents could be seen here. For non-mage children
this empathy will diminish as the entity enters Iquira. Mesaah
(ME-SA-AH) or mage children, will retain much of their empathy. (2-3
years) . Twins are almost unheard of and triplets are truly unknown.
Eyes are often pale and almost clear.

Iquira (Childhood)

	Empathy tends to drop to its lowest point. Much of the energies
turn toward care of almost all domestic activities. Farming is more
common than hunting and meat eating is rare. Most of the farming is
small lot based. As the elf matures ( 20-200 years)  In times of large
population growth a small percentage of Iquira never go on to the state
of Anatathan. The gradually diminishing empathy comes to be superseded
by a mild form of telepathy. Iquira have crystalline colors in their
eyes.  


Anatathan (Young Adult)  

	The anatathan are the warriors, the fighters. As they get older
, they gain in natural speed and perception. It is here that most elves
can become fertile though only during periods of stress for the race do
many anatathan have children. And , when they do, these same children
tend to be quick to become Anatathan. It is often that during these
periods of stress that Anatathan never become Laenya. It is said to be
a sacrifice that the elve's spirit made for the race. For this reason
it is appropriate to mourn the passing of an Anatathan where one would
not mourn a Laenya ( who did, after all, lived out a full life ).
Typically lasts between 20 - 300 years. Anatathan eyes are usually
brighter colored , hovering between translucent and transperant.


Laenya(Fullness)


	Those that live on to become Laenya gain in empathy agin and
tend to pursue their final goals. They become leaders and mages ,
craftsman and artists. More live to become Laenya during the peaceful
times. The natural magics intensify and become very noticeable. The
reflexes do not slow but the combat perceptions gradually fade. The
elf's knowledge of his body becomes nearly complete. Poisoning and
disease becomes rarer. The Laenya eyes tend to be darker and definitely
opaque. The period lasts between 900 and 1000 years.

  
Ea (Inward Turning)

	Those who live to this most venerated state are rare. The elfs
empathy becomes almost as great as when they were Chawara. Their
empathy gradually extends to all life within their perception. The eyes
darken to nearly black and their sight loses all IR and Visible acuity.
Only the UV and shorter wavelengths are used. The greatest philosophies
and thoughts of the elven culture come from those who have achieved
this state.  

Abilities of Bitadaran	

	In general the elves have a variety of talents. They have a
greater than average MA and are comfortable with minor magics. The
majority of the elven forms gain a +1 to all difficulty factors in
minor casting. Anatathan gain a -1 to minor magery. Anatathan often
produce unpredictable results with those minor magics they do use.

Faen

	Faen is the proximity sense that is first developed by the
Iquira and is most visible in the anatathan. At any point that an
entity enters within an Anatathans perception (PC in feet) their
perception doubles briefly.
	All perception rolls are made based on this doubled perception.
This perception comes to the elf during times of stress and is often
visible to others as a drastic change in the reflective patterns of the
eyes. Also, any agil or strength based feat is +1 in difficulty factor.

Alitharinaa(Sense of self)

	At a time of injury, infection, or poisoning. The Bitadara
often will go into a kind of "Healing Shock". This state is seen as a
complete darkening of the entire eye of the Elf. This state allows for
the regrowth of endurance as if it were fatigue. (Excludes cold Iron
damage)

Kiilan(Mind Seeing)

	During Early stages this shows itself as empathy and then
telepathy and finally, both.

Cold Iron(Irinal)

	Iron (not steel) is the true bane of Bitadaran life. All Iron
wounds (Fatigue or endurance) are burns as well as the normal damage.
Any such injury requires a WP s.t. to prevent being stunned. Such
wounds require 2X the normal time to heal.    
