\begin{document}
\title{The Races of Tanah}

\begin{itemize}
	\item Rupa Kechil(Ruu-pa Kee-Chil),Shapeshifters
	\item Bitadari(Bit-a-dar-ree),Elves
	\item Duwan(Duu-wan),Halflings
	\item Kurrock(Kur-Rok),Dwarves
	\item TorNimban(Tor-Nim-Ban),Cloud Giants
	\item TorRian(Tor-Ree-An),Fire Giants
	\item TorFrigan(Tor-Free-Gan),Frost Giants
	\item TorJemma(Tor-Gem-Ma),Stone Giants
	\item Torgan(Tor-gan)
	\item Erlan,The Isle
	\item Human
	\begin{itemize}	
		\item Kalifate(Kal-ee-faat), Spanish-Moorish
		\item Safoan(Sa-Foo-an), Island Subgroup of the Kalifate
		\item Kothan(Koo-Than), Germanik Viceral
		\item Tyronian(Tii-Roo-Nee-an), Kothan gone over to Horse Nomadic
		\item Emrik(Em-Rik), Kothan subgroup 	
		\item Vairman(Vair-Man), Kothan Highlander	
		\item Dalesman(Dal-Man), Kothan mormon
		\item Arsa'e(Ar-sa-Ee), Peublo based culture, Thai features.
		\item Tarmane(Tar-Maan), Masai Hunter Gatherer/Herder Types
		\item Sarsin(Sar-Sin), Persian
		\item Merovan(Mer-Oo-Van), Norman Farmer
		\item Hightan(Hii-Tan), Scottish Highlander
		\item Hairochon(Hair-o-Koon), Giant Dwarves	
		\item Thanaen(Tha-Naa-En), Venetian culture, sisterhood of steel, liaden
	\end{itemize}
\end{itemize}

\newpage

\section{Rupa Kechil}

Culture Name: Rupa Kechil
Avg. Height: NA
Avg. Weight: NA
Skin Color: NA
Hair Color: NA
Eye Color: NA
Stat Mods: NA
Inherent Skills: Shapeshifting
Description:
.DE
.PP
Recent Comers to the world of Tanah. The skin turners, in
general organise themselves along clan or totem lines. There
are several animals associated with the changers.  
.EP
.DS C 
Tiger	Harimau
Bear	Bidok 
Boar	Jantan 
Wolf	Anjing 
Cheetah	Mallini 
Eagle	Akila
.DE
.PP
Within the past 500 years the skinturners have entered the view of man.
The description of shapeshifters is dependent on what type of
humans run in their bloodlines and what animal they shift to.
.PP
In general, shapeshifters have no unique culture, they absorb
much of their culture from the societies around them.  It is said that
there is a greater form of shapeshifter which acts as a governer in
each loosely knit clan. These are given the title Rajah. 
Shapechangers have a fairly complex hand talk language called sift-rak. 
There is no written language per se but many changers use pictographs
of the sift-rak in order to convey a message.
.PP
Most clans that travel together do so as a gypsy like caravan. This is
very rare though and only seen in areas away from the Koran kingdom.
.PP
Changers, as a rule,acknowledge only the principle that might makes right. All
shapechangers make passive resistance rolls whether they want to or
not.

\section{Bitadari}

Culture Name: Bitadari
Avg. Height: 5'2"/5'0"
Avg. Weight: 114/104
Skin Color: NA
Hair Color: NA
Eye Color: Depends on Life Cycle
Stat Mods: PS -1; AG +1; EN -1; MA +1; WP +1; FT +1; PC +1; TMR +1 
Inherent Skills: See Below
.DE
.SH
Description:
.PP	
Elven culture is entirely connected and interwoven with their
life cycles. Elves speak of distinct "Life Ages" or Kii. These are
physiologically distinct forms. These forms are named and have almost
no correalation to the chronological ages of the entity. They are in
name : Chawara (infancy), Iquira (EE-KWER-A) (Childhood), Anatathan
(AN-A-TA-THAN) (Young Adult), Laenya (LAA-EE-NYA) (Time of Passing),
Sheerahnen (SHE-EE-RAH-NEEN) (Fullness), Eya (EE-YA) (Inward Turning).
.SH
Chawara (infancy)
.DS C
A path is decided by the first step, and no sooner. - Elven Proverb.
.DE
.PP
An elven child is born without hair or nails. Almost no real
vision is developed until a month after birth. Empathy, for many, is at
the strongest it will be ever be. The environment empathically
influences the future forms of the Elf. It is conceivable that the
first hint of mage talents could be seen here. For non-mage children
this empathy will diminish as the entity enters Iquira. Mesaah
(ME-SA-AH) or mage children, will retain much of their empathy. (2-3
years) . Twins are almost unheard of and triplets are truly unknown.
Eyes are often pale and almost clear.
.SH "Iquira (Childhood)"
.PP
Empathy tends to drop to its lowest point. Much of the energies
turn toward care of almost all domestic activities. Farming is more
common than hunting and meat eating is rare. Most of the farming is
small lot based. As the elf matures ( 20-200 years)  In times of large
population growth a small percentage of Iquira never go on to the state
of Anatathan. The gradually diminishing empathy comes to be superseded
by a mild form of telepathy. Iquira have crystalline colors in their
eyes.  
.SH "Anatathan (Young Adult)  "
.PP
The anatathan are the warriors, the fighters. As they get older
, they gain in natural speed and perception. It is here that most elves
can become fertile though only during periods of stress for the race do
many anatathan have children. And , when they do, these same children
tend to be quick to become Anatathan. It is often that during these
periods of stress that Anatathan never become Laenya. It is said to be
a sacrifice that the elve's spirit made for the race. For this reason
it is appropriate to mourn the passing of an Anatathan where one would
not mourn a Laenya ( who did, after all, lived out a full life ).
Typically lasts between 20 - 300 years. Anatathan eyes are usually
brighter colored , hovering between translucent and transperant.
.SH "Laenya(Fullness)"
.PP
Those that live on to become Laenya gain in empathy agin and
tend to pursue their final goals. They become leaders and mages ,
craftsman and artists. More live to become Laenya during the peaceful
times. The natural magics intensify and become very noticeable. The
reflexes do not slow but the combat perceptions gradually fade. The
elf's knowledge of his body becomes nearly complete. Poisoning and
disease becomes rarer. The Laenya eyes tend to be darker and definitely
opaque. The period lasts between 900 and 1000 years.
.SH "Ea (Inward Turning)"
.PP
Those who live to this most venerated state are rare. The elves'
empathy becomes almost as great as when they were Chawara. Their
empathy gradually extends to all life within their perception. The eyes
darken to nearly black and their sight loses all IR and Visible acuity.
Only the UV and shorter wavelengths are used. The greatest philosophies
and thoughts of the elven culture come from those who have achieved
this state.  
.SH "Abilities of Bitadaran"
.PP
In general the elves have a variety of talents. They have a
greater than average MA and are comfortable with minor magics. The
majority of the elven forms gain a +1 to all difficulty factors in
minor casting. Anatathan gain a -1 to minor magery. Anatathan often
produce unpredictable results with those minor magics they do use.
.SH Faen
.PP
Faen is the proximity sense that is first developed by the
Iquira and is most visible in the anatathan. At any point that an
entity enters within an Anatathans perception (PC in feet) their
perception doubles briefly.
.PP
All perception rolls are made based on this doubled perception.
This perception comes to the elf during times of stress and is often
visible to others as a drastic change in the reflective patterns of the
eyes. Also, any agil or strength based feat is +1 in difficulty factor.
.EP
.SH "Alitharinaa(Sense of self)"
.PP
At a time of injury, infection, or poisoning. The Bitadara
often will go into a kind of "Healing Shock". This state is seen as a
complete darkening of the entire eye of the Elf. This state allows for
the regrowth of endurance as if it were fatigue. (Excludes cold Iron
damage)
.SH "Kiilan(Mind Seeing)"
.PP
During Early stages this shows itself as empathy and then
telepathy and finally, both.
.SH "Cold Iron(Irinal)"
.PP
Iron (not steel) is the true bane of Bitadaran life. All Iron
wounds (Fatigue or endurance) are burns as well as the normal damage.
Any such injury requires a WP s.t. to prevent being stunned. Such
wounds require 2X the normal time to heal.    
.EP
\section{Duwan}
 
Culture Name: Duwan
Avg. Height: 3'5"/3'4"
Avg. Weight: 70/68
Skin Color: Full Range
Hair Color: Full Range
Stat Mods: PS -3; MD +3; AG +1; EN -2; MA -1; WP +1
Inherent Skills: 
.DE
.SH Description:
.PP
The Duwan are a very small group and fairly little is known about
them. They generally have roundish and clear bright eyes, Furry feet , and a
good appetite. There is a tendency towards good lying/ storytelling in
the culture.
.SH Resources
.PP
Usually they settle in areas that have enough farming land and some
iron ore.
.SH "Subsistence Patterns"
.PP
They tend to have a fairly sophisticated farming setup. Most food is
grains and rootstocks with some of the simpler meats such as fish
.SH "Values and Kinship"
.PP
Duwan value thrift and cunning. Orderliness is a desireable trait
and well thought of. Courtesy and style are foremost in most duwan
minds. They care well for their own and care little for the tall folk.
Not disdain, just disinterest.
.SH Language
.PP
Duwan speak Duwan. They rarely use trade talk. Most can read and
write in Duwan. 
.SH Deities
.PP
Duwan worship a full belly, a good story, and a sharp wit.
.SH Rituals and Traditions
.PP
Duwan traditions and rituals very from village to village and hutch
to hutch. In most cases , holidays are caused by events of local
noteriety and little else.
.SH Technology
.PP
Most Duwan settlemnents are fairly low on the technical end, but
they need little. If they do set out to get tools they are often
attracted to the intriguing rather than the useful. ???
.SH Politics
.PP
Most actual ruling is that of self rule combined with detailed traditions. Usually
there is a judge or elder to interpret the laws as necessary. The Duwan
truly believe that "There taint na sech ting as a fraa lunch", with the
corallary "'Cept dat which ya borra for y'self".
.PP
One of the strangest things about Duwan is that some goodly number of
their population often go on walkabouts. The walkabouts are rarely
short. An interesting sidenote is that because Duwan seem to be rather
careless of most others' property rights other than their own their need
to collect mementos of their travels has contributed to their reputation
as thieves.

\section{Kurrock}

Culture Name: Kurrock 
Avg. Height: 4'6"/4'6"
Avg. Weight: 140/135
Skin Color: chalky white
Hair Color: Usually dark brown to black.
Eye Color: Black.
Stat Mods: PS +2; AG -2; EN +1; MA -3; WP +3; PC +1; TMR -1;  
Inherent Skills: 
.DE
.SH Description:	
.PP
Kurrock are truly the most frightening fighters and drinkers around.
They tend to get a reputation for just those things as a result but in
reality, Kurrock are also skilled artisans, mechanicians, and miners. 
.PP
Kurrock are very hard to figure as a culture simply because they are
so directed towards creation and artisanry that the have little time for
politics. Skill in ones chosen field is what rules. Such are the tastes
of Kurrock that all will agree who does what netter than whom. If you ask
in a village, who is your best warleader they will all agree. If you ask
them who is the best smith they will agree. 
.PP	
They spend much of their time improving themselves. They practice
continually and contests of a monthly nature are not unheard of. All
Kurrock want to be known as being the very best at something.
.SH "Physical Resources"
.PP
Kurrock tend to settle into regions of rich mineral deposits and care
less for the aboveground fertility of the land than most races. Iron and
coal as well as the precious metals tend to be their favorite materials.
.SH  "Subsistence Patterns"
.PP
Kurrock tend to farm both below and above ground. 


\section{TorNimban}

Culture Name: TorNimban
Avg. Height: 17'/16'
Avg. Weight: ??/??
Skin Color: Clear to light
Hair Color: Almost always blond to white
Eye Color: Blue to green
Stat Mods: As book
Inherent Skills: 
.DE
.SH Description:	
.PP
TorNimbans are generally a Shipborne race with one known cultural
center: Sulkar Keep.
.SH 
.he //Races & Cultures of Tanah/TorRian/
.bp
Race: TorRian
Culture Name: TorRian 
Avg. Height: 12/11
Avg. Weight: 
Skin Color: Pink to Dusky Brown
Hair Color: Brown to red
Eye Color: Brown to Red
Stat Mods: As Book
Inherent Skills: 
Description:	
.PP
Found mostly in the volcanic regions far south of the holy empire
of light.

\section{TorFrigan}
Culture Name: TorFrigan 
Avg. Height: 19/18
Avg. Weight: 
Skin Color: Light to pale
Hair Color: Platinum blonde to Blue
Eye Color: Green, White, Silver
Stat Mods: As Book
Inherent Skills: 
Description:	
.PP
Found mostly in the Mountain regions regions far North of the 
Northern Reaches.

\section{TorJemma}
Culture Name: TorJemma
Avg. Height: 10/9
Avg. Weight: ??
Skin Color: Dark Brown to Black
Hair Color: Reddish Brown to Black
Eye Color: Gold, Green, Sapphire Blue, to Garnet Red
Stat Mods: As Book
Inherent Skills: 
Description:	

\section{Torgan}

Culture Name: Tairganik 
Avg. Height: 6'1"/5'11"
Avg. Weight: 200/170
Skin Color: Olive
Hair Color: Black to Dark Brown
Eye Color: Light colors
Stat Mods: PS +1; EN +1; FT +1; AG +1; MA -4; WP +1; PC +1
Inherent Skills: 
.PP
Their sight extends somewhat into the IR range which allows
them to differentiate between reds much more than most.
.SH 
Description:	
.PP
In general Torgans are a tall ( 6'1" Male and 5'11' Female)
race of olive skinned individuals. Dark of hair (Black to
dark brown with rare auburn ) with light eyes and Pronounced
jawbones and Bicuspids. Eyebrows tend to arch toward the
edges of the face. Ears are usually elongated and lobeless.
.PP
Exp Mul 1.3
.SH 
Subsistence Patterns
.PP
Both hunters and farmers. Their hunts tend to be of a
communal type. Well advanced in farming and erosion theory.
Generally comfortable with grains and root crops as well as
fruit orchards. Vine crops are also very common - Especially
wine grapes and climbing melon.
.SH 
Values and Kinship
.PP
Torgans value bravery, skill and beauty. They are much given
to song and music. Generally they will hold a singer or
harper inviolate unless the harper blasphemes. They
particularly honor bravery evidenced by self sacrifice and
favor tragic and loving songs. Kinships are reckoned by
descent through the female and are very important to
Torgans.
.SH 
Language
.PP
The Torgan language is not Orcish as would be expected from
their appearance. It is a fairly formal latinesque language.
It shares some common roots with the elven tounge spoken
today. In particular it uses the older elven phrases for
special names and formal phrases.
.PP
Literacy is restricted to Women, Seers, Mages and scribes. Fairly
widepread but with definitive degrees of literacy between
various classes. Military leaders often learn a basic battle
language called Habaksa. A mixture of old Sift-Rak and
written symbols derived from hand motions.
.PP
They use a stilted and formal runic language. Shares some traits with
written Bitadari and Dwarven.
.BTABLE
Vocabulary and Grammar

ambassador               Legatus
Yes                      Sertae
No                       Non
Hand                     Manus
Scout                    Konsilum
Trooper                  Katern
Hand Leader(Ldr of 5)    Praetor
Lance(Ldr of 50)         Sarisanar
Ldr of 100               Centurion
.ETABLE
Religion,Myths,and History
.PP
The Torgans believe in the Nadir or fates, and a pantheon of
gods reminescent of Roman and Syria.  They are fairly pious
and hold most reverence for the father and mother of the
gods.
.PP
Each household rests their fortunes with a founding spirit
and each legion believes themselves to be the incarnation of
their totem.
.SH 
Tradition
	Wedding
    Bedding
    Birthing
    Battle
    Other
Rites and Ritual
Institutions and Clergy
Religious Norms
Technology
.PP
Probably one of the most sophisticated races technologically, the
Torgans have the beginings of a true steel based economy. THey have
many skilled mechanicians and and understand much of basic physics.
Simple steam engines, Lanterns, Screws and levers are quite common.
Metal springs are known as are simple mechanical dart guns. The use of
a simple smoke powder is well known and so is the use of Naptha. Water
clocks and a standard set of weights and measures. Surveying and road
building are well honed skills. Plumbing is a known quantity as is
composting sewage.
.SH 
Art, Architecture, and Symbolism
	Significant Numbers
	Symbolism and Motifs
Politics and Warfare
	Leadership
	Armed forces status
	Class Controls
	Legal Code
	Judicial Structure
	Foreign Relatins
.sp 2
Military Structure
.PP
The command structure of the Torgan legions is fairly complex. The
complexity is not due to their chain of command this is actually fairly
simple, it is due to the additional layer of cultural interaction and
training.
.SH 
The Chain of command goes in the following order:
.BTABLE
The Senate Council
        |
        |
        V
  The 13 Legions ---> The High Battle Masters
                               |
                               |
                               V
                      Kinturions ( Leader of 1000 )
                               |
                               |
                               V
                      Centurions ( Leader of 100 )
                               |
                               |
                               V
                      Sarisani ( Leader of 50 )
                            (Lance Leader)
                               |
                               |
                               V
                      Praetor ( Leader of 5 (hand) )
.ETABLE
.PP
Each of the 13 legions actually varies in number between one thousand
and six thousand troopers or Katern. Each of the legions is noted for a
particular specialty , usually related in someway to the legion totem.
.SH 
.BTABLE
The 13 legions are :

       a) The Auric Dragon
               The Very Best
       b) The Crystal Pheonix
               Strategists and Tacticians
       c) The White Wolf
               Scouts and Hunters
       d) The Black Courser
               Mounted Lance
       e) The Red Bear
               Shock Troops
       f) The Scarlet Hynd
               Runners and Mappers and Signalers
       g) The Argent Pard
               Acrobatics and Climbing
       h) The Shadowed Falcon
                    
       i) The Wolverine Bronze
               Engineering
       j) The Verdant Griffon
               
       k)
       l)
       m)
       n) The Nameless
.ETABLE
Routine
.BTABLE
Arms
   Trooper
       Full Leather Cuirass, Bracers, Large Shield
       Short Sword    R2
       Running        R2
       Javelin        R2
       Dagger         R1
       Hvy Crossbow   R2
       Large Shield   R2
       Armoured Move  R1
   Squad Leader
       Chain and Leather, Bracers, Large Sheild
       Short Sword    R3
       Running        R2
       Javelin        R2
       Dagger         R1
       Hvy Crossbow   R2
       Large Shield   R2
       Armoured Move  R2
       Mil Sci        R1
       Horsemanship   R1
       Signaling      R1
   Scout
       Light Leather, Bracers, Small Sheild
       Short Sword    R2
       Running        R3
       Swimming       R1
       Tracking       R1
       Small Shield   R2
       Javelin        R2
       Dagger         R1
       Armoured Move  R3
       Signaling      R1
   Century Leader
       Improved Plate(+8), Bracers, Large Sheild
       Short Sword    R3
       Running        R2
       Javelin        R2
       Dagger         R1
       Hvy Crossbow   R2
       Large Shield   R2
       Armoured Move  R4
       Mil Sci        R5
       Horsemanship   R3
       Signaling      R1
.ETABLE            
    4. Outfitting
    5. Theory
.he //Races & Cultures of Tanah/Tor/
.bp
Race:
Culture Name: 
Avg. Height: 
Avg. Weight: 
Skin Color: 
Hair Color: 
Eye Color: 
Stat Mods: 
Inherent Skills: 
Description:	


