
city location

having established the geographic, manographic,and climatographic
patterns of his world, the games master should determine the location
of cities and towns. it is necessary to keep in mind that people (and
other intelligent creatures) do not gather without a reason. cities
must be placed with care if the map is to look realistic.

most cities and towns are located for convenience for trade. a city
often begins as a convenient port and/or trading post. furthermore,
no city may grow beyond a certain size without the availability of
transportation for food. an urban environment (given medieval
technology, or, for that matter, present-day earth technology cannot
feed itself. it must have convenient access to a stream of trade, and
it usually makes its living by facilitating that trade.

port cities tend toward great size. a port will likely be located at
a river mouth or within a natural bay that provides protection from
storms.  occasionally, if a river is navigable for a great distance,
a large port may be found inland . especially at a confluence. where
two sizeable rivers meet. a large lake may also have port cities; if
it is connected to an ocean, there will definitely be a port or two.
a port may be useful year-round, or it may only be open during the
warm season when ice retreats. as a rule, port cities are active and
cosmopolitan; they tend to be tolerant of strangers. port cities are
represented by a special symbol (*) on maps. the presence of this
symbol implies st least a minimum of docking and warehousing
facilities, as well as water deep and safe enough to allow approach
of ships.

trade routes also give rise to cities. a spot where caravans are
especially likely to pass (for example. a year- round spring or oasis,
or an especially convenient mountain pass) will give rise to inns. 
shops, homes, and eventually a town. a spot which is unremarkable in
other ways may eventually grown to house a great city merely because
it is at the inter- section of two great trade routes. once your main
cities are plotted on the map, you may wish to go back and figure
logical trade routes in order to add such meeting-places.

natural resources can lead to city growth. if a certain resource (for
instance, a jewel mine) requires people and/or technological support
in order to be properly exploited, a town grow up very quickly -and
die just as quickly if the resource is exploited. keep the "gold
rush" in mind.  resources that might justify town development (in
addition to the obvious) would include rare forest or jungle products
(i.e - spices); surface oil pools; stone quarries, etc..

boundary areas - spots where two or more terrain types meet - are
likely areas for towns and cities. here (for example) plainsdwellers
and forest folk can meet, trade their goods. settle disputes, and
learn the news.  such an interface area may even be a customary
meeting-place for two different races - i.e., men and elves. an
extreme example of an interface city would be the coastal town
inhabited jointly by land-dwellers and merfolk. half in the water. 
half ashore, such a city would be a wonder - and a delight to
merchants and intriguers alike. imagine a city where any basement
might conceal a tunnel leading to the ocean . . . where any sunken
building might hold rooms for air-breathers . . . where goods from
al1 lands and all seas were bartered in the markets. from half-sunken
stalls lining gondola-flecked canals . . .

market towns. most of the above descriptions imply sizeable towns -
but a town doesn't have to be large to facilitate trade. the
countryside is dotted with villages, each with its cluster of houses
and straggle of outlying farms. such farmers' markets are as
necessary to life and commerce as ere the big cities. and no map will
be complete without them.  such small villages are likely to contain
only one race - or at least one race will be in the majority. their
population will usually be under 500, and they will have little in
the way of "civilized" accommodations to offer, though the folk there
may be as friendly as any.

inn-villages are those isolated clusters of buildings likely to be
found.  a day's travel apart. along any trade route that passes
through less-inhabited territory. such a village will be very small
(under 100 souls) and will likely exist only to serve the needs of
travellers (and extract small profit as well). such small villages
should be spotted along major trade routes or at the junctions of
minor ones.

city locations may also be influenced by local mana levels. a
relatively high concentration of mana in an area may prompt the
building of a city there. year by year. as magic-inclined folk move
nearby. this is especially true of (for instance) a small mana-7 spot
in mana-6 territory, or mana-8 in mana-7 territory. if the general
mana level is 8, a spot of level 9 or 10 may become a city site. more
likely the city will develop around it, and the high-mana spot will
be given over to magical houses, temples, and the like. this is true
for two reasons. first. the sorcerors will want to pre-empt the areas
most conducive to the practice of their craft; second, mana weather -
which is peculiar to high-mana areas - can be a nuisance or worse to
those without the knowledge to dispel it.

an unusually low concentration of mana may also prompt the
construction of a city. a magic dead area makes a fine spot to build
a fortress in which one will be safe from adept foes. . . and any
fortress is likely to become the nucleus of a town (see below). and
certain crafts, notably that of the mechanicians, flourish best in an
area in which magic is little practiced.  there can be conveniences
in having an area nearby in which no magic operates at all.

a nearby high-mana area with a useful aspect or emotional aspect may
also give rise to a town. this will be especially likely if the
aspect involved is a weak but pleasant one. people are likely to
gravitate to such an area without even knowing why they do so. of
course, any type of aspected area may attract a temple of adepts
whose religion corresponds to that particular aspect, and a thriving
temple may engender a town just as a military post does (see below).

in wealthy or civilized areas, a town may be "planned" as a capital
or resort area. if enough money and labor is available, a town or
even a large city may be planned and built-from scratch. such a city
will be much move regular in appearance than normal cities. which
begin almost by accident and grow slowly. a planned city is often
located to take advantage of a particularly good view, salubrious
climate, or similar non-economic reason. however. it will still be
positioned in such a fashion that it is convenient to trade routes -
and if its builders are military-minded at all, it wil1 be made
defensible.

a town 15 very likely to grow up around any fortress or military post.
one reason is obvious: people will want to move within the walls for
protection - or, failing that, as close to the walls as possible. 
the second reason is often the most important: even a small military
garrison will want food, drink, and entertainment.  a smith and
armorer will be needed to look after their gear; a mounted troop will
require beast-handlers.  as more folk come to serve the soldiers'
needs, they themselves will have needs that must be met.  officers,
and then soldiers, will bring their wives - then there will be
children. and a school.  if the soldiers are doing their job. the
area will become peaceful and safe - or more soldiers will be sent.
enlarging the garrison.  either way. trade will grow.  while this
doesn't always work, it's a good bet that any military post will, in
time, grow until

therefore, any area of obvious military importance is likely to
contain a village as well. you may use the fortification- cation
symbol (see appendix i) to show such a town.

"areas of obvious military importance" will include natural invasion
routes (which often coincide with trade routes); especially
defensible areas which would be useful in case of war (for example, a
small area of badlands in the middle of a plains area, of an island
in the middle of a harbor); and border areas. for this reason, the gm
may wish to add "frontier forts" at the edges of uncontrolled areas.
and "watchtowers" at the borders between civilized nations. after
political boundaries have been established.

towns and villages may also be established in hidden places in order
to escape attention. a liveable valley concealed in mountain
fastnesses; a hidden cavern; an island perpetually hidden by fog
(courtesy of the local adepts?) . . . any of these is likely to
provide a home for a community that has chosen to absent itself from
others. there are many possible reasons - their invention is left to
the gm such a community will of course not appear on maps given the
players; neither will they be likely to wander there except by
unlikely accident (courtesy of the local gm?)

such a hidden town or city makes an excellent quest object or
motivating force in hidden plots. this is especially true if (as
often happens) it is dominated by a magical house which requires
solitude for its work but remains intensely interested (and perhaps
involved in) the doings of the world outside.

lakes and oceans are likely to contain the dwelling places of the
merfolk.  mermen can live in both salt and fresh water, though they
do not like cold (below 60) water

in general, the cities of merfolk are built for all the same reasons
that the cities of land-dwellers may be. the undersea mountain ranges
are favorite building places, since they offer interesting terrain. 
less mud, and easier access to the surface. tropical islands are as
popular with the merfolk as they are with air-breathers.


underwater cities can become empty, just as cities on land can (see
below). all the same sorts of reasons can apply. the commonest ones
are a change in the water temperature or in its quality. eruption of
a volcano upstream, for instance. would foul the water and drive the
merfolk away.

each intelligent race will build its cities and towns in a
characteristic style and location. human or mostly-human cities have
the greatest variety. places occupied mostly by other nonhuman races
are likely to fall into a pattern. characteristic of that race.

elves prefer woodlands for their villages and towns. in many cases an
elven city will be constructed in and among the trees in such a way
that a passerby will never find it. elves may "tame" a woodland
slightly, but will not destroy it or even turn it into a park.

dwarves prefer to live and build underground. if they do not live in
a cavern-city, they will live in a mountain village. and the houses
will have very deep basements. any dwarven city will be richly
ornamented with precious stones and metals - and even the living
stone of their walls will be polished to best advantage. dwarves are
great lovers of light and beauty, in their own way. though they
express this more with their hands than with words.

halflings are usually found in farming villages that could be human
towns save for the odd construction of the buildings. most of a
halfling's house is a snug, well-p hole in the ground - possibly with
a little cottage on top. but possibly with nothing more than a door
let into the hillside to announce its presence. a halfling village
will never look "wild," though; there will be above-ground gardens,
barns, taverns, and of course streets.

orcs. on their own. build little more complex than nomadic villages.
a "native" orc town is likely to be a collection of rude stone huts
and longhouses, surrounded by skin tents.usually such villages will
be surrounded a pallisade of earth and sharpened stakes with towers
at sharp angles and over the gate. if the tower has been long
established the towers may be partly or wholly of stone. while orcs
may not build well for themselves they can appreciate the value of a
town that others have built if an orc horde conquers a city. they are
likely to settle down and rule it - keeping a few slaves to do the
repair work.  after a few generations.  they're likely to claim that
the city has always been orcish.

there is one exception to the rule that orcs are not builders. they
have a talent for the construction of military structures - towers. 
forts, and the like. an organized group of orcs can throw up a
fortress/town in a surprisingly short period of time, as long as they
have strong leadership.  such an orc-built tower or fortress will be
very strong. and wholly unmistakable in its squat and efficient
ugliness.

giants live in small hamlets and villages in isolated areas. usually
each steading will be a single clan or family group. it is possible
that. far from human habitation. there might be whole nations of
giants, and whole cities: full of enormous buildings. most of the old
giant towns have long since fallen to ruins or worse. though. and the
giants prefer to avoid human company.

shapechangers usually live, incognito, amongst their human cousins. it
is possible that an occasional village might be made up entirely of
shapechangers. . . an interesting device for gms to use occasionally. 
the race is simply too rare for any larger concentrations to be
found.

neanderthals. ogres and suarimes: are likely to be found in groups of
20 to 100 - small hamlets. sasquatches, trolls.  and centaurs may
live in villages or they may be solitary.  villages of such creatures
will never be found close to civilization.

the fairy folk (except for those discussed above) are likely to live
in small villages,  such villages will not marked on human maps, nor
will they be easily found. the same goes for nixons. fossergrims, and
their ilk.


deserted cities

ancient ruins, housing nothing but lizards by day - and things less
wholesome by night - concealing a secret entrance to a mysterious
underworld - these are a staple of fantasy and fantasy gaming.  the
thoughtful gm will season his map with a generous helping of ruined
cities.

even in this, realism is needed.  for a ruined city to exist, people
must have had a reason to build it.  then they must have had a reason
to leave - and never return, anynumber of explanations are possible. 
the gm should have some idea of the history behind each ruin when he
first places it, though details can come later.

a chance in climate is the commonest reason for desertion of a
once-thriving city. an increase in rainifallcan cause jungle to choke
out cropland and drive civilization away. -leaving their once-proud
capital to the savages. a decrease in rainfall (or clumsy farming)
can turn fields into desert. too much heat or cold can have similar
effects- even shorelines may change. of course, a drowned city might
be taken over by merfolk, or vice versa . . . but it would be just as
likely to stay empty.

a change in manography could empty a city. in a civilization entirely
dependent on mana. it would be possible for a city to be completely
abandoned if. for some reason, "the magic goes away." even if mana
later returned. trade would have gone elsewhere - and the adepts
would be afraid that mana which had left once could leave again.

warfare is a great destroyer of cities.  if the conquerers are unable
or unwilling to occupy the lands they have taken - or if no one won -
or if great areas were blighted by powerful magics - then the battles
of a hundred years ago could leave empty cities and towns as their
legacy.

other disasters can be invented- perhaps plague struck. perhaps a
great dragon descended on the town, slaying the adepts and warriors
and eating all those folk who could not flee. (maybe he's there yet.
no one who has gone to look has returned to report.) it could be that
an adept loosed some power he could not control, making the entire
neighborhood highly unpopular. possibly the entire population simply
vanished one fine day. anything can happen.

not all deserted cities need be metropoli. small cities are far more
likely to die than large towns - in fact, a village may easily die
for purely economic reasons. (again, remember the gold rush.) a
deserted village is far easier to invent and map than a deserted city
- and may hold enough surprises to keep players busy for some time.

it is also possible to have a "deserted city" within a city. a
thriving metropolis might have an "old town" . ancient fortress. or
empty house of adepts into which no one dares venture. why? that's up
to the gm.

political boundaries

political boundaries should be added after most (if not all) cities
have been placed on the map. such borders are usually the most
transient sort of feature on a map. in a dragonquest world, it is
quite possible that the players' own efforts will lead to the
reshaping of national boundaries..


most political boundaries follow natural geographical lines. go back
to the atlas and observe: an obvious natural feature is one of the
best possible boundaries. whether two nations are setting their
borders by treaty or simply by "ancient custom," a boundary that can
easily be described and can be seen by everyone is the best type.
such a boundary also has the advantage of being easily patrolled and
(in many cases) providing a natural obstacle to invasion from either
side.. rivers (especially large ones) and coastlines are the best
example of this sort of boundary. other possibilities would include
large cliff or fault lines the peaks of a mountain range; or any
similar features. generally, maps of dragonquest worlds will not show
such boundaries except in very civilized areas since they will tend
be approximate in most places due to the ;lack of trained surveyors.

forest edges and other terrain changes may also mark boundaries. such
a boundary is a "softer" one than the above type; the edge of a
forest, swamp, or desert is quite likely to move over a period of
time. therefore this sort of boundary is likely to be a customary one
rather than a boundary fixed by treaty. if, for instance, a tribe of
elves lives in a forest, while men farm outside the woods. they are
likely to reach an informal but strict understanding that "the woods
belong to the elves."


manographic lines may determine territorial boundaries. although
these lines change, the change is rarely quick. if territory must be
divided. a line of manographic change sometimes provides a convenient
and relatively permanent reference point where no other exists.

manography may also have an entirely practical effect. if a sizeable
region with normal or high mana lies close to another large area with
little or no mana, the two areas are  almost certain to have
different rulers.  furthermore, neither is likely to invade the
other; the magic kingdom's adepts would be of no use in an invasion
of a low-mana area and the mundane kingdom's troops would be loath to
attack the adepts on their own ground.  the only reasonable division
between such areas would be that of actual spheres of influence -
that is, the manographic line.

some territories may be "uncontrolled," either because they lie
outside of any organized civilization or because the country that
"owns" them cannot police them. a large area of forest or badlands is
likely to be uncontrolled; the only law in such an area will be the
law of the jungle. there will always be uncontrolled areas of one
sort or another.

another sort of uncontrolled area is the "buffer zone." this may be
formal (the boundaries of two baronies do not touch, for instance) or
informal (the formal boundary is the river running through the great
awful swamp. but neither side has anything to do with the swamp if
they can help it. so an area for twenty miles on either side of the
river is effectively uncontrolled.) uncontrolled areas. of course.
are likely to harbor monsters, outlaws, and adventure.

just as an uncontrolled area may be an enclave in the midst of
civilization, a civilized enclave may lie in the middle of
wilderness.  such a "freehold" might typically be a town of
l,000people or so, with a fairly independent economy. it will very
likely be fortified to protect its inhabitants against incursions
from the surrounding wilderness.

divisions and subdivisions

political structures will be discussed in more detail in a later
section. at this point, though, the map-maker may want to set the
basic structure of the countries of his world.

the largest division is an empire. ruled by an emperor. an empire may
contain within it several kingdoms. ruled by kings or queens. a
kingdom may contain principalities (ruled by princes): duchies (ruled
by dukes): counties (ruled by counts) baronies (ruled by barons)
satrapies (ruled by satraps). et cetera. these may be nested (several
counties within a duchy, two duchies in a small principality, three
principalities in the kingdom). or they may be thrown in together
(the kingdom of wheeforth contains two principalities, seven duchies,
six baronies, two satrapies, nine city-states, and one
unclassifiable elven commune.)

as a general rule, control grows more tenuous as government becomes
move remote. thus. empires (and even kingdoms) are not all that
common. of course. a city-state may style itself "empire" if it wants
to. and may do. the usual pattern is a sprinkling of counts and
barons who divide the countryside between them and fight freely
among themselves, while sending token tribute to a "king" hundreds of
miles away - whose real power may be no greater than any of theirs.
great, sprawling, tightly-organized empires with tightly-disciplined
legions of soldiery are definitely the exception, rather than the
rule. the typical medieval map should be a hodgepodge of city-states
and small "nations", sprinkled with contested or uncontrolled areas.

each country 0r large sub-division should have a capital. capital
cities over a certain size are more likely to have certain facilities
convenient to the traveller. the gm may designate any city within the
state as a "capital," but it is likely (say, a 9o chance) that the
capital will be the largest city in the state. if the political
geography of an area consists of a large number of city-states, none
controlling any sizeable amount of land, give each such city a 1 in
10 chance of being designated a"pseudo-capital". treat it as a
capital city when rolling for guilds, etc. - and assume that this
city has a certain prominence in local affairs due to age. wealth,
energy of leadership, etc.

the ecology of an area will be affected by geography. climate.
manography. and local civililation. ecology may be defined as the
"web of life" in an area - from the microorganisms in the soil up to
the largest beasts. usually. only the larger creatures will affect
players - but it is still necessary to work out their natural
relationship.  the traditional fantasy game "dungeon" with its rooms
full of assorted monsters is unrealistic, not because of the treasure
that's always there for the taking. but because the creatures
guarding the treasure have no logical relationship to it or to each
other. a reasonable ecological balance is vital if a fantasy world is
to seem reasonable and realistic.


THE BASIC ECOLOGY OF A REGION MAY BE DETERNINED BY ANALOGY WITH THAT
OF EARTH. TAKING INTO CONSIDERATION GEOGRAPHY AND CLIMATE ONLY. 
Unfortunately. we have only a single planet from which to draw the
theoretical basis of our ecological fantasy.  However, one should
suffice.  From sea-dephs to mountaintops and above. Earth has a
bewildering variety of life-webs.  Somewhere on earth is a reasonable
comparison,  if not an actual model. for any livcable environment a
GM is likely to invent.  The one Thing Lacking from Earth (inasmuch
as our home planet is a regrQttably low-mana environment) is a
reasonable compliment of "fantestic" - i.e., magical - creatures.
Even this is not a serious lack, %inre most ma8ical beasts and 
bein&s have obvious non-ma&ical counterparts.  The &ryphon. 
for instance, flies - but in important particulars it is a 
larRc warm-blooded predator like a lion, and occupies a 
 similar niche in a hi&h-mana environment 
 
CREATURES OF AMAGICAL NATURZ WILL BE mOSt COMNON IN 
HIGH-MANA AREAS, AND WILL NOT BE FOUND AT ALL IN AREAS WITHA 
mana BELOW 7. Certain ma@ical or&anisms - for instance. the
"silver bush" found in Blade of Allectus - would vequire a 
mana level of 8 or hi@her to survive. In &eneral. thou&h. 
level 7 is the cutoff. Ma&ical cfeatures include all Fm.tastical 
monstefs and Avians; all Giant Humanoids, Fairy Folk, and 
Dra&ons. and such other creatures as Wyverns and Doppel&an&ers. 
Amon& human and humanoid types, only Shape-Chan@ers are 
considered magical. Undead are magical. but Their magic is of 
a different kind; thus. thoy are found : THOUGH with   less 
frequency) in lou-mana areas.  (It is very rare that untead 
will be so common in an area as to play a role in its ecology - 
but it could happen ...)

STUMTED VARIANT FORNS OF MAGICAL CREATURES may be found
in areas WITk A MANA LEVEL OF 6. This is most likely when
areas of a higher mana level are nearby. or in places :kat 
have slowly 3ecreased in mana. These'creatures will hav lost 
nost or all of their magical powers or abilities, but will 
still be recognizable. Examples of such stunted magical 
creatures miiht be small Dragons that have lost their high
intelligence and can no long6r breathe fire; flightless
feral Gryphons; sullen, Ereen-complexioned rivergank dwellers
whose great-grandparents were Nixons, or a village of hairy. 
faced peasants who (all unbeknownst to themselves? are ?ure 
Shapeshifters who will manifest their abilities if tht? 
travel to a high-mana area . . . Any such stunted or repressed 
magical creature will fill an ecological niche appropriate to 
its actual ajilities. However, such creatures will almost
never be cocmon; magical creatures are infertile in lcv- 
mana areas. and rarely make a successful 
adaptation.  Sometimes (as in the case of the village of
shapeshifter:) a stunted mggical creaturewill come into its 
heritage wh:n transported to a high-mand-area. Usually though. 
there will tz only a slight improvement. Conversely. a dragon
(for instonce) transported to a low-mana area would suffer c*nly 
a slight loss of obilities. unless it entered a mana-zero 
area . .  . which would kill it. 

AS A RULE, DE?!ONS, UNDEAD. AND SIMILAR CREATUkES WILL 
N2tVE NO EFFECT ON AN ECOLOGY. It might be possible to set up 
a local situation in vhich such cceatures filled a "predator" 
niche - for instance, a valley that happened to be tht favorite 
hunting ground of a murdorous demon. or a pack of blood- 
drinking ghoscs that frequented the area around a temple. 

In cost cases. though, such creatures will be both coo rare 
and too unu:orldly to affect an ecology. 

Tho undead in an ektensive "dungeon" type area may have 
a social structure or Pecking order among themselves, but 
this wil1 be merely a matter of custom - not a true 
ecolo$y. 

Demons and other such beings from other planes may be 
part of an ecological web on their own planes. We do not 
know,  and it does not concern us. If there is such a demonic 
ecolo$y. it Joes not seem to impinge upon our own worlds. 
o foc; fov which ue should probably bc very grateitl. 

'?;is is not to sa? that demons and undead maynot cause 
a chnnic in o locnl ccolo;y - especiolly bY drivin$ gway 
all the humans in an area! - but this is best subsumed 
under the "past history " concocted by the DM

THE ENCROACHMCKT OF CIVILIZATIONWILL f?LNOST ALWAYS 
'   CHANGE THE ECOLOGICAL BALAKCE IN AN AREA.  Once intelligent 
beinfs pass the most primitive tribal staZe, they stort to 
-  adjust tkcir envivonment. inccntionally or othzrwise- The 
process of designin$ an ecology for a civilized or partiy- 
civiiized area is quite different from that of designing 
wildcrness ecology. 

------?!KIND I5 THE RACE THAT MAKES THE GREATEST INTENTIOYJL ' 
CHANGES IN ITS ENVIRONNENT. human civilization usually results 
in at  change in actual terrain type. Fr0m pleins.jungle. or 
forest, man builds cit?es and fields. The cities are relatively 
small in r:ost cases, but the systematic replacement of the 
original  terrain by fields and hedgerows willmark an area 
almost forever. "Almost," because men fight among themselves; 
civilization may leave on area even more ragidly than it 
came- (d*en that happens. the fields turn to brush. and then 
to  forest .  - . and eventuolly the lar8e wild animols come


Buc the typicol terrain near human habitotion will 
be flat or rolling. :vitk fields broken by iences and hedges. 
There will be no giont or large creatures other thon the
tame herds.Smaller creatures,  especinlly herbivores,
may actually fncrease in number; mon kill them for 
food but, cannot keep their numbevs down as efficiently as their natural 
enrmies. Birds thrive on gvain and insects from the fields; 
rots multiply on stored food and scraps. 

Even in Less civilized areas. mon makes his mark. Larg* 
creaturcs - espccially Jon$orous ones - will bccomc less common. 
FLying predators will be warred against unremitcingly; if 
thcre is a local drogon, a series of heroes will visit his 
lair until he is killed, driven away, or grows irritated and 
destroys the countryside. Any herbivores that are especially 
slow tor tasty? are also likely to be wiped out. From the 
adventurer's point of view. the ecology of a human-occu?ied 
area becomes progressively simpler and more boring. 

mon is not alone, though, Almosc every inteiligent 
roce changes tho environment in its own way. 

dwarves,  IN THEIR mOUnTAIn TOwns, may DEsTROY wiLD 
CreATUres AND FOUL STreamZ WITH THE DETRITUZ from ThEIr DIGgings
dwarves naturally prcfer inanimanace mat:er to living 
beings . They will efficiently wipe out any creatures they think dangerous
when they build their towns , just as human do ... except that they
wont feel bad about it.

Dwarves also consider it their vi&ht to use stre&ms ant fivers 
to dispose of the silt and tailin&s from their mines and forfos- - 
The effect this may have on Lowland iish or crops is of no 
interest to the Dwarves. This can on occasion lead ;o bud 
feelin&s and even violence between Dwarves ard othev races. 

ELVZS HAVE VERY LITTLE EF;ECT ON THEIR ENVIRONbZ;NT. 
SAVE TO SOFTEN IT SLlGHTLY. Elves love natuve and try to 
chan&e it as little as possible. They wil1 kill dra$ons, 
,d kill or drive away any lar&e predators that cannot learn 
to leave the elves alone. Other than that.  they make few 
f;es in their woodlands. To the uninitiated. a &reat 
Elven metropolis may seem like nothin& more than a rather 
airy forest, somewhat free of under8rowth and without 
brambles and poison ivy. 

GIANTS  AFFECT AN AREA AS HUMANZ DO. howover.  this 
takes place on a smaller scale,since Giant cocmunities are 
few and iar between. ;ome Giant tribes are fcrc*t-iolk. ;ivin& 
in  such deep voods that Cheir huntinf has liitle eifecct ,  buc 
farmin& Giant &voups will try to tame thoir environment just
has human farmers do.

Halflings affect an area as humans do. A halfling 
Comm.unity is the most CiviliZ`d little plaCe ima&inable, in    ' 
the best s6nse of the term. The fields wfll be orderly; th6re 
will be no dan&erous animals of any size to be found; every- 
thin& will be Clean and neat. Halflin&s do not live in 
harmony with Nature as elves do. but neithev do they insult 
Nature in arran&in& life to their likin&. 

ORCZ ARE ENTIRELY DESTRUCTIVE. A tribe of orcs wi)-1 
down forests, slau&hter plains animals, pilla&e farmland,   , 
and kQep ri&ht on &ofn&. When a tribe of orcs finally settles 
down (usually in a conqueved city) they will practice a crude 
slash-and burn sort of a&riCulture, turnin& the surroundin& 
area to wasteland or desert within two &enerations. They will 
then nove on, leavin% behind them a ruined city in the middle 
ofR! desolation. A heavy Orc infestation will destroy all 
lar&e fish and animals, all forests and trees, and eventually 
the very fertility of the Land. 

SHAPE.CNANGERS bEhAVE NUCH LIKE Human  Farmers, wHEN 
THEY LIVE IN GROUPS. Many shape-ckan&ers live anonf hun;ns; 
se thot Rroup toRether form small farmin& coc:unities. They 
tend to hove a rapport with thc larger predators. though. and 
will not wipe them our of an area. In fact, th:y will o?pose 
anyone who attempts to hunt "thei:" wolves. beors. etc. 

2!EAT!DERTHALS AND SASUUATCH LIVE WITNIM THEIR ENVIRON- 
EINTSAS HULIERS AND GATHERERS. MAKING gEW CHANGES- They may 
simply be treated as lar&e omnivorous animtis when desi$nin& 
zzat  forest ecolo&y. althou&h of course they a;e intelli&ent- 

FANTASTICAL AVIANS DO NOT GATHER IN -JRGE ENOUGH GROUPS 
if'0 AFFECT THE ECOLOGY. C&: ---iiargoyles mi&ht be sz destructive as 
orcs if they massed in numbers. but they setm to breed 
sloo,ly and ff&ht much amon& themselves. Harjies never or&anize 
enou&h to do anythin& at all. 

WIRFOLK WILL ATTEMPT TO CIVILIZE A )?RINE ENVIRONNEXT 
`t5 HUMANS WILL A TERRESTRIAL ONE. Ic 
In game terms, this means 
cnly that an area frequented by merfolk is unlikely to harbor 
any 1ar&e or dan$erous creatures unwanted t-: the merfolk. 
Since the merfolk prefer to control the danierous sea- 
creatu:res rather than kill them, thou@h. tkz:e is always a 
chance that somethin& lav%e and hun&vy wil!)e about. The 
*fluence of the morfolk on their oteans, vkile profound 
by lheiv own standards, is almost unnotice*ile in human 
terms. 


Suarime are hunters who make few changes in their marshes. The
lizard men will destroy any dangerous predators.
tthey exterminate dinosaurs by destroyin% their e&%s? but 
will nske no other chan&es; they do not fann. In fact. they 
tvill war a&ainst humans who attempt to drain the swamp for 
farmland. A swamp that the suarime consider a fine and 
productive place is likely to be a dank horror by human standards. 

MOST FAIRY FOLK WILL MAKE NO CHANGES AT ALLIN THEIR 
HOME AREAS: THEY WILL AVOID DANGEROUS CREATUREZ RATBER THAN 
TCRYING TO ELIMINATE THEM. Brownies live near human homes and 
help the farmers. Dryads live within trees, and will try to 
persuade foresters to enter other trades. Fosser&rims and 
ixons are found i! aquatic caves. whith they modify only sli&htly; 
they do not farm. Leprechauns prefer Co live in deep woods, 
and will resist attempts to alter those woods. 
Satyrs. nymphs, pixies. and sylphs live in wild or forested 
areas;  they, too. will resist outside attempts to "tivilize" tkeir homes. 

GKOLLS. GOBLINS, AND HOBGOBGIMS BEHAVE LIKE ORCZ (JITH 
RESPECT TO THE ENVIRON)UINT. Fortunately. thcy are rore and 
do not appear in large numbers. 

Gnomes and kobolds behave like dwarves. They, too















