h19999
s 00151/00000/00000
d D 1.1 00/12/08 09:40:43 jmochel 2 1
cC
cF1
cK48506
cO-rw-rw-rw-
e
s 00000/00000/00000
d D 1.0 00/12/08 09:40:43 jmochel 1 0
c BitKeeper file f:/Repository/BardicTales/ShapeShifters/Concordance/FEY.LTX
cBjmochel@devilmountain|ChangeSet|20001208143925|39592|56cfc6eb
cHdevilmountain
cK08182
cPShapeShifters/Concordance/FEY.LTX
cR6776606d
cV3
cX0x180
cZ-05:00
c______________________________________________________________________
e
u
U
f e 0
f x 0x1a1
t
T
I 2
\documentstyle{report}
\begin{document}

\title{The Fey}
\author{AMJ}

\maketitle

The fey are the children of Correlan, the Eldar and the Golden
Ones. They are all affected by the elf-bane, the metal of earth pure
Iron. There are five types:

\begin{description}
	\item[Grey (Faer-Han)]

	6.5 - 8.5' tall . Light Build. Three Fingered and pointed ears.
	Large slanted eyes and eyebrows. Grey, Silver or blonde hair. Tend to
	be thinner. +5 to appearance. Pale skin.

	\begin{verbatim}
		+10 Power
		+20 Vision
		Str -5
		Con -5
		Dex +3
		Agl +1
		Aura +4
		Drv -1
		Int +3
		Dsc +3
    \end{verbatim}

	All grey elves have a gift (+30 to some sorceries) and no
	weapons training.

	All grey elves take a d4 (HTK) from touching Iron and also take
	x2 damage from Iron weapons and must save versus willpower or be
	stunned d4+4 cts. Grey elves cannot survive on this plane for longer
	than a few weeks. They lose one point of constitution each week until
	they reach 0 constitution, at which point they die.

	Upon death Faer-Han fade away after five minutes and their
	spirit becomes one with Corellan. They are creatures of AIR and LIGHT
	and have no LIFE to them. DEATH spells do not affect them. The Faer-Han
	serve Corellan in all things. They are immortal. But, if you ask
	Adrian, she will tell you that they are immoral.

	\item[Droh (Dark elves)(Punk Elves)(DarHan)]

	In all things the Droh are like the Gray elves but some take on
	the appearance of dark hair, black skin, and black eyes.

	\begin{verbatim}
		+10 Power
		+20 Vision
		Str -3
		Con -3
		Dex +1
		Agl +1
		Aura +3
		Drv -1
		Int +3
		Dsc +1
    \end{verbatim}

	All Droh have a gift(+30 to some sorcery). +10% to long sword, +5%
	to crossbow.

	Droh are as Faer-Han in terms of treatment of Iron and our plane. In
	sertvice they give worship to Kisoreth and the lord of Darkness. They
	are creatures of AIR and DARK and have no life to them. Hel is a Droh.
	Only forty still exist. They are immortal.

	\item[Sea Fey (Ossar-Ey)]

	4-5.5' tall. Medium Build( Never Heavy) ; Three fingered
	(webbed) Pointed, large ears. Large slanted eyes. No eyebrows, greenish
	dark hair, generally long and stiff ( Ossar ey hair dressers don't do
	perms) Greenish skin and glod scales. Gills.

	\begin{verbatim}
		+10 Power
		+20 Vision
		-10 End
		Str -1
		Con -2
		Dex +0
		Agl -1
		Aura +2
		Drv -0
		Int +2
		Dsc +0
	\end{verbatim}

	30 % of the Ossar-ey have gifts. +10% with harpoon, +5% Irith.

	Ossar-ey are as Faer-han with respect to Iron. Unlike Faer-han
	they last up to ten minutes after death. Also, every hour that they are
	out of water they lose one point of Con. When they reach 0 they die.
	This can be avoided by spending a tenth of that time doused with water.
	Ten minutes of water restores one point of Con.

	The Ossar-ey worship little but perhaps Correlan and Mannanon
	MacLir . They are creatures of LIGHT and WATER. They are the results of
	magical/genetic experiments by Faer-han. They are immortal to a point.
	Most Osssar-ey take the Long Path after 500 years.

	\item[High (Quentor)]

	The high elves are much like humans. They have a lighter build,
	pointed ears, and slanted eyes. The eyes are blue, green, or crystal
	eyes. Hair is blonde, white, grey, silver, brown or red hair; Usually
	the hair is thin and straight.

	\begin{verbatim}
		+2 Appearance. Pale skin.
		+10 Perception
		-5 end
		+5 Pow
		+10 vis
		Str -2
		Con -2
		Dex +2
		Agil +2
		Aur +2
		Drv -1
		Int +1
		Dsc +1.
    \end{verbatim}

	Some 30% of the Quentor have a gift. (+30 to some sorcery ).
	Quentor take but a d2 of damage upon contact with Iron and only take 1/2
	again damage from weapon strikes. Quentor are attuned to this plane.
	Upon death a Quentor will remain substantial for his or her Con in
	hours before disintegration. They are creatures of AIR and LIGHT but
	these are tinged with LIFE. They are truly aclimitized to the prime
	material plane. They have lifespans extending beyond 4 centuries.

	\item[Wood (Sylvantor)]

	The Sylvantor are short (3-4'); Of very lightbuild. Three fingered ,
	having large pointed ears. Large slanted eyes and eyebrows. Brown,
	Black, Auburn or ( occasionally) white hair. Usually they have green
	eyes though sometimes brownish black. Brownish skin. +3 App. +20
	Perception +10 Vision -5 End Str +0 Con +0 Dex +4 Agil +4 Aur +0 Drv -3
	Int -1 Dsc -1 Have sylvan gifts. (?????) +15\% Elven Bow.

	Sylvantor are affected by Iron as Quentor are.

	\end{description}
\end{document}
E 2
I 1
E 1
