

                             THE DOMAINS OF MAGIC
         *************************************************************
         *************************************************************
         *************************************************************

         UNIVERSAL- FORCES TO WHICH EVEN DIETIES FIND THEMSELVES
         SUSCETIBLE TO. EX: THE MANA INBALANCE

         DIVINE- FORCES BROUGHT INTO PLAY BY DIETIES . EX: DIETIES
         TELEPORTS.

         NEAR DIVINE- FORCES ORIGINATED BY A RITUAL EITHER ELEMENTAL
         OR PERSONA THAT CREATES A SYNERGISTIC EFFECT.

         ELEMENTAL- FORCES ORIGINATED/USED BY CREATURES VIA DIRECT
         MANIPULATION OF MANA. LESS COMPLEX THAN PERSONA MAGICKS BUT
         MORE ENERGY IS INVOLVED.

         PERSONA- POWERS BROUGHT INTO PLAY BY PERSONALITIES NOT
         NORMALLY CAPABLE OF IT. EX: MAGIC USERS

         PSIONICS- PURE POWERS OF THE MIND.


         When a detect magic is performed the spell displays a colored
         aura which is specific to each type or domain of magic.

         DOMAIN                 TYPE of COLOR
         ------------------------------------------------------------
         Divine                 Sparkling
         Elemental              Transparent
         Persona                Opaque
         Psionics               Wavering

         Each type of magic ( Abjuration, conjuration etc...) has a
         specific color associated with it.

         Conjuration/Summoning          Yellow
         Abjuration                     Blue
         Enchantment/Charm              Green
         Alteration                     Orange
         Necromantic                    Red
         Divination                     White
         Invocation                     Blue Gray
         Evocation



         Conjuration/Summoning          What it says
         Abjuration                     Denial or Renunciation
         Enchantment/Charm              What it says
         Alteration                     What it says
         Necromantic                    Acting upon fless
         Divination                     What it says
         Invocation                     To call upon
         Evocation                      Calling out or from
         Illusion/Phantasm              What it says




                                   ILLUSION:
         ------------------------------------------------------------
              ALL ILLUSION SPELLS ARE AREA BASED BUT MIND AFFECTING.
         THUS, MOST ILLUSIONS NEED NOT BE SEEN OR HEARD IN ORDER TO
         HAVE AN EFFECT. ERGO A SILENT PHAN FORCE WOULD AFFECT A BLIND
         MAN.
              ANY NPC EXPOSED TO AN ILLUSION FOR ONE ROUND OR MORE
         MUST ROLL 4D6 VS INTELL TO DETERMINE IF HE IS SUSPICIOUS. IF
         SUCH IS THE CASE HE THEN ROLLS A ST VS MENTAL MAGIC.
              THIS LENDS POWER TO FAST EFFECT SPELLS.

         ILLUSIONARY FIGHTERS ATTACK AS PER LEVEL OF ILLUSIONIST BUT
         ST'S VS THIS TYPE OF ILLUSION ARE FAIRLY EASY
         THROUGH. + 2 TO ST, -3 TO SUSPICION ROLL. AS FOLLOWS:



               LAWS OF MAGIC AND THE ENCHANTMENT OF MAGIC ITEMS
         *************************************************************
         *************************************************************
         *************************************************************

         FOR NONSTANDARD MAGICAL ITEMS THE CREATION RITUAL IS VERY
         COMPLEX AND INVOLVED.  IT REQUIRES AN INORDINATE AMOUNT OF
         TIME.

         THE CREATION METHOD IS GOVERNED BY THE LAWS OF MAGIC:

         I.  SYMPATHY:  LIKE PRODUCES LIKE

         II.  CONTAGION:  ONCE TOGETHER, ALWAYS TOGETHER.

         III.  PERSISTENCE:  PERFECTION IS ETERNAL

         IV.  TRINITARY:  THRICE PERFORMED, ONCE FULFILLED

         V.  UBIQUITY:  THE ELEMENTS PERMEATE ALL

         VI.  DICHOTOMY:  DOMINANCE OR SUBMISSION

         THE METHOD FOR DETERMINING RITUAL ENCHANTMENT COSTS IS AS
         FOLLOWS:

         A.  DETERMINE THE COMPARATIVE ABILITIES BETWEEN THE ITEM AND
         STANDARD ITEMS OF THE SAME ILK.

         B.  MATERIAL COSTS ARE EQUAL TO SALE COSTS FOR COMARABLE ITEM

         C.  THE COSTS OF THE RITUAL ARE DETERMINED BY THE RITUAL
         ITSELF.  THERE ARE NO SHORTCUTS!  THE MU MUST STATE THE EXACT
         PROCEDURE.  THE MINIMUM TIME IS ONE MONTH.




