\documentstyle{report}
\raggedbottom

\hbadness=10000                 % do not want underfull box messages
\hfuzz=\maxdimen                % no overfull box messages either
\topmargin=-.2in
\oddsidemargin=-.2in
\evensidemargin=-.2in
\textheight=9in                 % and are long
\textwidth=6.4in                % pages have very wide text
\marginparsep=.3in
\marginparwidth=.5in

\begin{document}
\title{Mordanith Alda'an Kaerlin Thalionsaer}
\author{J.S.M.}
\maketitle

\chapter{Description}
Mordanith is 5'8 and 143 lbs. He has an appearance of 17. He is 
slim and lithe. His Eyes are Silvery Violet. His hair is Platinum Blond.

Mordanith, whose name means Silent Shadows of Sorcery, is Half High
elf (Father) and Half Gray Elf( Mother). He is the Son of a Priest
and Priestess of THE WORD. Mordanith's family has expressed some
small amount of annoyance at the fact that he has choosen to exercise
his magery to the exclusion of his promising career as a priest.

Mordanith later trained under Abraxas the Unpleasable ( a High Elven
Diviner ) and Emeron a high elven church man that sets the wards for
the church of Light ( Correllion ).

Mordanith is a slight figured elf with very gray eyes and long
(usually brought together in a pony tail ) blond hair. Attractive by
human standards he evinces little emotion towards most humans. He is
a intense individual with only a minimal interest in mundane affairs.
With a somewhat Zen acceptance of the here and now, and a very strong
sense of curiousity, he is a born scholar and really fairly distant
from the everyday events. He views human society as just that, a
society, composed in great part by a set of rules and ethics that he
does not need to understand in anything other than an academic manner
( Though it is sometimes of interest to know why ) but only obey
whenever possible. Of course if it is not convienient to do so he is 
quite capable of smoothly using whatever means necessary to avoid 
disturbing his studies. In short he is amoral by human standards but 
he is quite bound by what he views as natural laws. He will strive to 
avoid taking a life whenever possible ( to an often unnatural extent ).
He will not turn down a well reasoned or well expressed plea for help.
If it is within his power and conveinient or useful, he will help.
He is gradually evolving into a more wide seeing entity than he was.

His full and correct name is 

{\em {\centering
	Mordanith Istari Selebdin Elenair \\
	Alda'an Rhyslaen Aredhel Rishaeni \\
	Kaerlin Elendil Amandil Kilurien  \\
	Thalionsaer Galensaen Nikithae Atalanta \\
}}

\pagebreak 

\twocolumn

\chapter{Possessions}

\begin{table}
\caption{Monetary Materials}
\centering
	\begin{tabular}{||l|r||} \hline
	Platinum Bits       &  12 \\
	Gold                &  2  \\
	Silver              &  10 \\
	Marden Copper       &  23 \\
	Emerald (6kt perfect) & 1 \\
	Sapphire (12 Fingers wt)i&  1 \\ \hline
	\end{tabular}
\end{table}

\begin{itemize}
	\item 10 Books from Abraxas and Emeron
	\item 1 Std Church Wards
	\item 1 History of the Seven Sorceries
	\item 1 Tolnedren Runes
	\item 1 Unknown Book
	\item 1 Unknown Book
	\item 1 Unknown Book
	\item 1 Unknown Book
	\item 1 Unknown Book
	\item 1 Unknown Book
	\item 1 Unknown Book
	\item Excellent Map of the world
	\item 3 Sets of silk robes
	\item 1 Set of Linen Robes
	\item A Set of Newly Enchanted Wards Minor
	\item 1 enchanted Cloak with 60+ spell point Air Elemental attached
    \item 150' Silk Rope
    \item 250' Silk Twine
    \item Small Shovel
    \item 1 hammers
    \item Mallet
    \item 7 Flasks of Oil in a wooden case
    \item 2 Lanterns
    \item 2 Tarps
    \item 2 Silver Mirrors
    \item 2 Incense Packs
    \item 1 Magic Incense
    \item Silver Throwing Stars
    \item Basic Medicines for a horse
    \item Healing Potion
    \item Wiepack Incense
    \item Black Lotus
    \item Opal Dust 6 gms
    \item 2 vials of powder to put out fire
    \item 2 boxes (8 Balls)
    \item 2 Glass Balls
    \item Black Opal Dust 2 oz
    \item Blue Diamond Dust 1oz
    \item 5 Flushed spell batteries
    \item Amber Dust 14 lbs
    \item 30 Glass spheres
    \item Sulfur 2 lbs.
    \item Powdered Steel 1 lb
    \item Tormaline Dust 1 oz
    \item 12 Brass Balls
    \item 30 Small Quartz Crystals 
    \item 6 Glass rods
    \item Copper Filings 20 oz
    \item Sand 6oz
    \item Sea Salt 4 oz
    \item 4 Silver Rings 
    \item 150' Silk Thread ( 4 skeins )
    \item 2 vials powdered Silver
    \item 2 Silver Mirrors
    \item 6 Pack Enchanted Incense
    \item 6 drams Coral Sea Snake Poison ( 3 vials)
    \item Moonwort 6 ozs
    \item Belladonna 2 oz
    \item Cinnamon 12 oz
    \item Coral Dust 3 oz
    \item Coral Agate 1 stone
    \item Amethyst Dust 12 oz
    \item Aquamarine 2oz
    \item Onyx 6 oz
    \item Onyx 2 stones
    \item Peridot 2 stones
    \item Topaz(Blue) 1 stone
    \item Beryl 1 stone
    \item Bloodstone Dust 6 oz
    \item Carnelian 6 stones
    \item Emerald Dust 4 oz. 
    \item Emerald 1 stone
    \item Gold Dust 2 oz
    \item Star Sapphire Dust 1/2 oz
    \item Sapphire Dust 1 oz
    \item Ivory Powder 1 oz
    \item Jade 2 stones
    \item Lapis Dust 2 oz
    \item Jet 1 stone
    \item Obsidian Dust 6 oz
    \item Lodestone 2 stones
	\item Malachite 2 oz
    \item Moonstone 1 oz.
    \item Dry dust from fine elven wine sans water.
\end{itemize}

\pagebreak

\onecolumn

\chapter{Ritual Descriptions}
\section{Mage Battery - Duraspell}

\begin{description}
	\item[DIFFICULTY FACTOR] -40
	\item[MINIMUM CAST TIME] .5 hr/(10 points of power to be stored)
	\item[MINIMUM POWER COST] 10 + (Amount of power to stored)
	\item[DURATION] 1 day/Rnk + linear decay for 1d/Rnk + 1 d/(12-Rnk) power
	\item[RANGE]  0
	\item[AREA OF EFFECT] One object
	\item[PREPARATION]
	This ritual requires a storage reservoir such as a block of
	ivory or wood, that has had a rune of power inscribed in it as well
	as a power binding performed on it.
\end{description}

When casting this ritual the caster must choose between two types
of power batteries : Initiation or Support.

An initiation power battery (type I) allows a person to store energy
for use only in casting other rituals. Thus a type I battery of 40 power
would contribute up to 40 points of power to the ritual as it is being
cast. 

A support battery can be used in two ways. The first is as continous
support for a spell(type II). The second is as a one time augmentation of
a spell (type III). Both of these are usable with spell and ritual. 

Type I batteries are used in casting to augment the power of a ritual. All stored
energy must be used during casting. The battery is not affected by the
discharge. One Half of the stored energy can be used for Sorceries.

Type II Batteries are used by a spell throughout its lifetime. It supplies power to
the spell on demand and prevents the loss of the spell until the battery
is exhausted.

Type III Batteries are used by the spell once during its lifetime. The 
first time the spell or ritual is perturbed the spell takes 
on all the power stored in the cell and temporarily gives the attributes 
of a spell of power X. X being the power of the battery. The temporary 
augmentation of 
the spell or ritual is one shot and has no effect on the spell it is
supplying. Thus a 10 point ward backed by a 30 point Type III cell when
first tested would give the effect of a 30 point ward. The second testing
of the ward would give the effects of a 10 point ward. Any attempt to
dispel the ward will go first against the 30 point warding and if it goes
down it still leaves the smaller 10 point ward.

The power batteries must be made from one block of material (wood or
metal or shell). They are not destroyed in the process of use and gain a
+1\%/20 times a ritual is successfully cast. 

\pagebreak

\section{MageLock}
\begin{description}
	\item[DIFFICULTY FACTOR] -15
	\item[MINIMUM CAST TIME] 20 Counts Base
	\item[MINIMUM POWER COST] 10 PTS + 10 PTS for password option
	+ 1PT/3\% of Negative Door Opening cHANCE
	\item[DURATION] Until Door is opened or magery is dispelled
	\item[RANGE] Normal cast range
	\item[AREA OF EFFECT] One Object that can be fastened
	\item[PREPARATION]
	The Magelock requires a small amount of some finely powdered
	material. Any material that can hold a static charge such as Amber or
	sulfur should give a bonus to the casting or increase the strength of
	the spell.
\end{description}

This spell creates a very tight interweave of Mana force lines that
resist any physical attempt to force them open.  The base resistance
generated is equal to the vision of the mage + 3% per PT added beyond
the Base cost. The Mana lines can be easily broken by magic of almost
any type. 10 % chance of breaking per pt of Mana used on them.  A
Password can be included in the spell. The forces are permanant until
disrupted.

\pagebreak

\section{Mordanith's Ritual of Warding}

\begin{description}
	\item[DIFFICULTY FACTOR] -10 + ( Spell Diff. Factor )
	\item[MINIMUM CAST TIME] 10 Minutes + (-Spell Diff Factor)/2 Minutes 
	\item[MINIMUM POWER COST] 20 Pow
	\item[DURATION] 6 HRS/Rnk + 6hrs/5 pts
	\item[RANGE] Normal Cast Range
	\item[AREA OF EFFECT] \( (2'\times RNK)^3 \)
	\item[PREPARATION]
	This ritual requires a set of Wards Minor.
\end{description}

This ritual allows the caster to create a volume of protected
space which has incorporated into any spell the mage may cast. It is
this spell that determines the attributes of the ward. The spell usd
can only be used in its primary configuration ( I.e. Lowest point
cost configuration ). It can be sensitied to Mana or physical presence .
Range of sensitivity is 2' per RNK radius.

If the mage specifies the ``password'' option it means that others 
than himself may pass and he may specify those individuals.

\section{{\it THE WARDS MINOR}}
8 Equal Sized blocks inscribed with each of the elemental
runes except dark - replace with Ward rune. Usually prepared from
shell,wood, or bronze. The objects must be found , marked and
polished, established with an elemental cast ( Except the Warding
runes which must accept an elemental binding of light )

The wards minor are of use in many wardings other than Mordanith's 
Ritual of Warding.

\pagebreak

\section{Bolt of Repulsion}

\begin{description}
	\item[DIFFICULTY FACTOR] 0
	\item[MINIMUM CAST TIME] 7 CTS
	\item[MINIMUM POWER COST] 10 PTS
	\item[DURATION] \(3 \times RNK\) in counts
	\item[RANGE] As far as the carrier object can be thrown
	\item[AREA OF EFFECT] One object
	\item[PREPARATION]
	This spell requires a thrown object to carry the spell. Typical 
	objects used include small balls of Amber (+20 to cast ), tourmaline (+30) 
	or sulfur (+10) can be used to carry the spell. In addition other common
	objects can suffice such as brass balls (-10) or silk balls (-5) .
\end{description}

This spell allows the caster to create a person specific field 
around any one object. This has the effect of reducing the character's 
THB and chance to critical by 5\% + 1/Power in the spell. The spell can 
be cast ahead of time and stored - allowing the caster to use 2 CTS to
activate it.

\pagebreak

\section{Spell Snare}

\begin{description}
	\item[DIFFICULTY FACTOR] 0
	\item[MINIMUM CAST TIME] 30 CTS
	\item[MINIMUM POWER COST] 10 PTS
	\item[DURATION] \(5 \times RNK\) in counts
	\item[RANGE] As far as the carrier object can be thrown
	\item[AREA OF EFFECT] 10' + 1' per rank radius.
	\item[PREPARATION]
	This spell requires an object to carry the magery. The object 
	that is used must have two attributes - it must be a small sphere and
	it must be composed of a non conductor - glass or quartz would be the 
	optimum . The object must then be inscribed with a rune of Attraction
	and have a power binding performed on it.
\end{description}

\pagebreak

\section{Identify}
\begin{description}
	\item[DIFFICULTY FACTOR]  Unknown
	\item[MINIMUM CAST TIME]  1 Hour
	\item[MINIMUM POWER COST] 10 PTS
	\item[DURATION]	 Unknown
	\item[RANGE] Normal Spell Range
	\item[AREA OF EFFECT] One Object
	\item[PREPARATION]		
	This ritual requires a mirror that has been painted with 
	the rune of Sight an the Rune of History. The Mirror is destroyed upon
	the successful completion of the spell.
\end{description}

This spell allows the caster to trace back to the creation 
of an item or material and determine the method used in its making 
as well as the type of magic used in its preparation.

\pagebreak

\section{Mordanith's Matter Shield}

\begin{description}
	\item[DIFFICULTY FACTOR] -25
	\item[MINIMUM CAST TIME] 24 CTS
	\item[MINIMUM POWER COST] \( 4 + 1/3 PTS  \)
	\item[DURATION] 
	\item[RANGE] \( 100 \times Drive \)
	\item[AREA OF EFFECT] 
	\item[PREPARATION]
    Pretty much the same as a standard Matter Shield based on sorcery.
\end{description}

\section{Mordanith's Power Shield}

\begin{description}
	\item[DIFFICULTY FACTOR] -20
	\item[MINIMUM CAST TIME] 16 CTS
	\item[MINIMUM POWER COST] \( 6 + 1/1 pts \) 
	\item[DURATION]
	\item[RANGE] \( 20 \times Drive \)
	\item[AREA OF EFFECT]
	\item[PREPARATION]
    Just and expansion of the sorcery.
\end{description}

\pagebreak

\section{Summon Sun Light}

\begin{description}
	\item[DIFFICULTY FACTOR] -30
	\item[MINIMUM CAST TIME] 20 CTS
	\item[MINIMUM POWER COST] 20 pts
	\item[DURATION] 
	\item[RANGE] \( 5 \times Drive \)
	\item[AREA OF EFFECT]
	\item[PREPARATION]
	Needs to be detailed.
\end{description}

\pagebreak

\section{Mordanith's Matter Blast}

\begin{description}
	\item[DIFFICULTY FACTOR] -20
	\item[MINIMUM CAST TIME] 48 CTS
	\item[MINIMUM POWER COST] \( 6 + 1/1 PTS  \)
	\item[DURATION] 
	\item[RANGE] \( 4 \times Aura \)
	\item[AREA OF EFFECT] 
	\item[PREPARATION]
    Pretty much the same as a standard Matter Blast based on sorcery.
\end{description}

\pagebreak
 
\section{Our Travels}
\begin{description}
	\item[110]
	Mordanith meets the Orange Mage 
	\item[114]
	Applied via the Orange Mage for Theriden Imperial Research 
	grant invlving the use of the Orb of Abjuration
	\item[115]
	Mordan patterns to thespesian and the Temple of Usul there.
	He studies in the library there until day 122
	\item[122]
	Creates a mage battery of type 1:50 pts
	Goes to talk to Drell(Said to be Healer,thief, and Warrior )
	\item[123]
	Conjured by Narene to Marden
	Met with some Dock Workers
	\item[124]
	Get a job as a scribe at 2 sp/day get lodging for 3 sp/wk
	\item[144]
	Having collected near enough money to join the mage's guild
	mordanith decides to talk to the guild members. 
	He talks to the Orange Mage regarding his application to use the
	orb of Abjuration and learns of the Abjuration Phobia of the area. 
	He learns of the DISSENTA - a set of southern ritual mages 
	He learns of the Black Cloud Assassins - who may still have
	contracts out for Abjurationists.
	He learns that in Tolnia - Abjuration is a death sentence 
	The Orange Mage gives Mordanith a gold coin in order that
	mordanith may join the guild as a first class member. In 
	exchange he wants to receive information over the next several 
	months. The Orange Mage says that he is one of the nine Elders.
	Taj Med. The Cost of guild membership is  1 pence per week or 
	1/20th share per week. Guild duties consist of 
	\begin{enumerate}
		\item Dues
		\item 3 Weeks Service
		\item Meetings 1/month
	\end{enumerate}

	I meet with a student who is interested in learning the Tolnidren 
	Runes.

	Note that the following colleges require Tolnidren runes.
	Abjuration,Alteration,Enchantment,healing,Divination
	Illusion, Air.

	\item[145]
	Mordanith meets Raven AKA Raven. I Receive a not from a
	friend in the mages guild that indicates that their may be a
	mage of interest in the Inn of the 3 Moons. We head to visit 
	that Inn. We encounter a press gang. We frighten them off with
	a brief show of magery ( and some shapechanging). We pass by 
	the usual city sights such a human beating another human. We 
	leave them alone to their entertainments.

	I meet with the elderly mage who calls himself Morphus. We are 
	joined by a older human who calls himself Zacalatar of the 
	Bright One . He inquires as to whether we are mages and what 
	we are planning. He claims that the Bright One is a patron 
	of mages. Later it was disclosed to Mordanith that the person
	was a cleric of Loki. We are recruited by a Bengali mercenary 
	to help as guards for a caravan to excavate a forbidden city
	and when we meet with a human about the jobs Morphus is challenged 
	to prove that he is a mage. Morphus blows a brazier to kingdom come 
	and we are asked to market our skills elsewhere.     

	We return to the Inn but Mordanith returns to the Bazaar and
	convinces the human who hires for the caravan that he would do
	well to hire us all. He consents to take us back but Morphus is 
	my responsibility ( Though they will feed him ). 
	When mordanith returns to the Inn of the 3 Moons he is accosted 
	by a dwarf. The dwarf challenges Mordanith to a single combat. 
	Mordanith returns to the Inn for witnesses. The two face off outside
	the inn and Mordanith blasts the Dwarf a 80 point Psi Blast.
	The dwarf staggers and attacks Mordanith. Mordanith dodges but 
	is also attacked by several of the dwarves' companions. Mordanith 
	survives, thanks in great part to his companions and a critical 
	matter blast against the axe handle of one the his attackers. The 
	blast vaporizes the haft of the axe.

	Booty Collected
    \begin{enumerate}
		\item A Gold meddallion with a black circle and inset red claw.
		\item 5 Gold Pieces
		\item 5 bones. Long for finger bones.
		\item The dwarfs armour.
	\end{enumerate}

	We collect the weapons and booty from the bodies after waiting in vain
	for some sort of city guard. Mordanith, Morphus, the Volga Dogman, 
	his dog, and Raven head back and get instructions regarding where we are
	going and why. 

	We are to head 30 miles SW from Marden to a the Burghers road. We 
	are to travel 20 miles down this road to a town called Grozz's
	End. It should be a small village. There should be a small church 
	of Hercules. There, we will talk with the priest and then investigate 
	the rumour that there is a new buried city. We will be supplied 
	with expenses. We are given 1 Gold and 16 sp up front.

	\item[146] 
    We go Gurka shopping. We trade a simple warding Cast for a lower 
    price and we head out. We spend the evening camped out and warded 

	\item[147] 
    We travel on and encounter a demon of possession. We deal with 
	one and then send to the city of Marden for a priest of Aurioch 
	to help with the others.

	\item[---]
    We encounter the temple of hercules

	\item[191]
    Mordaniths current horse is a 16 hands high brown gelding.
    The horse he is heading for is a Mare at 18 Hands.
    The singing warrior is wearing a light brown tunic with metal 
	armor, Cloak, and a longbow.

	\item[192]
    It is the middle of the summer. We start out to the south from 
	the Vale. We head out to see the King Kaleth. We leave the 
	borders of the Vale. and break for lunch. We rest that evening 
	and are attacked by Kresh. We slay one and Dullo scares the rest 
	away. Thus ruining Mordaniths Mage battery ritual. 

	\item[193]
    We leave the gypsies and travel on

	\item[198]
    We arrive at the city of Chipewing . We talk to the city militia
    We meet with the diviner Oleander.  She says that Catbird is not 
    a shapechanger. She is not a human. She is three with the same 
	mind but not the same soul.	Oleander states that Catbird should 
	go to the Tower of Temorth in Al Kahar or to the Citadel of the 
	Seven or she can just ask Mordanith Later on during his Quest.

	To Morphus she says . Will stand in the court of Gazadlath when 
	the net may be broken. Sigm,und recognizes that Gazadlath as a 
    chieften mage of a semi-nomadic tribe helping to rebel against 
	the golden empire. She says that Morphus will be there One year 
	and two months from now.

	We look at the things we captured on the road. Card with brand 
	displays and image of a Trellis covered with Vines in a chair. 
	Person with a purple robe, white jaw and black gloves.

	\item[199]
    The next morning the Dullo summons all the water in the area. All 
	the wine casks are broken and and left with a dry powder. 
	Mordanith discovers that his fine elven wine is now a fine elven 
	powder . 

	We head  out to the south. We travel past and a Butte. The butte 
	houses a monastery full of Orange robed Monks. wE TRAVEL ON AND 
	PASS ANOTHER bUTTE. We stop for lunch. We see a town laid out in 
	front of us. We appear to have been attacked by a flaming bird. A
	fast critical power blast destroys it. We see a town with a
	temple of Dal Pan. The high priest of the temple is Rorik 
	Kambeeleon Tenser of Family Arthel.

	We meet with a General Nasant of the Northern Tactical Command.
    Vartigan wnaders out among the crowd and argues.

	Our target:

	A brazier 3' across, bronze, \( \approx 200 lbs.\) It is being 
	delivered by a Caravan with two wagons with a driver, cook and 
	teamster  crew. 10 warriors with leather jazeraint on gurkas. 4
	adepts for controlling gates. and one alterationist or 
	pysromancer. 2 scouts.

	We meet with the master Diviner Regis Galtoon IV. We mete and we 
	plan, we get info from the diviner, we discuss a great deal.

	Mordanith buys 14 lbs of powdered amber. 

	\item[200] We head out. We are confronted by a small mob of 
	humans. We bluff them with a bit of flash. They back off. We head 
	on. 

	We are stopped at the gate and we wait for the gatesmen to find 
	out about our status. We are then allowed to travel on. 

	We exit the city. A poor theif tries to steal from us. The poor 
	guy gets his clothes repulsed from him as vartigan beheads him.

	We find a river bed.  Morphus casts a major ritual; and then the 
	falcon sees a group of people in the distnace on the other side of 
	the river bed. vARTIGAN AND THE TWO DOGS GO TO INVESTIGATE., 

	Steam rises from the ground, Morphus does a three hour ritual.
    He brings up out of the ground a 400' long, 50' wide bridge with 
	4' side walls. We see Regis's divination orb above us. We also see a
	summoned creature of Jareks attack the orb. Both disappear.

	Arak and Mordanith both find the horses and return to camp. We 
	leave the region abruptly and head north. 

	\item[201] 
    We reach the plateau we were siting on.

	\item[202]
    We pass some refugees.
    We make it to the valley and the peak. Mordanith sets a ward 
	against scrying.

	\item[203]

	We wake up. Mordanith inspects the area area of the ward that has 
	been set off. 

	Dullo changes into a perfect version of the bush he studied at 
the tempole of hercules. 

	He so perfectly mimicks the bush that he summons up some faery. 
	Mordanith aid s the summoning by granting it power. Morphus 
	takes advantage of the this to grow three trees (Oak, Birch, 
	Redwood) and uses them to produce a staff with three woods.

	Mordanith calls his father and tells him of his travels. 
    Father sends two scrolls , a pouch with 10 platinum wires in it. 
	A message from dad. A silver Holy Symbol, new clothes.

	Meanwhile Vartigan and Catbird go to see what is happening with a
	vulture circling above a point three miles away. 

	They encounter and slay a priest feeling up a dead body. The 
	priest had 2 pals whom they also slay. \dots
    As the second fireball impacts on the grove, Morphus absorbs its 
	power and feeds it to the golden tree. Mordanith , the archer, and 
	Vartigan ride towards the nearest plateau. We ride, we stop, we see a
	fire bird fly overhead. Mordanith casts a power shield over 
	himself. Vartigan heads back towards the grove. 

	\dots We succeed in getting a very good distance away. We ride 
	desparately and then dismount. Mordanith figures that the 
	FireHawk is between 88-60 minutes away. 

	I fail my dismount bu land nicely. When Mordnaith's dignity has 
	recovered He crosses the stream he starts casting at the river's 
	edge. 

	\begin{quotation}
	The summon water spell went something like this : Take out amnber 
	Chanrge Amber, Fill the chalicer with water and dust it with the 
	amber. Roll \dots
	\end{quotation}

	another gap in time \dots

	\item[208] We travel away from the site of the gate dissaster. We 
	encounter an encampment of Dorean military. We try to convince 
	the comander that we have a right to cross the bridge.

	Mordanith AUra bashes the cvommander and we meet a blonde red 
	robed mage with an SCF of \( \approx 18\). The commander is called 
	Draego ,the Padishah of Taleth.

	We travel on.

	\item[209] 
    We head into Taleth. A mage (Necromancer) jumps in front of us 
	and threatens us. Mordanith powershields. Vartigan goes forward 
	to slay the Necromancer in one slash. Mordanith attempts to flush 
	the death magick from the body.

	As Mordanith flushes the Body of death magick the body releases 
	three tendrils of dark power that lash out at mordanith and does 7
	points HTK. Mordanith flushes the body of power and thenn 
	cleanses himself of the Dark power, blinding Catbird, Morphus and 
	the Singing Warrior.

	Catbird shifts into cat and ends up in a tent. She leads 
	Mordanith to this tent and are attacked by an elderly human woman .  
	Mordanith Grapple throws the old woman.

	We ride on and encounter the guard and then head in.

	Dullo gets locked into a small magick storage area. In trying to 
	get out he critically unbinds himself. Mordanith critically saves 
	and thus lives. 

	SHIT HAPPENS

	We have seven days to recover and leave.

	\item[216] We go shopping. As we travel out from the temple we are 
	approached by one beggar with some semblance of power. Mordanith 
	gives her 4 silver. We travel on to the bazaar and get some rope. 

	We get two black scarves. 

	We encounter and Talk to a Gaudily dressed will worker who claims 
	to live in the tower of truth.
 
	We encounter a craft magicker of leather goods. (Illania of 
	Kalasan ). (Illania Kaldaer Farlane Karahal ).

	We meet a human Air mage of good skill. He offers an enchanted 
    cloak in exchange for taking his apprentice with us. The 
	apprentice bears the name Erithmaen. With Erithmaen we travel to 
	the north to the small town that contains Oleandar the Diviner.
    We stay overnight and talk to her of prophecy and what may be 
	done for the Grove of Morphus.

	\item[217] We travel on. We encounter and pick up Mala, a slave 
	refugee. She is very confused because she keeps referring to 
	Erithmaen as a great one. We travel for 4 days.

	\item[221] Catbird does a search for game. 
    Brown and dark dead grasses with some blue and red flowers 
	growing along a 15-20' wide river. Vartigan wants to bell the 
	bird. Arak cleans the area and we camp. We discuss things with 
	Vartigan. Vartigan and Mordanith exchange insults and slights.
    Vartigan leaves.

	\item[228] We perform the ritual of summoning for the Vordak. It 
	comes and takes up its duties as hoped. The ritual end s with 
	only Catbird, the singing warrior, and Mordanith in any fit shape to 
	act. We head down the mountain to find shelter. As we are riding 
	across an ice bridge Morphus links to the Grove while it is being 
	destroyed. We are stunned as Morhus is lifted from his saddle  by 
	an explosion and a sheet of flame. His horse is killed. He is 
	very close to a post toastie. Mordanith pours healing power into 
	him while the others find a place to crash.

	Catbird finds a comfortable mage retreat. 

	We train and study for five weeks.

	\item[264] 

\end{description}
 
\chapter{Information on the world}

\section{From the Gray Elven Libraries}
\subsection{The Book of Seven Sorceries}
	Chapter Three Warlock. 2,000 Years Old. Mentions the Linking Ward 
	of Nereneev (Facilitated Power Blast) 

\section{TOLLEN}
Encountered Immortal Abjurationist Dragon (Bronze) called worm

\section{DRAY}
Have Talked to DRAY the Black Obelisk and AJAX the Archeologist

The Pattern is an abjurational teleport.
Smokehewn - Bronze Dragon W. of the Free States, E.of Bengali.
Jalgor    - 40' Long Bronze

The third state of Theridden has the Orb of Abjuration
as part of the Emperor's Library

\section{Magic Items}

Spell draining - Ring of Channeling (Bronze - Runic)
Staff of Absorbing - Power in free flow.
Energy Damp - Ward constantly absorbs mana
( Near complete spell description from before the purge by Dazara ).

\section{Places}
\begin{description}
	\item[Library Temple of Usul] (Drell Acolyte) in thespesian: Dorean State
	Dalas - H. Priest      
	\item[City of Marden]
	\item[Citadel of the 7]
	\item[ Forbidden Zone]
	\item[Fuedal States]
	Dalsho - Wizard King Numedides
\end{description}

\chapter{Notes on the memory regression of Catbird}

\begin{description}
	\item Studies on shapechangers
	\item Lycanthropes
	\item Weres
	\item Dullos
	\item Lythar - demonic based creatures ??? Supposedly bred with Grey Elves
	to form Golden Children of the golden empire. Golden children and Humans
	combine to produce the Na'Kore.
	\item Woodelves
	\item Vampires
	\item Ven Shamans
\end{description}

We take the Urchin far back into its history. ::A monk in rainbow robes
is throwing a knife with regularity :: A man is carrying it in the
rain.:: Repeated views of long blond hair bright eyes :: Large Hallway
with patterned ceilings :: Sitting in the corner of the monastary hiding
out :: Being caught by a bodyguard with a dragon helm :: -- Mordanith
realizes that Catbird is what they call a theif -- :: Rainbow robes with
green hood :: Man carrying her is hit by a black shafted arrow with red
feather :: Priest in coloured robes is called Tev :: Tev threw aknife
near her :: -- Mordanith discovered he was to deeply tied in -- He Broke
out -- To discover that Morphus was losing it big ..... I slap him. He
turns, runs, and changes into a falcon . Mordanith sends a telepathic 
shot that says that Morpus is Morphus... I shout him into conciousness
as I back out. ::
\section{Conjecture Afterward}

The God Oriel ?  The Black Shafted arrows with red feathers. Morphus
remembers the loss of his Tantir guard to a similiar shaft.   

\section{Lore : History of Usul and the Sunbane}
Usul was a fairly powerful mage. Rumoured to have taught Heimdall his 
magery. During the second Chaos war he obtained the Orb of Light.
After several years of intensive study of the Orb he summoned 
Asmonar(Death) into his presence. Usul was considered a neutral 
party.
He patterned a curse \dots 

\chapter{Foreseeing of Vartigan's Future}

Singing Warrior with cuthair walking with an Old man.
Arak in desert robes , wearing a nimbus of power.
Orange Red rock walls, Huge wooden stakess with dried human bodies on 
them. 

A Dark room with a priest of Correlan looking outward. Blooby Runes 
on the wall\footnote{The Runes are Rikenian. From the leethar. Necron 
is derived from this rune set}.

Vartigan, dressed as a desert person, rides on. There is no sign of 
Arak. A hand pushes itself out of the sand as a dragon rises beyond.

City of Kester. The city worshipped death. Archmage Grumsch was one 
of these. Archmage and Paladin : Arkon.

\end{document}
