h38009
s 00244/00000/00000
d D 1.1 99/12/02 16:03:57 jmochel 2 1
cC
cK00086
cO-rw-rw-rw-
e
s 00000/00000/00000
d D 1.0 99/12/02 16:03:54 jmochel 1 0
c BitKeeper file G:/SpaceHybrid/worlds/ea/moonsing.ltx
cBjmochel@devilmountain.bedford.foliage.com|ChangeSet|19991202203126|52994|e2968a7f5cb68f67
cHdevilmountain.bedford.foliage.com
cK45023
cPworlds/ea/moonsing.ltx
cReb47879b5cb68f68
cZ-05:00
c______________________________________________________________________
e
u
U
f e 0
f x 33
t
T
I 2
\documentstyle[sh]{article}
\begin{document}
\title{The Moonsinger Culture}
\author{JSM}
\maketitle
\section{History}

In the time period following the raising of Roke, there came into
existence a small kingdom that came to be known as Kevar. Kevar was
ruled by a family that was admired by most of its people because, if
for no other reason, each ruler was trained and educated by a shade of
his or her predecessor. The people of Kevar were gifted in that the
land was rich for growing and hunting as well as having a good amount
of various mineral deposits. The Kevarans came to be known as gifted
sailors and traders with a strong wanderlust. 

In the third century after the establishment of this kingdom Kevar came
to be at odds with a nearby kingdom called Hiramar. The land of Hiramar
was held in the grip of a theocracy of a faith called O-Gon. The rulers
of this kingdom viewed Kevar with hunger, for its lands were rich in a
way that Hiramar could never be. The religion of the O-Gon was a brutal
one, requiring complete obedience and obeisence from the people of the
culture. Yet, this was not necessarily a source of discontent, for the
people of the Hiramar were secure in the strong belief that they and
theirs were the only people strong enough to rule over the islands.
They were a harsh and arrogant people , ruled over by an even harsher
clergy: known as the Ten-O-Gon. For nearly 50 years battles were waged
between the two island kingdoms. 

In the year, 1134, during the highest (noon) hour of the third day of
the month of the Hawk the Ten-O-Gon struck and killed most of the royal
family of Kevar. The survivors of the city of LysJal were hunted and
the guard scattered. Most succeeded in making it to the mainland and
became wanderers. Others settled down to a roving existence and lived
on to become what is now known as the "Rafters" or Kol. Those in exile
on the mainland maintained a roving existence rather than settle in any
area where they would come to owe alliegience to any specific ruler. 

As the exile entered its second decade those who had survived gathered
together , first in small groups and then in larger groups. The
leaders, often surviving members of the royal guard or of the Royal
heraldmages, met and discussed a common problem.  Their people were
losing their culture and their old skills.  If they were ever to take
back their land these skills needs must be preserved. It was then that
the last named ruler of Kevar came forward and presented all of his
people with the technique of calling up a shade. The
shade/instructors/teachers/companions, known as Tulathin, saved a large
portion of the skills and teachings that were the heritage of the
Kevarans. They were little talked about, even among those that possess
them. It is quite likely that they were little understood even
by those select few that could pass on the knowledge. The Ten-O-Gon
held the island with no obvious lessening in the strength of their hold
over the centuries. As these ages passed the people of Kevar began to
blend in with the cultures of the mainland. Despite this there are
always a few of their ancestors traits that cling to them.
Usually a love of bright clothing and gay music and dance. Those that
retained the skills of their ancestors came to be known as MoonSingers
or MoonDancers.

In the 1100s came the second cataclysm and with it the greatest days
for the Ten-O-Gon. They were free to hunt the surviving remnants of the
Kevar culture with relative freedom. Their skills in deception and
illusion aided them greatly in hunting their enemies. Only the
rapidly rising strength of the Tulathin trained Singers and Dancers
allowed any Kevarans to escape. The Dancers and Singers of the time
were sorely pressed and barely held when their traditional allies the
druids were defeated. They reached their lowest numbers with the death
of the Archdruid Ardren Forest-Heart in 1132. There were but 200
Singers on the continent at the close of the cataclysm. 

Gradually they developed new strengths and found new allies in the
church of Sif and the church of Uller. As the cataclysm faded into
memory, they became instrumental in the founding of Covenant and in the
pacification of the Kaylin ranges.
        
With their skills in divination and healing they came to be welcome in
most towns and villages on the mainland. They developed a reputation as
skilled midwives and healers. As if by common concensus, the Dancers
and Singers have avoided any displays of martial skills of any
type. As time went on the Singers gained greatly in numbers. They are
known of in almost all towns and villages though they avoid the larger
cities and keeps. They are viewed with suspicion by dwellers of the
larger towns because they have become confused with the gypsy
like Kol or their cousins of the plains, the Kolak. The Ten-O-Gon
continued their persecution of the descendants of the Kevaran though
they became less effective as the Druids again rose in power. Any man
or woman of the Ten-O-Gon would welcome the chance to kill any of
Kevaran blood that still live. In the year 1443 came the slaughter of
many of the Ten-O-Gon in the plains around The Stones of Tiberius. With
this defeat and the loss of their leader, Keeshin the Ten-O-Gon have
been badly hurt. And for the first time there has been news that has
originated in the Ten-O-Gon ruled lands of Kevar. There are
still some surviving Kevarans on Kevar but it is believed that their
long fight against the Ten-O-Gon have left them a worn and battered
group. It is said that the old skills have been turned to use as pure
survival weapons.

\section{Politics} 
\subsection{The Lines of Singers and Dancers}
\subsubsection{General} 
Each of the major lines of MoonSingers and
MoonDancers was established by the teachings of a particular survivor
of the Heralds or Royal Guard of the last ruler of Kevar. In each case
the line has developed a certain flavor to its skills and techniques.
Students of the various schools are protective of the "Secrets" of the
schools but not to the point of jepordizing the chance of the
"Returning"

\subsubsection{The Line of Yos'Talin}

Thar Yos'Talin was the last Master Herald of his time and he has
fostered one of the strongest lines of MoonSingers though there are no
Dancers of his line. His teachings were conservative and this is
reflected in their very stern view regarding the alter            ing
of tradition. Because of the ease with which they can summon their
shade tutor, they gain a +10% to their chance to the Summon Shade
skill.

\subsubsection{The Line of Nor'Jordan the Blind}

Nor'Jordan is one of the most interesting lines of MoonSingers because
there has always been a great deal of question regarding the fact that
his teachings best benefit female Singers. All woman who study within
this discipline gain a +10% to all healing effects and
Chances.

\subsubsection{The Line of Lin'Hathan}

The line of Lin'Hathan is descended from one of the most dazzling
figures of Kevaran history. Both healer and Royal Guardsman, Lin'Hathan
is credited with a large number of ballads and songs. This line treats
the summoning of a shade as a ritual and is unable to do so
without at least 10 rounds of concentration. But they are quite skilled
at the art of MoonSinging and gain a +5% in all MoonSinging activities.

\subsubsection{The Line of Kliander Oathkeeper}

Kliander Oathkeeper is Considered to be a very controversial figure
among the singers. Kliander was one of the few non-Kevaran Heralds that
served the King at the time of Kevar's fall. He taught a very pragmatic
method of summoning shades and was skilled at sorting myth
from fact in much of Kevaran mageries. Followers of the Oathkeeper gain
a Detect Lie spell and a TruthSee spell.

\subsubsection{The Line of Sol'Dan the Hound}

Atham Sol'Dan was a beast trainer in the Royal Guard and discovered
early on in his exile that his affinity for animals extended to
shapechanging teachings. Any who study his style gain a +5% to all
changing abilities.

\subsubsection{The Line of Hal'Kani}

Hal'Kani was a Royal Herald whose skill in outguessing the Ten-O-Gon (
Later discovered to be premonition based ) saved many of her people
from death. Any who follow her eachings gain a +10% to all divinations.

\subsubsection{The Line of Tal'Rus}

As Sol'Dan, Tal'Rus discovered a strong affinity to shapechanging. His
real talents lay in the darker areas of Hunting and Slaying. It is
Tal'Rus who fathered the line of "Human Shades" that haunt the hills of
Kevar.

\section{Descriptions}

\subsection{MoonSingers}

Singers are those of the Kevaran mage-skilled who have chosen to focus
their abilities through the use of an instrument or their voice. They
tend to be skilled in the spellcasting arts and less skilled in the
martial arts.  MoonSingers are able to see as an elf in the
night, without any color definition. All Singers must take one
non-weapon proficiency in Singing. Any additional proficiencies add 5%
to the MoonSinging bonuses. The MoonSingers, when using any instrument
at all, tend to favor the use of either the drum or tambor. In weaponry
the tend to favor daggers, scimitars, staves and bolas. All moonSingers
favor the Kevaran language as well as their "Native" tongue. In
general, female MoonSingers outnumber male Singers approximately 5:1 .
By the same token the ratio reverses itself in regards to MoonDancers.

\subsection{MoonDancers}

Dancers are similiar to the MoonSingers except that they have choosen
to focus all of their skills through dance.  They tend to be less
skilled in the casting arts. All Dancers must take a proficiency in
Dance. They have the same sight modifiers as Singers. They also
tend to favor the same languages and instruments as the Singer. Their
taste in weapons leans toward scimitars and short swords as well as
throwing knives and Jo sticks.

\subsection{Human Shades}

Humans Shades are the Assassin/Hunter/Mages of the Kevaran back hills.
They see in the Dark as a singer and gain a +5% on all Hide in
Shadow,Climb Walls, Walk Silently, and Tracking rolls. Tulathin gain a
+Lvl/2 on all saves against poison. They tend to speak only the Kevaran
tongue and are skilled in the use of Blowgun, daggers, and leaded rope.
They rarely deal with instruments.

\section{Skills}

\subsection{General}

Both MoonSingers and MoonDancers have access to three types of
mageries: Healing, Divination, and Changing. The base chance for each
of these skills to be used is equal to 4 * Wisdom of the character.
These chances are modified by the phase of the moon that governs the
specific type of magic. Healing is governed by the moon Litaha. Usually
MoonSingers and Dancers are better at performing the more subtle
healings of disease,Poison, and broken bones than at repairing various
wound trauma. Divination is governed by the moon Yrtha. Usually the
best auguries are those that regard events farther in the future than
tomorrow or the next day. Changing is governed by the moon Yamen. These
changes are exclusively aligned toward self-shapechanging.

\subsubsection{Effects of the moon. }

For each area of magery there is a moon that governs the chance of
casting a given spell Summoning Shade Tulathin or "Shades" are
companion/teachers that are either constructs made to simulate a
specific personality or the actual soul of an individual who is able to
teach a Singer or Dancer the skills necessary to his craft. The Base
chance to summon a shade is 5 * Wisdom. In addition there are modifiers
for the line that one has been trained in as well as the moon cycle,
etc.

1 Any Moon at Full                   +20%
2 Each Round of Setup                +1%
3 Dancing/Singing                    +Wisdom%
4 Night                              +5%

Usually the shade is first summoned when the student is apprenticed.
The shade is usually from the same line of study as the student is
being trained in and is of a level no greater than that of the
Singer/Dancer's wisdom. It is always of the same gender             as
the character and is of the same class as that of the student.

1 Only for the one peak night.
2 For a maximum of wisdom in rounds.
3 Based on the class of the character.
4 Based on actual sundown.

\end{document}
E 2
I 1
E 1
