\documentstyle[relate]{report}
\pagestyle{headings}
\setlength{\relateleft}{0.0in}
\begin{document}

\title{Races and Cultures of Tanah}
\author{JSM}
\maketitle

\part{General}

\chapter*{Introduction}

The following are the races and cultures in
the world of Tanah. Many of these may be known to the world by other
names and some may be almost unknown or mythical in reputation.
Player Characters are unlikely to know about all the other races.

\section*{The Races}

The races are listed here with the actual name followed by a
simple common name. Some of these races are similiar to what
players may already encountered, but most of them are {\it very}
different. There are a number of races that play a major part in the
world as NPCs. Those races are not typically available to players.
An example is the TakkanDari or Drow Elves.

The non-human races are:

\begin{relate}
        \item [Rupa Kechil (R\={u}-pa K\={e}-Chil)] Shapeshifters
        \item [Bitadari (Bit-a-dar-r\={e})] Elves
        \item [Duwan (D\={u}-wan)] Halflings
        \item [Kurrock (Kur-Rok)] Dwarves
        \item [TorNimban (Tor-Nim-Ban)] Cloud Giants
        \item [TorRian (Tor-R\={e}-An)] Fire Giants
        \item [TorFrigan (Tor-Fr\={e}-Gan)] Frost Giants
        \item [TorJemma (Tor-Gem-Ma)] Stone Giants
        \item [Torgan (Tor-gan)]
        \item [Erlani] The Isle
\end{relate}

The human and near human races are listed below with a
brief note that will hopefully help bring an image to mind:

\begin{relate}
        \item [Kalifate] Spanish features
        \item [Kothan] Germanic features
        \item [Arsae] Thai features
        \item [Vokan]
        \item [Tarmane] Masai features
        \item [Sarsin] Arab and Old Iranian features
        \item [Merovan] Norman features
        \item [Hightan] Scottish features
        \item [Hairochon] Giant dwarves
        \item [Thanaen] Danish featured red heads
        \item [Horesh] Egyptian features
\end{relate}

\section*{Human Cultures}

The human cultures available are:

\begin{relate}
        \item [Kalifate(Kal-\={e}-f\={a}t)] Moorish Spain
        \item [Safoan(Sa-F\={o}-an)] Island Subgroup of the Kalifate
        \item [Kothan(K\={o}-Than)] Germanik Viceral
        \item [Tyronian(T\={i}-R\={o}-N\={e}-an)] Kothan gone over to Horse Nomadic
        \item [Emrik(Em-Rik)] Kothan subgroup
        \item [Vairman(Vair-Man)] Non-Scott Highlander culture
        \item [Dalesman(Dal-Man)] Mormon
        \item [Arsa'e(Ar-sa-\={e})] Peublo based culture.
        \item [Tarmane(Tar-M\={a}n)] Masai Hunter Gatherer/Herder Types
        \item [Sarsin(Sar-Sin)] Persian Islamic, Jihads, Fanaticism
        \item [Merovan(Mer-\={O}-Van)] Norman Farmer
        \item [Hightan(H\={i}-Tan)] Scottish Highlander
        \item [Hairochon(Hair-o-K\={o}n)] Giant Dwarves, some similiarities to the
                BloodGuard of the Thomas Covenant series.
        \item [Thanaen(Tha-N\={a}-En)] Venetian culture, Sisterhood of Steel,
                Liaden
        \item [Horeshi] Egyptian Theocracy
\end{relate}

\part{Non-Human Racial Descriptions}

\input rupa.rac
\input bitadari.rac
\input duwan.rac
\input kurrock.rac
\input tnimban.rac
\input trian.rac
\input tfrigan.rac
\input tgemma.rac
\input torgan.rac

\part{Human Racial Descriptions}

\input Kalifate.rac
\input Kothan.rac
\input Arsae.rac
\input Vokan.rac
\input Tarman.rac
\input Sarsin.rac
\input Merovan.rac
\input Hightan.rac
\input Hairoch.rac
\input Thenaen.rac
\input Horesh.rac

\part{Cultural Descriptions}

\input duwan.cul
\input kurrock.cul
\input torgan.cul

\input kalifate.cul
\input arsae.cul
\input hightan.cul
\input dales.cul
\input vairman.cul
\input shan.cul
\input Thenaen.cul

\end{document}
