\documentstyle{report}
\title{Mimbrate Culture}
\author{J.S.M}
\begin{document}
\maketitle

\chapter{The Race}

Mimbrates are a Hardic culture located upon the northeastern
tip of the Rannock penisula. They are particularly noted for
the strength and prowess of their Knights.

        AVG HEIGHT           AVG WEIGHT

MALE  :    6'1"               210 LBS.
FEMALE:    5'9"               135 LBS.

Mimbrates tend to be tall and are usually very sturdy. They
have very sharply defined features with strong chins.
Complexions are usually dusky to bronze with dark brown to
auburn hair and brown eyes.


\chapter{The Culture}

\sectioin{Noticeable Raw Materials}

The Mimbre region is a heavily wooded and warmer clime. Much
of the land is rolling hills and drumlins. There are a large
number of fast growing hardwoods to be found in the area.
There are Foxwood trees, Quickleaf,Kudana,Gloomtrees and
Aliantha. The hilly regions house a large number of Iron,
copper, tin and silver mines. In addition Cinnabar and
Arsenic are mined from the seacoast regions. Much of the
northern edge of Mimbre is alluvial blue clay with some
large deposits of diamonds.

\section{Hidden Assets}

There is an area in the middle of Mimbre that is heavily
cratered as a result of several large meteorite strikes in a
semicircular region. This area, known as fistfall, is home
to several large deposits of meteorite steel and shiral
crystals. This is a relatively protected and watched area,
with only a limited amount of meteorite steel being mined
during a given time period.

\section{Neighboring Assets}

Some of the finest wines in the world come from the port
cities of Kroldor. Some other imports are the bright cloths
of rannock and the woodworking of Elfredam. Though the
Mimbrates carry on a strong trade they are not sailors and
have a great distrust of the sea. They often trade with the
Kol for silks and shark hide for armour.

\section{Subsistence Patterns}

Much of the Mimbrate sustenance comes from the farming of
the rich woodland soil and valley plantations. A great deal
of hunting accounts for the majority of red meat found on
the dinner table. Most of the crops are surface or vine
crops along with many different orchard crops. Little or no
fish is gained natively despite the incredibly well
developed coastline.

\section{Values and Kinship}

Descendence is traced through the male line and the society
could overall be considered to be patrilineal. The only real
exception is that of noble born women. Noble ladies are
expected to be able to read and write and often serve as
stewards for their husbands or fathers. It should also be
noted that a few women have been able to gain and maintain a
leadership position in this society ( See Baroness Halasa of
Liegemon ).

\section{Language}

The mimbrates speak a set of refined versions of Hardic, a
language already known for its grace and courtesy.

\subsection{Language Tree}

Hardic is most closely related to the tongue called Aroyan.
The resemblance is near enough that someone used to Low
Hardic can effectively communicate with an Aroyan.

\subsection{Dialects}

There are several versions of Hardic spoken within Mimbre.
The first of these is Low Hardic. Low Hardic is fairly
straight forward in phrasing and usage. It is used by almost
all of the population.

The second form of the language is High Hardic or Holiday
Tongue. This is routinely used in Church ritual and Holiday
Rites. All noble born are expected to be conversant in the
language and almost all peasants are capable of using basic
phrases in it.

The third form is Court Hardic or Old Hardic. Used in a rote
form to lay a petition before a Royal court, to Coronate the
King, and in Noble weddings. It is said that there are over
two hundred ways in which you can issue a polite challenge
for a death duel in court Hardic.

\subsection{Literacy}

True literacy in the Hardic language is usually limited to
noble houses and the church. Usually a merchant can expect
to be able to read and write basic tallies. Scribes of known
trustworthiness can command a high price.

\subsection{Writing Forms}

The written form of Hardic is very similiar to that of English.

\subsection{Sounds}

A stilted and formal phrasing is the most persistent feature
of Mimbrate speakers.

\subsection{Vocabulary and Grammer}

Thee
ere
Thou
o'er
Yon
Sparth  -  Axe
Horse   -  Courser
War Horse - Destrier
bid       - ask
nigh      - Near  
ken       - view or knowledge     

\section{Religion,Myths,and History}

\subsection{Cosmology and Dieties}

The Mimbrates are firmly of the belief that there are only
two divine beings: The Goddess and the God. These two beings
rule all aspects of the Mimbrate lifestyle in much the same
way that the Catholic church ruled over Western Europe.

The God is believed to rule over all aspects of a male's
life and the Goddess is believed to take a great interest in
the life path of all Mimbrate women.

\subsection{Tradition}

	\subsubsection{Wedding}

          Mimbrate culture does use a dowry system where the father of
          the bride gives the groom a certain amount of land or other
          items of value. If a women ( Usually around sixteen years )
          is left without a father, the nearest male relative is
          expected to dower her. There is no such thing as a divorce
          in a Mimbrate life. Indeed, there is usually no need for
          such, as most women in the culture seem quite content.

	\subsubsection{Bedding}

          Mimbrate society places a great deal of importance upon the
          virginity of a women. They have a pronounced double standard
          and while it is not unknown for a fighter to take a tumble
          with a wench at an inn, it is considered a great crime to be
          caught comitting adultery. A women who has been raped is
          believed to have been dishonored. There are special words
          reserved to describe the offspring of a rape.

	\subsubsection{Birthing}

          Almost all portions of Mimbrate society respect midwives and
          a good midwife will gain a reputation that extends far
          beyond her native area.

          As expected the birth of sons is considered to be a
          particularly important event.

	\subsubsection{Battle}

          The Mimbrates view war as an extension of personal combat
          and have confused the normal chivalric view even further by
          adding in great complexities of rank and protocol.

	\subsubsection{Other}

\subsection{Rites and Ritual}

\subsection{Institutions and Clergy}
\subsection{Religious Norms}

\section{Technology}
\section{ Art, Architecture, and Symbolism}
	\subsection{Significant Numbers}
	\subsection{Symbolism and Motifs}
\section{Politics and Warfare}
	\subsection{Leadership}
	\subsection{Armed forces status}
	\subsection{Class Controls}
	\subsection{Legal Code}
	\subsection{Judicial Structure}
	\subsection{Foreign Relatins}
\section{Military Structure}
	\subsection{Command}
	\subsection{Routine}
	\subsection{Arms}
	\subsection{Outfitting}
	\subsection{Theory}

THE MIMBRATE CULTURE IS A CULTURE OF THE HARDIC RACE.
         THE CULTURE IS TO BE FOUND ON THE NORTHEASTERN MOST TIP OF
         THE RANNOCK PENNINSULA. THE AREA IS A HEAVILY WOODED AND
         WARMER CLIME.(OLD EIRE IN A HEAT WAVE). THE REGION HAS
       MANY
         LARGE, FAST GROWING HARD WOODS. THE TERRAIN, WHILE HILLY,
       IS
         STILL FAIRLY NAVIGABLE.
         THE AREA IS RICH IN IRON, COPPER, ARSENIC, MERCURY,
         TIN AND SILVER. MUCH OF THE NORTHERN EDGE OF MIMBRE IS
         ALLUVIAL BLUE CLAY WITH SOME LARGE DEPOSITS OF DIAMONDS.
         THERE IS AN AREA IN THE MIDDLE OF THE REGION THAT IS
         HEAVILY CRATERED AS A RESULT OF SEVERAL LARGE METEOR
       STRIKES
         IN A SEMICIRCULAR REGION. THIS AREA, KNOWN AS FISTFALL,
       HAS
         SEVERAL LARGE DEPOSITS OF METEORITE STEEL AND SHIRAL
       STONES.


              **TRADE**

         THE MIMBRATES HAVE ALWAYS ENJOYED STRONG TRADE IN
         ARMOUR AND STEEL ALOING WITH BRONZE AND SILVER. THE CHIEF
         IMPORTS ARE THE BRIGHT CLOTHS OF RANNOCK AND WOODWORKING
       OF
         ELFREDAM.  THEY ARE NOT SAILORS AND HAVE A STRONG DISLIKE
       FOR
         THE SEA.

            **LANGUAGE**

         THE MIMBRATES SPEAK AN EVEN MORE POLITE VERSION OF
         HARDIC, THAT ALREADY OVER CURTEOUS LANGUAGE.



          THE MIMBRATE CULTURAL BREAKDOWN


             ARISTOCRACY

       ============================================================
       ===

                KING

        DUKE  - A PROVINCIAL COMMANDER LARGE DEMENSE
        MARQUIS  - A MARCH LORD - USUALLY A TROUBLESOME BORDER
             DISTRICT

        COUNT,EARL - OFTEN AN ARMY NUCLEUS

        BARON

        KNIGHT

              MERCENARY       - RARE, IN MIMBRE LANDS

              MILITIA



               CLERGY

       ============================================================
       =====

              PRIMATE        - A GEOPOLITCALLY BASED SEAT

              CARDINAL        - A BISHOP SELECTED TO SERVE ON THE
       ROYAL
           COUNCIL

              ARCHBISHOP      -

              BISHOP        - ITINERINT VS FIXED

              ABBOT OF A MOTHER HOUSE

              ARCH DEACON

              ABBOT

              RICH PRIEST

              MIDDLIN PRIEST

              MONK

              POOR PRIEST

              LAY BROTHER     - USUALLY FREE

              FRIAR

              LAY BROTHER     - SERF

\end{document}

