History
    Distant
        In the time period following the raising of Roke, there came into existence a small kingdom that came to be known as Kevar. Kevar was ruled by a family that was admired by most of its people because, if for no other reason, each ruler was trained and educ        ated by a shade of his or her predecessor.
        The people of Kevar were gifted in that the land was rich for growing and hunting as well as having a good amount of various mineral deposits. The Kevarans came to be known as gifted sailors and traders with a strong wanderlust.
        In the third century after the establishment of this kingdom Kevar came to be at odds with a nearby kingdom called Hiramar. The land of Hiramar was held in the grip of a theocracy of a faith called O-Gon. The rulers of this kingdom viewed Kevar with hunge        r, for its lands were rich in a way that Hiramar could never be.
        The religion of the O-Gon was a brutal one, requiring complete obedience and obeisence from the people of the culture. Yet, this was not necessarily a source of discontent, for the people of the Hiramar were secure in the strong belief that they and their        s were the only people strong enough to rule over the islands. They were a harsh and arrogant people , ruled over by an even harsher clergy: known as the Ten-O-Gon.
        For nearly 50 years battles were waged between the two island kingdoms. In the year, 1134, during the highest (noon) hour of the third day of the month of the Hawk the Ten-O-Gon struck and killed most of the royal family of Kevar. The survivors of the cit        y of LysJal were hunted and the guard scattered. Most succeeded in making it to the mainland and became wanderers. Others settled down to a roving existence and lived on to become what is now known as the "Rafters" or Kol.
        Those in exile on the mainland maintained a roving existence rather than settle in any area where they would come to owe alliegience to any specific ruler. As the exile entered its second decade those who had survived gathered together , first in small gr        oups and then in larger groups. The leaders, often surviving members of the royal guard or of the Royal heraldmages, met and discussed a common problem.  Their people were losing their culture and their old skills.  If they were ever to take back their la        nd these skills needs must be preserved. It was then that the last named ruler of Kevar came forward and presented all of his people with the technique of calling up a shade.
        The shade/instructors/teachers/companions, known as Tulathin, saved a large portion of the skills and teachings that were the heritage of the Kevarans. They were little talked about, even among those that possess them. It is quite likely that they were li        ttle understood even by those select few that could pass on the knowledge.
        The Ten-O-Gon held the island with no obvious lessening in the strength of their hold over the centuries. As these ages passed the people of Kevar began to blend in with the cultures of the mainland. Despite this there are always a few of their ancestors         traits that cling to them. Usually a love of bright clothing and gay music and dance. Those that retained the skills of their ancestors came to be known as MoonSingers or MoonDancers.

    Near
        In the 1100s came the second cataclysm and with it the greatest days for the Ten-O-Gon. They were free to hunt the surviving remnants of the Kevar culture with relative freedom. Their skills in deception and illusion aided them greatly in hunting their en        emies. Only the rapidly rising strength of the Tulathin trained Singers and Dancers allowed any Kevarans to escape.
        The Dancers and Singers of the time were sorely pressed and barely held when their traditional allies the druids were defeated. They reached their lowest numbers with the death of the Archdruid Ardren Forest-Heart in 1132. There were but 200 Singers on th        e continent at the close of the cataclysm.  Gradually they developed new strengths and found new allies in the church of Sif and the church of Uller. As the cataclysm faded into memory, they became instrumental in the founding of Covenant and in the pacif        ication of the Kaylin ranges.
        With their skills in divination and healing they came to be welcome in most towns and villages on the mainland. They developed a reputation as skilled midwives and healers. As if by common concensus, the Dancers and Singers have avoided any displays of ma        rtial skills of any type.
        As time went on the Singers gained greatly in numbers. They are known of in almost all towns and villages though they avoid the larger cities and keeps. They are viewed with suspicion by dwellers of the larger towns because they have become confused with         the gypsy like Kol or their cousins of the plains, the Kolak.
        The Ten-O-Gon continued their persecution of the descendants of the Kevaran though they became less effective as the Druids again rose in power. Any man or woman of the Ten-O-Gon would welcome the chance to kill any of Kevaran blood that still live.
        In the year 1443 came the slaughter of many of the Ten-O-Gon in the plains around The Stones of Tiberius. With this defeat and the loss of their leader, Keeshin the Ten-O-Gon have been badly hurt. And for the first time there has been news that has origin        ated in the Ten-O-Gon ruled lands of Kevar.
        There are still some surviving Kevarans on Kevar but it is believed that their long fight against the Ten-O-Gon have left them a worn and battered group. It is said that the old skills have been turned to use as pure survival weapons.

Politics
    The Lines of Singers and Dancers
        General
            Each of the major lines of MoonSingers and MoonDancers was established by the teachings of a particular survivor of the Heralds or Royal Guard of the last ruler of Kevar. In each case the line has developed a certain flavor to its skills and techniques.
            Students of the various schools are protective of the "Secrets" of the schools but not to the point of jepordizing the chance of the "Returning"

        The Line of Yos'Talin
            Thar Yos'Talin was the last Master Herald of his time and he has fostered one of the strongest lines of MoonSingers though there are no Dancers of his line. His teachings were conservative and this is reflected in their very stern view regarding the alter            ing of tradition. Because of the ease with which they can summon their shade tutor, they gain a +10% to their chance to the Summon Shade skill.

        The Line of Nor'Jordan the Blind
            Nor'Jordan is one of the most interesting lines of MoonSingers because there has always been a great deal of question regarding the fact that his teachings best benefit female Singers. All woman who study within this discipline gain a +10% to all healing             effects and Chances.

        The Line of Lin'Hathan
            The line of Lin'Hathan is descended from one of the most dazzling figures of Kevaran history. Both healer and Royal Guardsman, Lin'Hathan is credited with a large number of ballads and songs. This line treats the summoning of a shade as a ritual and is un            able to do so without at least 10 rounds of concentration. But they are quite skilled at the art of MoonSinging and gain a +5% in all MoonSinging activities.

        The Line of Kliander Oathkeeper
            Kliander Oathkeeper is Considered to be a very controversial figure among the singers. Kliander was one of the few non-Kevaran Heralds that served the King at the time of Kevar's fall. He taught a very pragmatic method of summoning shades and was skilled             at sorting myth from fact in much of Kevaran mageries. Followers of the Oathkeeper gain a Detect Lie spell and a TruthSee spell.

        The Line of Sol'Dan the Hound
            Atham Sol'Dan was a beast trainer in the Royal Guard and discovered early on in his exile that his affinity for animals extended to shapechanging teachings. Any who study his style gain a +5% to all changing abilities.

        The Line of Hal'Kani
            Hal'Kani was a Royal Herald whose skill in outguessing the Ten-O-Gon ( Later discovered to be premonition based ) saved many of her people from death. Any who follow her eachings gain a +10% to all divinations.

        The Line of Tal'Rus
            As Sol'Dan, Tal'Rus discovered a strong affinity to shapechanging. His real talents lay in the darker areas of Hunting and Slaying. It is Tal'Rus who fathered the line of "Human Shades" that haunt the hills of Kevar.

Descriptions
    MoonSingers
        Singers are those of the Kevaran mage-skilled who have chosen to focus their abilities through the use of an instrument or their voice. They tend to be skilled in the spellcasting arts and less skilled in the martial arts.  MoonSingers are able to see as         an elf in the night, without any color definition. All Singers must take one non-weapon proficiency in Singing. Any additional proficiencies add 5% to the MoonSinging bonuses.
        The MoonSingers, when using any instrument at all, tend to favor the use of either the drum or tambor. In weaponry the tend to favor daggers, scimitars, staves and bolas. All moonSingers favor the Kevaran language as well as their "Native" tongue.
        In general, female MoonSingers outnumber male Singers approximately 5:1 . By the same token the ratio reverses itself in regards to MoonDancers.
        Statistics
            A MoonSinger needs must have the following stats:
            Str: 12 Dex: 15 Con: 12 Int: 15 Wis: 14

        Combat Tables
            They attack and save as thieves of the same level

        Experience
            Experience Points      Level    HD  PROF   Title

                    0 -     2,500      1       2d6  2/4  1st Novice
                2,501 -     5,000      2       1d5  -    2nd Novice
                5,001 -     9,500      3       1d5  1    3rd Novice        
                9,501 -    16,250      4       1d5  -    4th Novice
               16,251 -    25,000      5       1d5  1    1st Initiate
               25,001 -    43,000      6       1d5  -    2nd Initiate
               43,001 -    75,000      7       1d5  1    3rd Initiate
               75,001 -   112,500      8       1d5  -    4th Initiate
              112,501 -   150,000      9       1d5  1    1st MoonSinger
              150,001 -   250,000      10      1d5  -    2nd MoonSinger
              250,001 -   375,000      11      1d2  1    3rd MoonSinger
              375,001 -   937,500      12      1d2  -    4th MoonSinger
              937,001 - 1,800,000      13      1d2  1    Master Singer
            1,800,001 - 3,600,000      14      1d2  -    Arch Master

        Spell Level Table
                                  Spell Levels

                   LVL       1    2    3    4    5    6    7

                   1         2    -    -    -    -    -    -
                   2         2    1    -    -    -    -    -
                   3         3    2    -    -    -    -    -
                   4         3    2    1    -    -    -    -
                   5         4    2    1    -    -    -    -
                   6         4    3    2    1    -    -    -
                   7         5    3    2    1    -    -    -         
                   8         5    3    2    2    -    -    -    
                   9         6    4    3    2    1    -    -
                   10        6    4    3    3    1    -    -
                   11        7    5    3    3    2    1    -
                   12        7    5    4    4    2    1    1
                   13        8    6    4    4    3    2    1
                   14        8    6    5    5    3    2    2

    MoonDancers
        Dancers are similiar to the MoonSingers except that they have choosen to focus all of their skills through dance.  They tend to be less skilled in the casting arts. All Dancers must take a proficiency in Dance. They have the same sight modifiers as Singer        s.
        They also tend to favor the same languages and instruments as the Singer. Their taste in weapons leans toward scimitars and short swords as well as throwing knives and Jo sticks.
        Statistics
            A MoonDancer needs the following stats:
            Str: 12 Dex: 15 Con: 14 Int: 15  Wis: 12

        Combat Tables
            They attack and save as thieves of the same level

        Experience 
            Experience Points      Level    HD  PROF   Title

                    0 -     2,500      1       2d6  4/2  1st Novice
                2,501 -     5,000      2       2-5  -    2nd Novice
                5,001 -     9,500      3       2-5  1    3rd Novice        
                9,501 -    16,250      4       2-5  -    4th Novice
               16,251 -    25,000      5       2-5  1    1st Initiate
               25,001 -    43,000      6       2-5  -    2nd Initiate
               43,001 -    75,000      7       2-5  1    3rd Initiate
               75,001 -   112,500      8       2-5  -    4th Initiate
              112,501 -   150,000      9       2-5  1    1st MoonDancer
              150,001 -   250,000      10      2-5  -    2nd MoonDancer
              250,001 -   375,000      11      1d3  1    3rd MoonDancer
              375,001 -   937,500      12      1d3  -    4th MoonDancer
              937,001 - 1,800,000      13      1d3  1    Master Singer
            1,800,001 - 3,600,000      14      1d3  -    Arch Master

        Spell Level Table
            Spell Levels

                   LVL       1    2    3    4    5    6    7

                   1         1    -    -    -    -    -    -
                   2         2    -    -    -    -    -    -
                   3         2    1    -    -    -    -    -
                   4         3    1    -    -    -    -    -
                   5         3    2    1    -    -    -    -
                   6         3    2    1    -    -    -    -
                   7         4    2    2    1    -    -    -         
                   8         4    3    2    1    -    -    -    
                   9         4    3    2    2    -    -    -
                   10        5    3    3    2    1    -    -
                   11        5    4    3    2    1    -    -
                   12        5    4    3    3    1    1    -
                   13        6    4    4    3    2    1    1
                   14        6    5    4    3    2    2    1

    Human Shades
        Humans Shades are the Assassin/Hunter/Mages of the Kevaran back hills. They see in the Dark as a singer and gain a +5% on all Hide in Shadow,Climb Walls, Walk Silently, and Tracking rolls.
        Tulathin gain a +Lvl/2 on all saves against poison.
        They tend to speak only the Kevaran tongue and are skilled in the use of Blowgun, daggers, and leaded rope. They rarely deal with instruments.
        Statistics
            A Kevar "Human Shade" needs the following stats:
            Str: 13 Dex: 15 Con: 16 Int: 13 Wis: 12

        Combat Tables
            They attack and save as thieves of the same level

        Experience Points
              Experience Points      Level    HD  PROF   Title

                    0 -     2,500      1       2d7  6/1  1st Novice
                2,501 -     5,000      2       1d6  -    2nd Novice
                5,001 -     9,500      3       1d6  1    3rd Novice
                9,501 -    16,250      4       1d6  -    4th Novice
               16,251 -    25,000      5       1d6  1    1st Initiate
               25,001 -    43,000      6       1d6  -    2nd Initiate
               43,001 -    75,000      7       1d6  1    3rd Initiate
               75,001 -   112,500      8       1d6  -    4th Initiate
              112,501 -   150,000      9       1d6  1    1st MoonSinger
              150,001 -   250,000      10      1d6  -    2nd MoonSinger
              250,001 -   375,000      11      1d4  1    3rd MoonSinger
              375,001 -   937,500      12      1d4  -    4th MoonSinger
              937,001 - 1,800,000      13      1d4  1    Master Singer
            1,800,001 - 3,600,000      14      1d4  -    Arch Master

        Spell Level Table
                                  Spell Levels

                   LVL       1    2    3    4    5    6    7

                   1         -    -    -    -    -    -    -
                   2         1    -    -    -    -    -    -
                   3         1    -    -    -    -    -    -
                   4         1    1    -    -    -    -    -
                   5         2    1    -    -    -    -    -
                   6         2    1    1    -    -    -    -
                   7         2    2    1    -    -    -    -         
                   8         3    2    1    1    -    -    -    
                   9         3    2    2    1    -    -    -
                   10        3    3    2    1    -    -    -
                   11        4    3    2    2    1    -    -
                   12        4    3    3    2    1    -    -
                   13        4    4    3    2    1    1    -
                   14        4    4    3    3    2    1    -

Skills
    General 
        Both MoonSingers and MoonDancers have access to three types of mageries: Healing, Divination, and Changing.
        The base chance for each of these skills to be used is equal to 4 * Wisdom of the character. These chances are modified by the phase of the moon that governs the specific type of magic.
        Healing is governed by the moon Litaha. Usually MoonSingers and Dancers are better at performing the more subtle healings of disease,Poison, and broken bones than at repairing various wound trauma.
        Divination is governed by the moon Yrtha. Usually the best auguries are those that regard events farther in the future than tomorrow or the next day.
        Changing is governed by the moon Yamen. These changes are exclusively aligned toward self-shapechanging.

    Effects of the moon.  
        For each area of magery there is a moon that governs the chance of casting a given spell
        Summoning Shade
            Tulathin or "Shades" are companion/teachers that are either constructs made to simulate a specific personality or the actual soul of an individual who is able to teach a Singer or Dancer the skills necessary to his craft.
            The Base chance to summon a shade is 5 * Wisdom. In addition there are modifiers for the line that one has been trained in as well as the moon cycle, etc.

            *1 Any Moon at Full                   +20%
            *2 Each Round of Setup                +1%
            *3 Dancing/Singing                    +Wisdom%
            *4 Night                              +5%

            Usually the shade is first summoned when the student is apprenticed. The shade is usually from the same line of study as the student is being trained in and is of a level no greater than that of the Singer/Dancer's wisdom. It is always of the same gender             as the character and is of the same class as that of the student.

            *1 Only for the one peak night.
            *2 For a maximum of wisdom in rounds.
            *3 Based on the class of the character.
            *4 Based on actual sundown.

Spell Lists
