h06102
s 00090/00000/00000
d D 1.1 99/12/02 16:07:40 jmochel 2 1
cC
cK32560
cO-rw-rw-rw-
e
s 00000/00000/00000
d D 1.0 99/12/02 16:07:37 jmochel 1 0
c BitKeeper file G:/SpaceHybrid/worlds/tanah/races/races.ltx
cBjmochel@devilmountain.bedford.foliage.com|ChangeSet|19991202203126|52994|e2968a7f5cb68f67
cHdevilmountain.bedford.foliage.com
cK45046
cPworlds/tanah/races/races.ltx
cReb4787de5cb68f68
cZ-05:00
c______________________________________________________________________
e
u
U
f e 0
f x 33
t
T
I 2
\documentstyle{report}
\pagestyle{headings}
\begin{document}

\title{Races and Cultures of Tanah}
\author{JSM}
\maketitle

\part{General}

\chapter*{Introduction}

The following are the races and cultures in
the world of Tanah. Many of these may be known to the world by other
names and some may be almost unknown or mythical in reputation.
Player Characters are unlikely to know about all the other races.

\section*{The Non-Huan Races}

The races are listed here with the actual name followed by a
simple common name. Some of these races are similiar to what
players may already encountered, but most of them are {\it very}
different. There are a number of races that play a major part in the
world as NPCs. Those races are not typically available to players.
An example is the TakkanDari or Drow Elves.

The non-human races are listed below along with a brief note to help 
bring a useful image to mind:

\begin{itemize}
        \item [Rupa Kechil (R\={u}-pa K\={e}-Chil)] Shapeshifters
        \item [Bitadari (Bit-a-dar-r\={e})] Elves
        \item [TakkanDari (Tak-kan-dar-r\={e})] Dark Elves
        \item [Duwan (D\={u}-wan)] Halflings
        \item [Kurrock (Kur-Rok)] Dwarves
        \item [TorNimban (Tor-Nim-Ban)] Cloud Giants
        \item [TorRian (Tor-R\={e}-An)] Fire Giants
        \item [TorFrigan (Tor-Fr\={e}-Gan)] Frost Giants
        \item [TorJemma (Tor-Gem-Ma)] Stone Giants
        \item [Torgan (Tor-gan)] Civilized Orcs
        \item [Erlani] Australian Shapechangers
        \item [Sil] Winged Folk
\end{itemize}

\section*{The Human Races}

The human and near human races are listed below with a
brief note that will hopefully help bring an image to mind:

\begin{itemize}
        \item [Kalifate] Spanish features
        \item [Kothan] Germanic features
        \item [Arsae] Thai features
        \item [Vokan]
        \item [Tarmane] Masai features
        \item [Sarsin] Arab and Old Iranian features
        \item [Merovan] Norman features
        \item [Hightan] Scottish features
        \item [Hairochon] Giant dwarves
        \item [Thanaen] Danish featured red heads
        \item [Horesh] Egyptian features
\end{itemize}

\part{Non-Human Racial Descriptions}

\input rupa.rac
\input bitadari.rac
\input duwan.rac
\input kurrock.rac
\input tnimban.rac
\input trian.rac
\input tfrigan.rac
\input tgemma.rac
\input torgan.rac

\part{Human Racial Descriptions}

\input Kalifate.rac
\input Kothan.rac
\input Arsae.rac
\input Vokan.rac
\input Tarman.rac
\input Sarsin.rac
\input Merovan.rac
\input Hightan.rac
\input Hairoch.rac
\input Thenaen.rac
\input Horesh.rac

\end{document}
E 2
I 1
E 1
