h29107
s 00257/00000/00000
d D 1.1 00/12/08 09:40:45 jmochel 2 1
cC
cF1
cK55856
cO-rw-rw-rw-
e
s 00000/00000/00000
d D 1.0 00/12/08 09:40:45 jmochel 1 0
c BitKeeper file f:/Repository/BardicTales/ShapeShifters/MordanithPossessions.tex
cBjmochel@devilmountain|ChangeSet|20001208143925|39592|56cfc6eb
cHdevilmountain
cK06035
cPShapeShifters/MordanithPossessions.tex
cR67b8f7f6
cV3
cX0x180
cZ-05:00
c______________________________________________________________________
e
u
U
f e 0
f x 0x1a1
t
T
I 2
\documentstyle[fanhead]{article}
\pagestyle{fancy}
\chead{Mordanith's Possessions}

\def\bblock #1{{\hsize 2 true cm\noindent  \bf#1}}

\def\spell NAME:#1DF:#2CT:#3COST:#4DUR:#5RNG:#6AOE:#7
\par{
    \bigskip
    \hrule height1pt
    \medskip
    \noindent{\LARGE\bf\sf #1}
    \small
    \bigskip
    \hrule height1pt
    \medskip
    \begin{list}{}{\setlength{\leftmargin}{0in}\setlength{\labelwidth}{1in}\setlength{\rightmargin}{0in}}
        \item{\bblock{DF}}#2
        \item{\bblock{CT}}#3
        \item{\bblock{COST}}#4
        \item{\bblock{DUR}}#5
        \item{\bblock{RNG}}#6
        \item{\bblock{AOE}}#7
    \end{list}
    \medskip
    \hrule height1pt
    \bigskip
}

Mordanith's Possessions


Monetary Resources

Item            | Quantity | Value
Platinum Wires  | 18       | 126,000
Gold            | 2        | 2
Silver          | 10       |
Marden Copper   | 23       |
Gold Talons     | 6        | 100
White Diamonds  | 4        | 1000

Books

Standard Church Wards:Design and Implementation
A very useful guide to fixed ward preparation. But is very high level and is
more of an overview than a beginner's guide(which is no prob.. for
Mordanith)

History of The Seven Sorceries this is clear. No eye-witness
accounts. All taken from other sources.

Tolnedran Runes
This is a high-level dictionary/lexicon designed to
allow the user to learn single runs or specific types or groups
of runes at a time.

Pattern Stacking: Minimizing Interference
obvious(is referring to Ritual patterns laid down on top of one
another..)

Object Fixing and Cleansing for Mobile Wards

The Song of Hope
A set of religious poems written at the end
of the Dwarven-Elven War cycle.

The Highest Hill
A story of the human movement to destroy abjuration
and the flight of the high elves from persecution

Enchanting an Item: A Beginner's Source Book
-obvious- but not that
useful on Prime. It is slanted to the  Elven environment. Does
contain useful basic principles.

To Light the Way
A poem of instruction in the forming of light magics. It was written
by the Bard Halienthiel Akkentis Paramar.

Words on Truth: A Devotional Aid
A Theological guide to the Church
of Correllan. Contains a mixture of philosophy,ethics, and history. Written
by a high priest of the Word.

Book on Theology


Five books describing the original design of the Wizard King's
wards.

One spell book: In Tolnidren with 13 spells intact including 
"Plane Bore".

Maps


Excellent Map of the world
Map of the Area around Kiev in Dau Shao
Map of the path from Marden to Kiev in Dau Shao


Clothing


Sky Blue Silk robes  3
White Silk Robe
Dark Gray Linen Robes
White w/Blue Trim Cotton Tunic
Light Gray Faer-Han Cut Cotton Tunic
Yellow Silk Tunic
Silvery White Silk Trousers
Purple Silk Cape
Royal Blue Trousers  2
Black Silk Tunic  4
Turquoise Cotton Trousers with Silver Braid  2
White Silk Sash
Light Blue and Silver Sparkled Silk Scarf
Bright Red Silk Robe.
Black Silk Cloak



Magic Items


Enchanted Wards Minor
Mordanith Enchanted Wards Minor
Enchanted Cloak (60+ power Air Elemental)
A Mithril Irith, Enchanted.
Irith Scabbard, Enchanted
Staff, Magic Neutral
High Elven Rope 200' (Responds to High Elven )
Bag of Holding for Healing Materials


Tools


150' Silk Rope
250' Silk Twine
Small Shovel
Large Pick
2 hammers
Mallet


General Camping Equipment


7 Flasks of Oil in a wooden case
2 Lanterns
2 Tarps
2 $ 20' \times 20' \times 15' $ Magical tents
2 $ 10' \times 10' $ storage tents
1 $ 40' \times 30' $ Cat Tent

Magic Components

Herbs

Black Lotus  12 oz
Moonwort     6 ozs
Belladonna   2 oz
Cinnamon     12 oz

Gems

Opal Dust          6 gms
Black Opal Dust    2 oz
Blue Diamond Dust  1oz
Small Quartz Crystals  30
Amber Dust         14 lbs
Tormaline Dust     1 oz
Coral Agate        1 stone
Amethyst Dust      12 oz
Aquamarine         2oz
Onyx               6 oz
Onyx               2 stones
Peridot               2 stones
Topaz(Blue)               1 stone
Beryl               1 stone
Bloodstone               Dust 6 oz
Carnelian               6 stones
Emerald Dust               4 oz.
Emerald               1 stone
Star Sapphire Dust               1/2 oz
Sapphire Dust               1 oz
Jade               2 stones
Lapis Dust               2 oz
Jet               1 stone
Moonstone               1 oz.

Minerals and Such

Obsidian Dust               6 oz
Sea Salt               4 oz
Sulfur               2 lbs.
Sand               6oz
Coral Dust               3 oz
Ivory Powder               1 oz
Lodestone               2 stones
Malachite               2 oz

Metals

Powdered Steel               1 lb
Brass Balls               12
Copper Filings               20 oz
Silver Rings              4
Gold Dust               2 oz
powdered Silver         2 vials

Glass

Glass spheres  30
Glass rods  6

Incense

2               Incense Packs
1               Magic Incense
3               Wiepack Incense
6               Pack Enchanted Incense, for power restoration

Fire Fighting


powder to put out fire  2 vials
Fire Fighting Globes  2 boxes (7 balls)
Glass Balls for Magic Fire Fighting  2


Medicine


Healing Potion  2 flasks
Coral Sea Snake Poison  6 drams ( 3 vials)
Basic Medicines for a horse
Shape Healing Potions  10 vials (5d/vial)
Potions of Order  2 vials (5d/vial)
Poison Antidote  2 vials (4d/vial)
Anti-infection Creme  2 pots (6d/pot)
Mental Healing  1 vial (5d/vial)

Misc

Dry dust from fine elven wine  1 skin
Silver Mirrors  4
Silver Throwing Stars  12
Flushed spell batteries  5
150' Silk Thread   ( 4 skeins )
50 Skeins Silk Thread
2 Skeins Silver Thread
Silver Holy Symbol of Corellen  1

\end{document}
E 2
I 1
E 1
