h44471
s 00111/00000/00000
d D 1.1 99/12/02 16:08:30 jmochel 2 1
cC
cK06783
cO-rw-rw-rw-
e
s 00000/00000/00000
d D 1.0 99/12/02 16:08:26 jmochel 1 0
c BitKeeper file G:/SpaceHybrid/worlds/tem/combat.ltx
cBjmochel@devilmountain.bedford.foliage.com|ChangeSet|19991202203126|52994|e2968a7f5cb68f67
cHdevilmountain.bedford.foliage.com
cK45051
cPworlds/tem/combat.ltx
cReb4787d05cb68f68
cZ-05:00
c______________________________________________________________________
e
u
U
f e 0
f x 33
t
T
I 2
\documentstyle{article}
\begin{document}
\title{Combat Clarifications and Extenmsions for DQ}
\author{J.Mochel}
\maketitle

\section{Combat Sequence}
\begin{enumerate}
	\item Initiative is determined for all unengaged figures and
    engaged figures.
	\item Actions are performed in the order of their Initiative.
\end{enumerate}

The System is a serial based system of initiative. Each pulse is broken 
up into 10 counts. Initiative is the result of a die roll and the
characters IV. 

The actual formula for initiative is \(Initiative = d10 + 5 - (IV/10) \)
For quick usage the character can record an actual initiative modifier for
each weapon which consists of the \( 5 - (IV/10) \). 

For general usage try the Initiative table.

\begin{table}[h]
\caption{Initiative}
\centering
	\begin{tabular}{||c||l|l|l|l|l|l|l|l|l||} \hline
    Die	&   &   &   & IV/10 &&   &   &   & \\
    Roll&   &   &   &       &&   &   &   & \\ \hline
	    & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\ \hline
	1	& 6 & 5 & 4 & 3 & 2 & 1 & 0 & 0 & 0 \\
    2   & 7 & 6 & 5 & 4 & 3 & 2 & 1 & 0 & 0 \\
    3   & 8 & 7 & 6 & 5 & 4 & 3 & 2 & 1 & 0 \\
    4   & 9 & 8 & 7 & 6 & 5 & 4 & 3 & 2 & 1 \\
    5   & 10& 9 & 8 & 7 & 6 & 5 & 4 & 3 & 2 \\
    6   & 11& 10& 9 & 8 & 7 & 6 & 5 & 4 & 3 \\
    7   & 12& 11& 10& 9 & 8 & 7 & 6 & 5 & 4 \\
    8   & 13& 12& 11& 10& 9 & 8 & 7 & 6 & 5 \\
    9   & 14& 13& 12& 11& 10& 9 & 8 & 7 & 6 \\
    10  & 15& 14& 13& 12& 11& 10& 9 & 8 & 7 \\ \hline
	\end{tabular}
\end{table}

Actions are broken down into several general speed classes

\begin{table}[h]
\centering
\caption{Speed Classes}
	\begin{tabular}{||l|c|r||}           \hline
	Class		&Speed(cts) &Examples \\ \hline
	Extra-Short	&1			&Perception, Talents, Spell Preparation \\
    Short		&2			&Dagger Attack, Counter Spells \\
    Medium		&3			&Sword Attack, General Knowledge \\
    Long		&4			&T-Sword Attack, Special Knowledge \\
    X-long		&5			&Halberd \\ \hline
	\end{tabular}
\end{table} 

\clearpage
	
\section{Special Combat Actions}
\begin{description}
	\item[Iajutsu]
	A skill roll is made and a bonus is added on to
	the initial IV. The bonus does not add in to all the following
	IVs.

	\item[Disarm]
	One Half of the defender's Weapon's Base Chance is
	subtracted from the strike chance. If the strike is successful
	the defender rolls a Manual Dex save at DF=1. If the disarm is being 
	attempted with a missile or thrown weapon the full base chance of 
	the weapon is subtracted.

	\item[Blocking]
	Blocking is the act of giving up a chance to attack and instead 
	, attempting to actively block the attackers weapon from
	reaching you. Upon each attack, the defender rolls a block
	using the attackers SN as a modifier against his roll. (ie.
	Ralph attacks Leroy and hits by 37. Then leroy has to roll his
	normal strike chance less 37\%.) If a successfull block is made
	then damage is rolled for both sides. Any damage that the
	attacker inflicts over and above that done by the defender,
	gets through. If the attack is a grievous strike then a normal
	block would reduce it to just an endurance strike, a endurance 
	rolled block would reduce the damage to fatigue, and a grievous
	effect block would nullify the damage. 

	Ralph attacks Leroy with an endurance hit for 7 points. Leroy
	blocks all the damage and gets it bounced up to just fatigue.
	Leroys strikes Ralph for an Endurance shot but Ralph can only
	block out most of the damage , the rest of the damage goes
	against Endurance.

	\item[Parrying]
	Parrying is the act of defending one's self from attack using 
	a weapon to aid in avoiding damage. There is no attempt to directly 
	oppose your opponents weapon with your own. 

	Parrying is done as the book states but the minus is based on
	\(defense + dexterity + 4\% * Rnk in weapon. \)

	A successful parry resulting in a roll of 8+ leads to the next 
	initiative roll occurring as if it were the next higher IV class. 
	A roll of 3 or less	leads to the next initiative occuring as if 
	it were the next lower IV class.
	\item[Evasion]
	For now, as per book
\end{description}

\end{document}
E 2
I 1
E 1
