\documentstyle{report}
\title{The Confederation of Systems}
\author{J.S.M}
\begin{document}
\maketitle

\chapter{Description}

The Confederation of Systems, more commonly known as the 
Confederation or Confed, is a collection of solar systems and colonies banded 
together for both defense and trade. There has been a concerted 
effort by the Confed to limit interference in the internal workings of the 
actual systems.

The Confed emcompasses a number of major racial groups. The Terrans 
and the various derivative races of {\it Homo Terra Prime} 
constitute a major portion of the current population. The Alpha 
Centaurans and the derivative races of {\it Homo Alpha Centauran 
Prime} constitute the next largest group followed closely by the 
Proximans {\it Homo Proxima Prime}. There are no other known races 
currently members of the Confed.

The duties of the Confederation as a governing body are quite simple: 
keep the peace {\em Between member systems}. To this end each system 
donates a portion of its military services to the Confed as well as 
some monetary support.

\chapter{History}
The history of the Confederation is most properly the history of the 
Terrans. The Terrans were one of the primary forces behind the 
formation of the Confederation. 

\section{Early Terran History}

The Terran History of the years immediately preceeding the year 2530 is
found to have a nearly hysterical flavour to those used to reading the
histories of less divided cultures. Most other cultures in the 
Confederation of Systems have a sharply defined predilection toward or
away from war. Few cultures have the ambivalence of a Terran towards
violence.

During the time period following the Second World War the world focused
in conflicts around the two main super powers of the time period. With
a strong technological lead over the Soviet Bloc, the USA spent a great
deal of energy and influence in combatting any gains made by the Soviet
Bloc. 

\begin{verbatim}
1969   NEIL ARMSTRONG SETS FOOT ON LUNA
1981   1ST PATENT ISSUED FOR GENETICALLY ALTERED BACTERIA
1982   FUSION BREAKEVEN WAS REACHED (R.I.T)
1986   CHALLENGER SHUTTLE ACCIDENT
\end{verbatim}

During this time period there was a gradual decline in the health of
the economies of the two Blocs as well as in actual scientific rather
than technological knowledge growth. In addition there was a marked
increase in religous fundamentalism in both the US and abroad in
various Islamic and Hindu countries. Both of the superpowers of the 
time period tended to ignore the economic build up of other countries 
except when their own immediate well being seem threatened. Certainly 
, both countries had a great deal to worry about.

\begin{verbatim}
1989	Berlin wall comes down
1989	Major instabilities within the Soviet Union
1990	Fairly minor economic hardship in many regions of the United States of America
1994	Increasing virulent strains of Aquired Immuno Deficiency virus surface
1995	Two prominent Catholic church officials die in Boston and NYC of AIDS-2
1995	Israel claims total annexation of Lebanon.
1996	Poland becomes a member of the EEC
1996	Costa Rica is purchased by the Nature Conservancy
1996	Argentina announces first cases of what is later to be described as Andes plague
1996	Renewed hostilities between Mohawk nation and Quebec.
1996	Japan announces successful cloning of Coelecanth
1996	France suffers from the explosion and destruction of the ``Super Pheonix''
reactor
1997	General Electric establishes its own armed security force
\end{verbatim}

As the technological wonders mounted in number and variety, so did the
need for energy to grow and expand. Conventional sources proved
insufficient and standard nuclear methods proved to be to dangerous.
During this time period public confidence in conventional
power sources was on the decline. 

The stresses placed on some of the smaller countries by the three ``super powers''
(EEC,Soviet Union, USA) caused many of the countries to form serious coalitions
with similiarly inclined republics. Thus came into being the United Islamic States,
sthe Indos Island States (Phillipines and Indonesia), and the loosley allied 
Scandinavian Coalition (the Scandic).

Multinational Corporations became commonplace as each country's industrial 
complex bought into the financial structure of several others. Space travel 
was almost an ignored project with only small bits of developement going on 
at a relatively low intensity . 

\begin{verbatim} 
1997 Low Temperature Superconductor (214\degree K) commercially available
1998 Long Island Blast - Detonation of Shoreham fission plant.
	 accident ? 180,000 killed.
1998 South American University of Ecological Engineering (SAUEE) established in Costa Rica
1999 Johannesburg established as only legal residence for whites in South Africa 
1999 Desertification renders large parts of Somalia and Nigeria uninhabitable
1999 Korea is made a client state of Japan 
1999 Anti-Fission Referendum Approved in the USA
\end{verbatim}

Other methods of energy production became standard. With the 
discovery of a highly efficient technique for solar energy conversion 
came an increased traffic flow between the planet and its moon.

\begin{verbatim} 
2000 Discovery of Mirashi Sun Screen effect by Sanford Ezekial Jackl. 
2000 First reconstruction of Tristamy 13 fetus
2000 Assassination of USA president Pat Schroeder. 
2000 Guiseppe Lapilito demonstrates the first power armoured suit to a 
group of skeptical military procurement officers by walking through the
Pentagon and into the office of the Secretary of the Army, uninvited.
2000 Japanese/Korean team demonstrates cybernetic helmet hookup 
2000 U.N. Research and observation base at tycho Brachae is established
2001 U.N. is asked to vacate N.Y. by USA.
2001 U.N. Establishes its Meeting site at Point 7, Antartica
2001 EEC begins to make all UN support payments as one unit.
2001 G.E. puts first Mirashi Sun Screen power plant online using black 
box units supplied by Jackl Power Inc. Power plant comes on line from
Los Alamos, Texas.
2001 USA and Canada, acknowlegding a growing interdependence, agree 
to merge their current economic systems. USA agrees to go metric. 
2002 Quebec and California declare their independence of the ``NorAm Combine''
2002 First offline run of white sands fusion plant 
2002 October : First L-5 orbiting station  ``Lagrange-Five'' made operational 
by NorAm Combine. Soviet aid accounts for 30% of labor and 20% of materials.
2002 December : Second L-5 orbital station made operational by U.N. Joint 
Technology Mission, SAUEE and Australian Mining concerns.
\end{verbatim}

The smaller countries begin to use the U.N. as a fairly sophisticated 
lever against both of the two super powers. The EEC, Israel, the 
Islamic state coalition, and the republic of India are primary 
supporters. in doing so they establish a fairly strong tradition for 
the U.N. as a military force and the use of Israeli Officers as advisors. 

\begin{verbatim} 
2003 Quebec Food riots
2003 Cray VMOP-40 put online at Socorro Research Center, New Mexico .
VMOP = virtual memory optical plaques
2003 General Dynamics demonstrates the first prototype ``Screen-Shuttle''
2003 General Dynamics and SovMhD together offer screen shuttle 
service between Moscow, New York, Antartica, and Tycho Brachae. 
2003 California is brought back into the NorAm Combine by use of Blockade.
2003 Soviet Secretary General Gosseyn is killed as a result of 
terrorist bombing. The ecological terrorist group ``Golden Monkey 
Wrench'' claims responsibility.
2003 Regular "screen shuttle" service between the earth and
moon is established.
2003 Darrel Kaven psychic research center is established in Santa 
Barbara California.
\end{verbatim}

Unrest over food shortages continued. in addition there was
a slight resurgence of territoriality within the
northwestern hemisphere.

\begin{verbatim} 
2004 Establishment of lunar penal colony "Selene" by NorAm Combine.
2004 Montreal massacre 1,534 dead.
2004 Sandoz starts marketing male and female contraceptive implants 
based on non-abusive hormal regulation.
2004 Mitsubishi unveils first commercially obtainable shuttle craft, the
Infiniti-2.
\end{verbatim}

A small group of dedicated visionaries succeeded in secretly
launching a colony ship from the sirius orbital station. the
"Gang of l-5" was tried and convicted of treason. later
pardoned as a result of public outcry.

\begin{verbatim}
2005 Launch of gauss jammer "Einstein" by L-5 society with
1221 volunteer colonists.
\end{verbatim}

Exploration increased rapidly. all planets except saturn and
Jupiter are successfully landed upon.

\begin{verbatim} 
2020 Creation of Ares city on Mars.
\end{verbatim}

United Nations Standard units of Exchange become a standard 
media of exchange for all but NorAm Combine and the Soviet Union. 

Resource tensions cause the first major conflict of the 21st century, 
the Brushfire war, which lasts for all of 13 days and renders goodly 
portions of Somalia and the United Islamic Coordinate unihabitable. 
The Iraqi valley oil fields are made useless by heavy fallout.   

In the year 2021 a the lunar colony selene discovers the
presence of a space craft landing site - over 2000 years
old.

In the early part of the 2020s there comes a long series of 
conflicts in the middle European and South American arena 
that feature major losses for each of the two super powers.

\begin{verbatim} 
2021 Citing unpaid debts Argentina invades Chile against opposition 
from NorAm and Chilean troops. War continues for 3 years before the 
Belmopan Armistice is signed. 
2023 Costa Rican Conservancy acquires Panama and Nicaragua. All three
countries become subject to a Conservation Council government. In 8
years both of the newly acquired regions become profitable and 
develop one of the highest health and living standards. The region 
is renamed the Conservancy States. 
2023 Launch of gauss jammers Dyson and Hawkings
2025 Mexico attempts to invade Gautemala. NorAm funded Mexican forces 
are defeated and disbanded in less than 6 months by Israeli Officered 
U.N. forces. The NorAm Combine withdraws from the U.N. 
2026 Conservancy designed underwater biosphere ``Jerusalem II'' is 
established by Israel in Mediteranean.
2027 1st contact between gauss jammer Einstein and Alpha
Centauran manned probe firanaun
2027 1st atificial factor humanoid produced by General
MagnetoheteroDynamics, inc. (gmd)
\end{verbatim}

The Soviet Union switches over to the U.N. Standard of exchange and 
agrees to adhere to U.N. Resource management restrictions. The 
founder of Jackl Power Inc. , suffering from a terminal illness, 
wills his fortune, his entire stock holding in Jackl Power (74\%) , 
and his land holdings in upper New York State to the Mohawk Nation of 
Quebec. The Mohawk Nation uses the money to finance the building of 
the ``Red Jacket University of Power Engineering ''. In addition, 
they begin one of the largest public relations campaigns in history 
as part of an attempt to separate from the NorAm combine. 

\begin{verbatim}
2030 Discovery of Mak'kasonar (Alphan) and Cagson (Terran)
transition made possible by centauran spacial mathematics and terran 
fusion technology. 
2030 First use of artifacts in mining operations off terra
2031 Return of "Einstein " to terra.
2033 Formation of the joint alphan/terran coalition. This coalition 
deals as a non-binding advisory council in matters of trade.
2037 Encounter and destruction of gauss jammer Hawkings
by proximan war vessel.
2038 Production of first military artificial factor
humanoid "artifact" for combat in proximan space.
2038 Production of bacterial augmentation sera for terran
troops. 
2039 The battle " terragoth" marks end of triculture war. The ``Three 
Suns Armistice'' lays down the foundation of the Confed council. 
2041 Declaration of "artifact" non citenship by terra
declaration of alphan / proximan aftifact citizenship
2055 You are here \dots
\end{verbatim}

\chapter{Major World Powers}

\section{The Conservancy}

The Conservancy is both a set of Terran republics and the governing 
body that rules them. It is a quasi-mercantile organization funded by 
controlled tourism and payment for its Terraforming services.

In land area it controls much of what is currently Mexico, Guatamala,
all the way down to Peru and Brazil. 

\section{NorAm Combine}

The North Americam Combined States is the loose coalition of the 
Mohawk Nation, the United States of America, Canada, and Greenland.

While it has adopted the U.N. currency as a monetary standard the NorAm 
Combine is not a member of the U.N.

\section{United Islamic Coordinate}

\section{The United Nations}

The largest single world organization on Terra. It is composed, in 
the main, of the EEC countries, the Soviet Union, Australia, and 
Israel. 

\chapter{Religious Organizations}

\section{Wiccans}

A semi-mystical coalition of churches derived from the pagan 
movements of the 1990s, the Unitarian Universalist and Humanist 
movements of the 2000s, and the New Bhudda movement of 2020.

\section{Cestus Dei}

A result of the ``Fire Reformation'' of the Catholic Church and
vatican IIII, the Cestus Dei are a missionary organization derived 
from the original Society of Jesus. As the name implies, the Cestus 
Dei is a militant brotherhood/Sisterhood

\section{The New World church}

Moonies in space.

\chapter{Marshalls}

\section{Description}

The Confederation Marshalls were established in the year 325 (CONFED) 
as a civilian enforcement arm of the Confederation Council by 
Confederation Governance Action 172-01/325 at the request of 
Ex-Council Factor Dan Forest-Kell(Terra). Its duties are fairly 
simply stated: To act as direct representatives of the Confederation 
in any matter involving the enforcement of Confederation laws on a
scale smaller than a full scale military action without regard to 
planetary or spatial boundaries.  

The Confederation Marshalls are direct representatives of the 
Confederation Council and as such can request military action or 
complete quarantine of a solar system. They are used as guards in 
situations where military personell are not needed or are 
undesirable.

They are often involved in criminal investigation where a local 
investigation would be the subject of some discomfort.

The Marshalls have little or no access to spacecraft. They typically 
use military craft or commercial transport, on which they travel at 
no cost. In addition they are usually able to get access to most 
government computer systems (within reason ) .

\section{Regulations}

Confederation Marshalls on duty are expected to be armed at all times 
and to carry their ID with them at all times. While there is no 
standard armament, there is a strong push for the rokie to train and 
use a slug weapon. The reason seems to lie in the Terran wild west 
origins of the Marshall concept. 

\section{Ranks}

Ranks are very simple. ( Two points of status are required for each rank )

\begin{tabular}{||l|l||}
provo	 & A rooky - typically assigned to a senior Marshall. \\
4th Star & Attached to a specific region or beat   \\
3rd Star & Attached to a specific duty area \\
2nd Star & Semi Attached - Qualified for Council Level diplomatique missions \\
1st Star & Unattached - Direct council representative. Picks his beat and reports in as necessary. \\
\end{tabular}

Unattached Marshalls have almost no salary. All of their normal 
expenses on duty are paid simply by their ID card. Charges accrue to 
the Confed  Council. They may commander equipment as necessary.

\chapter{Confederation Mechanised Infantry}

\section{Description}

The Mechanized Infantry is one the primary reasons for the continued 
existence of the Confederation in these troubled times. They 
constitute a package of deadly force on a highly mobile platform with 
the ability to perform everything from full scale assualts and 
armoured support to pinpoint actions in densely populated civilian 
areas.

In the MI, there are no armchair officers. When the time to do some
ground pounding comes around the officers are right there with their 
men. An officer in many respects is a very skilled individual simply 
because he must be able to direct the action and defend himself at 
the same time. 

The chain of command is painfully simple. 

\begin{verbatim}
The Commander General ( Marion Sutaken )
       |
	   V	
Legion						1,011,101	
	Battalion Commander
	100 Jump Battalions   

Jump Battalion				10,111
	Division Commander           
    10 Jump Divisions      

Jump Division               1,011 
	Field Commander
	10 Jump Plexes	      

Jump Plex					101
	Sargent Commander         
    10 Jump Squads		    

Jump Squad or Hand			10 
	1 Sargent                
    9 Infantryman       	 
\end{verbatim}

A simple schema but fairly effective. 

The MI have a need for men or women that are tough, flexible and 
capable of learning. As a result they have raided jails for potential 
troopers as well as normal recruiting. If an confed citizen can pass 
the examinations and initial training then he has a clean record. Any 
criminal record possessed up to that point is eradicated. By the same 
token the MI has a far more stringent set of laws and codes with 
fairly harsh penalties. 

All troopers enter a two year training program. This boot camp 
process is expensive but effective. They are exposed to a wide range 
of technological skills and are given Bacterial Augmentation 
injections to improve response speed. 

The MI get their name from the powered battle suits which they use almost
to the exclusion of all other equipment. 

\subsection{Types of suits}

\begin{itemize}
	\item Spook
	\item Scout
	\item Command
	\item Marauder
	\item Mauler
\end{itemize}

\end{document}

