\chapter{Environmental Enhancements, Special Abilities and Limitations}

\section{Outline}

After a character has some points in the four pools associated with 
character creation ( health, wealth, status, skill) he may choose to 
use them to buy Enhancements that will add flavour to the character. 

There are always the base enhancements allowed to the character. The
points in the Skill pool can be used to buy skills at the generation
cost. The points in the Stat pool can be used to buy stats at the costs
listed in the stat cost tables.

Enhancements are gains in either background or special abilities that 
can be paid for with points from one of the pools. There are two main 
types. There are special abilities or SPABS and there are 
Environmental Enhancements.  

SPABS are natural aptitudes that are typically permanent and inherent 
to the character's makeup.

Environmental Enhancements are typically advantages that depend on  the
character to maintain them. Such as wealth and various components of
status. 

% Read in the Cost tables 
\include{tcgen4}

\section{Special Abilities}

SPABS have both Depth and Scope to help govern their cost.

Depth refers to the numeric advantage given by the SPAB in a given 
area. The scope denotes the number of different areas that the spab 
may be applicable to. 

In the case of raising a character statistic the scope refers to the 
number of other stats affected.

A SPAB that involves enhancing a statistic is different from raising the
statistic. A raised statistic ends up increasing the SB of the character
in that stat. The enhanced stat SPAB increases the Rank of the character
for any direct rolls against that stat. Thus an Enhanced Stat SPAB
affects Saving Throws and Concentration Checks.

\subsection{Enhanced Stats}
SPABs that involve stats have a cost identical to the cost of raising
the stat with the following exceptions.

Physical Awareness (PAW) has a scope of 5, Hearing, Feeling, Tasting, 
Seeing, Smelling. This means that to get a SPAB: Enhanced Physical
Awareness costs \( 5 \times 2 \) or 10 points. As an example:

\begin{quote}
Samuel T'ganin, of the Terran Intelligence Unit has an extremely acute 
sense of hearing. This would be taken as Enhanced Hearing(ie PAW). 
Thus the cost of getting one level of Enhanced Hearing is 2 points. 
\end{quote} 

MAW has a scope of one. 

GAW has a scope of 6. 5 PAW and 1 MAW.

\subsection{Ambidextrous}
\subsection{Eidectic Memory}
\subsection{Presence}
\subsection{Lightning Calculator}
\subsection{Mage Ability ?}
\subsection{Other SPAB Costs}

Most other SPABs have effects that can be linked to one of the
statistics. 

\section{Environmental Enhancements}

Environmental Enhancements have both Depth and Scope to help govern 
their cost. 

\subsection{Wealth}

The first and most commonly used is the wealth advantage. This differs
from the basic wealth that can be gained by spending the points from the
wealth pool in that the gain is approximately one third that of a pure
monetary spend, but the gain so obtained is income that will continue to
be generated for as long as the PC pays attention to the interests that
generate the funds. The larger the income the more work involved in
maintaining it. 

\subsection{Friends and Allies}
Another important Environmental Enhancement is that of Friends. Friends
have a depth associated with them dependent on how much they can be
counted upon. The scope is dependent on how easily the PC can access
that Friend. 

\begin{tabular}{||l|l|l||} \hline
	Value	&	Dependability & Scope \\ \hline
	1		&	10 \% & 10 \%	\\
	2		&	20 \% & 20 \%	\\
	3		&	30 \% & 30 \%	\\
	4		&	40 \% & 40 \%	\\
	5		&	50 \% & 50 \%	\\
	6		&	60 \% & 60 \%	\\
	7		&	70 \% & 70 \%	\\
	8		&	80 \% & 80 \%	\\
	9		&	90 \% & 90 \%	\\
	10		&	100 \% & 100 \%	\\ \hline
\end{tabular}

\begin{quote}
Terran Intelligence Operative Samuel T'ganin has the friendship of both
a wealthy widow and the Free Traders of Asozan. The wealthy widow is
fond of Samuel and be counted upon for occasional assistance so her cost
as a friend is Depth 1 \( \times \) Scope 1 or 1. The Free Traders owe a
debt of honor that some take more seriously than others, but on average
Samuel can count on their aid about 60\% of the time and the Free
Traders are a ubiquitous lot ( Available at 60\% of planets that Samuel
frequents).
\end{quote} 
 
\subsection{Reputation}
\subsection{Continued Careers}
A continued career as  LEO or soldier is a balanced ad and disad situation.




