\documentstyle[palatino,makeidx,shape,relate]{report}
\makeindex
\title{Shape Shifteren Dialogs}
\author{Jim Mochel}

\begin{document}
\maketitle

{\Large\sf The Discussion Between the Vordack and Morphus as
the latter lay recovering from the destruction of the grove}

{\bf Vordack} "Summoner?"

{\bf Morphus}
``I hope you fare better than I Avenger. You may have noticed
that my staff was linked to the Grove, and I to my staff; I am feeling
[KIF roll]{not good}. Was all lost? Were we too late?''

{\bf GM} {\sc
You are floating in a misty blue SPACE\dots there are no walls, no
ceilings and no floors. Everything you say or the VORDACK says
echoes and stretches in weird ways\dots you think your body is
in physical danger\dots}

{\bf Vordack}
``Despair\dots the trees are burnt, the pool is dried,
the Grove is leveled{you sense hurt and pain from the Vordack}. But
all is not lost. I have kept the children of the Grove within myself
and pulled the Gate around me. I think they that burn will leave in
their impatience. They have not sensed my presence I came cloaked in
wind and illusion. There is much wrong with you Summoner\dots..''

{\bf Morphus}
``I sense that as well. Do you know of the [I will describe the
pool that the elder trees allowed and or helped me to drink from]?
Perhaps if I drink from the pool it will heal me or at least sustain me
while the grove and my staff recover. If not I must attempt to enter a
KI trance or attempt a healing spell. I am not sure that I can do
either while unconscious.

{\bf Vordack} ``The pool of which you speak is no longer on the road from
here to there. When blossoms unfold this road will be rebuilt. You must
send your roots to different Earth. And so, Summoner, I must tell thee
that you are in a state of within\-ness already. Your bark was badly
damaged by the Storm. You must turn your sap to Life\dots ''

{\bf Morphus}
"Can you guide me to a source of Earth Power?

{\bf GM}
{\sc you feel cut off from the earth\dots you have no sense of dimensional
space at all. You can sense your own power, but no manna in the
environment around you.}

{\bf Vordack}
``You are far closer to a source than I, Summoner. I am bound
in a Faerie ring. I can not perceive as well as thou through thy senses.
And so, Summoner, I must also tell thee that I know not who though art
and what thy purpose is upon this dream, nor can I assist you in the
application of thine power as thine power is as a mystery to me, and
thus beyond mine ken. But thou shouldst look to thine healing ere your
sap turns to amber.''

{\bf Morphus}
``Mine healing is a lot tougher than you might think. I can't
do much without Mana and there doesn't seem to be any around here.
Without the pool, or assistance in contacting the Earth Power, my POW is
not great enough to make a difference. I have some skills in many
Schools and Sorceries, though Shaping, Prophesy, and Summoning are my
strengths; but even in these I am close to helpless without Mana.
[this has bit me before and if I get out of this you can bet your buns I will
figure out something that costs Minimal POW to link me with a
significant source of Mana (or power that I can shape)]
But I have friends and perhaps they will be in time to save me. Until
then, since we both seem to have time and nowhere to go, let us share
our knowledge and histories.''

``I am Morphus, Demon Bane, Abjurationist, Diviner, Summoner, worker of
Earth and Water, Alterations and Evocations, Enchantments and Elemental
Sorceries.  [hey! sounds good doesn't it? I bet that's almost as long as
Mordanith's full name!]  Long have I lived upon the mortal plane, far
longer than I can remember if truth be told. I am warded, by who and for
what I know not save that divinations of my past or future give diviners
bad headaches. I have old friends, like \ndx{Falstaff} of the white staff and
new friends, like Mordanith, son of elvish priests. Foes have I as well,
like the \ndx{Wizard King} and \ndx{Jarek Fireload}, Desecrator of Trees. My goals
are plain,Go everywhere, learn everything and work great magics.
Venerate the Mother, have respect for She Who Weeps, and nurture Life
and Nature where I can. Light too, of course, though those of Light
can usually look after themselves and they oft have different goals than
I \dots  Most of all, live life now, for we are but ripples in the
currents of They That\dots ''

``What of you, Avenger? Tell me of the place where you come from, the
wonders that you have seen, the creatures and beings that you have known.''

{\bf Vordack}
``Tis mine hope that thine Healing is as strong as thou
believeth\dots.In the Realm of Dream where thine self now resides it is
difficult to perceive the way of the material world.  Perhaps thou
couldst bind thy soul to thine body? It would aid you should you
be disconnected for a time. I know little of this but I know pain\dots and
the Staff of the Wood cries out to me in its anguish.''

``Greetings Morphus, Demon Bane, Abjurationist, Diviner, Summoner, worker
of Earth and Water, Alterations and Evocations, Enchantments and
Elemental Sorceries. Thou art not the being I expected when I heard thy
call\dots. I expected an enemy.''

``Thy ward, it is self struck, methinks. Thy future is twisted with Wild
and Dangerous Magicks of a most untemperamental leaning. I fear even
thou doth not know where thou willst tread\dots thou canst truly remember
only little?''

``This Falstaff I know\dots he hath fought on the fey side afore now and
thy speaking of his name in friendship brings my doubts once more to me\
dots\dots''

``Thou speakest Forbidden names as glibly as they were the names of common
rocks\dots. watch thy tongue Wizard of Many Arts. There are those who
would harm thee if they suspected what it is that I now believe of thou.
Thou namest me right when thou sayest Avenger, Wizard. Know me\dots. I
am he who hath guarded the Gates of Chronos for the Lords of Time, I am
he who brought the Book of Winds to the High Elves of Yisvaeaounnaaie
Kai\-Talientir. I have fought a Greater Dark and its Legions\dots. I am
the Warden of the \ndx{Kerestaen} and Lord of Air, Light, and Conjurations\
dots. also know that I am skilled in the Human\-Forbidden Art of
Abjuration\dots though not, maychance, as skilled as thou? Hmm?
Perhaps thou hast dual meaning for mine Summoning\dots..''

{\bf Morphus}
``I may try to bind my soul, that should be within my Power.
What enemy were you expecting? I hope that I did not pull
you away from a fight that you were looking forward to. ''

``You have doubts BECAUSE Falstaff fought for fey? I thought that you
were closely tied to Fey? What doubts do you have?
Forbidden names? Which are forbidden and why? If forbidden because
uttering it might alert an enemy to my presence, that is a good reason.
I utter not the name of he of Death because of old he and I have had\dots
words), but many speak \ndx{Wizard King} and a call name is not the
same as a true name, though there is some danger, I'll grant you.
Especially since I summoned his entire herd of prize horses, and Storm
their Stallion, right out from under him. And Old Fireload is just
{\bf starting} to piss me off. The only direct contact we have had is his
contact with my creations, the Bridge over the trickle Quai and the
Grove\dots.I will be avenged against him for that if he wasn't finished
by the Mages of Marden.''

``What is it that thou, uh, you believe of me? I can not tell you if 'tis
true lest I know what it is.''

``\ndx{Kerestaen}? I have heard of the Kerestaen, but I know not from where. Who
what or where is Kerestaen?''

``Forbidden Art! Abjuration is not forbidden, it is discouraged\dots.It is
only Shaping that is forbidden and that is because certain fools
believed that by forbidding Shaping they would eliminate the problems
caused by irresponsible Mages. Instead they created an imbalance \- If
patterns exist, they must be studied and used. If they aren't, the
uninitiated will stumble upon them and wreak even greater destruction.
And the Dark Powers against which Shaping was most effective\dots well
whose wolves kill the most Shapers?''

``Gladly will I exchange information with you, if you so desire, in any of
the subschools that I have knowledge in. What mean you \- dual meaning?''

{\bf Vordack}
``Thine call was similar to another that I hath known, Summoner.
And, nay, thou didst not take me from a fight\dots I thought thy call
was a challenge when I first tasted it. Falstaff hath been a friend to
all things Fey\dots..''

\begin{quotation}
{\sl {\bf Flashback}
The scene is a small room of wood, with a single bed made with fur on
your left, a stool, a mirror of copper to your right, a bureau with
three drawers beneath it, and a swinging door behind you. There is a oak
table between yourself and Falstaff. He is flushed and you are yelling
``You cantankerous, senile, blundering, weak\-hearted, emotional,
immature, sentimental old fool! I can't believe it\dots. have you gone mad!?''

With crack of thunder Falstaff smashes the table in half in a downward
sweep of white. His face glows with fury and the air around him crackles
with flashes of power. ``The Faer\-han would have died if I hadn't\dots.
would you lose \ndx{Tyriontill Kyrvaeon Alan\-ad} to a Raver!?! Hmm, you
lecherous, Earth\-grubbing, addle head!?? Would that be worth it for our
Grand Cause?! Wake up\dots people are not playthings, Damn it! Sometime's
we have to sacrifice the straight line to our goals to
retain our humanity!!''

You sense Darkness sweeping towards the inn in which you are standing.
``The Ghoul will lead them right here, Fals! I hope you're ready to face a
Death Lord and his Knights\dots. I certainly won't help you.. I have to
heal the breach in the Earth you caused.''

``Hurry up then, my friend\dots the breach widens as we speak and the
Darkness is upon us.''

There is a rending of space as a Greater Death
steps through the wall of the room.. and then you are gone as you plane
shift away\dots..
}
\end{quotation}

``\dots. and so I believeth you to be connected. Summoner? As I was saying
the names of They That Were Before, even the "call names" as you say are
tokens of power. As to the \ndx{Kerestaen}.. I may not speak of them to those
who know them not. Soon perhaps I may tell thee. As to forbidden.. I say
to thee twas truly forbidden by the Great Human Councils of Mages, the
Priesthoods of your World, and The Elven Council. While it twas not
forbidden to study in theory it twas deemed too dangerous to study for
humans and their ilk. Of course it tis not a true skill in Faerie as
shaping is like unto walking.  Thy point on Wolves is well taken, Shaper.
I believe that thought art not the \ndx{Dragon} I feared thee to be when thou
first summoned me and instead what I have been growing to suspect as we
hath spoken\- something far more dangerous\dots Didst thou summon me to
entrap me in this Grove ?''

``Art thou of the \ndx{Preceptors}? Speak true for mine senses are
keen.''

{\bf Morphus} ``Forgive me, sometimes my mind wanders. When you mentioned
that "Falstaff hath been a friend to all things Fey", I remembered
this =>(a language filtered version of the flashback, with all the
pertinent facts). What were you saying while I was wool gathering?
I'm sure that I have heard of the \ndx{Kerestaen}, perhaps I will remember.
Needless to say, I will look forward to hearing of them when I may.
No. I'm no dragon. Though I am almost positive that a dragon in human
form was watching us cast our summoning. Mordanith believes him to be a
bronze dragon whose name escapes me at the moment.
Dangerous, perhaps. Hopefully only to my enemies. I summoned you for the
purpose that I set forth in the spell, to protect, nurture, and care for
the grove as I would if I had the Time or Power, and were free to do
such a thing. But I do not yet, and can not yet, so I needed you. It is
a prison. A prison of which you are both prisoner and warden. You
control the boundaries. The farther the grove spreads, the greater are
the limits that you may walk without purpose, the greater the area that
is blessed with the beauty of my plane and that of Fey Light, Life, and
Nature. All those who YOU deem non\-harmful to the grove and those who
are its guests, may enter. You are the Guardian, the Warder\dots
You are  Lord of the Grove; even I who created it must bow to your will there,
until you pass the wardship to another who will accept it.  Even the
boundaries of the Grove do not bind you You may go where ever you feel
you must to fulfill the requirements of your office. You were told and
you accepted.''

``I know not of the \ndx{Preceptors}. Who are they?''

{\bf GM}
Things sound more hollow now\dots the expanse around you gets
darker\dots you begin to feel a little cold\dots. you have not yet
completed the binding\dots. you aren't sure if it worked or not but you
think so\dots.

{\bf Vordack}
``Thine mind is confused as it hath no point of reference. I
wert saying that I believeth that I shouldst know thee and indeed tis
mine belief that I might knoweth of thee indeed. Where didst thou learn
thy art, Summoner? Didst thou not suckle at a Druid's bosom? Art thou
not of the \ndx{RING}? If thou be he whom thou impliest, thou art then that
one I feared\dots Earth Lord. Tis possible thine goals and mine art not
well met. I do now believe {whisper\dots. whisper} as it would have ill
fit thee to tell myself of thy disagreement with the White Staff. I
believe thou hast hidden thyself from thy enemies by hiding thyself from
thyself. As such, it couldst be thou art a better person now. I think {
whisper\dots. whisper} and well met. Think with care of what thou hast
done\dots. thine brother Falstaff is not without his wisdom.''

``Thou art{ whisper\dots whisper} to both enemy and friend. Thy danger
comes from thy great skill and human enthusiasm. Lord and Slave to the
Grove I am. I hath come willingly and, I now { whisper\dots whisper}
fair benefit. I think thou acted in good faith and I can but hope that
thy inner self didst not have thee choose {whisper \dots. whisper}
sinister purpose.''

``The \ndx{Preceptors} are a sect of humans that serve CHAOS. They {whisper}
masters of the \ndx{Wild Magic}. Their goal {whisper}ruction of She upon Whom
we Rest {whisper} May Not Speak Of\dots. as {whisper} the enemies of {
whisper} our people\dots''

``Summoner?\dots {whisper}\dots SUMMONER!''

{\bf GM}{\sc
There are roiling swirls of various hues of blue all around
you\dots some are so dark as to be almost black. Most of the darker ones
are clustered to your left; to your right there are much brighter
elements of blue and it is from there that the Vordack's voice seems to
emanate. Around you the lighting is approximately that of a very stormy
day at dusk with spots of orange dancing in the distance like far off
campfires. It is cool enough to make you feel uncomfortable. You seem to
be floating in your physical body. Eyes, ears, arms, legs, blue robe\-
no staff. You can hear sounds like the crashing of water on a far away
shore\dots..
}

\begin{quotation}
{\sl {\bf Flashback}
Off shore, purple tinted storm clouds hang on the horizon as if they are
going to leap off the edge of the world\dots. The cool, salty wind
brings you the smell of dead seaweed and brine as it whips your black
hair around your face.

``I don't understand it,'' you say as you lower your eyes from the dark
cliffs looming over you to the small, bent man sitting in the sand at
your feet. ``Why did she close herself to us? What possible purpose could
she have?''

``She needs no purpose, young \ndx{Kheldar}. She walks the \ndx{Path of Dreams}. You
have walked that Path yourself.''

``But never for this long\dots what if she doesn't return?''

``She will\dots. she will.''  He stands up awkwardly, brushing your
helping hand away as he straightens his faded orange robe. His eyes, the
color of a winter sky, peer deeply into yours as he begins to limp away.

``Someday, \ndx{Kheldar}, when you are no longer Kheldar, you will tread those
paths for far longer than \ndx{Miriel} ever will\dots'' He paused to hop over a
piece of driftwood as he headed down the long, empty beach, ``You will be
lost, and you will remember this day and know that in the Realm of
Dreams the only sign posts are those that you cause to be made. Do not
wander far\dots the most deceptive enemy is often yourself.'' He smiles
to himself, panting with the effort of walking, ``That's one of those
wise sayings to keep in a big book in your reading room. Keep it handy
because you can answer half the questions you get asked with that one.''

He pauses to look out to sea and to catch his breath. His bare brown
feet make a startling contrast with the white sand. ``Have I ever taught
you about the \ndx{Kerestaen} ?'' He points out over the black waves\dots
``Look at that bird.''

You look out and see a patch of dark rock, covered with moist fungus,
around which a flock of white and grey birds circle wildly. You point
with your staff, raising your left hand to shield your eyes against the
bitter wind.

``Not the seagulls, dolt! The orange one.''

You see a spot of orange drop away from the flock of birds. It drops
near the water and rises once more, just brushing the caps of the waves.
As it swings towards shore you see it is a magnificent bird\- a wingspan
fully eight feet across and its entire body covered in a thick coat of
feathers the color of the setting sun.

``The Ferthan bird knows the ways and winds of every ocean, it is one of
the most powerful symbols of that people. Notice the\dots''
}
\end{quotation}

{\bf Vordack}
``SUMMONER!!!!! THOU DREAMWALKS TOO LONG\dots\dots.AWAKEN!''

{\bf GM}{\sc
You are in the Realm of Dreams once more\dots. you feel your body
changing but know not for good or for ill.  You can feel a powerful
mind seeking yours.. it is the Vordack.
}

{\bf Morphus}
``Avenger? HELLO? MY SURROUNDINGS HAVE CHANGED. IT IS DARKER AND
COLDER THAN BEFORE. I CAN'T HERE YOU. I COMPLETED THE BINDING, MIGHT
THIS BE AN EFFECT? OR AM I DEAD?''

{\bf GM}{\sc
You can't remember what Dream Walking is\dots it escapes your mind.
There are more dark clouds then light now. You hear the rhythmic sounds
that reminded you of surf. Slowly, your body moving in slow motion, you
turn towards the lighter clouds. Your hand reaches out with agonizing
slowness as you try to will yourself towards the "direction" the Vordack
seems to be in. You feel wind whip around you coming from the direction
of the Vordack, pushing you down and back. You don't seem to be moving\
dots As you`re mind pushes forward your thoughts flow back to the memory
you just had\dots
}

\begin{quotation}
{\sl {\bf Flashback}
You place the leather scrollcase down on the marble tabletop, your eyes
flicking over to the rack of eight blue candles at the other side of the
table. The rest of the room is shrouded in the flickering shadows caused
by the candles. You can hear the drumming of a hard rain on the wooden
roof over your head. The smell of wet wool and candlewax lingers in the
air. Before you sit the two scroll rollers. You sigh, look at them both,
and then rub your hands together muttering ``Scrolls? I can do SCROLLS!''

You cackle as you pull an empty scroll from under the table and fasten
it into the right scroll roller. First, the main body fits into the
lower notches and then scroll out a little and attach the start of the
scroll to the upper notches. You insure that the paper is flat, and then
read the aura of the paper. Not bad\dots.

You turn to the scrollcase on the table and reach to pick it up. The
candlelight flickers off the heavy bronze ring on your left hand as you
gently lift the scrollcase and untie the red lace that symbolically
binds it. You place your finger on the top of the scrollcase and say the
word of releasing while giving it a light mental nudge.
The locks on the scroll release. You gently and carefully pull the
ancient, brittle leather off the scroll. The scroll is old and yellowed.
One of its rolling pins is larger than the other and both have large,
broad, wooden caps at both ends. They are of a very dark color
impossible to distinguish in this light\dots Their is a green ribbon
tied twice around the scroll. Light explodes around you with a crack of
thunder!

You start back as lightning from the storm outside illuminates the room
you are in through the high, narrow window on your right. In a split
second you receive an impression of a large, stone room; of tapestries
on the walls; of a rickety wooden door on the far wall to your left\-
and then blackness. You cackle to yourself about being a "scaredy cat"
and get up from the long wooden bench you've been sitting on. Your butt
aches from sitting on the hard bench for too long, your open slippers
are soggy and too cold. You go over towards the door and almost trip
over the tray stand holding this morning's breakfast. Or was that supper?

You carefully lock the door, and then hobble over to the window and
close the old black shutters\- getting sprayed by rain in the process.
The timbre of the rain immediately changes. You stop and listen to the
sound for a while. You then carelessly grab your beard and tuck it into
the neckline of your robe.

You compose yourself and then, still standing in the middle of the room,
you drop into a Mage Trance. You slip into Mage Sight as smoothly.
Cautiously, you look around the room. Spotting some points and a few
weak streams of stray magic you wander around the room shaping them into
compact form and binding them in place. You call the \ndx{Abjurational
Pattern} to you and suddenly everything looks as if it is structured
power, and you lose most of your sight in the material world. You go to
the wall in front of you\- tripping on the food tray once more, but not
losing your concentration\- and fumble a piece of yellow chalk out of
one of the belt pouches slung below your swordbelt. The yellow glow from
the chalk makes the wall seem dirty and pitted. You concentrate, and
then, muttering to yourself in \ndx{Ancient Elvish}, you draw a \ndx{Tolnedran Rune}
\index{Runes!Tolnedran} of Sealing on the wall. You repeat this
procedure three times for each wall.

After putting the chalk away, and washing your hands in the water basin
below the food tray, you sit back down in front of the scroll. You gaze
appreciatively at the complex weave of wardings and triggered
enchantments guarding it. You shift in your now damper robe.
}
\end{quotation}

{\bf GM}{\sc
You suddenly find yourself amidst great roiling clouds of
purple and dark blue. There is a circle of brighter blue in front of you
\dots it appears to be about the size of a large plate\dots.it is cold as
death, your head is swimming, and your skin is crawling as if to pull
off your body. You fight to escape the memory but its hold on you is too
strong\dots. you feel yourself pulled in again\dots\dots
}

\begin{quotation}
{\sl {\bf Flashback}
You are sitting at the desk finishing up the scroll. The light blue
feather quill in your hand is warm to the touch as your hand quietly
brushes out the last few strokes of the last glyph. You finish off the
Rune and place the quill back in the lead crystal ink well to the left
of the roller. Moving very slowly you blow on the ink in an attempt to
make it dry faster. You barely contain the impulse to sorcerously pull
the water from it, and just lean back to wait. Pain shoots up from your
back and your butt. Your eyes wearily observe the daylight streaming in
through the cracks in the black shutters. With a groan you get to your
feet and hobble over to the large clay pot sitting next to the window.
You pull up your robe, undo your loincloth and relieve yourself. Your
knees ache as you squat down. When you finish you wipe yourself with the
towel left there for that purpose. You re\-wrap your loincloth, and
stand up, letting your robe drop back around your legs. You stagger over
to the tray
}
\end{quotation}

{\bf GM}{\sc
Your mind struggles out of the memory and holds desperately onto a
conscious state\dots Your head clears and you are in the place of blue
clouds once more\dots..
}

{\bf Vordack}
``Summoner? Shaper?''

{\bf GM}{\sc
Your weight is fairly severely reduced. As you heal you will gain
weight. You will end up being at the correct weight for the next stage
when you are done healing.

>Exercise is a must and I have wielded a sword before, By following the
>singing warriors guidance and exercises, can I develop myself into a
>swordsmans body? (like Falstaff not Vartigan)

Yes\dots.. this follows the line of thought of your physical
development.  You are sort of doing that as you increase your physical
stats. Did you have something else in mind?

>In our conversation, what was the time, in surges, that the Vordack
>gave me for the A) Budding B) regrowth of the Grove (and my staff)?
>Before I wake up I ask how much time, in surges, we have been
>conversing. When, in my time, using this info, will A) \& B) happen?

About 6 surges (33 days) occurred while you were unconscious.
According to the Vordack Budding can begin in 12 \-14 surges;(60\-77 days)
Regrowth will start to set in 15\- 20 surges after that.(+75\-110 days)
It will take at least 40 surges after that before the trees are even close
to the level where they were at when you left the grove. (+200\-220 days)
Total 335 \- 407 days

>Now that I am in 'Conscious' trance, can I contact the trees? If so,
>I will let my companions know what I am doing and I will inform
>the trees as to all that has happened, is happening, and will happen.
>I will ask if drinking from their pool will aid in the recovery of
>my body and will ask if I can drink.

Yes, you could contact the trees. Write to Mochel or call him and let
him know what you want to do\dots..get his input. Then get back to me.
}

{\sf\Large Mordanith Ticking off Morphus}

OK, Let us talk about Morphus/Kheldar. First off let us discuss his general
stances on topics. You seem to be saying that Morphus/Kheldar is neutral
towards Faer-Han. Interesting statement that. Keeping in mind that almost all
Faer-Han and Quentar I have met have warned Mordanith about Kheldar. This
warning usdually refers to Kheldar as an enemy of the Elves, rather than a
neutral party. The best recommendation I recieved from an elf about Kheldar
came from Anthea, the healer that never wants to see you again.

It is clear that Kheldar was not neutral towards Elves. In some way he felt
that he had some reason to believe that there would be hostilities between
himself and Elves. Why else would the wards he had designed automatically
designate a Faer-Han as a hostile target ?

Kheldar has always been ruthless. He used people. Remember the K-memory about
the argument between you and Falstaff regarding Tyriontil ! You may have met
someone who has good memories about him. Mordanith has not. Even Falstaff,
your ex-partner, has stated that you were a bit extreme. Come on, we are
talking about a man who designs specialized mage-assassins like Sigmund and
(maybe) CatBird.

Mordanith has no real fears for himself at this time. He is worried about the
lives of those to whom he stands beholden in wone way or another. CatBird and
the Singing Warrior especially. As well you keep harping on the qualities of
your enemies, they are Dark, they are Evil, etc... Yes, it is true, most of
them are not people Mordanith would align themselves with. That doesn't
matter. What does matter is that they are incredibly numerous ! The Dissenta,
the Black Cloud, A Number of Tolnian Priesthoods, these are people who would
try and kill you because you are an Abjurationist. The Dissenta, The Wizard
King, and the Lich, these are people who would kill you because you are who
you are. Oops, I forgot, add the priests of Archon and Archon himself. Jarek
Firelord want's to kill you just because you pissed him off. And then there
are those we are not sure about. Prince Taliesien and the Elves of Heimdella,
THe Heimdellian Church, Kay, Others of the GRay Wanderers, the MAge Guild if
your profile gets to high for them to ignore, the GodKing of Theridden, etc..

You, as Kheldar, have walked this earth before. You stepped on a few toes !
The problem is with don't know who's toes they are ! I give the same advice
that Falstaff gave you, that Anthea gave you, that Oleander gave you, that
the Priest of Dal Pan gave you, etc.. and you will probably igniore it as you
have ignored it from them: "Keep to the Cover", "Show yourself only when
necessary!". Whenever possible, use stealth, you humans are said to be good
at it.

As for whether you can trust me. I will stay with you, in common cause, until
such time as the Wizard King is defeated. There are things normally left
unsaid, that should be stated now, especially to one such as yourself. To one
whose honor, obligations, and responsibilities may be sacrificed on the altar
of expediency I say : "I will stay with you in common cause as agreed until
such time as we have reached our goal, or until your actions cause injury to
the honor or body of those innocent".

Morphus, I am fond of you, and for this as much as anything else I travel
with you. But I am not blind. I am along to protect others as much as I
protect you. I continue to travel with you despite the intimations of others
, who have dealt with you as Kheldar, that you will likely be the cause of my
death. Do not speak to me of whom can trust who, old man. I will not be the
one who puts your life second to that of some random goal ! This plane is
only worth saving becuase of those who walk it. Otherwise, it has no
intrinsic value. Try, I say to you as Falstaff has, to remember what you want
to preserve and why.

Mordanith Alda'an Kaerlin Thalionsaer, Body Son of Ardana'al and Q'aelinah ,
Spirit Son of Corellan.

{\sf\Large Discussion about Tev Between a thief and CatBird}


Subject: Re: Tev and the rainbow guys...

{\sc NOTE: If you can't understand that is fine- I am going to try and give a 
feel of Marden street slang without going \_CLockwork Orange\_ on you... If you 
have any interpretation questions- Susan can ask. The rest of you will have to 
ask Catbird!;-) }

First report comes from a young street messenger for the Guild..

"Haven't learned much but I think this guy is a wig? Yaknow? Tev...

"There was guy wit da name \ndx{Tev} that wa sin the Monastary of the Flaming 
Heart you know- the biggun in the middle of Faith Square? He was, ummm.. 
different.  FOr one thing- he was a lifa. Heh! I guess they all are lifas 
there! HAHAHAAH!  umm.. right. Well- he seemed to be sticking around. He showed 
up about 10 years ago or so- maybe 9 or 1. Hard to say unless you a looker, 
yaknow? So- he been around since then. He's in bad with the Imps 'cause 'e was 
involved in that big 'sanation that happed over at Temple Street by the Dragon 
Temp by the Gardens- yaknow? But the local jakes don't .  mess wit 'im.

"I got a name-- \ndx{Tevarion Marsakanis}. Pretty glitter, huh? If he's da same 
guy as dis Tev, and da dr- ma source- near da temple thinks so. He's trouble. 
He's knife in a big way. Some knocker for a big G.O. in the Blue Star district. 
I think the G.O. was in the mind-muck biz. Yaknow-with drugs.

"If you gonna hit dis guy- I would watch out. He is still shakin' but he don't
live in da monastary no more. Dey might no more about where he is. He shows up
every week or so at the market looking for info...

"I got told you can get one level o' followup for free. Don' know why you
rate, but what do you wanna know... "

Alex: I give the kid a couple of silvers (or whatever's a generous tip
in Marden.) I pass the questions on. I am willing to pay for additional
followup. I respond to the kid's comment about not hitting Tev, with something
to the effect that this is only a remote possibility, and its good to have as
much info as possible.

In case it is not clear, I am trying to make a reputation in the guild
as being generous with those who help me. Time may come when I have to do the
flip side of that, but right now, I am trying to do the ally thing. I very
much want to build up an info network.


\printindex
\end{document}
