
{\bf Chris} 
What can the Vordach tell me about the Gates of Chronos/Lords of Time?

{\bf Alex}
The Gates of Chronos is a spell construct made by a Mage of unbelievable power 
about 3,000 years ago. It has no "real" position in space or time but 
rather exists almost everywhere. In that sense it is similar in construction 
to the Pattern of Tyriontill that the elves use to travel across the 
Great Water (what they call the Ethereal that seperates the World from 
Faerie\- what you were floating in).

The Gate is a flow regulator\- of Time itself. It is similar in that sense 
to the Ward of Dof\-Sifrin that surrounds the World (also known as the Bridge 
of Heimdell, or the Bifrost). These "constructs" are macro's of the universe.
They regulate physical and temporal laws and force them into certain patterns.

When the Gates are open it is possible to use them to manipulate/travel 
through/change time. Kheldar has worked on a Gate node before\dots

The Lords of Time are those beings that have access to the Keys to Time. 
They can control the flow/speed/direction and feel of time in specific 
areas\dots 
there are only three time lords known to exist at this time Heimdell, Labelas 
Enoreth, and, of course, Lord Carolyn of the Elves himself\dots.

{\bf Chris} 
Can anyone use the Gates or the Bridge? Do you need somethings permission ?

{\bf Alex }
No. Yes. 

{\bf Chris} 
What are the Keys to Time? 

{\bf Alex }
You are not sure\dots

{\bf Chris} 
Is a Time Lord someone who has/Knows these keys or is there more to the title? 

{\bf Alex }
Much more! You must have mastered the art of manipulating time!

{\bf Chris} 
You said that Kheldar has worked on a Gate node before, does that mean 
that Kheldar was a Time Lord?

{\bf Alex }
Kheldar was certainly not a Time Lord.

{\bf Chris} 
What can the Vordach tell me about the Book of Winds/High Elves of Yis Etc.?

{\bf Alex }
The Book of Winds is a holy text of the Grey Elven Church of Correllan. 
It is a book that supposedly contains the design specifications for the 
Element AIR. It is considered the seminal work on light craft, weather magery, 
and wardings of air. It is also rumored to contain a history of the 
Elvish people that goes back to their creation! 

Yis is the High Elven city to the North of ther human Feudal Kingdoms that 
is the largest Elven population center in the World. Coventree in western 
Bengalli, and Woodshome in north western Dau\-Shao are the only cities that 
could rival it\dots\dots

{\bf Chris} Are Non\-elves allowed to visit Yis? To look at the Book?

{\bf Alex }
Yes. No.

{\bf Chris} What can the Vordach tell me about Fighting and defense methods against 
a Greater Dark? 

{\bf Alex }

LIGHT. And Light. And more Light. No\dots seriously. One of the easiest 
ways to fight a Dark that is on this World is to Banish it. Using light 
power perform a Reverse Summoning on the Dark and it will be forced 
to retreat back to Darkness, or be destroyed.

If you are facing it on neutral ground, it is best to do as much light and/or 
fire damage as possible as quickly as possible. They recover frighteningly 
fast and don't stop until they are destroyed. They are not intelligent so you 
need not fear much in the way of tactics. They will tend to head straight 
for their target (usually the nearest source of Nature or Life). 
They are often controlled by Dark Mages though so be warned that a 
controlled Dark CAN have tactics!

They are so powerful though that you would not want to fight a Greater Dark 
unless you had a real good plan or lots and LOTS of spare power.

{\bf Chris} What, if anything does he know of Greater Death's? What effects does 
death and death magic have on creatures of Light?

{\bf Alex }
Little. They appear in the form of Death typical of your culture, and they 
are undefeatable by a mortal being\- though you have heard of men who have 
done so. Death magic has no effect on beings with no Life or Nature in them.

{\bf Chris} What can the Vordach tell me about Warden of Kerestaen

{\bf Alex }
That is "the Warden of the Kerestaen". The Kerestaen are an ancient race/group 
of people/beings that are rumored to have some vital significance to the 
survival 
of humanity and life. The Vordach will say almost nothing about them except 
that they are on one of the other planes and they are not like humans in 
their violence. They are a peaceful people. They are rumored to hold 
tremendous power\dots..

{\bf Chris} If the Kerestaen have a vital link to the survival of humanity and life, 
then I would like to learn more. If the Vordach is willing and able, 
I would like him to contact one of the Kerestaen and arrange a meeting, 
a mental one would be fine, and on their (or his) terms. 
I wish to try to remember all I can about the Ferthan Bird, I'd like to 
try to take its shape; or are they like the wolves and dolphins, 
intelligent and improper to take their shape?

{\bf Alex }
He will not discuss them and you don't know.

{\bf Chris} What can the Vordach tell me about "Lord of Air, Light, and Conjurations" is 
this a title? how achieved?

{\bf Alex }
This is not an official title. With some small amount of embarrassment 
the Vordach will tell you that it merely means that he has achieved 
mastery over the magical arts of Air, Light, and Conjuration. 
It doesn't really mean anything but that!

{\bf Chris} 
Who or where is Tyriontill Kyrvaeon Alan\-ad?

{\bf Alex }
Tyriontill is a living legend\- he is the elf who created/became/is the 
Elvish Conjuring Pattern known as the Pattern of Tyriontill. He 
is supposed to still be there and guides and maintains the pattern.

{\bf Chris} 
Could Mordanith introduce me to/teach me the Pattern of Tyriontill? 
When did he turn himself into the Pattern?

{\bf Alex }
Yes. A long time ago.

{\bf Chris} Does the Vordach know when, if ever, Tyriontill 
Kyrvaeon Alan\-ad was endangered by a Raver?

{\bf Alex }
Constantly\dots.. 

{\bf Chris} 
Since this predicament came about because of my staff, I will describe the 
events leading to the contruction of the staff, how it was created (
appologize for rushing the trees), how it and I are related and my future 
plans. I believe that the Earth and Fire components are still at full 
strength and that the water component still buffers the Earth and Fire 
adaquately. The final Binding will be of Air, but that time has 
not come yet. The three woods embody the Aspects of Light, 
Life(mine), and Nature. I will express my belief that to fully charge \& 
complete the staff and stabilize the considerable Light, Life and Nature 
power that I hope it will hold, it will be necessary to bind to it (
magically not physically) some quantity of Death, Dark and Decay. 
It is my hope that the completed staff will be 

a) less likely to spontaneously detonate because of the balanced forces

b) better able to "defend" itself because it will contain part of the forces 
that might be directed against it and 
thereby able to shunt or absorb some of the corresponding power 

c) At least a powerful focus for my spells

d) At best, who knows power source, sanctuary for my soul (it does have my pattern), gateway to places that have tree clones growing there or elsewhere for that matter.

What comments, criticisms, or suggestions does the Vordach have for me? 
(From both a Personal level (in view of the three D's) 
and a Mage's point [of View])

{\bf Alex }	
The Vordach says your staff will be better off not being a complete balance 
of forces as it was not created as such. It says you are foolish to bind 
darkness, death, and decay into the staff because although it will 
"balance " the power of your staff\- it will also weaken it \dots 
Leave it as it is and re\-enforce the elements that exist within it now.

{\bf Chris} 
To clarify The Vordach says "as it was not created as such". Does this mean 
that if all elements had been installed in it "at the beginning", it would not 
have been "weakened" by the addition? Or that it would not be "as weak" as me 
adding Death, Dark, and Decay now? 

{\bf Alex }
It would not be "as weak". 

{\bf Chris} 
Chris's premise on this comes from the my thought of Druidic "Balance" in 
D\&D where a power of Good attracts evil and a power of evil attracts good, 
but a balanced or neutral power acts only where there is imbalance. 
Also from the physics thought of lightning where massive charge 
differences in the air and on the ground cause a discharge, 
but a balanced positive/negative charge has potential but is 
basically neutral. 

Am I (Chris) working under a false assumption of something similar in your 
world?

{\bf Alex }
You are not working under any incorrect theory\- but remember\- both the 
real world and mine are more complicated than the level of complexity of 
simple postulates can explain. The elements have more complex interactions 
than simple polarity to one another\- and Morphus' elemental lore isn't 
quite high enough to warrant extremely detailed knowledge.

{\bf Chris} 
I realize that I might know enough, but I was wondering if Chris had a 
definite misunderstanding of how this relationship was implemented in 
your world. One of the times when the character should know what he 
is doing even when the player does not.

Which, in His opinion, would be more stable a staff with light and dark 
or a purified staff with more controls on the elements therein now?

{\bf Alex }
A purified staff with more controls would be more stable\dots 
elemental oppositiion has to be very carefully maintained\- if 
the balance gets skewed one side or the other the item becomes 
dangerous and begins to go more over to the dominant side.

{\bf Chris} 
Does he think the likelyhood to be small for spontaneous detonation or 
detonation during use? Or is that what he is refering to by 
"re\-enforcing the elements that are in it now"?

{\bf Alex }
Yes\- the chance of spontaneous detonation is VERY small! The Vordach 
was refering to purifying and putting more controls on the elements 
therein now\- it would make the staff more stable. But remember, Chris, you 
are hearing THE VORDACH'S OPINIONS\- he may not be correct.

{\bf Chris} 
What is his opinion of its capability to "defend" itself because it 
will contain part of the forces that might be directed against it and 
thereby able to shunt or absorb some of the corresponding power?

{\bf Alex }
Can be true but requires precise balancing.

{\bf Chris} 
What about enchanting the staff such that any power cast 
(by something other than my pattern and not willingly accepted by me) 
within my pattern's aura, be shaped and stored in the staff? with a 
certain amount being used up in 
overhead (shaping and storing) and a limit on what it could handle 
"at one time" based on it's current energy level. 

It would serve the same purpose to me as would my original suggestion and 
would not have the negative powers bound to it. Seem's to have less 
drawbacks too, so I might need to think of some balances.

{\bf Alex }
Ummm.. that is POSSIBLE. You will make a lot of enemies from mages! 
You are talking about sucking constantly at Mordanith's power! It is possible 
though if that is what you really want\dots. Mordanith could probably design 
a Ward that could stop the effect with a Trigger attached so you could turn 
off the Ward.

{\bf Chris} 
Meaning that when I trigger the staff it allows a spell to be cast within 
its aura without affecting said spell? I like that. I would prefer that 
absorption be the default and this would enable me to have that 
without pissing off my non\-aggressive mage encounters.

Jim

(in reference to Chris Alex Chris above)
The idea is very bad in my mind. I think that you should instead set up 
a Morphus initiated draw of power. Morphus links to the staff add 
performs what ever magery he is going to do without using his own fmen. 
It would instead use the surrounding areas ambient energies.

This is better because it

1)	Is less likely to cause Mordanith to mangle the staff in a fit of Faer\-Han
annoyance at the damn thing screwing up his rituals or off\-hand sorceries and
maybe even Catbird's shifting. 

2)	If the link is passive enough and you make it somewhat like a mana diode you
can have it absorb when you are casting and using it without overload. 

I honestly think that you are not perhaps approaching the design of the staff 
from the right perspective. 

What is your main goal for the staffs usage ?

{\bf Chris} 
I'm not quite sure what Mochel is suggesting here(below), but 
it looks interesting. What do you think Alex?

{\bf Chris} 
a)	It is me and I am it. Until I learn enough to disassociate myself of it, 
I have to care for it as much as I care for myself.

b)	enchanted in such away that it can take care of itself, preferably on a 
sliding scale energy level that starts out low and increases over time. 
The primary reason for this being that over time my opponents power will 
increase.

c)	Focus for casting

d)	The same enchantment for b) should probably handle taking care of 
me at the same time since I will never be willingly out of Aura's range of 
it.

{\bf Jim}
To Cover just the details above why not just create it as an alter ego. 
Imbue it with power derived from the grove. In other words, create a symbiotic 
magical construct with little inherent SCF but high MEN and Magical Defense.
By linking to it you can add your SCF to its MEN and crank. In addition, 
make it trainable. In certain basic skills so that it can augment your skills 
as a secondary caster would. I am sure that this would create an interesting 
psuedo\-morphus\-personality "binary Image" that could grow slightly 
differently than Morphus himself. It could be given personality, 
thus entertaining the GM, and basic dictums about caring for you as 
you care for it.

{\bf Chris} 
e)	My original concept at the time of creation was one of theme rather than 
utility.

I wanted a staff that would embody the magics that seemed to be growing more
important to Morphus \- the elementals. A staff composed of all ten of the
Elements of the world seemed to be an interesting and Unique concept. Many
characters have magic items that others know them by, this would be Morphus's
trademark, just as his old friend Falstaff has always been known in the
"industry" by his white staff.

f)	I am not against utility however. Morphus needs his own version of your spell
batteries, ie some non\-environment dependent power source. It could act as a
sanctuary for my soul (it does have my pattern). Or a gateway to places that
have tree clones growing there or planes associated with the powers in the staff.
I'm still thinking, looking for suggestions. Who knows, maybe a magical version
of a swiss army knife.

{\bf Jim}
I am rarely in favor of environment drawing power sources except at the 
lowest level of energy. Instead, either let it gain and lose MEN 
the way we do. Or let it gain it through concious absorption of hostile 
or neutral magic. whether it be at your concious control or its, 
just be sure that there is little chance of it absorbing Mordanith's workings. 
You do not want to see a pissed Faer\-Han. (Not that I could do much to you but 
I can make life very miserably. ) Repercussions on the Catbird and Erithmaen 
front have to be watched very carefully also. Catbird is very nervous as is, 
be very careful about random magics else you may wake up to the little dear 
slitting your throat. I am not saying it is likely but it is within the realm 
of possibilty. 

Remember that two thirds of survival is knowing who your friends are 
so try not to make the rest of the characters nervous.

{\bf Chris} 
Did I learn my pattern enough(while creating my staff) to use my pattern 
itself as my focus?

{\bf Alex }	
No.

{\bf Chris} 
What are the MODs for Salteration (the one I'm doing to prevent scarring)?

{\bf Alex }	
Normal mods\dots. for Salter shape.

{\bf Chris} 
I will describe some of the spells that I have cast. What are some of the 
Vordachs favorite Air spells? Light spells? Conjuration spells? 
Abjuration spells? Would it be possible to go over any of them 
to the point where I would have enough info to make an attempt at casting it? 
I will gladly share with it anything it cares to know and that I can teach.

{\bf Alex }	
It won't say much\dots but he may have given you small clues.
No data now\dots it is sitting in the library with your books.

{\bf Chris} 
What do I remember of My master? Of druids I have known? Of the title 
Earth Lord? Of the small, bent man sitting in the sand at my feet?

{\bf Alex }	
Nothing. Little\dots in play maybe I give you more. Earth lord\- 
that's YOU! That was ONE of your masters at your feet\dots.

{\bf Chris} 
What was the relationship between that man and Kheldar?

{\bf Alex }	
He was a teacher.

{\bf Chris} What was his name?

{\bf Alex }	
You can't remember

{\bf Chris}
Who is/was Miriel?

{\bf Alex }	
A student of the man at the beach. She learned to Dreamwalk with you. 
Later\- much later\- you would be lovers. You can almost see her face!

{\bf Chris}
What did he tell me about the Kerestaen?

{\bf Alex }	
You can't remember\dots

{\bf Chris}
What do I remember of a heavy bronze ring on my left hand?

{\bf Alex }	
It was a seal to something\dots.. it was a ring of power as well\dots
it was a gift from a King or Lord or Prince or somesuch. In it is 
bound something powerful\dots. the ring is bound to you\dots 
it is a legendary ring\dots

{\bf Chris}
Does the Vordach know anything about a heavy bronze ring, a seal to 
something\dots..a ring of power as well.. a gift from a King or Lord 
or Prince or somesuch. In it is bound something powerful\dots. 
the ring is bound to someone\dots it is a legendary ring\dots=> if yes 
who was it bound to?

Morphus wanted to know if the Vordach
a) new anything about the ring
b) new anything about the owner \-\-> Like maybe his full name?

{\bf Alex }
No. No.

{\bf Chris}
Can I recall where that place, that tower(?) was? or what the scroll 
was that I was working on?

{\bf Alex }	
The Tower of ForTal on the edge of the Wasted Lands north of the 
Bay of Sargon\dots.. You were working on a scroll of shaping to 
repair a breach in the Wall of Thelaya.

{\bf Chris}
Does the Vordach or Me know anything (history etc) of	The Tower of ForTal 
on the edge of the Wasted Lands north of the Bay of Sargon\dots..?
How about the Wall of Thelaya and the breaching of the Wall?

{\bf Alex }
NO. No. The Vordack can tell you that the Tower of ForTal is one of the 
Bastions of the RING. It is one of the power nodes that sit on the 
outside of the wasted lands along the Wall of Thelaya. 
It is run down and not often visited now. The wall was breached most seriously 
in recent times about three years ago when 
Prince Keliet\-ah\-Ventir was slain while fighting a goblin horde advancing 
into the World. In that battle a Lord Paladin of Heimdell, Duke Mallard, 
was slain by No\-Rennan(dark God of Darkness and CHaos and Evil), 
and Arioch slew an Avatar of Arken(God of Death) as it was forming. 
Many goblins slipped over the wall and raided the Elvish lands.

{\bf Chris}
Does he know how many lines are at that node? (Tower of ForTal)

{\bf Alex }
No.

{\bf Chris}
Does he know how many Lord Paladin's of Heimdell there are at one time?

{\bf Alex }	
The pertinant numbers are three per aspect, with three aspects. The Vordack 
cannot explain aspects to you. Technically there are only three Lord Paladins 
at any one time\dots 

{\bf Chris}
What do I know about the RING?

{\bf Alex }	
The RING is an organization you belong to. There are druids involved\dots and 
it involves the Mother\dots 

{\bf Chris}
What does 'fairy tale existence' mean in the descriptions in the 
Book of Answers?

{\bf Alex }
Eastern Dau\-Shao is a land of unicorns, elves, faerie and dragons. The 
princedoms are ruled in peace(for the most part) and you have enchanted 
woods, ancient wizards, and holy places\dots.. that's why. 
(Morphus also knows it is a very high Will area\dots magic is easier 
there. Dau\-Shao is approx. 500\-800 miles north of present 
Position. Hetasian\-Dorian border.

{\bf Alex }	
The DAHR HAN are not your friends. You don't remeber anything about them 
but respecting and fearing their power levels, and thinking of them as 
bitter eenemies. The TREEVHAN are more commonly known as Wood elves. They are 
small, low INT, tree dwelling elves. Often live in barbaric conditions without 
much civilization\dots.

{\bf Chris}
rock children and light elementals are they intelligent? friendly to humans?

{\bf Alex }	
Intelligent sort of, and not really. Rock children have been known to be 
friendly to humans\dots light elementals don't often notice humans but they 
are friendly when they do.

{\bf Chris}
Cetaneans

{\bf Alex }	
SCUM\dots.. the Cetaneans are a sub\-group of the Tolnian racial block which 
includes Tolnians, Pentarens, and Cetaneans. The Hetasian and Maeran people 
have elements of the Tolnian racial stock in them as well.
They are typically found on the eastern coast of the continent on the coast. 
They are organized in city\-states, poli, and they are run by a 
representational government. Their are strong alliances between the poli\dots 
unlike their northern neighbors the Pentarens who are constantly having infighting 
amongst the poli(which are feudally run by hereditary and challenge based 
nobiltiy that ride winged horses\dots.)

{\bf Chris}
Hetasia

{\bf Alex }	
Hetasia refers to a land or a people. They exist in the free states and to 
the South. they are a dark small people(they look like Mexicans). The hetasian 
kingdoms to the far south of Tareth are ruled by the Wizard\-King. if 
you want more details see me in person or ask me again when I have more time.

{\bf Chris}
What information is available on the worship practices of the people in the Wizard\-Kings area? Political structure? Mercantile structure? Academic structure? Mage Hierarchy and practices? Feelings towards outsiders? I don't need this information until after Jarek is taken care of, but I thought that I would ask now to start gathering information.

{\bf Chris}
Kymri

{\bf Alex }	
They are a Celtic people, clan oriented that live to the north of the feudals. 
They are ruled by chieftains, druids, and bards. North of north of Dau\-Shao. 
Dwarves are north of north of Kymri.

{\bf Chris}
Na\-Kor

{\bf Alex }	
The Na\-Kor are a race of half elves who fought against the Golden Empire. They 
were reknown for their efficiencey and fighting talent. They were ruthless hunted 
down by witch hunters thousands of years ago\dots few remain. But those that 
do are champions of the cause aginst the domination of human kind. They are 
feared by those ignorant of their true cause.

{\bf Chris}
Symbian

{\bf Alex }	
Rune system\dots long story.. no time to explain\dots it is not worth pursuing 
right now\dots when we have some time Chris, and are sitting around I will tell 
you the story\dots

{\bf Chris}
Kisstan \& Multath

{\bf Alex }	
From the epoch before this one \dots.. used by beings before their were any 
men.

{\bf Chris}
Arkenian

{\bf Alex }	
From about 2000 years ago the language spoken by the people from whom Vardigan 
is descended\dots.. the language of the magic of death and life. The rune language, 
its written form is used for most wizardries involving life and death.

{\bf Chris}
Estarren

{\bf Alex }	
No time now. Is an old Tolnian /Dorian language from a 1000 years ago\dots\dots\
dots spoken by Madra

{\bf Chris}
Madra

{\bf Alex }	
Now worshipped as the Mother. Responsible for Schools of LIFE, NATURE, Possibly 
WATER and others. Period approx. 1500 years ago. Her teacher was from (last 
of?) another epoch.

{\bf Chris}
relationships between Madra \& Wizard King \& Madra's Teacher

{\bf Alex }	
No new data. It is believed Madra may have taught the Wizard King in his youth
\dots.

{\bf Chris}
Tolnia
RE Language of Necromancy
QUERY Relationship to Estarren/Madra; Relationship to Hetasia/Wizard King

{\bf Alex }	
My roman culture. Tolnia Wizard King was born in Tolnia. He was an alchemist. 

{\bf Chris}
Bodak rune language's source?

{\bf Alex }	
Hell. Rune language\dots.. not sure with out looking in my notes at home\dots

{\bf Chris}
Language/Runes/Color for the following schools which I currently have rank in

\begin{verbatim}
School		R				L				Color
Shaping		RTolnedron		LMultath			Yellow/Blue
Binding		R				L				Yellow/Red
Prophesy	RTolnedron		LDau\-Shao		Light Blue
Lssr Summoning		RBodak			LAncient Dorian		Gold
Geomancy	RAncient Korvanir	LAncient Dorian		Earth
\end{verbatim}

{\bf Alex }
Give me time about runes and languages. 

{\bf Chris}
trees (can) embody Nature, Life, and Light, what physical things or materials
embody Decay, Death, and Dark? disease fungus birds obsidian =>dark 
bronze =>dark, silver=>light

Can you give me some examples of elemental sight? Use Earth sight for detect 
Jade. Tag sight geomagically

Things I've heard The Orb of abjuration is in Thariden (sp?) it is 
huge and  very powerful. It is under the control of the Godking. 
There are 117 artifacts ? 30 stones, ? 25 swords, ?20 staffs. The 
stones were created by a Thaumaturge  named Halga (sp?) 


{\bf jim} What are the gates of Chronos

They are a series of patterns created by several beings in 
conjuncture, including Labalas Eneroth, Avatar of Correllan and Time 
Lord.  You don't know all that much about them.

{\bf jim}
 Is it possible that Catbird is unconciously using the Gates of Chronos?

Anything is possible \dots but no, it is very unlikely.  She might be 
managing to slip through the Gates and not be stopped by them.  They 
as much ward time and space as control it.

{\bf jim}
 What do I know about the Book of WInds ?

It is written by one of the first elves!  It is said one the Elder 
Ten wrote its first five chapters called the Five Songs of the Winds. 
 It contains a preface that is said to be 876 pages long, and 
supposed to reveal the purpose of elven creation.  Your father has 
didainfully shot down this rumor saying that the preface only hints 
at vague prophesies concerning the purpose of the elves... dozens of 
authors over millenium have added to it....

{\bf jim}
Does Mordanith know what a Greater Dark is ?

Yes.  It is one of the highest, and most powerful form of 
elemental darkness known.  They are not all that bright and very reactive-
they haed for the nearest, brightest light source and try to destroy
it.  What makes them scary is their power- average power- 3000 -5000
points of darkness; average size- 200 meters high!

{\bf jim}
What do the Kerestaen ward or watch for ?

You have heard that they ward and watch for the blance of humanities 
power and the powers of darkness to make sure that neither side 
overpowers the  other.  You think there is more to it than that but 
it is a well-kept secret. 

{\bf jim}
 Concentrating on Kheldar/Morphus's history for a second. 

>It is unlikely, in my mind, that Kheldar and his group have made 
>no impression on history. With all I know ofhis master, his endeavors and
>their locations, his companions, and his skills. Can I get a good fix 
>on his Historical Niche ?

Your sense of human history isn't all that it could be.  You think he 
and his friends have NOT had a major impact on the Elves.  You think 
Falstaff and he date back to the pre-Purge days of  over 500 years 
ago, but probably after the founding of Marden 1800 years ago.  I am 
not exactly sure what you mean by this so please ask more 
specifically.  Falstaff and he belong to a group of mages known 
historically as the Grey Wanderers.  They were NOT specifically 
Abjurationists, but most were, and they fought against the forces of 
Death and Chaos... they did not always fight with the Elves.  These 
men had ambiguous morals, and goals, they entered an area, wreaked 
their changes, and then left again.  It is they, and the group of 
individuals  called the RING that made the Wall of Thelaya.  They had 
a leader who was known as the  BLADE OF STONE that, it is believed, 
may have caused the Mage Purge by assassinating  a Death Lord that 
had taken a country from a weak King.  The Death Knight was a  
creature of darkness and great power but the evil of the purge may 
have done more  damage.  By slaying the Death Lord the Blade of Stone 
released one hundred  Faer-Han that were trapped by the Black Cloud's 
wizards, and he broke the hold Death was gaining on the entrances to 
Faerie.  It also had major effects on the prime Material but you 
never studied that.   

It is a historical hot subject as to whether or not that was just an  
inevitable spark in the power pool, or did the BLADE OF STONE truly 
not care about the consequences of his actions.  

{\bf jim}
When was the breach that Morphus was repairing ?

Unknown.

{\bf jim}
What is the RING ? 

The RING is a group of humans who have achieved a very high state of 
order  and are bound to the force of nature.   Despite this they 
serve a balance between  Decay and DEath and Life and Nature.  They 
are pro-world, possibly linked to the  Kerestaen.  There are many 
historical links between the RING and the Grey Wanderers. 

{\bf jim}
Is it possible that the secondary ward placed on Morphus is 
will magic ?

Yes.  It is also Abjurational - Warding mucho grande.


{\bf jim}
Do I remember any mention of Falstaff saving Tyriontill  from a raver

Yes.  One of the Grey Wanderers- Known as the White Mage- fought the  
Air Raver Oleanth who tried to link to Tyriontill and absorb him.  
The White Mage is said to be a Binder and a Willworker of some Power. 
  
The White Mage and The Blade of Stone were said to often be at odds.  
The  Ice Wolf and the Stormlord were other Grey Wanderers that were 
rumored or storied to interact with the elves.

{\bf jim}
Now that I know which Vordak this is (Guards the Gates of Chronos, 
He who brought the Book of Winds back, etc..) can I figure out who 
else has summoned him ?

Not a chance.  Your lore of the Vordock is much to small.  This 
is a BIG, and super unusually, powerful Vordock.  You think your 
summoning probably  should not have called one so powerful.


{\bf jim}
How easily cold the Vordak have mistaken Morphus's pattern for that of
a dragon ?

Unlikely.  You think Morphus' mind doesn't look anything like a Dragon's.


{\bf jim}
I get the impression that Kheldar may have done something to help
initiate the original purge. Do I remember the names of any of those who
did so ? Wh may have performed some heedless action and endangered or
killed others ?

Yes.  The Ice Wolf is said to havehad something to do with the 
orignal purge  but it was primarily, according to conservative elven 
scholars, the Blade of Stone that caused the Purge.  Others argue the 
"it was inevitable, and the Grey Wanderers did  what they had to" 
argument.   

The Lord of The Dorian Empire Chepu Akanasi was the first major Lord 
to declear Purge.  The rest of the human world quickly followed suit. 
It happened fast- irrationally fast!  It was probably aided by 
external forces but noone knows who. 

{\bf jim}
By Morpus's past memories I can guessthat Morphus has been keyed  to 
Abjuration in the Human manner. Is it possible that he has 
incorporated that key into himself ? 
  
Yes.  It seems almost certain that he has been keyed.  It is also 
possible,  though less so that he incorporated the Key into himself.

{\bf jim}
Is there any quiet way for me to contact Lord Carolyn of the High 
Elves? Does he  accept messages from Itinerate Wizards ?

Pray. Not usually!  A priest of Labelas is a likelier bet if you 
still wanted to contact a higher up.

{\bf jim}
How does one break the connection between a Greater Dark and the  
Dark Mage controlling it ? Does the Sunbane have any effect on 
Greater Dark ?

Kill the Dark Mage.  Destroy the material pattern of the 
control(there will always be one).  Shape it out of existence.  Tear 
it up with a power attack. 	Yes, the sunbane effects them but they 
are so strong they can fight it. 

{\bf jim}
Can a greater Death dodamge  to a FaerHan-Quenyan hald breed ?

Only physical damage. Its illusions and enchantments would be at 
half effective against you, and its death attacks would not work.  

{\bf jim}
Is there enough left to Tyriontil to communicate with ? 

Yes and no.  There can be slow translated communication.  There are 
experts  at that process.

{\bf jim}
The stone of fire is a prophetic allusion, does it refer to the 
Fire Mountain ?

What reference have you had the stone of fire?  Please tell me where 
you are coming from?

{\bf jim}
What were the causes that triggered the purge ?

See above.  Way above.

{\bf jim}
What is destroying the Linking Ward in the Hall of kings ? Is it 
likely that this only one of severallinking wards ? 

Hard to say.  Hard to say.  There are probably other linking wards.


