\documentstyle{report}

\hbadness=10000                 % do not want underfull box messages
\hfuzz=\maxdimen                % no overfull box messages either
\topmargin=-.2in
\oddsidemargin=-.2in
\evensidemargin=-.2in
\textheight=9in                 % and are long
\textwidth=6.4in                % pages have very wide text
\marginparsep=.3in
\marginparwidth=.5in

\begin{document}

\title{{\huge Shape-Shifteren}}
\author{JSM,CC,POOKY,JSS,SPR}

\maketitle

\part{Our History}

\chapter{Our Travels}

\begin{description}

	\item[11]{\em Mordanith}
	Mordanith meets the Orange Mage

	\item[14]{\em Mordanith}
	Applied via the Orange Mage for Theriden Imperial Research 
	grant involving the use of the Orb of Abjuration

	\item[15]{\em Mordanith}
	Mordanith patterns to thespesian and the Temple of Usul there.
	He studies in the library there until day 122

	\item[122]{\em Mordanith}
	Creates a mage battery of type 1:50 pts and then 
	goes to talk to Drell(Said to be Healer,thief, and Warrior )

	\item[123]{\em Mordanith}
	Conjured by Narene to Marden. Met with some Dock Workers

	\item[124]{\em Mordanith}
	Get a job as a scribe at 2 sp/day get lodging for 3 sp/wk

	\item[144]{\em Mordanith}
	Having collected near enough money to join the mage's guild
	Mordanith decides to talk to the guild members. 
	He talks to the Orange Mage regarding his application to use the
	orb of Abjuration and learns of the Abjuration Phobia of the area. 
	He learns of the Dissenta - a set of southern ritual mages 
	He learns of the Black Cloud Assassins - who may still have
	contracts out for Abjurationists.
	He learns that in Tolnia - Abjuration is a death sentence 
	The Orange Mage gives Mordanith a gold coin in order that
	mordanith may join the guild as a first class member. In 
	exchange he wants to receive information over the next several 
	months. The Orange Mage says that he is one of the nine Elders.
	Taj Med. The Cost of guild membership is  1 pence per week or 
	1/20th share per week. Guild duties consist of 
	\begin{enumerate}
		\item Dues
		\item 3 Weeks Service
		\item Meetings 1/month
	\end{enumerate}

	I meet with a student who is interested in learning the Tolnidren 
	Runes.

	Note that the following colleges require Tolnidren runes:
	Abjuration, Alteration, Enchantment, Healing, Divination, 
	Illusion, Air.

	\item[145]{\em Mordanith}

	Mordanith meets Raven AKA Raven. I Receive a note from a
	friend in the mages guild that indicates that their may be a
	mage of interest in the Inn of the 3 Moons. We head to visit 
	that Inn. We encounter a press gang. We frighten them off with
	a brief show of magery ( and some shapechanging). We pass by 
	the usual city sights such a human beating another human. We 
	leave them alone to their entertainments.

	\begin{quote}
	Scene Inn of the 3 Moons. 10' Ceiling, 5 lamps, smokey, 4 tables, 
	3 booths, small bar, bartender\-rose tattoo on forehead, dual 
	tulwars. Morphus is seated here.
	\end{quote}

	I meet with the elderly mage who calls himself Morphus. We are 
	joined by a older human who calls himself Zacalatar of the 
	Bright One . He inquires as to whether we are mages and what 
	we are planning. He claims that the Bright One is a patron 
	of mages. Later it was disclosed to Mordanith that the person
	was a cleric of Loki. We are recruited by a Bengali mercenary 
	to help as guards for a caravan to excavate a forbidden city
	and when we meet with a human about the jobs Morphus is challenged 
	to prove that he is a mage. Morphus blows a brazier to kingdom come 
	and we are asked to market our skills elsewhere.     

	We return to the Inn but Mordanith returns to the Bazaar and
	convinces the human who hires for the caravan that he would do
	well to hire us all. He consents to take us back but Morphus is 
	my responsibility ( Though they will feed him ). 
	When mordanith returns to the Inn of the 3 Moons he is accosted 
	by a dwarf. The dwarf challenges Mordanith to a single combat. 
	Mordanith returns to the Inn for witnesses. The two face off outside
	the inn and Mordanith blasts the Dwarf a 80 point Psi Blast.
	The dwarf staggers and attacks Mordanith. Mordanith dodges but 
	is also attacked by several of the dwarves' companions. Mordanith 
	survives, thanks in great part to his companions and a critical 
	matter blast against the axe handle of one the his attackers. The 
	blast vaporizes the haft of the axe.

	Booty Collected
    \begin{enumerate}
		\item A Gold meddallion with a black circle and inset red claw.
		\item 5 Gold Pieces
		\item 5 bones. Long for finger bones.
		\item The dwarfs armour.
	\end{enumerate}

	We collect the weapons and booty from the bodies after waiting in vain
	for some sort of city guard. Mordanith, Morphus, the Volga Dogman, 
	his dog, and Raven head back and get instructions regarding where we are
	going and why. 

	We are to head 30 miles SW from Marden to a the Burghers road. We 
	are to travel 20 miles down this road to a town called Grozz's
	End. It should be a small village. There should be a small church 
	of Hercules. There, we will talk with the priest and then investigate 
	the rumour that there is a new buried city. We will be supplied 
	with expenses. We are given 1 Gold and 16 sp up front.

	\item[145]{\em Morphus}

	An Elf walks in and introduces himself as Mordanith Etc. A man 
	past middle age joins us and says he is Zacalatar of the Bright 
	One. He asks if we are mages and whether we have plans. He claims 
	that the Bright One is a patron of mages.  

	So What?

	We move about Marden, inquire about a buried city (Zakatlin?) 
	we've heard  about. We go to Narvi, a caravan master, for employment 
	and possibly some interesting information at the end of the trip. I
	attempt to show him my worth by lighting his brazier. Unfortunately, 
	Mordanith helps me and we both critical. We obliterate the brazier. 
	Narvi sends us packing. We go back to the Inn but Mordanith returns 
    gets us back in good graces, and convinces Narvi to hire us, \dots er 
    well, him, and I get to come along, food but no pay. 

    When Mordanith comes back, he calls us to be witness' at a duel. The 
    dwarf who challenged him gets blasted, attacks, and when Mordanith 
    dodges, he is attacked by the dwarf's companions. We join in and help 
    and he blows up one of the dwarves axe handles. They either die or 
    scatter. The dwarf and his party were members of the Fire Claw 
    Mercenaries. We retrieve a gold medallion with a black circle and an 
    inset red claw, 5 gold pieces, 5 bones(long finger bones), the 
    dwarf's armour, gold ring, silver necklace. We encounter an old 
    beggar who offers a prophesy. I know I can do better. I challenge him 
    to a prophesy duel. 

	I Prophesy

	\begin{quote}
	Fire, Blood, Gold, Blade
	Beware, the Stone of Fire
	Will lead into damnation
	and for the same reasons.
	Like a cat.
	\end{quote}

	The other Prophesies

	\begin{quote}
	The Purge will return, is coming again.
	\end{quote}

	Mordanith gives silver to both of us. We negotiate for gherka, 
	decide not to get them.

    No guard appears, so we take our booty and get our instructions 
    regarding our trip. We are to head 30 miles SW from Marden, to the 
    Burghers road. Travel 20 miles down this road to a small village 
    called Grozz's End. We are to find the Church of Hercules, speak to 
    the priest, and investigate the rumor of part of a buried city. Paid 
    on return, 1 gp per two week period. In addition, 1 gp and 16 sp for 
    food and lodging for two weeks on the road. 

	\item[146] {\em Mordanith}
    We go Gurka shopping. We trade a simple warding Cast for a lower 
    price and we head out. We spend the evening camped out and warded 

	\item[146] {\em Morphus}

    We meet Catbird who turns into a cat(?). The temple of Archon gets 
    trashed by a tall gold guy with a black shield. Mordanith interrupts 
    priest of Archon during ethereal travel.

	Mordanith \& Morphus cast a Major Ward with magelocks around the 
	Gherka dealer. Anyone not mageborn cannot open without password. 
	Keyed on dealer and his staff.

	Go to Uncle Toms (weird). He sells everything. Buy equipment, provisions, 
	and clothes.

	\item[148]{\em Morphus}

    The Dullo falls from a great height and breaks. Mordanith BINDs him 
    together, I heal him (Life and Earth magic). He becomes a real rock. 
    We get accosted by  Mage Guild. I get fined for Shaping, is 
    suspended. We exit the city. Red dragon fighting greek god of war 
    over city. 20 miles till we camp. No encounters that night.

	\item[149] {\em Mordanith}
    We travel on and encounter a demon of possession. We deal with 
	one and then send to the city of Marden for a priest of Aurioch 
	to help with the others.

	\item[149]{\em Morphus}

    Great Heal to myself. Met singing Warrior (What a pain in the 
    ass!) in next town. Left real fast. We are attacked by a Major Demon 
    of Possession (Nasty).  We don't do so good, but Mordanith heads into 
    the ether for help. He brings back a Paladin of Arioch. The Paladin 
    Kicks Ass! We learn they travel in threes, so the Paladin goes after 
    one and we say we'll take care of the other. They turn  into some 
    kind of powder(yuc!) 

	We encounter and talk a small creature called a Ringman.

	We go back to the village and meet the singing warrior. The 
	Priest of  Dau Pan welcomes us and we rest. I fail a silence 
	spell and summon air  elementals. The priest dispels the 
	whirlwind and creates an area of  Null Air. I drink a lot, cast a
	telekinesis spell, blow self across  room. Attempt to remove 
	alcohol, end up doubling it, become comatose.  Bandits are 
	approaching on gherka back.   

	Mordanith helps me, uncovers some of my hidden power. I attempt 
	to  Meditate (No Skill of course =>02) and see a swordsman, 
	someone weilding 2  swords, an elven mage wearing green robes; 
	sometime in the past or future I  see a high vaulted room, falcon 
	laid out on alter Creature, big tattered black  robe, black 
	fangs, talons, long black hair, red eyes, pointed ears. Long obsidian 
	 knife, sprinkles red liquid over unconcious bird. He sees me and 
	starts to  move toward me. I back out, go forward, and then 
	dissipate it. Crtitical  Meditate when I try to set up shield for 
	Mordanith. Shield dissapears. I turn  into cardinal (true 
	alteration) fly to ruins, avoid blue mist, break into tower,  
	find Mordanith, Catbird, dark aura, Foresee past Abjuration 
	symbols  on green  robe elf, break down binding on mind, leave 
	weak, release power, attempt to  shape change and shape remaining 
	power to put peg back in. Go unconcious.  Wake up and use points 
	to go astral, flap to Mordanith, use all but 1 POW to heal  
	Mordanith with Light and Air (09 on heal) Must drop back to 
	regular plane. Go  into mage trance to conserve power. 
	Catbird picks me  up in mouth and flys out  of tower. 

	Time passes, the Dullo helps me regain Morphus. I get Mordanith 
	and heal  him. A few days go by, Catbird gets elvish priest, 
	cures Mordanith and does it  in the other priest's church which 
	destroys the priest's wards. We leave  quickly. We ride south. As 
	we set up camp that evening the dogs (jaws and  Dullo) go 
	hunting. The Elf sets up wards. During the night the Falcon spots 
	a  group of glowing eyed  

	Save caravan from Targs.

		1 month along crescent road. Cashon Seek Large Statue 9ft. 6
	arms. Goddess of death. Black. Scimitar and Living  Flame in top 
	hands, Rod 2'x1" carved and bowl in middle hands, bottom hands  
	behind back with kris and empty hand. At the Gate in Caromar 
	Passive evocative power grid detected Casotul
	Full power after encounter with teeth/claw creature (from woman 
	or  grid)(helena blond) blue sphere circling us with pulses 
	returning to it from  grid (shape changed batthing killed earlier 
	had same blue) I draw in full  power, release into grid, overload 
	dot and it blows up. Five person party sighted, two heavy 
	armoured, two light armoured, one black  robed with rune carved 
	staff. Coming from divination direction. I foresee big  
	reptillian hand giving staff to black robe and 2 orcs, M\-U, 
	Martial  Artist. I get it  from behind, blast attacker, not good 
	enough \- I fall unconsious. Time Passes Priest of Hercules 
	comes, Dullo removes "soul wrap", priest heals,  

	I sleep.

	I wake up at Hercules temple.

	I have ambrosia and do Helena again. The ambrosia causes 
	flashbacks. Pass near silver runed arch. I crit vision, 1 mile 
	abjuration, wave encompassed  entire grid=> unbinding, a wizardry 
	older than any I have used. I foresee roof falling in. We begin 
	moving toward pulse source. We enter the hall of Kings. Two 
	guardian statues. One moves as we enter but  stills. Statues 
	inside explode as black eats yellow on pedestals and blue  
	retreats. Two statues move, one leaves immediately the other 
	is  Sigmund. Mordanith casts, Vartigan hits, it shoots blue/green 
	 spiral at Dullo, Mordanith  fails to deflect, I shape to Life 
	(trying for light). Good roll not crit. Dullo  changed into real 
	dog. Morphus possessed and hit by 30 point loss to power.  wake 
	up statue destroyed. Come back to Check statue area and hall of 
	Kings  for  library. (endurance, Storing=> crystal) 

	Possessed by Demon Lord, approx 6000 years old "Altzar", Love of 
	violence,  antipathy to elves, violent temper, contemptuous of 
	humans, frightened of  Mordanith, but try to remain hidden. From 
	Abyss, Sargasso sea of Soul (Black  Hole) from 3rd level(radius) 
	come from another age, before humans. A Lethar  Humans possessed 
	by the Lethar are werewolves and vampires. Lethar are from  realm 
	of death. Shapechangers. Derive sustenance from Life energy. Wants me 
	 to grow in power. 

	Morphus wakes up, feels disoriented. Prisoner leads catbird 
	through gate. I  see flare of power, head towards bamboo "gate", 
	I know dark key word. I urge  Mordanith through. Think there is a
	better chance if I go too. Nethar Plane. We arrive see Cedric's 
	entrails in pentacle. Morphus draws dark  power. Says hello (in 
	Lethar) to black cat shape=>Altzar, Demon Lord of  
	Possession.(lord of Demons of Possession) take 3 gold from 
	catbirds payment. 

	Three weeks prior I speak to Sigmund about mind work, tap 
	Mordaniths head \-  his shield goes up. There is an 
	Altzar\-cation. Telepathy gets knocked back and  forth. He 
	detects me, I stomp off. The kids throw a discus at me, I blow it up. 
	 Catbird yells at me and I attempt to manipulate matter to create 
	a discus  (which I intend to throw into orbit). I fail bigtime. 
	Altzar projects his pattern  into one of the gold coins. The next 
	time it is touched\dots\dots Pookie makes power batteries, draws 
	power diagrams with ease, (was a wizards  familiar 17000 years 
	ago) 

	Sigmund, Mordanith and Myself perform a rite of summoning. 
	Classic success.  Setup for 4 hours, cast at noon, 6 hours of 
	casting and 40\-100 horses (sort of)  show up. Lead by 20 hand 
	high black stallion. I take full notes on the symbols  for my 
	notebook and also write down all that I can remeber about the 
	actual   spell. 

	Mordanith and Morphus link\-> Morphus only makes it because 
	Mordanith does.  We recall the urchins memories, I get too 
	involved. After many memories we  stop and I think that I'm 
	catbird. When Mordanith attempts to snap me out, I  shift to 
	falcon (4 Auras)(Purple power) 

	The Net begins to decay, I am at the city of Kuresh, the 
	abjuration net is  disintegrating. It's much too soon. I must 
	reweave it or I'm doomed. I set off  one of a number of pre\-set 
	reponses (green) and become me again with a  gentle transform. 
	Sigmund is a Guardian \- created by immensely powerful  
	Alterationist\- Evocationist 

	I recall a guardsman of Tantir during a flashback. He is hit by a
	balck arrow  meant for me while I am in the process of 
	strengthing the walls of Marden  during a siege. I am using an 
	Earthstate spell. I make notes when I recover. 7 riders. 
	Something tracking horses? 

	Get scimitared in chest, critical miss foresee. Mordanith heals 
	me. I am still  casting. I stop. I faint. 

	\begin{quote}{\em Vision}
	I am in the hall of the Wizard King, Numedides. It has a
	400'\-500' high ceiling.  Hellish walls, ribcage columns. On a
	throne of human bone sits a small grey  robed, grey gloved, 
	powerful figure. Huge trolls stand on either side of the  throne 
	as well as mages in purple robes. There are others there in black 
	 robes.  A human sacrifice is in progress; I detect life draining 
	magic and Nedron words  of summoning. I am the Arch\-Mage Kheldar 
	and with me is Falstaff, a Master  Conjuror and Evocationist, 
	gold robed and with a white staff. We are here about  the 
	Necromancy Stone. 	
	\end{quote}

	Morphus rides a gelding, 16 hands, black horse with white sock. 
	The horse  from the herd is 19 hands, a pinto with a long 
	mane. The three dryads, at my request, each give me a branch from 
	 their grove,  Helena a birch twig two feet long with yellowish 
	leaves, Deirdre a redwood  twig two feet long heavy brown with 
	heart shaped leaves, M\-\-\-\-\- an oak twig two  feet long with 
	green leaves. 

	\item[---]
    We encounter the temple of hercules

	\item[191]{\em Mordanith}
    Mordaniths current horse is a 16 hands high brown gelding.
    The horse he is heading for is a Mare at 18 Hands.
    The singing warrior is wearing a light brown tunic with metal 
	armor, Cloak, and a longbow.

	\item[192]{\em Mordanith}
    It is the middle of the summer. We start out to the south from 
	the Vale. We head out to see the King Kaleth. We leave the 
	borders of the Vale. and break for lunch. We rest that evening 
	and are attacked by Kresh. We slay one and Dullo scares the rest 
	away. Thus ruining Mordaniths Mage battery ritual. 

	\item[192]{\em Morphus}

    We ride and Dullo appears in horse form. We left the valley, we come 
    to the  Great Crescent road, turn right, ride till twelve, stop at 
    lunch. I am in  considerable pain, slide off back of horse, cold 
    fruit and steaks in pack. Have  trouble remounting. Ride till we see 
    someone in the road, kneeling. Many  weapons. Executioner Arek comes 
    with us. At 500 we arrive at stream. Some  weapons are there. We 
    camp. I attempt to approach pinto after grooming my  horse. I fail. I
    practice staff. Exhausted wake up at night=> Kresh lead shadow wolves

	\item[193]{\em Mordanith}
    We leave the gypsies and travel on

	\item[193]{\em Morphus}
	Nothing specific; Like serrengeti plains; Five days of riding and 
	training 

	\item[198]{\em Mordanith}
    We arrive at the city of Chipewing . We talk to the city militia
    We meet with the diviner Oleander.  She says that Catbird is not 
    a shapechanger. She is not a human. She is three with the same 
	mind but not the same soul.	Oleander states that Catbird should 
	go to the Tower of Temorth in Al Kahar or to the Citadel of the 
	Seven or she can just ask Mordanith Later on during his Quest.

	To Morphus she says . Will stand in the court of Gazadlath when 
	the net may be broken. Sigm,und recognizes that Gazadlath as a 
    chieften mage of a semi-nomadic tribe helping to rebel against 
	the golden empire. She says that Morphus will be there One year 
	and two months from now.

	We look at the things we captured on the road. Card with brand 
	displays and image of a Trellis covered with Vines in a chair. 
	Person with a purple robe, white jaw and black gloves.

	\item[198]{\em Morphus}
    Walled town, Chippawing, no smoke coming from chimneys. There are 
    people. We meet a diviner and she gives me this information and gets 
    a big headache doing it

    "I will stand in the court of Gazad\-Lath when the NET may be 
    removed. Wizard Chieftain of semi\-nomadic tribes to south of Golden 
    Empire. Wild magics hide 1 year 2 months. Vartigan should be there." 

    Sue's card Vines coming up over trellis seat. person in purple robes, 
    hands in  black gloves, hood, white jaw. 

	\item[199]{\em Mordanith}
    The next morning the Dullo summons all the water in the area. All 
	the wine casks are broken and and left with a dry powder. 
	Mordanith discovers that his fine elven wine is now a fine elven 
	powder . 

	We head  out to the south. We travel past and a Butte. The butte 
	houses a monastery full of Orange robed Monks. wE TRAVEL ON AND 
	PASS ANOTHER bUTTE. We stop for lunch. We see a town laid out in 
	front of us. We appear to have been attacked by a flaming bird. A
	fast critical power blast destroys it. We see a town with a
	temple of Dal Pan. The high priest of the temple is Rorik 
	Kambeeleon Tenser of Family Arthel.

	We meet with a General Nasant of the Northern Tactical Command.
    Vartigan wnaders out among the crowd and argues.

	Our target:

	A brazier 3' across, bronze, \( \approx 200 lbs.\) It is being 
	delivered by a Caravan with two wagons with a driver, cook and 
	teamster  crew. 10 warriors with leather jazeraint on gurkas. 4
	adepts for controlling gates. and one alterationist or 
	pysromancer. 2 scouts.

	We meet with the master Diviner Regis Galtoon IV. We mete and we 
	plan, we get info from the diviner, we discuss a great deal.

	Mordanith buys 14 lbs of powdered amber. 

	\item[199]{\em Morphus}
	Finally taking care of Pinto. Dullo summons water (what a
	disaster). Five good sized containers of powdered wine.

	We ride and see white walls on a butte. Monastery, possibly 
	friends of Jarek.  Priest creates flaming bird. A larger flaming 
	bird is blown up by Mordanith. We  ride on and come to Taleth. 

	We meet General Nasant, Northern TAC commander, at the gate. He 
	perceives  a lot about us. He brings us to the temple of Dau Pen. 
	We see swords under  pilgrims robes. Priest casts truth spell and 
	we are asked questions. High  Priest Rorek Cambelian Tensor of 
	the family of Arthelian (Carethon Horses) 5 Mages of the 6th 
	circle in monastery, 6 other monasteries, trained adepts  
	channeling power. Possible task intercept new brazier installation. 

	\begin{verbatim}
	Typical caravan personnel				
	1 brazier 200 lbs. 3 feet across
	10	warriors leather wtih metal, shortbows and light spear
	4	adepts	gate specialists
	2	wagons	brazier, driver, adepts,cook \& teamster, food
	1	Mage Pyromancer or Alterationist or Enchanter
	2	Scouts horseback, Diviner and outriders flaming hand sigil
	\end{verbatim}

	Regis Galtur the IV \- Diviner (I know him?) speaks with 
	Mordanith 

	I speak with Corian the Pyromancer who learned from the Firelords 
	school,  Numeste'. The braziers channel 500 pts at a time, up to 
	2000 pts per hour,  1200 pts per day. Each additional brazier 
	adds a non\-linear amount. The max  is 20 braziers which can 
	provide 40000 pts at any one time. This link is  reversible from 
	either side. From the master others can be destroyed. Others  can 
	be linked to each other. Transport is possible in fire form. Each 
	brazier is  warded against physical damage and a 20 pt ward 
	sealed against magic and the  fey. It requires 3 days to cast A
	ritual of setting, ritual of opening, ritual of  linking, and a
	ritual of permanence. The adepts are thaumaturges, a ritual of  
	closing should deactivate it. Firelord uses them as eyes and 
	mouth.  His temple  is 400' on a side, octagonal in shape, and a
	pillar of flame 600' in the air  coming from it. Corian has 30 
	books on his shelf, one is be Aicroven (sp?) of  the seven 
	towers. 

	see high priest and ask for book from corians shelf after 
	advising that they be  removed from his possession. I make a list 
	of the books written in multath and  get a list of the books 
	written in Hetasion. 

	\item[200] {\em Mordanith}
	We head out. We are confronted by a small mob of
	humans. We bluff them with a bit of flash. They back off. We head 
	on. 

	We are stopped at the gate and we wait for the gatesmen to find 
	out about our status. We are then allowed to travel on. 

	We exit the city. A poor theif tries to steal from us. The poor 
	guy gets his clothes repulsed from him as vartigan beheads him.

	We find a river bed.  Morphus casts a major ritual; and then the 
	falcon sees a group of people in the distnace on the other side of 
	the river bed. vARTIGAN AND THE TWO DOGS GO TO INVESTIGATE., 

	Steam rises from the ground, Morphus does a three hour ritual.
    He brings up out of the ground a 400' long, 50' wide bridge with 
	4' side walls. We see Regis's divination orb above us. We also see a
	summoned creature of Jareks attack the orb. Both disappear.

	Arak and Mordanith both find the horses and return to camp. We 
	leave the region abruptly and head north. 

	\item[200]{\em Morphus}
    We start out at 500 am. The temple guards knock people out of the 
    courtyard to clear our path. 

    Morphus and the party come to a 20' wide gap with a stream at the 
    bottom (10' down). While others decide what to do, Morphus dismounts 
    and begins a spell to create a small bridge of stone. The results are 
    a 50' wide rock bridge, 60 ft high at the center, 400' long, side 
    walls 4' above bridge surface, shallow angle roughened surface. Regis 
    long "sees" us and shields us from the firebird. I add a Rune of 
    direction and a Rune of Penetration to my notes. (I called  
    sigmund Nygold during the casting. My apprentice?) 07 on my memory 
    roll to remember Earth State.

    When the horses return I tell the Pinto that I can't have a mount 
    that runs away. We mount up and ride. We stop and camp. I rub down 
    horse. Night passes. When we wake we travel till sighting plateau and 
    arrive at midday. Sigmund informs us that we have been traveling in 
    old ocean bed. We come upon refugees and pass through them. 

	\item[201] {\em Mordanith}
    We reach the plateau we were siting on.

	\item[201]{\em Morphus}
	Stop and camp, no training

	\item[202]{\em Mordanith}
    We pass some refugees.
    We make it to the valley and the peak. Mordanith sets a ward 
	against scrying.

	\item[202]{\em Morphus}
	We sight men in red \& white livery, we ride toward ridge 
	(north). We arrive at  final plateau at 400 in the afternoon. 
	Mordanith sets divination ward. It gets set off. 

	\item[203]{\em Mordanith}
	We wake up. Mordanith inspects the area area of the ward that has 
	been set off. 

	Dullo changes into a perfect version of the bush he studied at 
	the tempole of hercules. 

	He so perfectly mimicks the bush that he summons up some faery. 
	Mordanith aid s the summoning by granting it power. Morphus 
	takes advantage of the this to grow three trees (Oak, Birch, 
	Redwood) and uses them to produce a staff with three woods.

	Mordanith calls his father and tells him of his travels. 
    Father sends two scrolls , a pouch with 10 platinum wires in it. 
	A message from dad. A silver Holy Symbol, new clothes.

	Meanwhile Vartigan and Catbird go to see what is happening with a
	vulture circling above a point three miles away. 

	They encounter and slay a priest feeling up a dead body. The 
	priest had 2 pals whom they also slay. \dots
    As the second fireball impacts on the grove, Morphus absorbs its 
	power and feeds it to the golden tree. Mordanith , the archer, and 
	Vartigan ride towards the nearest plateau. We ride, we stop, we see a
	fire bird fly overhead. Mordanith casts a power shield over 
	himself. Vartigan heads back towards the grove. 

	\dots We succeed in getting a very good distance away. We ride 
	desparately and then dismount. Mordanith figures that the 
	FireHawk is between 88-60 minutes away. 

	I fail my dismount bu land nicely. When Mordnaith's dignity has 
	recovered He crosses the stream he starts casting at the river's 
	edge. 

	\begin{quotation}
	The summon water spell went something like this : Take out amnber 
	Chanrge Amber, Fill the chalicer with water and dust it with the 
	amber. Roll \dots
	\end{quotation}

	another gap in time \dots

	\item[204]{\em Morphus}

		Sunrise \- Minor interaction, Vartigan puts on full armor, 
	sees  black bird 	Dullo uses many types of magic and transforms 
	into bush.  I plant my three  twigs and prepare to pump Nature, 
	Life, and Light  into my creation (and summon water). They flower 
	(birch has golden  leaves) temperature lowers. Mordanith has 
	opened a door to faire. I have planted in faire. I reclaim three  
	twigs. Mage trance, setup,  wizardry. Hold tree magic back, a
	small spring  appears at each tree.  I link with Sigmund and ask 
	him to wait. Sigmund  access the power  the Ward of Nureyev was 
	created with. Mordaniths father  casts a spell and the trees grow 
	more rapidly. Dullo regains shape but leaves  most of the bush 
	behind. A shooting star impacts, Sigmund channels to  me and  the 
	excess to his power source (sink?), space enclosed with  rock. He 
	 deactivates, but I shape twice and bind it to the rock that  
	Sigmund threw into  the Faire area. I change it into a
	crystalling  form. ( it glows and the trees don't want to be anywhere 
	near the  fire energy.) 7 hours go by. 

	Another fire ball approaches. Isetup for a shape of fire to 
	light. I do so but fail  to channel it to the tree. Good thing, 
	because it takes only a portion of a  potential overdose. 

	All three trees now have the same growth amount. The stone is 
	glowing  brighter, its form more compact. I have used a lot of 
	spell points. I feel that I  am currently at 15 spl points. I
	drop into mage trance and telepath Mordanith.  We will attempt to 
	create a shaping ward to shield against future fireballs.  
	Mordaith says he can't spare the power. I realize that I can't 
	maintain for the  1.5 hours needed to complete the spell. I setup 
	for a last ditch attempt to  finish in minutes. I will need to 
	summon water, shape and bind. I summon  water and shape the stone 
	into an oblate spheroid. I address each tree in turn  and ask for 
	help from its Dryad. I shape the power of faire and my own POW  
	and create the staff, surrounding the stone at the crown. I fail 
	a will power roll  however. I finish my binding. I am onewith all 
	three treesand the staff  (physically one). I manage to seperate 
	the staff from the trees. I draw power  from outside\-from 
	Mordanith\-reach earth and trees and shape earth into the  old 
	form of Morphus. The grove of trees stops growing, with the pool  
	still off\- center, and the bush in the center. Between the trees 
	is an elvish pattern of  transfer.

	Morphus unconcious, Mordanith and Catbird put me on horse. I wake 
	up on  ground, mount and ride. I have 1 POW and 3 HTK. The 
	firebird fans a fire  towards us. We run into a gulley. I try to 
	stop, but the horse goes forward. I  hang on for dear life, 
	realize that the horse won't make it and let go. Magic  grasps 
	me, my staff glows golden, I land softly on the other side. We follow 
	the  gulley. We find Vartigan and he sees the cut on my horse. I
	had put something  on the cuts. The horses leg is starting to 
	swell. I dismount, spread my bedroll,  enter a mage trance and 
	sleep. I wake up to see a dessenta, hobble in back of  him as he 
	and Sigmund fight. When I get in back of him I attempt to stab 
	him  in the back with my staff, miss and as he turns to me, jaws 
	gets  him. I get up  and the singing warrior starts to attack me. 
	( He has been hit by a dessenta  dagger) I hobble to Mordaith, 
	warn him, and slip into mage trance, sleep.  I go back to the 
	horses, mount and mage trance and afeter a while I slip into  
	healing trance. for the four days necessary for the trip back to 
	the  city. 

	\item[208] {\em Mordanith}
	We travel away from the site of the gate dissaster. We 
	encounter an encampment of Dorean military. We try to convince 
	the comander that we have a right to cross the bridge.

	Mordanith AUra bashes the cvommander and we meet a blonde red 
	robed mage with an SCF of \( \approx 18\). The commander is called 
	Draego ,the Padishah of Taleth.

	We travel on.

	\item[208]{\em Morphus} 
	Three uneventful days go by (up to 2 POW). We get up and ride for 
	an hour and  see the bridge and many tents in the distance. We 
	reach the end of the bridge.  I come out of trance. We are 
	greeted suspiciously. The leader is Pragon \-  Padasha of Taleth 
	\- we talk with him. 

	\item[209] {\em Mordanith}
    We head into Taleth. A mage (Necromancer) jumps in front of us 
	and threatens us. Mordanith powershields. Vartigan goes forward 
	to slay the Necromancer in one slash. Mordanith attempts to flush 
	the death magick from the body.

	As Mordanith flushes the Body of death magick the body releases 
	three tendrils of dark power that lash out at mordanith and does 7
	points HTK. Mordanith flushes the body of power and thenn 
	cleanses himself of the Dark power, blinding Catbird, Morphus and 
	the Singing Warrior.

	Catbird shifts into cat and ends up in a tent. She leads 
	Mordanith to this tent and are attacked by an elderly human woman .  
	Mordanith Grapple throws the old woman.

	We ride on and encounter the guard and then head in.

	Dullo gets locked into a small magick storage area. In trying to 
	get out he critically unbinds himself. Mordanith critically saves 
	and thus lives. 

	SHIT HAPPENS

	We have seven days to recover and leave.

	\item[209]{\em Morphus}
	We have been riding through the refugees. Death/Dark is cast from 
	a man in  tattered black. A hedge witch "curses" Dullo, binds him 
	in air form. We start  moving. We enter the city. We enter the 
	stable. We enter the mosque and are  brought to our quarters. I
	KI trance  

	Dullo unbinds his spell, his self, and a good portion of the 
	temple All except  MOrphus and his possessions. Dau Pen 
	intercedes and puts everything  together. All magic items are 
	dead, all evil gone completely. Dullo is gone. All  power is gone 
	from here. Vartigan is healed. The Patriarch gives us 7 days  
	until we must leave the church. We are not kicked out of the kingdom 
	of  Taleth. We Decide to head to see the "Seer" we met back north 
	and then make  plans to destroy Jarek firelord. Morphus will KI 
	trance for 7 days except to  speak to regis about his staff and 
	priests about Dau Pen. 216	We go to the bazaar to buy Mordanith 
	a Magic Cloak(cool) Star night hood to  morning on bottom rim. He 
	gets it for the price of taking the weavers  apprentice with us. 
	They charge Mordanith 20 GP for a Ghurka. We have  trouble in 
	town. We ride.  

	\item[216] {\em Mordanith}
	We go shopping. As we travel out from the temple we are 
	approached by one beggar with some semblance of power. Mordanith 
	gives her 4 silver. We travel on to the bazaar and get some rope. 

	We get two black scarves. 

	We encounter and Talk to a Gaudily dressed will worker who claims 
	to live in the tower of truth.
 
	We encounter a craft magicker of leather goods. (Illania of 
	Kalasan ). (Illania Kaldaer Farlane Karahal ).

	We meet a human Air mage of good skill. He offers an enchanted 
    cloak in exchange for taking his apprentice with us. The 
	apprentice bears the name Erithmaen. With Erithmaen we travel to 
	the north to the small town that contains Oleandar the Diviner.
    We stay overnight and talk to her of prophecy and what may be 
	done for the Grove of Morphus.


	\item[216]{\em Morphus}

	We go to the bazaar to buy Mordanith a Magic Cloak(cool) Star 
	 night hood to morning on bottom rim. He gets it for the price of 
 	taking the weavers  apprentice with us. They charge Mordanith 20 GP  
	for a Ghurka. We have trouble in town. We ride.  

	\item[217] {\em Mordanith}
	We travel on. We encounter and pick up Mala, a slave 
	refugee. She is very confused because she keeps referring to 
	Erithmaen as a great one. We travel for 4 days.

	\item[217]{\em Morphus}

	We find a pond on a hill, stop and see an approaching figure 
	singing in fuedal  Marin. Gold robed, white rune carved staff, 
	sword. Names himself  Yosdovan(which in ancient Dau Shao means 
	'white staff'). I name myself  Yosnergen (Staff of three woods). 
	Some of the Runes on his staff are bodak. He  speaks modern Noble 
	Dau Shao. He speaks cat. Tolnedron warding runes on  sheath. 
	Mentions Marden and the Evocation Key. He plane shifts to find 
	info  about Catbird. He says Kalil is dead. The grove will fall 
	in  two weeks and a day. I commune with trees. 

	\item[221] {\em Mordanith}
	Catbird does a search for game. 
    Brown and dark dead grasses with some blue and red flowers 
	growing along a 15-20' wide river. Vartigan wants to bell the 
	bird. Arak cleans the area and we camp. We discuss things with 
	Vartigan. Vartigan and Mordanith exchange insults and slights.
    Vartigan leaves.

	\item[221]{\em Morphus}

	I wake up in Diviners village. A prophesy is mentioned about 2
	mages, the  waking of the dragon, man \& sword

	\item[222]{\em Morphus}

	We leave the town at 300 Pm. We have trouble. Morphus casts a lightning 
	shield and a Bolt of Damnation (Blow hole through attacker and house behind 
	him and wall behind it\dots.) We ride at full speed for 4 hours. We stop and make 
	camp. We bump into Falstaff. 

	We travel for 9 days. We pass a trail, we see a cut in the mountains. Snow 
	everywhere. On day 226 we split with Vartigan (see Morphus and Vartigan 
	document). We prepare for a ritual of summoning. Nothing untoward happens 
	but it gets very cold. We arrive at site.

	\item[228] {\em Mordanith}
	We perform the ritual of summoning for the Vordak. It 
	comes and takes up its duties as hoped. The ritual end s with 
	only Catbird, the singing warrior, and Mordanith in any fit shape to 
	act. We head down the mountain to find shelter. As we are riding 
	across an ice bridge Morphus links to the Grove while it is being 
	destroyed. We are stunned as Morhus is lifted from his saddle  by 
	an explosion and a sheet of flame. His horse is killed. He is 
	very close to a post toastie. Mordanith pours healing power into 
	him while the others find a place to crash.

	Catbird finds a comfortable mage retreat. 

	We train and study for five weeks.

	\item[232]{\em Morphus}
	Greater Summoning Summon Guardian (from Fairy) to shepherd the 
	growth of  the Threefold Wood Qualities of an Ideal Guardian

	\begin{enumerate}
		\item Must be strong enough to guard the Trees, their seedlings, 
		the Dryads, and the other future creatures of the Wood from 
		enemies Material and Magic, from the  Powers of Death, Dark, 
		Decay, and Fire. 

		\item Must be capable of conversing with the inhabitants of 
		the Wood. 

		\item Must be skilled in the nurturing of Trees.

		\item Must be tolerant of visitors so long as they do not 
		harm its charges. 

		\item Must be patient and long lived. (in keeping with trees) 

		\item Must consider my summoning as a great opportunity and 
		take the job of Guardian more because of interest than the 
		summoning. 

		\item Should be able to draw its sustenance and power from Earth, 
		Light, and Nature. 
	\end{enumerate}

	Spell was very successful. A bronze dragon observes our actions 
	and a mage  comes down to clean up our mess afterwords. I write 
	down the patterns and  all the words and movements. I open a
	mental gate to the grove just as it is  getting annihilated. I
	get seriously incinerated. I speak with the Vordach  while 
	unconcious. See "While we rest in Stasis\dots" in Morphus and 
	Vordach	discussion document) 

	\item[264] {\em Mordanith}

	\item[270]{\em Morphus}

	I cast three Life/aterations per day for 7 days and reduce my 
	scarring  dramatically. I have woken up in a cabin. Some sort of 
	mages rest stop. It has  funky controls. I make notes. I practice my 
	language skills with anyone who  will talk with me. A caravan 
	goes  by. My companions invite them to stop for the  night and we 
	will  travel with them the next day. They say that they are  
	followers of  Dau Pen journeying to Kalentorah (a major earth 
	center) There  doctor  treats me. A walker goes by. A creature of 
	Death. They destroy it.   	

	\item[276]{\em Morphus}	

	We set out with me asleep in a sled. I have a nightmare at some 
	point. A  ferthan bird with a decenta arrow in it. Vordach 
	crucified. Amulet with open  scroll with quill on one side and a
	man in robes with sash and crown (marden).  (Old gold coin that 
	the demon was in). I am in the wizard king's hall, the wizrd  
	king is there in black, many decenta with red sashes. In comes  
	Vartigan with a  jet Black scimitar, artifact class, in his hands. He 
	tells me that he will take the decenta and I should take the wizard king.

	\item[283]{\em Morphus}
	When I wake up it is very cold and my scarring is much better

	\item[287]{\em Morphus}
	Still travelling. The Mana level is increasing. We approach a
	circle of big large  stone pillars (12\-13) radius 200', 5 node 
	line crossing, 4 are artificial in some  way. SCF PER, Detect 
	Power, Identify Power 

	This is the highest point where the earth line comes to the 
	surface. It is a  place of earth Summonings, Earth elemtal Lords. 
	An entrance to Kalentorah. I  have spoken with the gold dragon 
	here. The markings are wardings of the  Ring. The pilgrims 
	perform a variant of the ritual of Summon EarthPower. The  last 
	time I was here was the 5th year of the Dragon, 10th Decade of 
	the  orange  time. By the reconning of the people of the 5th 
	outer plane. (Kerestaen).  Todays date is the 24th decade of the 
	orange time. The three moons are  known as the Dragon, the Snake, 
	and the Messenger. An event know as the  waking of the dragon 
	occured 14 days ago. 

	\item[288]{\em Morphus}
	Sigmund carries me into the circle so that I can worship. I
	commune with  earth (non\-magically) and my inner voice tells me 
	to leave. The earth node is  stronger than the last time I was 
	here. We descend to the gate. Someone who  speaks. Faer Han, 
	dorian, Golden Empire, cat, Dao Shao. We see a small  hairless 
	greyed man in a white shift. We stay for a while and then 
	mordanith  says that we have to leave. Sigmund links with the 
	ward  and the little guy goes nuts. He knows me and wants to 
	help me. We leave. (Sigmund is a fortu) 

	\item[288] {\it Mordanith} We make it to the bottom of the cliff.
    Mordanith does a simple foreseeing to determine the next safe 
	location.

	Morphus finds a food cache. He drinks from it. 

	We head left 2.3 miles, turn left to an oasisand continue on to 
	the village.

	We ride into an oasis. There is a Dissenta buried near the oasis.
	
	We encounter Bel, a guide to the desert. He teaches us a few 
	words of the language used in the desert. 

	{\it Ya-D\={e}} means Hello. \\
    {\it Ke-sh\={u}} means Welcome. \\
    {\it Na-V\={e} ben Ku-sar-\={e}} means No Spika da Kusari. \\
    {\it Kol-leer} means Water. \\
	{\it Kaf-fa } means Food. \\
    {\it Na Spa\={e} Dorean} We speak only Dorean.
	\\

	Mordanith does a simple foreseeing for Bel.

	\begin{quote}{\it Foreseeing}
    He will be attacked by several men with long knives  underneath a
	large overhanging stone.
    \end{quote}

	\item[290] {\it Mordanith} After traveling a good portion of the 
	night we come within sight of a small village. On the way we 
	encounter a dark robed individual that is able to dance a dance 
	of {\it Comprehend Languages} that allows us to communicate. 

	We go into the village and trade the villagers horses for 
	mammalian ghurka-like beasts that resemble aircraft carriers 
	{\it (Lotas)} and others that walk upright {\it (LaVitien)}.

	We obtain 1 Ghurka, IIII Lotas, and II LaVitien.

	Mordanith performs a critical foreseeing.

	\begin{quote}{\it Foreseeing} 
    What is the best path for us to take in order to meet with Nadi,
    a guide ?

	Travel South East along the path of living Snakes.
	\end{quote}

	We stay overnight.	

	\item[291] We travel on that morning. We encounter and are 
	attacked by some death and dark individuals in robes near a
	deserted building.

	We counter by drawing on a great deal of earth power from a
	nearby node. We are then attacked by a glowing, flying, godlet 
	who opens fire at us with power that is barely stopped by the 
	wards around Mordanith. Between Mordanith's wards and batteries 
	we seem to be holding him but not much more. When we seem to be 
	bothering him he appears to call for aid. Meanwhile, Sigmund, in 
	stealth mode, moves slowly towards him and sneaks next to him. 

	We are approached by a Firehawk that Erithmaen grants the 
	courtesy of a severe downdraft that brings it into the earth 
	stream (Giant Sand Blast) we have been directing at the Godlet. 
    
    \begin{quote}
    {\huge BOOM ! }
	\end{quote}	

	Sigmund backstabs the imp riding on the godlet's shoulder. 
    Godlet smashes Sigmund to the ground as he gets badly burned by 
	earth power flooding over him from the PASED. Power Amplification 
	by the Stimulated Emmission of Dirt. 
	
    Godlet takes to the air as we extend our PASED to reach over 
	500'. 

	We travel on.

	
\end{description}

\part{The Discussion Between the VorDak and Morphus}

\include{discuss}

\part{The Questions we have asked}

\include{shdata}

\end{document}
