\chapter{Education}

\section{Outline}

The begining character is assumed to have some form of education. The 
education may simply be general life experience or it may be formal 
educational training. 

As a result of this education the character gains 20 points worth of
skills or skill packages. Those skill points may be used to buy basic  
education skills or other basic skills or skill packages.

The initial skills that can be gained by using these points 
are simple educational and cultural skills. As an example,
a formally educated individual may buy a basic education package
that is equivalent to a present day high school education. A
non-formally educated individual could use those same skikll points 
to buy a basic street survival skill package that would alllow him 
the basic skills needed to survive as an independent entrepeneur of 
the streets.

As a result of just living in the environemnt he or she 
grew up in the character automatically gets skills in the lore of 
their own culture, skills in the language, and simple skills 
covering movement in the home environment.

These skills are listed in the table below.

\subsection{Automatically Gained Skills}
\begin{enumerate}
	\item 20 points of basic education skills.
	\item 20 points of skills in written and spoken language.
	\item 20 points of skill in Cultural Lore. Both local and larger scale.
	\item 20 points of skill in Lore:[Tech Index] of Culture.
	\item 15 points of manuevering skills for the native environment
\end{enumerate}

\section{Upper Limit to Skill Rank}

There is a limitation to the highest rank in a skill a character can 
achieve during the process of character generation. This limitation 
is based on the stat basis of the skill and is only applicable to to 
the basic education skills. The limitation to highest 
rank reachable\footnote is based on a 50\% learning roll in that 
skill. In \marginpar{Expand and demystify this} 
other words when spending Experience gained from base education and 
careers the character may not gain any ranks higher than those that 
he has a 50\% chance of getting in an experience roll.\footnote{ ee 
the section describing learning rolls}

A summary of that limitation is presented in table \dots.

% Include the Learning Limitations Table
\input{tcgen3.tex}

\begin{quotation}
As an example. Victor SquareJaw starts with 20 points in basic 
educational skills. He buys the basic education package for a human 
of his culture at rank 4. This costs 10 points because the package 
costs 2 points per rank. Rank 0 = 2 points and each rank thereafter 
costs 2 points. With the remaining 10 points Victor gets rank 9 in 
rhetoric. 

Victor uses his 20 points in language skills to buy rank 9 in 
Language: Written and rank 9 in Language: Spoken. He uses his 
Cultural Lore points to get Cultural Lore: Confederation at rank 9,
Cultural Lore: Planetary at rank 5, and (Because he has always wanted 
to be in the Confederation Spacefleet ) Cultural Lore: Navy at rank 
3.

In addition Victor uses the 20 points in Tech Index to get a
Lore:Tech Index at rank 19. He uses the 15 points in maneuvering 
skill points to buy rank 14 in Maneuver: 1-g Environement. 

this produces a profile like this:
	
	\begin{verbatim}
	Basic Education - 4	
	Spanglish: Written - 9
	Spanglish: Spoken - 9
	Cultural Lore: Confederation - 9
    Cultural Lore: Planetary - 5
    Cultural Lore: Confed Navy - 3
	Lore: Tech Index 12 - 19
    Maneuver: 1-G Environement - 14
	\end{verbatim}

\end{quotation}

Another example details out the creation of a smuggler who has no 
formal education.

\begin{quotation}

Sarah Sirenian starts with 20 points in basic 
educational skills. She buys the basic street survival package for 
her culture at rank 5. This costs 20 points because the package 
costs 3 points per rank. Rank 0 = 3 points and each rank thereafter 
costs 3 points. With the remaining 2 points Sarah gets rank 1 in 
Deception: Verbal. 

She uses her 20 points in language skills to buy rank 4 in 
Spanglish: Written and rank 5 in Spanglish: Spoken. She also buys 
rank 4 in Proximan: Spoken and rank 3 in Alphan: Spoken.

She uses her Cultural Lore points to get Cultural Lore: Confederation at rank 9,
Cultural Lore: Planetary at rank 5, and Cultural Lore: Free Traders at rank 3.

Sarah uses the 20 points in Tech Index to get a
Lore:Tech Index at rank 19. She uses the 15 points in maneuvering 
skill points to buy rank 10 in Maneuver: 1-g Environement and rank 3
in Maneuver: 0-G environment. 

this produces a profile like this:
	
    \begin{verbatim}
	Basic Street Survival - 5	
	Deception: Verbal - 1
	Spanglish: Written - 4
	Spanglish: Spoken - 5
	Cultural Lore: Confederation - 9
    Cultural Lore: Planetary - 5
    Cultural Lore: Free Traders - 3
	Lore: Tech Index 15 - 19
    Maneuver: 1-G Environement - 10
    Maneuver: 0-G Environement - 3
	\end{verbatim}

\end{quotation}

Don't worry if many of the skill names and costs don't make sense 
yet, they will be explained.

% EOF
