The Book of Constructions

Being a compendium of the facts major and minor known about the
planet Ea.(AAA-Yaa) 
 
The Universe:  

     More correctly called the multiverse. There is a large
number of planes related to the plane of interest called the
prime material plane.  

The Solar system:

     The star is a single sun of the white dwarf form. There are
three moons in near circular orbits. None of the moons can
support life. The moons are Litaha,Yrtha,Yamen. 
 
The World of Ea:

     The world itself is a planet with G=1.2 times
that of Sol III. The planet has 60% water coverage with one
large continent and several large islands. The year is 400
days(24 hrs) long with 40 10 day weeks. There are 10 4 week
months.
 
Days:
     Religous    Grey Elven   Human    Dwarfish
 
1    sunday      Primus       Odeen    Guild
2    Ill day     Secundus     Dva      Argens
3    Heal Day    Teras        Tree     Mitras
4    Life day    Kwartus      Shet     Adama
5    Death Day   Pentast      Yach     Cupras
6    God Day     Sextus       Shest    Stibnas
7    Threat Day  Heptan       Sem      Ferrum
8    Peace Day   Octas        Vosem    Nickala
9    Growth Day  Quintus      Devat    Khol
10   Moon Day    Lunast       Desat    Lunan
 
Months:
 
#    Human       Elvish       HOLIDAYS
1    KAT         BEAST        Day  Holiday
2    HAWK        SIGHT         
3    WHALE       STRENGTH     075  Prophets day, Odins Birth
4    UNICORN     SAFETY       090  Spring'scoming
5    BEAR        WILL         123  All Hallowed Day
6    WOLF        CUNNING      154  Lycan's end
7    PEGASI      FREEDOM      231  Night's ending ( Dwarvish Elvish Pact)
8    GRIFFON     SCENT        200  Midsummers eve
9    RAT         FEAR         281  Harvest Day
10   SPHINX/OWL  WISDOM

.bp
Moons Cycles: 
     See Figure
 
Two Moon Eclipses:        Three moon Eclipses:
____________________________________________________________
Day 275 every 26 years     day 171 every 108 years
 
     1422                  781
     1448                  |
     1474                  1429
 
The Continent: 
     This is a fairly young planet. The mountains are very young
and fairly sharp. The crust is fairly well defined in its metal
bearing regions.  
     The south western area of the continent has many hot water
geysers of a fairly violent nature. Along with these geysers and
springs comes a wealth of mineral salts and heat based
ores(cinnabar and copper sulfide). There are some earthquakes
here though they are rare and of low damage potential. 
     To the north lies an area of some limited volcanic
activity. The Valtier ranges has several active volcanoes as
does Osterland,Temoroth,and the Kaylins. The mountains of Isig
have only residual activity of this sort. The southern Dwarvish
ranges are almost devoid of volcanism . 
     The Northern most areas beyond the Isig range and east are
without any real mineral wealth. Yet there are many coal and
water based gemstones(amber) to be found here. 
 
The Climates:
     The northern most area are artic tundra. The areas of
Osterland and Temoroth are similiar to Denmark and Finland.
Felice and Canias display a climate closer to the northern coast
of Ireland. The belt of land between Meremont and the Kaylins
are identical to the North American continent. The Shir has a
climate like that of the Pacific Northwest. 
     Below the Kaylins the clime warms considerably. The plains
are large semi-arid and windy. The San-Sir area is even drier
and warmer. Below the dry and Tough Dwarvish mountains the land
becomes a full fledged and vicious desert with only the western
coast having any respite from the high heats and dry Sirriccos
or Hershinas of the Kasan. 

The Wildlife:
     The powers of natural mana are strong and because of this
it is unlikely that any of the fantastical creatures of the land
will become extinct. Dragons and Their ilk are unlikely to be
pushed out by anything as puny as man. The area of the Kaylins
are a place where an armed dwarf walks warily.
     The woods of Elhayns deep, fully consecrated in 200-1443 ,
are a perfect refuge for many of the more scarce faery folk. 
     The plant life and woods of Ea are best covered elsewhere.
.bp
The Races of Ea:
 
     The races of Ea are somewhat LESS varied than those of the
standard AD&D World . 

	Humans-PC
	Centaurs-PC
	Gnomes-Rare-PC
	Dwarves-PC
	Uru-Very Rare
	Sulimane-Ghost Riders-Rare
	Gray Elves-Niramaa-Rare-PC
	High Elves And Wood Elves-PC
	Drow-Very Rare-Pc(Only Drow Of The Silver Lives)
	Halflings-PC
	Shapechangers-Hengeyokai-Pc-Rare-(5%)
	Half Elves:Half Orcs
	Val-Tier-Rare-Only Barbarians-PC
	Silkie


The Val-Tier:
	The Average HT is 8' plus or minus 11". The average weight is
260 lbs. They are a fairly dark skinned (copper to bronze) race
with light blonde hair. 7% of all women are platinum blonde(
Y-linked ). They have a high resistance to alcohol (DF+1 on all 
EN rolls vs. intoxication ) and are well adapted to heights. 
 
The Grey Elves:
     The Gray elves are a race that is not native to Ea . The
are, on average, 6'2" and 165 Lbs. Their hair varies from Blond
to platinum blond in color. Their eyes go from Violet to Silver.
They gain a +2 MA +1 APP -2 EN 
0 Rank in Longsword
0 Rank in Long Bow 
All Gray Elves are psionic.  

The Sulimane:
     Commonly known as the Ghost Riders. They are a group of
tribesmen from another plane. They are strong and fast +1 PS,+1
MD yet they are adversely affected by the atmosphere(low oxygen)
-2 to EN on this plane. They are black skinned with a high
density low bulk muscalature giving them the appearence of
skeletons. Their eyes flouresce even in the weak ultraviolet of
night. They are almost exclusively night dwellers.

The Uru:
     The Uru are also known as the black dwarves. They fit that
description with their ebony skin and dark brown eyes. They are
strong and tough giving a +1 PS and +1 EN with minimums of
PS:18 and EN:18 and they are much less than charismatic (DF -2
on all persuasion rolls) They average the same in height and
weight as a normal dwarf. 0.1% of all uru have the blue eyes
that mark the born leader of the Uru nation. The Uru have a very
high magic resistance that prevents them from being affected by
or using persona based magic ( ALL mana based rolls are at +/-3)
. Only a druidic magery may directly affect them with spells of
less than 6th level.

High Elves:
     High elves fit the character race description found in the
manual except that high elves gain a +1 AP, -1 EN. They are
light skinned with brown hair and green eyes. some 10% of all
high elves display a set of yellow eyes.
 
Wood Elves :
     Wood elves gain a +1 to MD and -1 to EN. Their appearence
is as High elves though 30% are found to have yellow eyes. 
 
Drow Elves:
     The Drow are a race of elves that spend their time as
underground dwellers. They are sensitive to the light and bright
light or sunlight reduces their MD by 2 and all their
saves are at a -20% for the duration. Fairy fire and other lower
intensity sources reduce MD by one and all attacks are at
a -10%.
     Their skin is a deep black that contains almost no melanin.
They have either white or silver hair and black eyes. Drow do
not have the +1 for bow and longsword. Instead they may attack
with two weapons without penalty.
     Drow speak the languages of the underground in much the
same way as gnomes. Also they have their own private toungue
which is a hand speech or finger talk. Their vision is
infravision for 60 ' and they have the normal charm resistance
and find concealed percentages. 

Centaur:
     Centaurs gain a +2 EN -1 AG -1 FAT. They gain a +5% and PS
bonus when using bows and a -10% using any bladed weapon.
Centaurs of a healer family are +1 EN and -1 AG. Centaurs prefer
short bows or wheel bows. 
 
Gnomes:
     The gnomes of Ea are scarce and rarely seen. They tend to
be coloured similiar to dwarves and have gem like eyes.
 
Korobokuru:
     The Korobokuru is a gnome variant found in the Eastern
islands. They gain a +1 PS +1 EN and -2 MA. 

Dwarves:
     Dwarves are short stout thick skulled . They gain a +1 to
EN and a -1 to AG. 
 
Halflings:
     They tend to have human coloring and are quite lazy. They
gain a +1 to MD and a -1 to PS. 
 
Hengeyokai:
     These are animal folk whose features and statistics are dependent
upon their animal form.. 
 
ShapeChanger:
     Shapechangers are similiar to Hengeyokai with some
exceptions. They have only a animal form and human form. They
are dependent upon the moons changes for their shapechange.
They may only be hit by silver or +1 weapons in animal form.
They are affected by all magics affecting lycanthropes. 

half-elves:Half-Orcs:
     Though they are not a unique race these two types of
humanoids often have a profound effect upon the world. 
 
Silkie:
     Also called the Acha Sidhe . The Silkie are a race of
aquatic half elf/shape changers or Wereseals . There statistics
are as half elves except in animal form.  

