h39186
s 00160/00000/00000
d D 1.1 99/12/02 15:43:56 jmochel 2 1
cC
cK01670
cO-rw-rw-rw-
e
s 00000/00000/00000
d D 1.0 99/12/02 15:43:53 jmochel 1 0
c BitKeeper file G:/SpaceHybrid/Doc/Design/wpndes.ltx
cBjmochel@devilmountain.bedford.foliage.com|ChangeSet|19991202203126|52994|e2968a7f5cb68f67
cHdevilmountain.bedford.foliage.com
cK44903
cPDoc/Design/wpndes.ltx
cReb47852a5cb68f68
cZ-05:00
c______________________________________________________________________
e
u
U
f e 0
f x 33
t
T
I 2
% wpndes.ltx
% SH Weapon Design Notes
% 01/24/92      JSM     Created


\documentstyle[stable]{report}
\title{SH Weapon Design}
\author{Jim Mochel}
\maketitle

\begin{document}
\section{Weapon Types}
Space Hybrid\ has several weapon types: Hand-to-Hand, Melee, and Missile.
Hand-to-Hand weapons are simply descriptions of techniques used 
in hand-to-hand combat. Melee weapons are any hand held 
and non-thrown weapon. Missile weapons are any weapon that 
projects its damage at a distance.

\section{Weapon Speed}

Weapon speed is the time needed to bring a weapon to bear on a 
target. For melee weapons this includes the actual process of striking.


\section{Simplified View of Damage}

Damage is caused by the transfer of energy to the body by the injury
causing element. The main energy involved is the so called
``Energy of Deformation''. It is calculated as below:

\[ \Delta E = \frac{1-{\epsilon}^{2}}{2} \frac{M_{1} \times M_{2}}{M_{1} + M_{2}} \nu^{2} \]

where \( \Delta E \) is the Energy of Deformation and \( \epsilon \) is the
coefficient of restitution. \( \epsilon \) is 1 for inelastic collison
and 0 for an elastic collision.

\section{Hand to Hand}

Kicks and Punches have an energy derived from the velocity and mass of
the objects involved. From measurements in biomechanics literature we can
get a fairly good feel for the energies involved in most strikes.

\subsection{Velocities of Karate Strike}

In general trained Karate-ka have average punch speeds that are
25-30\% greater than non-trained.

\begin{stable}{Velocities of Karate Strikes}{ll}
	Technique			& Velocity \( M/S\)  \\
\TableSubtitleRule
	Front Punch		&	5.7 - 9.8 \\
	HammerFist		&	10 - 14 \\
	KnifeEdge		&	10 - 14 \\
	Wheel Kick		&	7.3 - 10 \\
	RoundHouse		&	9.5 - 11 \\
	BackKick		&	10.6 - 12 \\
	FrontKick		&	9.9 - 14.4 \\
	SideKick		&	9.9 - 14.4 \\
\end{stable}

\subsection{Body Masses Involved}

Assuming that the average person masses in at 70 kg.

For Hand Techniques it is assumed that \(M_{1}\) is the mass
of the forearm-fist couple and has a mass of
\( M_{1} = 0.10 \times {Body\ Mass} \) or 7 kg.
The mass of the target (In this case I choose the
head as the standard target) \( M_{2} \) is assumed to be the
\( M_{2} = 7kg \).

For foot techniques the mass of the foot-lower-leg couple and the
head are 14 kg and 7 kg. respectively.

\subsection{Energies of Deformation}

\begin{stable}{Deformation Energies of Various Strikes}{lllll}
Technique	& \(\Delta E\) & \(\Delta E\) & \(\Delta E\) &	\(\Delta E\) \\
\TableSubtitleRule
			& Untrained	  & Untrained	 & Trained		&  Trained		\\
			& Lo			&  Hi		  &  Lo			 &  Hi			  \\
Front Punch	& 32			 &  95		  &  56			 &  168			\\
HammerFist  & 98			 &  193		  & 175			 &  343			\\
KnifeEdge	& 98		   &  193		  & 175			 &  343			\\
FrontKick	& 128			 &  271			& 228			  &  483		  \\
SideKick	& 128			&  271			& 228		  &  483		 \\
RoundHouse  & 118			  &  158		  & 210			 &  282			 \\
BackKick	& 147			&  189			& 261		  &  335		 \\
\end{stable}

All energies are expressed in joules.

The relative \( \Delta Es \) for HTH techniques are described below.
I am using the Average/Untrained punch as the 1.0 baseline. This
is approximately 65J

\begin{stable}{Relative Energies of Various Strikes}{lllll}
Technique	& \(\Delta E\) & \(\Delta E\) & \(\Delta E\) &	\(\Delta E\) \\
\TableSubtitleRule
			& Untrained	  & Untrained	 & Trained		&  Trained		\\
			& Lo			&  Hi		  &  Lo			 &  Hi			  \\
Front Punch	& 0.5			  &  1.5		  & 0.9			 &  2.6			\\
HammerFist  & 1.5		 &  3.0			& 2.8		   &  5.4		  \\
KnifeEdge	& 1.5		 &  3.0			& 2.8			 &  5.4		  \\
FrontKick	& 2.0			 &  4.3			& 3.6			  &  7.6		  \\
SideKick	& 2.0			&  4.3			& 3.6		  &  7.6		 \\
RoundHouse  & 1.9			  &  2.5		  & 3.3			 &  4.4			 \\
BackKick	& 2.3			&  3.0			& 4.1		  &  5.3		 \\
\end{stable}

\section{Projectiles}

In dealing with projectile damage we are dealing with two ways that energy is
transferred into damage. The first is the crushing of tissue by the slug
and the second is the temporary displacement of the tissue which often
causes "shockwave" effects further into the body cavity. I am not yet going
attemp to quantify the shockwave. The permanent tissue damage can be measured
and most of my notes deal with it.

\subsection{Major Misconceptions}

The following sections discuss the major misconceptions that have arisen in the
study of projectile damage.

\subsubsection{Velocity Effects}

Contrary to popular belief, faster is not always better. When dealing with
simple Full Metal Jacket slugs that don't fragment a higher velocity simply
increases the speed with which the slug exits the body.

Fragmentation has been demonstrated to be of much more importance than
the velocity of the slug . This assumes of course that the slug does havce
enough power to penetrate in the first place.

\subsection{Tumble in Flight}

Bullets do not tumble in flight. The actual angle of yaw for a slug impacting
a target should be no more tha 1-5\%.

Bullets do yaw after impact in tissue. This does not cause as much damage
as the same slug would if it fragments in the wound but it is still notable.
Of course this effect is typically seen to start after 15-20cm penetration in
the target. Most targets on the body would allow the bullet to exit before that point.

\subsubsection{Wounding Mechanism}

While energy transfer is an important part of the process , the size of the
projectile it very important. A large slow projectile will cause a great deal
more tissue damage than a small much higher velocity projectile with the
same kinetic energy.

\end{document}








E 2
I 1
E 1
