{\em Vordock}
"Summoner?"

{\em Morphus}

"I hope you fare better than I Avenger. You may have noticed 
that my staff was linked to the Grove, and I to my staff; I am feeling 
[KIF roll]{not good}. Was all lost? Were we too late?"
[Aside to Alex Am I unconcious?]

You are floating in a misty blue SPACE\dots there are no walls, no 
ceilings and no floors. Everything you say or the VORDACK says 
echoes and stretches in weird ways\dots you think your body is 
in physical danger\dots 

{\em Vordock}		

"Despair\dots the trees are burnt, the pool is dried, 
the Grove is leveled{you sense hurt and pain from the Vordock}. But 
all is not lost. I have kept the children of the Grove within myself 
and pulled the Gate around me. I think they that burn will leave in 
their impatience. They have not sensed my prescence I came cloaked in 
wind and illusion. There is much wrong with you Summoner\dots.."

{\em Morphus}
			
"I sense that as well. Do you know of the [I will describe the 
pool that the elder trees allowed and or helped me to drink from]? 
Perhaps if I drink from the pool it will heal me or at least sustain me 
while the grove and my staff recover. If not I must attempt to enter a 
KI trance [Will this help bodily damage?] or attempt a healing spell. I 
am not sure that I can do either while unconcious.
[If I am linked to the staff and thus the grove, and if the staff will 
appear as a young branch while recovering, when my burns go will I 
appear younger as well?]

{\em Vordock}
"The pool of which you speak is no longer on the road from
here to there. When blossoms unfold this road will be rebuilt. You must 
send your roots to different Earth. And so, Summoner, I must tell thee 
that you are in a state of within\-ness already. Your bark was badly 
damaged by the Storm. You must turn your sap to Life\dots "
{Younger You don't know\dots.. and you spelled `unconscious' wrong, wise mage}
[Let he who is without typing errors cast the first stone.
Can I cast spells in this state? I have SLife 2.0, so I could try to 
cast a healing but my instinct is to try to draw strength from some 
other source first (like I did from Nature). I would first try to draw 
strength from the Earth itself. After all, I am Morphus\dots when have I 
ever done anything the easy way? Earthblood, I can draw Earthblood!]

{\em Morphus}
"Can you guide me to a source of Earth Power?
[I will Earth Sense if it cannot \- and if I can Earth Sense; my roll 
14, my chances \- who knows in my present condition].
{You could use SLife but you would have to use POWER. You don't seem to 
be able to connect to any outside anything. Earthblood indeed! If you 
are serious this is what you would have to do

Make a link to the Earth\-
SLink+Earth sorcerey minuses\-20 (for being unconscious)\-`cost20 points'.
SEarth Shape into the channel(normal mods \- 20)      \-`cost10 points'.

Once you have done this you can begin drawing power at 4*normal 
endurance cost. You may use set\-up and double time if you can make a 
willpower save each time you use one of them. You can use Geomancy if 
you can activate it at a \- 20. That is how you would do that. If you 
try it\dots. good luck. Also when you send me a skill roll send me your 
normal success chance with it so I will know whether you made it or not 
i.e. I don't know what your normal Earth Sense is so I have nothing to 
apply mods to.

{you feel cut off from the earth\dots you have no sense of dimensional 
space at all. You can sense your own power, but no manna in the 
environment around you.}

{\em Vordock}
		"You are far closer to a source than I, Summoner. I am bound 
in a Faerie ring. I can not perceive as well as thou through thy senses. 
And so, Summoner, I must also tell thee that I know not who though art 
and what thy purpose is upon this dream, nor can I assist you in the 
application of thine power as thine power is as a mystery to me, and 
thus beyond mine ken. But thou shouldst look to thine healing ere your 
sap turns to amber.

{\em Morphus}

"Mine healing is a lot tougher than you might think. I can't 
do much without Mana and there doesn't seem to be any around here. 
Without the pool, or assistance in contacting the Earth Power, my POW is 
not great enough to make a difference. I have some skills in many 
Schools and Sorceries, though Shaping, Prophesy, and Summoning are my 
strengths; but even in these I am close to helpless without Mana. [this 
has bit me before and if I get out of this you can bet your buns I will 
figure out something that costs Minimal POW to link me with a 
significant source of Mana (or power that I can shape)]
But I have friends and perhaps they will be in time to save me. Until 
then, since we both seem to have time and nowhere to go, let us share 
our knowledge and histories.

I am Morphus, Demon Bane, Abjurationist, Diviner, Summoner, worker of 
Earth and Water, Alterations and Evocations, Enchantments and Elemental 
Sorceries.  [hey! sounds good doesn't it? I bet that's almost as long as 
Mordaniths full name!]  Long have I lived upon the mortal plane, far 
longer than I can remember if truth be told. I am warded, by who and for 
what I know not save that divinations of my past or future give diviners 
bad headaches. I have old friends, like Falstaff of the white staff and 
new friends, like Mordanith, son of elvish priests. Foes have I as well, 
like the Wizard King and Jarek Fireload, Desecrator of Trees. My goals 
are plain \-Go everywhere, learn everything and work great magics. 
Venerate the Mother, have respect for She Who Weeps, and nurture Life 
and Nature where I can \- Light too, of course, though those of Light 
can usually look after themselves and they oft have different goals than 
I \dots  Most of all, live life now, for we are but ripples in the 
currents of They That

What of you, Avenger? Tell me of the place where you come from, the 
wonders that you have seen, the creatures and beings that you have known.

{\em Vordock}

Tis mine hope that thine Healing is as strong as thou 
believeth\dots.In the Realm of Dream where thine self now resides it is 
difficult to perceive the way of the material world.  Perhaps thou 
couldst bind thy soul to thine body? It would aid you should you 
sdisconnected for a time. I know little of this but I know pain\dots and 
the Staff of the Wood cries out to me in its anguish.

Greetings Morphus, Demon Bane, Abjurationist, Diviner, Summoner, worker 
of Earth and Water, Alterations and Evocations, Enchantments and 
Elemental Sorceries. Thou art not the being I expected when I heard thy 
call\dots. I expected an enemy.

Thy ward, it is self struck, methinks. Thy future is twisted with Wild 
and Dangerous Magicks of a most untemperamental leaning. I fear even 
thou doth not know where thou willst tread\dots thou canst truly remeber 
only little?

This Falstaff I know\dots he hath fought on the fey side afore now and 
thy speaking of his name in friendship brings my doubts once more to me\
dots\dots

Thou speakest Forbidden names as glibly as they were the names of common 
rocks\dots. watch thy tongue Wizard of Many Arts. There are those who 
would harm thee if they suspected what it is that I now believe of thou.
Thou namest me right when thou sayest Avenger, Wizard. Know me\dots. I 
am he who hath guarded the Gates of Chronos for the Lords of Time, I am 
he who brought the Book of Winds to the High Elves of Yisvaeaounnaaie 
Kai\-Talientir. I have fought a Greater Dark and its Legions\dots. I am 
the Warden of the Kerestaen and Lord of Air, Light, and Conjurations\
dots. also know that I am skilled in the Human\-Forbidden Art of 
Abjuration\dots though not, maychance, as skilled as thou? Hmmm?
Perhaps thou hast dual meaning for mine Summoning\dots..

{\em Morphus}

I may try to bind my soul, that should be within my Power (
Alex is it?). What enemy were you expecting? I hope that I did not pull 
you away from a fight that you were looking forward to. I can remember (
a few k\-memory rolls 25, 70 ,14 => K\-Memory=32)

You have doubts BECAUSE Falstaff fought for fey? I thought that you 
were closely tied to Fey? What doubts do you have?
Forbidden names? Which are forbidden and why? If forbidden because 
uttering it might alert an enemy to my presense, that is a good reason. 
I utter not the name of he of Death because of old he and I have had\
dots words \-), but many speak Wizard King and a call name is not the 
same as a true name, though there is some danger, I'll grant you. 
Especially since I summoned his entire herd of prize horses, and Storm 
their Stallion, right out from under him \-)). And Old Fireload is just 
STARTing to piss me off. The only direct contact we have had is his 
contact with my creations, the Bridge over the trickle Quai and the 
Grove\dots.I will be avenged against him for that if he wasn't finished 
by the Mages of Marden. 

What is it that thou, uhh, you believe of me? I can not tell you if 'tis 
true lest I know what it is.

Kerestaen? I have heard of the Kerestaen, but I know not from where. Who 
what or where is Kerestaen?

Forbidden Art! Abjuration is not forbidden, it is discouraged\dots.It is 
only Shaping that is forbidden and that is because certain fools 
believed that by forbidding Shaping they would eliminate the problems 
caused by irresponsible Mages. Instead they created an imbalance \- If 
patterns exist, they must be studied and used. If they aren't, the 
uninitiated will stumble upon them and wreak even greater distruction. 
And the Dark Powers against which Shaping was most effective\dots well 
whose wolves kill the most Shapers?

Gladly will I exchange information with you, if you so desire, in any of 
the subschools that I have knowledge in. 
What mean you \- dual meaning?

To Chris You could bind your soul\dots it would take binding minuses on a 
MAP roll or under S Binding if you have it, 5 base points of power, and 
each point of power will keep you bound for some unit of time depending 
on how well you roll. The minimum time you think it is is 1 minute per 
point but could be as long as a month per point if a hugely successful 
roll is made.]

Vordack			Thine call was similar to another that I hath known, Summoner. 
And, nay, thou didst not take me from a fight\dots I thought thy call 
was a challenge when I first tasted it. Falstaff hath been a friend to 
all things Fey\dots..

FLASHBACK
{the scene is a small room of wood, with a single bed made with fur on 
your left, a stool, a mirror of copper to your right, a bureau with 
three drawers beneath it, and a swinging door behind you. There is a oak 
table between yourself and Falstaff. He is flushed and you are yelling "
You cantankerous, senile, blundering, weak\-hearted, emotional, 
immature, sentimental old fool! I can't believe it\dots. have you gone mad!?"

With crack of thunder Falstaff smashes the table in half in a downward 
sweep of white. His face glows with fury and the air around him crackles 
with flashes of power. "The Faer\-han would have died if I hadn't\dots. 
would you lose Tyriontill Kyrvaeon Alan\-ad to a Raver!?! Hmmm, you 
lecherous, Earth\-grubbing, addle head!?? Would that be worth it for our 
Grand Cause?! Wake up\dots people are not playthings, Damn it! Sometime's 
we have to sacrifice the straight line to our goals to retain our humanity!!"

You sense Darkness sweeping towards the inn in which you are standing. "
The Ghoul will lead them right here, Fals! I hope you're ready to face a 
Death Lord and his Knights\dots. I certainly won't help you.. I have to 
heal the breach in the Earth you caused."

"Hurry up then, my friend\dots the breach widens as we speak and the 
Darkness is upon us." There is a rending of space as a Greater Death 
steps through the wall of the room.. and then you are gone as you plane 
shift away\dots..}

\dots. and so I believeth you to be connected. Summoner? As I was saying 
the names of They That Were Before, even the "call names" as you say are 
tokens of power. As to the Kerestaen.. I may not speak of them to those 
who know them not. Soon perhaps I may tell thee. As to forbidden.. I say 
to thee twas truly forbidden by the Great Human Councils of Mages, the 
Priesthoods of your World, and The Elven Council. While it twas not 
forbidden to study in theory it twas deemed too dangerous to study for 
humans and their ilk. Of course it tis not a true skill in Faerie as 
shaping is like unto walking.  Thy point on Wolves is well taken, Shaper.
I believe that thought art not the Dragon I feared thee to be when thou 
first summoned me and instead what I have been growing to suspect as we 
hath spoken\- something far more dangerous\dots Didst thou summon me to 
entrap me in this Grove?

Art thou of the Preceptors? Speak true for mine senses are 
keen.
[What is the effect of my binding my soul to my body once I am healed? I 
will attempt this Binding unless there is a consequence that you feel I 
should know about first. I will spend 7 of my power. 5 plus 2 time 
units. I have the following ranks SBinding 3.0, Meditation 6.2, 
Willpower Save 54%, SCF 17.5, MAP 40, my rank in Shaping is 6.1 which 
gives me a WBINDING of 2.4. I will attempt whatever setup and doubletime 
that I can PROVIDED that the total cast time remains in counts not 
minutes \- I can't afford minutes. What else do you need?

{\em Morphus}
			Forgive me, sometimes my mind wanders. When you mentioned 
that "Falstaff hath been a friend to all things Fey", I remembered 
this =>(a language filtered version of the flashback, with all the 
pertinent facts). What were you saying while I was wool gathering?
I'm sure that I have heard of the Kerestaen, perhaps I will remember. 
Needless to say, I will look forward to hearing of them when I may.
No. I'm no dragon. Though I am almost positive that a dragon in human 
form was watching us cast our summoning. Mordanith believes him to be a 
bronze dragon whose name escapes me at the moment.
Dangerous, perhaps. Hopefully only to my enemies. I summoned you for the 
purpose that I set forth in the spell, to protect, nuture, and care for 
the grove as I would if I had the Time or Power, and were free to do 
such a thing. But I do not yet, and can not yet, so I needed you. It is 
a prison. A prison of which you are both prisoner and warden. You 
control the boundries. The farther the grove spreads, the greater are 
the limits that you may walk without purpose, the greater the area that 
is blessed with the beauty of my plane and that of Fey Light, Life, and 
Nature. All those who YOU deem non\-harmful to the grove and those who 
are its guests, may enter. You are the Guardian, the Warder\dots
You are  Lord of the Grove; even I who created it must bow to your will there, 
until you pass the wardship to another who will accept it.  Even the 
boundries of the Grove do not bind you You may go where ever you feel 
you must to fulfill the requirements of your office. You were told and 
you accepted, you w

I know not of the Preceptors. Who are they?

{To Chris things sound more hollow now\dots the expanse around you gets 
darker\dots you begin to feel a little cold\dots. you have not yet 
completed the binding\dots. you aren't sure if it worked or not but you 
think so\dots.}

{\em Vordock}

Thine mind is confused as it hath no point of reference. I 
wert saying that I believeth that I shouldst know thee and indeed tis 
mine belief that I might knoweth of thee indeed. Where didst thou learn 
thy art, Summoner? Didst thou not suckle at a Druid's bosum? Art thou 
not of the RING? If thou be he whom thou impliest, thou art then that 
one I feared\dots Earth Lord. Tis possible thine goals and mine art not 
well met. I do now believe {whisper\dots. whisper} as it would have ill 
fit thee to tell myself of thy disagreement with the White Staff. I 
believe thou hast hidden thyself from thy enemies by hiding thyself from 
thyself. As such, it couldst be thou art a better person now. I think { 
whisper\dots. whisper} and well met. Think with care of what thou hast 
done\dots. thine brother Falstaff is not without his wisdom.

Thou art{ whisper\dots whisper} to both enemy and friend. Thy danger 
comes from thy great skill and human enthusiasm. Lord and Slave to the 
Grove I am. I hath come willingly and, I now { whisper\dots whisper} 
fair benefit. I think thou acted in good faith and I can but hope that 
thy inner self didst not have thee choose {whisper \dots. whisper} 
sinister purpose.  

The Preceptors are a sect of humans that serve CHAOS. They {whisper} 
masters of the Wild Magic. Their goal {whisper}ruction of She upon Whom 
we Rest {whisper} May Not Speak Of\dots. as {whisper} the enemies of {
whisper} our people\dots

Summoner?\dots {whisper}\dots SUMMONER!

{To Chris There are roiling swirls of various hues of blue all around 
you\dots some are so dark as to be almost black. Most of the darker ones 
are clustered to your left; to your right there are much brighter 
elements of blue and it is from there that the Vordocks voice seems to 
emanate. Around you the lighting is approximately that of a very stormy 
day at dusk with spots of orange dancing in the distance like far off 
campfires. It is cool enough to make you feel uncomfortable. You seem to 
be floating in your physical body. Eyes, ears, arms, legs, blue robe\- 
no staff. You can hear sounds like the crashing of water on a far away 
shore\dots..

FLASHBACK

Off shore, purple tinted storm clouds hang on the horizon as if they are 
going to leap off the edge of the world\dots. The cool, salty wind 
brings you the smell of dead seaweed and brine as it whips your black 
hair around your face.

"I don't understand it," you say as you lower your eyes from the dark 
cliffs looming over you to the small, bent man sitting in the sand at 
your feet. "Why did she close herself to us? What possible purpose could 
she have?"

"She needs no purpose, young Kheldar. She walks the Path of Dreams. You 
have walked that Path yourself."

"But never for this long\dots what if she doesn't return?"

"She will\dots. she will."  He stands up awkwardly, brushing your 
helping hand away as he straightens his faded orange robe. His eyes, the 
color of a winter sky, peer deeply into yours as he begins to limp away.

"Someday, Kheldar, when you are no longer Kheldar, you will tread those 
paths for far longer than Miriel ever will\dots" He paused to hop over a 
piece of driftwood as he headed down the long, empty beach, "You will be 
lost, and you will remember this day and know that in the Realm of 
Dreams the only sign posts are those that you cause to be made. Do not 
wander far\dots the most deceptive enemy is often yourself." He smiles 
to himself, panting with the effort of walking, "That's one of those 
wise sayings to keep in a big book in your reading room. Keep it handy 
because you can answer half the questions you get asked with that one."

He pauses to look out to sea and to catch his breath. His bare brown 
feet make a startling contrast with the white sand. "Have I ever taught 
you about the Kerestaen?" He points out over the black waves\dots "Look 
at that bird."

You look out and see a patch of dark rock, covered with moist fungus, 
around which a flock of white and grey birds circle wildly. You point 
with your staff, raising your left hand to shield your eyes against the 
bitter wind.

"Not the seagulls, dolt! The orange one."

You see a spot of orange drop away from the flock of birds. It drops 
near the water and rises once more, just brushing the caps of the waves. 
As it swings towards shore you see it is a magnificent bird\- a wingspan 
fully eight feet across and its entire body covered in a thick coat of 
feathers the color of the setting sun.

"The Ferthan bird knows the ways and winds of every ocean, it is one of 
the most powerfull symbols of that people. Notice the\dots

SUMMONER!!!!! THOU DREAMWALKS TOO LONG\dots\dots.AWAKEN!

{You are in the Realm of Dreams once more\dots. you feel your body 
changing but know not for good or for ill.  You can feel a powerfull 
mind seeking yours.. it is the Vordack.}

{\em Morphus}
Avenger? HELLO? MY SURROUNDINGS HAVE CHANGED. IT IS DARKER AND 
COLDER THAN BEFORE. I CAN'T HERE YOU. I COMPLETED THE BINDING, MIGHT 
THIS BE AN EFFECT? OR AM I DEAD? 

K\-Memory 41%=> What do I know about dream walking? 61
If I float in my physical body, can I will myself to move?
NOTE IF THESE K\-MEMORIES AND FLASHBACKS ARE CAUSING THE DREAM WALKING, AND I REALIZE THIS, WHETHER BY MEMORY OR COMMON SENSE ie. MOVING FARTHER AWAY FROM THE VORDACH WHEN I TRY TO REMEMBER, I WILL MAKE EFFORT TO MOVE TOWARD THE VORDACH. IF I CAN MAKE HEADWAY AND STILL TRY TO REMEMBER, I WILL. IF I CONTINUE TO MOVE AWAY FROM THE VORDACH, I WILL ATTEMPT TO WILL A "SIGNPOST" INTO EXISTENCE.
What was the relationship between that man and Kheldar? (34)
What was his name?  (10  If necessary)
Who is/was Miriel?  (01 00 58  If necessary)
What did he tell me about the Kerestaen?  (09  If necessary)

You can't remember what Dream Walking is\dots it escapes your mind. 
There are more dark clouds then light now. You hear the rythmic sounds 
that reminded you of surf. Slowly, your body moving in slow motion, you 
turn towards the lighter clouds. Your hand reaches out with agonizing 
slowness as you try to will yourself towards the "direction" the Vordack 
seems to be in. You feel wind whip around you coming from the direction 
of the Vordack, pushing you down and back. You don't seem to be moving\
dotsAs you`re mind pushes forward your thoughts flow back to the memory 
you just had\dots

You place the leather scrollcase down on the marble tabletop, your eyes 
flicking over to the rack of eight blue candles at the other side of the 
table. The rest of the room is shrouded in the flickering shadows caused 
by the candles. You can hear the drumming of a hard rain on the wooden 
roof over your head. The smell of wet wool and candlewax lingers in the 
air. Before you sit the two scroll rollers. You sigh, look at them both, 
and then rub your hands together muttering "Scrolls? I can do SCROLLS!"

You cackle as you pull an empty scroll from under the table and fasten 
it into the right scroll roller. First, the main body fits into the 
lower notches and then scroll out a little and attach the start of the 
scroll to the upper notches. You insure that the paper is flat, and then 
read the aura of the paper. Not bad\dots.

You turn to the scrollcase on the table and reach to pick it up. The 
candlelight flickers off the heavy bronze ring on your left hand as you 
gently lift the scrollcase and untie the red lace that symbolically 
binds it. You place your finger on the top of the scrollcase and say the 
word of releasing while giving it a light mental nudge.
The locks on the scroll release. You gently and carefully pull the 
ancient, brittle leather off the scroll. The scroll is old and yellowed. 
One of its rolling pins is larger than the other and both have large, 
broad, wooden caps at both ends. They are of a very dark color 
impossible to distinguish in this light\dots Their is a green ribbon 
tied twice around the scroll. Light explodes around you with a crack of 
thunder!

You start back as lightning from the storm outside illuminates the room 
you are in through the high, narrow window on your right. In a split 
second you recieve an impression of a large, stone room; of tapestries 
on the walls; of a rickety wooden door on the far wall to your left\- 
and then blackness. You cackle to yourself about being a "scaredy cat" 
and get up from the long wooden bench you've been sitting on. Your butt 
aches from sitting on the hard bench for too long, your open slippers 
are soggy and too cold. You go over towards the door and almost trip 
over the tray stand holding this morning's breakfast. Or was that supper? 

You carefully lock the door, and then hobble over to the window and 
close the old black shutters\- getting sprayed by rain in the process. 
The timbre of the rain immediately changes. You stop and listen to the 
sound for a while. You then carelessly grab your beard and tuck it into 
the neckline of your robe. 

You compose yourself and then, still standing in the middle of the room, 
you drop into a Mage Trance. You slip into Mage Sight as smoothly. 
Cautiously, you look around the room. Spotting some points and a few 
weak streams of stray magic you wander around the room shaping them into 
compact form and binding them in place. You call the Abjurational 
pattern to you and suddenly everything looks as if it is structured 
power, and you lose most of your sight in the material world. You go to 
the wall in front of you\- tripping on the food tray once more, but not 
losing your concentration\- and fumble a piece of yellow chalk out of 
one of the belt pouches slung below your swordbelt. The yellow glow from 
the chalk makes the wall seem dirty and pitted. You concentrate, and 
then, muttering to yourself in Ancient Elvish, you draw a Tolnedran Rune 
of Sealing on the wall. You repeat this procedure three times for each 
wall.

After putting the chalk away, and washing your hands in the water basin 
below the food tray, you sit back down in front of the scroll. You gaze 
appreciatively at the complex weave of wardings and triggered 
enchantments guarding it. You shift in your now damper robe.

{To Chris You suddenly find yourself amidst great roiling clouds of 
purple and dark blue. There is a circle of brighter blue in front of you\
dots it appears to be about the size of a large plate\dots.it is cold as 
death, your head is swimming, and your skin is crawling as if to pull 
off your body. You fight to escape the memory but its hold on you is too 
strong\dots. you feel yoursef pulled in again\dots\dots}[I need more 
general rolls from you Chris]

You are sitting at the desk finishing up the scroll. The light blue 
feather quill in your hand is warm to the touch as your hand quietly 
brushes out the last few strokes of the last glyph. You finish off the 
Rune and place the quill back in the lead crystal ink well to the left 
of the roller. Moving very slowly you blow on the ink in an attempt to 
make it dry faster. You barely contain the impulse to sorcerously pull 
the water from it, and just lean back to wait. Pain shoots up from your 
back and your butt. Your eyes wearily observe the daylight streaming in 
through the cracks in the black shutters. With a groan you get to your 
feet and hobble over to the large clay pot sitting next to the window. 
You pull up your robe, undo your loincloth and relieve yourself. Your 
knees ache as you squat down. When you finish you wipe yourself with the 
towel left there for that purpose. You re\-wrap your loincloth, and 
stand up, letting your robe drop back around your legs. You stagger over 
to the tray

{Your mind struggles out of the memory and holds desperately onto a 
conscious state\dots Your head clears and you are in the place of blue 
clouds once more\dots..}

{\em Vordock}
"Summoner? Shaper?"

>How does this burning affect my stages of development OR
>How does the spell on myself affect my recovery and my appearance?

The burning will allow you to make the transition to the next level of 
development very smoothly\dots\dots.

>What is my weight?
Your weight is fairly severely reduced. As you heal you will gain 
weight. You will end up being at the correct weight for the next stage 
when you are done healing.

>Can I affect the regrowth of skin tissue to prevent scarring?

That would be a Life sorcery combined with an Alteration Sorcery. It 
would be a related florentine action(\-30 to both); You would have the 
normal difficulty mods; it would cost you 10 MEN per point of scarring 
and you have about 134 points of scarring damage. I would not reccommend 
healing more than 10 \- 20 points a day because if you backfire you can 
really hurt yourself\dots\dots

>Does this situation aid me (in a perverse way) by burning away the old 
chaf that was my previous stage of Morphusness?

See above

>Exercise is a must and I have wielded a sword before, By following the 
>singing warriors guidance and exercises, can I develop myself into a 
>swordsmans body? (like Falstaff not Vartigan)

Yes\dots.. this follows the line of thought of your physical 
development.  You are sort of doing that as you increase your physical
stats. Did you have soemthing else in mind?

>In our conversation, what was the time, in surges, that the Vordoch
>gave me for the A) Budding B) regrowth of the Grove (and my staff)?
>Before I wake up I ask how much time, in surges, we have been 
>conversing. When, in my time, using this info, will A) \& B) happen?

About 6 surges (33 days) occured while you were unconscious.
According to the Vordock Budding can begin in 12 \-14 surges;(60\-77 days)
Regrowth will start to set in 15\- 20 surges after that.(+75\-110 days)
It will take at least 40 surges after that before the trees are even close to the level where they were at when you left the grove. (+200\-220 days)
Total 335 \- 407 days

>Now that I am in 'Concious' trance, can I contact the trees? If so,
>I will let my companions know what I am doing and I will inform 
>the trees as to all that has happened, is happening, and will happen.
>I will ask if drinking from their pool will aid in the recovery of
>my body and will ask if I can drink.

Yes, you could contact the trees. Write to Mochel or call him and let 
him know what you want to do\dots..get his input. Then get back to me.


