\documentstyle[relate]{shart}

\begin{document}

\begin{titlepage}
    \vspace{1.0in}
    \begin{flushright}
          {\huge\bf Spell/Psionics Design System} \\[.25cm]
          {\rule[.1in]{4.5in}{.02in}}\\[.25cm]
          {\large\bf Version 1.3 interim} \\[4.0cm]
          {\bf Jim Mochel}\\
    \end{flushright}
\end{titlepage}

\section{Introduction to Spell Casting}

There are three basic steps in casting a spell. The first is to 
gather the energy, the second is to focus that energy and the third 
is to release it. This diagram below simply denotes those three steps.

\setlength{\unitlength}{1in}
\thicklines
\begin{picture}(5,5)
\put(1,4){\framebox(2,1){Raise Energy}}
\put(2,4){\vector(0,-1){1}}
\put(1,2){\framebox(2,1){Focus Energy}}
\put(2,2){\vector(0,-1){1}}
\put(1,0){\framebox(2,1){Apply Energy}}

\put(3,4.8){\vector(1,0){.4}}
\put(3.4,4.8){Some Components Apply}
\put(3,4.2){\vector(1,0){.4}}
\put(3.4,4.2){Usually from caster}

\put(3,2.8){\vector(1,0){.4}}
\put(3.4,2.8){Most Components Apply}

\put(3,0.8){\vector(1,0){.4}}
\put(3.4,0.8){Actions Applied Here}

\end{picture}

\subsection{Raising the Energy}

Raising the energy is an important part of the casting process. Most 
spells will simply use the mage's internal energy and thus expend 
Mental Fatigue during the cast process. This can be augmented or 
replaced by energy from Material Components, Magic Items, Living 
Sacrifice, Worship, Physical Exertion, or just by being given the 
energy by another.

The type of energy involved is very critical in determining the speed
or casting time of the spell. The faster a given energy type is, the
more it costs in Spell Design Points.

\subsection{Focusing the Energies}

Once the energies are raised they must be brought to bear on the 
desired effect. If the cast is directed at a specific individual or 
object then the spell has a target. In addition, the spell has a path 
or method by which it reaches the target. 

If the cast is not directed at anything other than one of the energy 
types that may be manipulated, then there is no target to the spell.

Focus implies that the caster is directing or channeling the energies 
toward a specific end. Most material components used during this part 
of the spell would be used for channeling the energies involved and 
could be used up if they cannot efectively contain the energies 
involved.

Somatic and verbal components would add to this part of the spell 
process as would any meditative state or trance.

It is during this part of the cast that the caster mentally links 
parts of the spell together and determines how much energy is applied.

Note that the time taken up here is spent in focusing and setting up 
the various actions to be later taken by the energies involved. Thus 
the time spent in applying the energy is fairly constant compared to 
the time spent focusing the energies.

\subsection{Apply the Energy}

As the energy is released it should (if the cast is good) follow 
the form laid out by the caster when he focused on the spell.

It is here that the target type is brought to bear.

\subsection{Simple Starting example}

In designing a spell we start with all spell attributes at 0.
CEF = 0, Resistance = 0; DUR = 0; RNG = 0; QE = 0; EC = 0.

Suppose I am playing a mage that wishes to design a simple fire 
summoning spell. We start with a set number of Spell Design Points:
(27). We first look at the process of raising the Energy for the spell. 
We buy the Energy Type of fire at a cost of 7. Thus, the speed is 3
and We have \( 27 - 7 = 20 \) Spell Design Points left.

Next we look at the process of focusing the spell. Since the spell is
going to be doing a summoning of the fire, the  first action taken
should be an actual summoning. Again using a table, we determine that 
the Summoning action costs 1 Spell Design Point and has a speed of 3.

Finally we look at the process of applying the spell. There is no target
type involved here since there is no attempt to apply the energy to
anything, simply to summon it. No Target costs 0 Spell Design Points.

So we have 19 Spell Design Points. And we have all spell stats at 0.

!!!! To be continued
\dots 

\section{Factors involved in Spell Design}	

The two main factors involved in the design of a spell are the Energy 
Type being used and the actions being performed with that energy.

\subsection{Factors involved in Raising Energy}

\subsubsection{Energy Type}

This describes the types of energies to be used. In a magical context 
these would be the elementals such as Light, Dark, Fire, Air, Life, 
Death, and Electricity.

There are the two pseudo elementals Shadow and Starlight.
Shadow is the energy produced as a result of the interaction of large
amount of light with a small amount of dark. Starlight is the energy 
produced as a result of the interaction of a large amount of dark 
with a small amount of light 

In addition there are three other types of energy. Belief is the 
energy created by the worship or investment of faith in another 
entity, being, or object. Stream is the energy derived from the 
dynamics of the time continua. Fabric is the energy derived from the 
shifts of equilibrium of seemingly static forces involved in the here 
and now.  

In psionics these are Telekinetics, Phanokinetics, Temporokinetics, 
Energetics, and Biokinetics.

\subsection{Factors involved in Focusing Energy}

\subsubsection{Actions}

This is what the energies are to be used for. These actually spend 
time during the Focusing process.

\marginpar{
	Some of these actions require a target to work against.
	Specifically Influence, Control, Damage, and Restoration
}

These actions are often described in a pairing between an action and 
its opposite.

The actions are Detection or Concealment, Divination or 
Anti-Divination, Summoning or Banishment, Creation or Destruction, 
Concentration or Dissapation, Transport or Anti-transport, Binding or 
Releasing, Transmutation or Stasis, Translocation or Anchoring, 
Influence, Control, Damage or Restore, and Hold.

\subsubsection{Casting Components}
Casting Components covers external props, preparation,  and other 
components. 

\begin{relate}
	\item [Verbal] Verbal Components are vocal actions that aid in 
	the casting of the spell. This is the default. It assumes a
	normal speaking voice chant. 
	\item [Somatic] Somatic Components are physical actions such as 
	hand waving or finger moving.
	\item [Material] Material components are physical objects or 
	materials that aid in supplying, channeling, or directing energy. 
	\item [Preparation] Preparation covers any activity that may be 
	performed before the spell is cast.
	\item [True Name]
\end{relate}

\subsubsection{Casting Components Properties}

Each casting components value to the design of the spell may be 
modified by the various properties of the Casting Components.
If the material is rare or particularly fine, it will add to the 
spell's abilities.

\begin{relate}
	\marginpar{
    	Most Casting Components may have more than one property. A
		material component may be Rare and Non-Renewable. 

		{\bf None of these properties may be aoplied to True Names}
    }
	\item [Expensive]
	\item [Cheap]
	\item [Rare]
	\item [Common]
	\item [Renewable]
	\item [Non-Renewable]
	\item [Reusable]
	\item [Non-Reusable]
	\item [Complex]
	\item [Loud]
	\item [Quiet]
	\item [Long]
	\item [Short]
\end{relate}

\subsection{Factors involved in the Application of the Energy}

\subsubsection{Target Type}
	\marginpar{
		The term Target Type simply refers to the fact that the spell 
		has a focus other than the type of energy being used. If 
		the spell is simply the summoning or transportation of a
		given type of energy it is considered to have no target.
		If the energies are to be directed against an object or 
		creature in order to have the desired effect the spell is 
		considered to have a target. 
	}

Target type describes whether the energies affect a target, multiple 
targets, or no targets at all. 

\begin{relate}
	\item [No Target] The spell is not intended to effect anything 
	other than the base energy type used in the spell. 
    \marginpar{
		If the spell is targeted to act against any other type of 
		energy than that used by the spell than the spell is considered to 
		have a target and must be either Single Target or Area of Effect as 
		detailed in the listing
	}    	
	\item [Target,Self] The spell is directed against the caster 
	only.
	\item [Single Target] The spell is intended to effect on one 
	object or entity.
	\item [Multiple Targets] The spell is intended to effect multiple 
	objects or entities. 
	\marginpar{
		Note that the assumption here is that the Quantitative Effect 
		is {\bf split} between the multiple targets wheareas an Area of 
		Effect spell has that Quantitative Effect apply equally among 
		all of the targets.
	}
	\item [Area of Effect] The spell is intended to effect all 
	targets within a given area. 
\end{relate}


\subsubsection{Target Components}

Each target may have has many as five components as part of its 
``Elemental'' makeup. If the spell is targeted, it must be determined 
what components of the target the spell energies affect. 

\begin{relate}
	\item [Matter(Inanimate)] 
	\item [Body(Animate)]
	\item [Mana(Inanimate)]
	\item [Lifeforce(Animate)]
	\item [Thought]
	\item [Perception]
	\item [Essence(spirit or soul)]
\end{relate}

\section{Spell Statistics}

\subsection{Resistance (RES)}

How easily can the spell be resisted. The higher this value is the
better it is for the caster. When doing spell design the
designer will be modifying Resistance. When the spell design is complete
the value for RES will be used to generate the REF stat.

\subsection{Resistance Ease Factor (REF)}

How easily can the spell be resisted. \( REF = 7 - Resistance \).

\subsection{Quantitative Effect (QE)}

A pseudo-quantitative value for the total effect a spell can have. This
is expressed as a numeric constant. This must be translated to  actual
effect via a table. For Damage or Restoration spells this directly
translates as the damage done by the spell.

\subsection{Casting Ease Factor (CEF)}

The Ease Factor involved in casting the spell. Expressed as a
standard EF, not as a modifier.

\subsection{Energy Cost (EC)}

What is its cost in Mental Fatigue.

\subsection{Casting Time (CT)}

How long does the action take in counts or any appropriate time unit.
In dealing with both casting time and duration there is a cost 
associated with the time unit and the multiple of that time unit 
used.

\subsection{Duration (DUR)}

How long does it last? Instaneous spells is any spell that lasts for 
a very small and fleeting duration. Active Concentration duration 
spells last for as long as the caster concenmtrates on the spell. Any 
other actions the  caster may partake of will be considered 
florentine actions. Passive Concentration duration spells last for 
as long as the caster is concious and or clear minded. Permanent 
spells last until dispelled or disrupted. Default duration spells 
have a duration derived from the energy type. 

Default duration spells may have their time scale unit bought to some 
larger unit.

\subsection{Range}

Touch range spells require the caster to come into physical contact 
with the target. Default range spells are typically expressed as 
multipliers of the mages own Magical Potential. 
 
\begin{relate}
	\item [No Range] Implies that the caster is affecting himself.
	\item [Touch] Requires the casters body to come into contact with 
	the Target.
	\item [Default] Derived from the Energy Type and Actions taken.
\end{relate}

\section{Examples}

The best way to learn is to do so lets look at the design process 
with several different types of spells. Let us first design the 
{\it Laser} spell.

\marginpar{

	{\bf Quick Aside} 

	A quick explanation of EF for those who have not encountered the 
	topic. In \SH the chance to perform an action is based on the Ease 
	Factor of the action times the Stat Basis of the action plus 5\% 
	times the Rank of the action. For discussion's sake we will assume an 
	average Stat Basis (SB) of 7. So a mage with rank 0 in the fireball 
	spell would have an average chance of \( 4 \times 7 + 1 \times 5\% \) 
	or 33\%. This is without setup or any spell purification. 
}

We start with the Base spell type. 
We choose the Energy Type of Light. This gives us :
The first action needed for the spell is the Summoning of the Light. 
The next action is to transport the Light to the target.
After transporting the Light, we must apply it to the target in order 
to damage it.

The effects of the spell factors get totaled up and this gives use 
the default values for the spell. When totaling the spell we take the 
effect of the Energy Type and add it to the highest value in any 
	\marginpar{
		The highest column calculation is done for each group of 
		three actions. If there are nine actions for a spell then the 
		three highest are added to the modifiers for the Energy Type.
	}    	
given column.

Thus:

So the spell has a Casting Ease factor of 7, a Resistance Ease Factor 
of 7, a Quantitative Effect of 1, a Base Casting Time of 5 counts, an
Energy Cost of 6 Mental Fatigue, and a default Duration of \( 7 \times \)
the Mental Strength of the designer.

We should keep track of the Default Casting Time, Default 
Quantitative Effect and the Default Duration.

At this point the spell appears to be pretty wimpy. It takes six points 
of MFT to do one point of damage to the target.

It is time to modify the defaults to get some more reasonable looking 
numbers. All modifications we make should increase or decrease the 
Spell Design Points.

The first thing to do is to drop the duration down to 0. Once this 
\marginpar{See table~\ref{tab:FactorChanges} }. 
has been done the spell is considered to be Instantaneous.
This gives us 7 points for the Spell Design Pool 

This gives us :

Since the spell we are designing has a target, we must include that 
fact as part of the design. 

Let us add in an expensive, rare, reuseable material component.
Let us also require the caster to use a to-hit roll as part of the 
targeting process.

Next let's lower the Casting Ease Factor by two. This gives us four 
more Spell Design Points as per table~\ref{tab:FactorChanges}

Now we can use the Spell Design Pool to build up the other attributes 
of the spell.
 
Lets add \( 10 \times \)effect on QE. That costs 9 Spell Design Points.
Let us also lower the Energy Cost to 1/3 of what it is now. That 
costs 2 SDPs. 

Thus we have :

Let us use the rest of the SDPs for lowering the Resistance Ease 
Factor so that this spell becomes very hard to save against.

Now there is one last thing we can do to get some more SDPs. Since 
each Target has several components as part of its makeup, we can 
narrow the focus of the spell down to affect only the Body or Matter  
of the target. See the description about Target Components earlier.
By narrowing the focus to one Target Component, we exclude four 
Target Components. That gives us four more SDPs to use. 

We can use those points to increase the range to 5 times the default 
of MST/3 in Meters.

There are some things to note about the spell. First of all, because 
the Default Quantitative Effect is 1, the caster can up the damage of 
the spell by 1 point for each point of Mental Fatigue he places in 
the cast beyond the base cost. Because the spell is narrowed to 
effect only Body/Matter it has no effect on most immaterial entities 
except for those specifically effected by Light. Also, by default the 
Concentration Type is that of Simple Spell.

Now let us design another spell. We will design a {\it Lightnings 
Hand} spell.

We specify multiple targets.

Lets lower the Casting Ease Factor by 4 and add a non-renewable 
material component(Mistle Toe). Since the material component requires 
special preparation (Gathered on Midsummer's eve) we should include 
that.

The spel is Finren's so it should be flashy. Lets add a somatic 
component. As well, lets make it a Standard Spell in Concentration type. 

Now, lets spend those points ! Lowering the Energy Cost to 2 costs us 
2 SDPs, raising the Damage to 4 times what it is costs 3 points, 
Allowing the spell energies to be held until needed costs 5, 
lowering the REF by 3 costs 6.

\section{Other Notes that are of interest}

Investment Rituals are specific to the energy being used. Normally,
invested items can resist. With sufficient preparation the 
resistance can be dropped to 0. 

Warding rituals are similiar.

Remember that this spell design process is simply intended to speed
the actual creation of spells. Once a spell has had its values determined
it may be manipulated by putting more power into it in order to
"turbo-charge" the spell. 

\section{Spell Design Tables}

\begin{table}
	\begin{tabular}{lcc} \hline
	Energy Type		&	SDP 	&	Speed	\\ \hline
	Light			&   -7 		&		0		\\
	Dark			&	-7 		& 		0		\\
	Shadow			&	-6		&		1		\\
	Starlight		&	-6		&		1		\\
	Fire			&	-5		&		2		\\
	Water			&	-3		&		4		\\
	Air				&	-5		&		2		\\
	Earth			&	-3		&		4		\\
	Electrical		&	-5		&		2		\\
	Life			&	-3		&		3		\\
	Death			&	-3		&		3		\\
	Belief			&	-1		&		6		\\
	Stream			&	-7		&		0		\\
	Fabric			&	-7		&		0		\\
	Telekinetics	&			&				\\
	Phanokinetics	&			&				\\
	Temporokinetics	&			&				\\
	Energetics		&			&				\\
	Biokinetics		&			&				\\ \hline
	\end{tabular}
\caption{SDP Energy Types}\label{tab:EnergyTypes}
\end{table} 

\begin{table}
	\begin{tabular}{lcc} \hline
	Action Type		&	SDP 	&	Speed	\\ \hline
	Det/Conceal		&	-1		&	1		\\
	Div/A-Div		&	-1		&	1		\\
	Summon/Banish	&	-1		&	2		\\
	Create/Destroy	&	-1		&	10		\\
	Conc/Dissapate	&	-1		&	3		\\
	Transport/A-Tra	&	-1		&	4		\\
	Bind/Release	&	-1		&	7		\\
	Trans/Stasis	&	-1		&	8		\\
	Translocate		&	-1		&	9		\\
	Hold			&	-1		&	1		\\

	Influence		&	-2		&	1		\\
	Control			&	-3		&	2		\\
	Damage			&	-3		&	2		\\
	Restore			&	-2		&	3		\\ \hline
	\end{tabular}
\caption{SDP Actions}\label{tab:ActionTypes}
\end{table}

\begin{table}
	\begin{tabular}{lc} \hline
	Casting Component			&	SDP 			\\ \hline
	Verbal						&	0				\\
	Somatic 					&	4				\\
	Material 					&	4				\\
	Preparation 				&	4				\\	
	True Name					&	8				\\
	Requires to-hit roll		&	4				\\
	Energy Held for duration	&	-4				\\	\hline
	\end{tabular}
\caption{SDP Casting Component Type}\label{tab:CastingComponentType}
\end{table}

\begin{table}
	\begin{tabular}{lc} \hline
	Component Properties		&	SDP 			\\ \hline
	Cheap 						&	0				\\
	Moderate					&	1				\\
	Expensive 					&	2				\\
	Common 						&	0				\\
	Uncommon					&	1				\\
	Rare 						&	2				\\
	Renewable 					&	0				\\
	Non-Renewable 				&	2				\\
	Reusable 					&	0				\\
	Non-Reusable 				&	1				\\
	Simple						&	0				\\
	Moderate Complex			&	1				\\
	Complex 					&	3				\\
	Quiet 						&	0				\\
    Normal Speech Level			&	1				\\
	Loud 						&	2				\\
	Short 						&	0				\\
	Same Length as Spell		&	1				\\
	Long 						&	2				\\ \hline
	\end{tabular}
\caption{SDP Casting Component Properties}
\end{table}


\begin{table}
	\begin{tabular}{lc} \hline
	Factor Name 				&	SDP 	\\	\hline
	No Target					&	0				\\	
	Directed,Self				&	-2				\\
	Single Target				&	-4				\\
	Multiple Targets			&	-8				\\
	Area of Effect				&	-16				\\	\hline
	\end{tabular}
\caption{SDP Target Types}\label{tab:SDPTargetType}
\end{table}

\begin{table}
	\begin{tabular}{lc} \hline
	Target Component	&	SDP \\ \hline
	Matter(Inanimate)	&	-1			\\
	Body(Animate)		&	-1			\\
	Mana(Inanimate)		&	-1			\\
	Lifeforce(Animate)	&	-1			\\
	Thought				&	-1			\\
	Perception			&	-1			\\
	Essence(Soul)		&	-1			\\ \hline
	\end{tabular}
\caption{SDP Target Components}\label{tab:SDPTargetComponents}
\end{table}

\begin{table}
	\begin{tabular}{lc} \hline
	AOE Scale	&	SDP \\ \hline
	0			&	0	\\
	1 Meter		&	2	\\
	2 Meters	&	4	\\
	5 Meters	&	8	\\
	10 Meters	&	16	\\
	20 Meters	&	32	\\ \hline
	\end{tabular}
\caption{SDP AOE Scale}\label{tab:SDPAOEScale}
\end{table}

\begin{table}
	\begin{tabular}{lc} \hline
	Range Scale	&	SDP \\ \hline
	0			&	0	\\
	0.1 Meter	&	-2	\\
	0.5 Meter	&	-4	\\
	1 Meter		&	-8	\\
	5 Meters	&	-12	\\
	10 Meters	&	-16	\\ 
	100 Meters	&	-24	\\
	1 Km		&	-32  \\ \hline
	\end{tabular}
\caption{SDP Range Scale}\label{tab:SDPRNGScale}
\end{table}


\begin{table}
	\begin{tabular}{lc} \hline
	Casting Time Scale	&	SDP \\ \hline
	Pulse				&	2	\\
	Second				&	4	\\
	5 Seconds			&	6	\\
	1/2 Min				&	8	\\
	2 Minutes			&	12	\\
	10 Minutes			&	16	\\
	1 Hour				&	24	\\
	4 Hours				&	32	\\
	1 Day				&	40	\\
	1 Week				&	48	\\ \hline
	\end{tabular}
\caption{SDP Casting Time Scale}\label{tab:SDPCTScale}
\end{table}

\begin{table}
	\begin{tabular}{lc} \hline
	Duration Time Scale	&	SDP \\ \hline
	Instantaneous		&	0	\\
	Pulse				&	-1	\\
	Second				&	-2	\\
	5 Seconds			&	-3	\\
	1/2 Min				&	-4	\\
	2 Minutes			&	-6	\\
	10 Minutes			&	-8	\\
	1 Hour				&	-12	\\
	4 Hours				&	-16	\\
	1 Day				&	-20	\\
	1 Week				&	-24	\\ \hline
	\end{tabular}
\caption{SDP Duration Time Scale}\label{tab:SDPDURScale}
\end{table}

\begin{table}
	\begin{tabular}{lc} \hline
 	Factor						&	SDP 		\\	\hline	 
	Rank linked QE				& 	5/1			\\
	Rank Linked RES				&	4/1			\\
	Rank Linked DUR				&	3/1			\\
	Rank Linked RNG				&	3/1			\\ \hline
	\end{tabular}
\caption{Costs for Misc. Factor Changes}\label{tab:MiscFactorChanges}
\end{table}

\begin{table}
	\begin{tabular}{lc} \hline
 	Factor Manipulation			&	Factor/SDP Ratio	\\	\hline	 
	CEF							& 	2/1			\\
	RES							&	2/1			\\
	QE							&	2/1			\\
	DUR							&	1/1			\\
	RNG							&	1/1			\\
	EC							&	3/1			\\ \hline
	\end{tabular}
\caption{Costs for Factor Changes}\label{tab:FactorChanges}
\end{table}

\end{document}
