\title{Shape Shifteren Glossary}
\author{Jim Mochel}
{\bf [Acrivan]}
\index{Acrivan}
\index{Fortal!Tower of}
\index{Tower!of Fortal}
Also Acrivan of the Seven Towers. Possessed the \ndx{Ring of
Channeling}. Wore it at the Tower of ForTal.

{\bf [Altzar] }
Demon Lord of Possession. Has killed an Avatar.

{\bf [Bennet Oth]} Weapon representative for Triam Hellspitter. Weapons
dealer in Marden.

{\bf [Black Sword]}
\index{Sword!Black}
\index{Black Sword}
Made by Aurioch. When he was through with the blade it
was so dangerous that he threw it into the earth and set three
guardians over it.

{\bf [Dau Pen] }
Dragon king that is worshipped primarily in Bengali and southern Doria.
\index{Dau Pen} The Elves know of him as the first dragon.

{\bf [Dau Shao]}
country NE of Doria, based on Russia circa 1300 or so

{\bf [Dal Sho]}
Actually a city that was the capital of Dau Shao. Now
inhabited by undead and ruled by a Lord Vampire. Known  affectionately as
"The Dead City"


{\bf [Demon of Possession] }
Morphus recognizes Demons of Possession because
he has hunted them before.

{\bf [Dissenta]}
Mage Assassins. Often recruit from the Black Cloud.

{\bf [Eye of Arkan] }
There is a Fortu connected to the Eye of
Arkan (Alteration Stone). An Elven Mage carries the Eye of Arkan.

{\bf [Karistean]}
\index{Karistaen}
Elves deal with them. They like crystals.
Mordanith has heard that they ward and watch for the balance of humanities
power and the powers of darkness to make sure that neither side overpowers the
other.  There is more to it than that but it is a well-kept secret.

{\bf [Lethar]}
\index{Lethar}
\index{Vampire}
Ancient race of body changers that was almost eradicated
before man was evolved. They and the elves are of an age , the Lethar are
slightly older. A non-corporeal creature that bonds parisiticly to a
human host to form a vampire.

{\bf [Linking Ward of Nureyev] }
Sigmund need not serve his creator while the
ward holds. Sigmund considers himself the brother of the ward.
\LWON talks to Sigmund. The \LWON is connected to the Citadel of the Seven .

{\bf [Orange Mage]}
\index{Orange Mage}
Named Taj Med. One of the Nine Elders that runs Dorea.

{\bf [Muriel] }
CatBird recognizes the name Muriel. She often visited
the Monastery in Marden. She comes and goes remarkably easily.

{\bf [Triam Hellsplitter] }
Ex-Gladiator. Now a weapon maker.

{\bf [Tyrethi] }
A runic language. They were named after a group of peoples.
They predate the Lythar. The Rikenian rune set is derived from it.
The Lythar were created by or descended from the Tyrethi.

{\bf [Gates of Chronos]}

According to Morphus the \ndx{Gates of Chronos} is a spell construct made
by a Mage of unbelievable power
about 3,000 years ago. It has no "real" position in space or time but
rather exists almost everywhere. In that sense it is similar in construction
to the \ndx{Pattern of Tyriontill} that the elves use to travel across the
Great Water (what they call the Ethereal that separates the World from
Faerie\- what you were floating in).

The Gate is a flow regulator\- of Time itself. It is similar in that sense
to the \ndx{Ward of Dof\-Sifrin} that surrounds the World (also known as the
\ndx{Bridge of Heimdell}, or the \ndx{Bifrost}). These "constructs" are
macro's of the universe.  They regulate physical and temporal laws and force
them into certain patterns.

When the Gates are open it is possible to use them to manipulate/travel
through/change time. Kheldar has worked on a Gate node before\dots

According to Mordanith they are a series of patterns created by several
beings in conjuncture, including \ndx{Labalas Eneroth}, Avatar of Correllan
and \ndx{Time Lord}.

{\bf [Lords of Time]}
The \ndx{Lords of Time} are those beings that have access to the Keys to Time.
They can control the flow/speed/direction and feel of time in specific
areas\dots
there are only three time lords known to exist at this time Heimdell, Labelas
Enoreth, and, of course, Lord Carolyn of the Elves himself\dots.

{\bf [Book of Winds]}
The Book of Winds is a holy text of the Grey Elven Church of Correllan.
It is a book that supposedly contains the design specifications for the
Element AIR. It is considered the seminal work on light craft, weather magery,
and wardings of air. It is also rumored to contain a history of the
Elvish people that goes back to their creation! Non-elves are not allowed
to look at the book.

{\it mordanith:} It is written by one of the first elves!  It is said one the Elder
Ten wrote its first five chapters called the Five Songs of the Winds.

It contains a preface that is said to be 876 pages long, and
supposed to reveal the purpose of elven creation.  Your father has
disdainfully shot down this rumor saying that the preface only hints
at vague prophesies concerning the purpose of the elves... dozens of
authors over millennium have added to it....

{\bf [Yis]}
Yis is the High Elven city to the North of the human Feudal Kingdoms that
is the largest Elven population center in the World. Coventree in western
Bengali, and Woodshome in north western Dau\-Shao are the only cities that
could rival it\dots\

{\bf [Greater Dark]}

The best way to fight it is LIGHT. And Light. And more Light. No\dots
seriously. One of the easiest
ways to fight a Dark that is on this World is to Banish it. Using light
power perform a Reverse Summoning on the Dark and it will be forced
to retreat back to Darkness, or be destroyed.

If you are facing it on neutral ground, it is best to do as much light and/or
fire damage as possible as quickly as possible. They recover frighteningly
fast and don't stop until they are destroyed. They are not intelligent so you
need not fear much in the way of tactics. They will tend to head straight
for their target (usually the nearest source of Nature or Life).
They are often controlled by Dark Mages though so be warned that a
controlled Dark CAN have tactics!

They are so powerful though that you would not want to fight a Greater Dark
unless you had a real good plan or lots and LOTS of spare power.

{\it mordanith:} It is one of the highest, and most powerful form of
elemental darkness known.  They are not all that bright and very reactive-
they head for the nearest, brightest light source and try to destroy
it.  What makes them scary is their power- average power- 3000 -5000
points of darkness; average size- 200 meters high!

How does one break the connection between a Greater Dark and the
Dark Mage controlling it ? Does the Sunbane have any effect on
Greater Dark ?

Kill the Dark Mage.  Destroy the material pattern of the
control(there will always be one).  Shape it out of existence.  Tear
it up with a power attack. 	Yes, the sunbane effects them but they
are so strong they can fight it.

{\bf [Greater Death]}
What effects does death and death magic have on creatures of Light?

Little. They appear in the form of Death typical of your culture, and they
are unbeatable by a mortal being\- though you have heard of men who have
done so. Death magic has no effect on beings with no Life or Nature in them.

{\it MORDANITH:}Can a greater Death do damage to a Faer Han/Quentar half breed ?

Only physical damage. Its illusions and enchantments would be at
half effective against you, and its death attacks would not work.

{\bf [the Warden of Kerestaen]}

The Kerestaen are an ancient race/group
of people/beings that are rumored to have some vital significance to the
survival
of humanity and life. The Vordack will say almost nothing about them except
that they are on one of the other planes and they are not like humans in
their violence. They are a peaceful people. They are rumored to hold
tremendous power\dots..

{\it MORDANITH:} You have heard that they ward and watch for the
balance of humanities
power and the powers of darkness to make sure that neither side
overpowers the  other.  You think there is more to it than that but
it is a well-kept secret.

{\bf [Tyriontill Kyrveon Alan-ad]}
Tyriontill is a living legend\- he is the elf who created/became/is the
Elvish Conjuring Pattern known as the Pattern of Tyriontill. He
is supposed to still be there and guides and maintains the pattern.

Is there enough left to Tyriontil to communicate with ?
Yes and no.  There can be slow translated communication.  There are
experts  at that process.

{\bf [Morphus's Staff]}

Since this predicament came about because of my staff, I will describe the
events leading to the construction of the staff, how it was created (
apologize for rushing the trees), how it and I are related and my future
plans. I believe that the Earth and Fire components are still at full
strength and that the water component still buffers the Earth and Fire
adequately. The final Binding will be of Air, but that time has
not come yet. The three woods embody the Aspects of Light,
Life(mine), and Nature. I will express my belief that to fully charge \&
complete the staff and stabilize the considerable Light, Life and Nature
power that I hope it will hold, it will be necessary to bind to it (
magically not physically) some quantity of Death, Dark and Decay.
It is my hope that the completed staff will be

a) less likely to spontaneously detonate because of the balanced forces

b) better able to "defend" itself because it will contain part of the forces
that might be directed against it and
thereby able to shunt or absorb some of the corresponding power

c) At least a powerful focus for my spells

d) At best, who knows power source, sanctuary for my soul (it does have my pattern), gateway to places that have tree clones growing there or elsewhere for that matter.

What comments, criticisms, or suggestions does the Vordack have for me?
(From both a Personal level (in view of the three D's)
and a Mage's point [of View])

{\bf Alex }
The Vordack says your staff will be better off not being a complete balance
of forces as it was not created as such. It says you are foolish to bind
darkness, death, and decay into the staff because although it will
"balance " the power of your staff\- it will also weaken it \dots
Leave it as it is and re\-enforce the elements that exist within it now.

{\bf Chris}
To clarify The Vordack says "as it was not created as such". Does this mean
that if all elements had been installed in it "at the beginning", it would not
have been "weakened" by the addition? Or that it would not be "as weak" as me
adding Death, Dark, and Decay now?

{\bf Alex }
It would not be "as weak".

{\bf Chris}
Chris's premise on this comes from the my thought of Druidic "Balance" in
D\&D where a power of Good attracts evil and a power of evil attracts good,
but a balanced or neutral power acts only where there is imbalance.
Also from the physics thought of lightning where massive charge
differences in the air and on the ground cause a discharge,
but a balanced positive/negative charge has potential but is
basically neutral.

Am I (Chris) working under a false assumption of something similar in your
world?

{\bf Alex }
You are not working under any incorrect theory\- but remember\- both the
real world and mine are more complicated than the level of complexity of
simple postulates can explain. The elements have more complex interactions
than simple polarity to one another\- and Morphus' elemental lore isn't
quite high enough to warrant extremely detailed knowledge.

{\bf Chris}
I realize that I might know enough, but I was wondering if Chris had a
definite mis-understanding of how this relationship was implemented in
your world. One of the times when the character should know what he
is doing even when the player does not.

Which, in His opinion, would be more stable a staff with light and dark
or a purified staff with more controls on the elements therein now?

{\bf Alex }
A purified staff with more controls would be more stable\dots
elemental opposition has to be very carefully maintained\- if
the balance gets skewed one side or the other the item becomes
dangerous and begins to go more over to the dominant side.

{\bf Chris}
Does he think the likelihood to be small for spontaneous detonation or
detonation during use? Or is that what he is referring to by
"re\-enforcing the elements that are in it now"?

{\bf Alex }
Yes\- the chance of spontaneous detonation is VERY small! The Vordack
was referring to purifying and putting more controls on the elements
therein now\- it would make the staff more stable. But remember, Chris, you
are hearing THE VORDACK'S OPINIONS\- he may not be correct.

{\bf Chris}
What is his opinion of its capability to "defend" itself because it
will contain part of the forces that might be directed against it and
thereby able to shunt or absorb some of the corresponding power?

{\bf Alex }
Can be true but requires precise balancing.

{\bf Chris}
What about enchanting the staff such that any power cast
(by something other than my pattern and not willingly accepted by me)
within my pattern's aura, be shaped and stored in the staff? with a
certain amount being used up in
overhead (shaping and storing) and a limit on what it could handle
"at one time" based on it's current energy level.

It would serve the same purpose to me as would my original suggestion and
would not have the negative powers bound to it. Seem's to have less
drawbacks too, so I might need to think of some balances.

{\bf Alex }
Ummm.. that is POSSIBLE. You will make a lot of enemies from mages!
You are talking about sucking constantly at Mordanith's power! It is possible
though if that is what you really want\dots. Mordanith could probably design
a Ward that could stop the effect with a Trigger attached so you could turn
off the Ward.

{\bf Chris}
Meaning that when I trigger the staff it allows a spell to be cast within
its aura without affecting said spell? I like that. I would prefer that
absorption be the default and this would enable me to have that
without pissing off my non\-aggressive mage encounters.

Jim

(in reference to Chris Alex Chris above)
The idea is very bad in my mind. I think that you should instead set up
a Morphus initiated draw of power. Morphus links to the staff add
performs what ever magery he is going to do without using his own men.
It would instead use the surrounding areas ambient energies.

This is better because it

[1] Is less likely to cause Mordanith to mangle the staff in a fit of Faer\-Han
annoyance at the damn thing screwing up his rituals or off\-hand sorceries and
maybe even Catbird's shifting.

[2] If the link is passive enough and you make it somewhat
like a mana diode you
can have it absorb when you are casting and using it without overload.

I honestly think that you are not perhaps approaching the design of the staff
from the right perspective.

What is your main goal for the staffs usage ?

{\bf Chris}
I'm not quite sure what Mochel is suggesting here(below), but
it looks interesting. What do you think Alex?

{\bf Chris}
a) It is me and I am it. Until I learn enough to disassociate myself of it,
I have to care for it as much as I care for myself.

b) Enchanted in such away that it can take care of itself, preferably on a
sliding scale energy level that starts out low and increases over time.
The primary reason for this being that over time my opponents power will
increase.

c) Focus for casting

d) The same enchantment for b) should probably handle taking care of
me at the same time since I will never be willingly out of Aura's range of
it.

{\bf Jim}
To Cover just the details above why not just create it as an alter ego.
Imbue it with power derived from the grove. In other words, create a symbiotic
magical construct with little inherent SCF but high MEN and Magical Defense.
By linking to it you can add your SCF to its MEN and crank. In addition,
make it trainable. In certain basic skills so that it can augment your skills
as a secondary caster would. I am sure that this would create an interesting
pseudo\-morphus\-personality "binary Image" that could grow slightly
differently than Morphus himself. It could be given personality,
thus entertaining the GM, and basic dictums about caring for you as
you care for it.

{\bf Chris}
e) My original concept at the time of creation was one of theme rather than
utility.

I wanted a staff that would embody the magics that seemed to be growing more
important to Morphus \- the elementals. A staff composed of all ten of the
Elements of the world seemed to be an interesting and Unique concept. Many
characters have magic items that others know them by, this would be Morphus's
trademark, just as his old friend Falstaff has always been known in the
"industry" by his white staff.

I am not against utility however. Morphus needs his own version of your spell
batteries, i.e. some non\-environment dependent power source. It could act as a
sanctuary for my soul (it does have my pattern). Or a gateway to places that
have tree clones growing there or planes associated with the powers in the staff.
I'm still thinking, looking for suggestions. Who knows, maybe a magical version
of a swiss army knife.

{\bf Jim}
I am rarely in favor of environment drawing power sources except at the
lowest level of energy. Instead, either let it gain and lose MEN
the way we do. Or let it gain it through conscious absorption of hostile
or neutral magic. whether it be at your conscious control or its,
just be sure that there is little chance of it absorbing Mordanith's workings.
You do not want to see a pissed Faer\-Han. (Not that I could do much to you but
I can make life very miserably. ) Repercussions on the Catbird and Erithmaen
front have to be watched very carefully also. Catbird is very nervous as is,
be very careful about random magics else you may wake up to the little dear
slitting your throat. I am not saying it is likely but it is within the realm
of possibility.

Remember that two thirds of survival is knowing who your friends are
so try not to make the rest of the characters nervous.

{\bf Chris}
Did I learn my pattern enough(while creating my staff) to use my pattern
itself as my focus?

{\bf Alex }
No.

{\bf [Miriel]}
A student of the man at the beach. She learned to Dreamwalk with you.
Later\- much later\- you would be lovers. You can almost see her face!

{\bf [That Damn Ring of Kheldar's]}
It was a seal to something\dots.. it was a ring of power as well\dots
it was a gift from a King or Lord or Prince or some such. In it is
bound something powerful\dots. the ring is bound to you\dots
it is a legendary ring\dots

{\bf [Tower of ForTal]}

The \ndx{Tower of ForTal} on the edge of the Wasted Lands north of the
\index{Tower!of ForTal|ii}
Bay of Sargon\dots.. You were working on a scroll of shaping to
repair a breach in the \ndx{Wall of Thelaya}.

The Vordack can tell you that the Tower of ForTal is one of the
Bastions of the RING. It is one of the power nodes that sit on the
outside of the wasted lands along the Wall of Thelaya.
It is run down and not often visited now. The wall was breached most seriously
in recent times about three years ago when
Prince Keliet\-ah\-Ventir was slain while fighting a goblin horde advancing
into the World. In that battle a Lord Paladin of Heimdell, Duke Mallard,
was slain by No\-Rennan(dark God of Darkness and CHaos and Evil),
and Arioch slew an Avatar of Arken(God of Death) as it was forming.
Many goblins slipped over the wall and raided the Elvish lands.

{\bf [The RING]}
The \ndx{RING} is an organization Kheldar belongs to. There are druids
involved\dots and it involves the Mother\dots

{\it MORDANITH:} The RING is a group of humans who have achieved a very high state of
order  and are bound to the force of nature.   Despite this they
serve a balance between  Decay and DEath and Life and Nature.  They
are pro-world, possibly linked to the  Kerestaen.  There are many
historical links between the RING and the Grey Wanderers.

{\bf [Dau\-Shao]}
Eastern Dau\-Shao is a land of unicorns, elves, faerie and dragons. The
princedoms are ruled in peace(for the most part) and you have enchanted
woods, ancient wizards, and holy places\dots.. that's why.
(Morphus also knows it is a very high Will area\dots magic is easier
there. Dau\-Shao is approx. 500\-800 miles north of present
Position of the Hetasian\-Dorian border.

{\bf [Cetaneans]}
SCUM\dots.. the Cetaneans are a sub\-group of the Tolnian racial block which
includes Tolnians, Pentarens, and Cetaneans. The Hetasian and Maeran people
have elements of the Tolnian racial stock in them as well.
They are typically found on the eastern coast of the continent on the coast.
They are organized in city\-states, poli, and they are run by a
representational government. Their are strong alliances between the poli\dots
unlike their northern neighbors the Pentarens who are constantly having infighting
amongst the poli(which are feudally run by hereditary and challenge based
nobility that ride winged horses\dots.)

{\bf [Hetasia]}
Hetasia refers to a land or a people. They exist in the free states and to
the South. they are a dark small people(they look like Mexicans). The hetasian
kingdoms to the far south of Tareth are ruled by the Wizard\-King. if
you want more details see me in person or ask me again when I have more time.

{\bf [Kymri]}
They are a Celtic people, clan oriented that live to the north of the feudals.
They are ruled by chieftains, druids, and bards. North of north of Dau\-Shao.
Dwarves are north of north of Kymri.

{\bf [Na\-Kor]}
The Na\-Kor are a race of half elves who fought against the Golden Empire.
They
were reknown for their efficiency and fighting talent. They were ruthless
hunted
down by witch hunters thousands of years ago\dots few remain. But those that
do are champions of the cause against the domination of human kind. They are
feared by those ignorant of their true cause.

{\bf [Symbian]}

Rune system\dots long story.. no time to explain\dots it is not worth pursuing
right now\dots when we have some time Chris, and are sitting around I will tell
you the story\dots

{\bf [Arkenian]}
From about 2000 years ago the language spoken by the people from whom Vardigan
is descended\dots.. the language of the magic of death and life. The rune language,
its written form is used for most wizardries involving life and death.

{\bf [Estarren]}

No time now. Is an old Tolnian /Dorian language from a 1000 years ago\dots\dots
spoken by Madra

{\bf [Madra]}
Now worshipped as the Mother. Responsible for Schools of LIFE, NATURE, Possibly
WATER and others. Period approx. 1500 years ago. Her teacher was from (last
of?) another epoch. It is believed Madra may have taught the Wizard King in his youth

{\bf [Wizard King]}
Wizard King was born in Tolnia. He was an alchemist.

{\bf [Rune Languages]}
\begin{verbatim}
School		R				L				Color
Shaping		RTolnedron		LMultath			Yellow/Blue
Binding		R				L				Yellow/Red
Prophesy	RTolnedron		LDau\-Shao		Light Blue
Lssr Summoning		RBodak			LAncient Dorian		Gold
Geomancy	RAncient Korvanir	LAncient Dorian		Earth
\end{verbatim}

{\bf [Magic Items]}
There are 117 artifacts ? 30 stones, ? 25 swords, ?20 staffs. The
stones were created by a Thaumaturge  named Halga (sp?)

{\bf [CatBird]}
Is it possible that Catbird is unconsciously using the Gates of Chronos?

Anything is possible \dots but no, it is very unlikely.  She might be
managing to slip through the Gates and not be stopped by them.  They
as much ward time and space as control it.


{\bf [Falstaff and Kheldar]}

{\it MORDANITH:} Your sense of human history isn't all that it could be.
You think he
and his friends have NOT had a major impact on the Elves.  You think
Falstaff and he date back to the pre-Purge days of  over 500 years
ago, but probably after the founding of Marden 1800 years ago.  I am
not exactly sure what you mean by this so please ask more
specifically.  Falstaff and he belong to a group of mages known
historically as the Grey Wanderers.  They were NOT specifically
Abjurationists, but most were, and they fought against the forces of
Death and Chaos... they did not always fight with the Elves.  These
men had ambiguous morals, and goals, they entered an area, wreaked
their changes, and then left again.  It is they, and the group of
individuals  called the RING that made the Wall of Thelaya.  They had
a leader who was known as the  BLADE OF STONE that, it is believed,
may have caused the Mage Purge by assassinating  a Death Lord that
had taken a country from a weak King.  The Death Knight was a
creature of darkness and great power but the evil of the purge may
have done more  damage.  By slaying the Death Lord the Blade of Stone
released one hundred Faer-Han that were trapped by the Black Cloud's
wizards, and he broke the hold Death was gaining on the entrances to
Faerie. It also had major effects on the prime Material but you
never studied that.

It is a historical hot subject as to whether or not that was just an
inevitable spark in the power pool, or did the BLADE OF STONE truly
not care about the consequences of his actions.

{\bf [Morphus]}

{\it MORDANITH:} Is it possible that the secondary ward placed on Morphus is
will magic ?

Yes.  It is also Abjurational - Warding mucho grande.

How easily cold the Vordak have mistaken Morphus's pattern for that of
a dragon ?

Unlikely.  You think Morphus' mind doesn't look anything like a Dragon's.

I get the impression that Kheldar may have done something to help
initiate the original purge. Do I remember the names of any of those who
did so ? Who may have performed some heedless action and endangered or
killed others ?

Yes.  The Ice Wolf is said to have had something to do with the
original purge  but it was primarily, according to conservative elven
scholars, the Blade of Stone that caused the Purge.  Others argue the
\index{Stone!Blade of}
"it was inevitable, and the Grey Wanderers did  what they had to"
argument.

The Lord of The Dorian Empire Chepu Akanasi was the first major Lord
to declare Purge.  The rest of the human world quickly followed suit.
It happened fast- irrationally fast!  It was probably aided by
external forces but no one knows who.

By Morphus's past memories I can guess that Morphus has been keyed  to
Abjuration in the Human manner. Is it possible that he has
incorporated that key into himself ?

Yes.  It seems almost certain that he has been keyed.  It is also
possible,  though less so that he incorporated the Key into himself.


{\bf jim}
What is destroying the Linking Ward in the Hall of kings ? Is it
likely that this only one of several linking wards ?

Hard to say.  Hard to say.  There are probably other linking wards.

{\bf [Falstaff]}
One of the Grey Wanderers- Known as the White Mage- fought the
Air Raver Oleanth who tried to link to Tyriontill and absorb him.
The White Mage is said to be a Binder and a Willworker of some Power.

The White Mage and The Blade of Stone were said to often be at odds.
The Ice Wolf and the Stormlord were other Grey Wanderers that were
rumored or storied to interact with the elves.

{\bf [Vordack]}
Now that I know which Vordak this is (Guards the Gates of Chronos,
He who brought the Book of Winds back, etc..) can I figure out who
else has summoned him ?

Not a chance.  Your lore of the Vordock is much to small.  This
is a BIG, and super unusually, powerful Vordock.  You think your
summoning probably  should not have called one so powerful.


{\bf [The Book of Seven Sorceries]}
Chapter Three Warlock. 2,000 Years Old. Mentions the Linking Ward
of Nureyev (Facilitated Power Blast)

{\bf [Dal Sho]} Actually a city that was the capital of Dau Shao.
Now inhabited by undead and known as the Dead City.

{\bf [Tollen]}
Encountered Immortal Abjurationist Dragon (Bronze) called worm

{\bf [DRAY]}
Have Talked to \ndx{Dray} the Black Obelisk and AJAX the Archeologist
Dray is said to be Healer,thief, and Warrior.

{\bf [The Pattern]} is an abjurational teleport.

{\bf [Smokehewn]} Bronze Dragon W. of the Free States, E.of Bengali.
{\bf [Jalgor]} 40' Long Bronze

The third state of Theridden has the Orb of Abjuration
as part of the Emperor's Library

{\bf [Ring of Channeling]} (Bronze - Runic)
{\bf [Staff of Absorbing]} Power in free flow.
{\bf [Energy Damp]} Ward constantly absorbs mana
( Near complete spell description from before the purge by Dazara ).

{\bf [Library Temple of Usul]} (Drell Acolyte) in thespesian: Dorean State
Dalas - H. Priest

{\bf [Marden]}
Marden is composed of roughly 60\% Hispanic , 20-30\% seem to be pure white
persian (Dorean), the balance seems to be everything else. Moorish Mexico or
Portugal, temperature is 90\% (there does seem to be weather control) Brightly
colored clothing, little or no leathers - only silk. Few open wells in public,
seem mostly be cisterns. Lots of noise. Cleanliness is not striking.

{\bf [Marden Mage Guild]}
In the mages guild they are maybe 30 mages of Mordanith's level or greater
(counting the council) out of 10,000 mages. There are two or so warders of
Mordanith's level or greater.


{\bf [Citadel of the 7]}
{\bf [Forbidden Zone]}
{\bf [Fuedal States]}
Dalsho - Wizard King Numedides

{\bf [ShapeChangers]} Lycanthropes, Weres, Dullos, Lythar, Woodelves, Vampires
Ven Shamans

{\bf  Lythar - demonic based creatures - Supposedly bred with Grey Elves
to form Golden Children of the golden empire. Golden children and Humans
combine to produce the Na-Kor.

\item[Catbird's Memory Regression]}

We take the Urchin far back into its history. ::A monk in rainbow robes
is throwing a knife with regularity :: A man is carrying it in the
rain.:: Repeated views of long blond hair bright eyes :: Large Hallway
with patterned ceilings :: Sitting in the corner of the monastery hiding
out :: Being caught by a bodyguard with a dragon helm :: -- Mordanith
realizes that Catbird is what they call a thief -- :: Rainbow robes with
green hood :: Man carrying her is hit by a black shafted arrow with red
feather :: Priest in colored robes is called Tev :: Tev threw a knife
near her :: -- Mordanith discovered he was to deeply tied in -- He Broke
out -- To discover that Morphus was losing it big ..... I slap him. He
turns, runs, and changes into a falcon . Mordanith sends a telepathic
shot that says that Morphus is Morphus... I shout him into consciousness
as I back out. ::

The God Oriel ?  The Black Shafted arrows with red feathers. Morphus
remembers the loss of his Tantir guard to a similar shaft.

{\bf [Usul]}
Usul was a fairly powerful mage. Rumored to have taught Heimdall his
magery. During the second Chaos war he obtained the Orb of Light.
After several years of intensive study of the Orb he summoned
Asmonar(Death) into his presence. Usul was considered a neutral
party. He patterned a curse \dots

{\bf [Foreseeing of Vartigan's Future]}

Singing Warrior with cut hair walking with an Old man.
Arak in desert robes , wearing a nimbus of power.
Orange Red rock walls, Huge wooden stakes with dried human bodies on
them.

A Dark room with a priest of Correllan looking outward. Bloody Runes
on the wall\footnote{The Runes are Rikenian. From the lethar. Necron
is derived from this rune set}.

Vartigan, dressed as a desert person, rides on. There is no sign of
Arak. A hand pushes itself out of the sand as a dragon rises beyond.

{\bf [Kester]} The city worshipped death. Archmage Grumsch was one
of these. Archmage and Paladin : Arkon. \index{Cities!Kester}

{\bf [Kilsorana]}
Kilsorana has contributed three spells of not, two of which were lost with
her.

One was her Web spell. It is a trapping spell of serious kick butt power.
She once stopped a cavalry charge cold with one cast of it\dots This can be
reconstructed from work she did at the \ndx{Seeing Eye Monastery} on the
Southern shore of the \ndx{Immyrl Sea}

One was her transmute element spell. It allowed for the actually alteration
of one elements into another. It is unknown how she achieved this but she
was witnessed performing it at least twice. It was a long, slow ritual.

The other lost spell was a very powerful trigger spell that altered
the nature of the item the bound spell was cast in to release the
spell. Very subtle because it does not look like a trigger because
it is not the correct form and purity of material until it is transformed.

You know she was known to \ndx{Krell} and she has a reputation for being rude
and brash and very cold to other mages.

Mordanith knows of her as the Green Elven Mage that was involved in
the defeat of the Raver \ndx{Oleanth}. She was "lost" during the battle.
She was said to be bad tempered and quixotic at best.
She traveled with a skilled monk named Way-li.

{\bf [Seeing Eye Monastery]}
\index{Seeing Eye Monastery}
There are ten major mages there - it is a divination library, a
massive alteration library(surprise), a magic item creating
library, a linguistics library, and some weird assorted books collected
by one of the mages who is an "Ice Mage" whatever that means...His 
name is Passas. 

{\bf [The Green Elves]}
The "Green Elves" are a bastard sub-race of the Sea Elves that result
from sea elven and wood elven cross breeding. Kilscarana Moonmist was
one of these half-breeds. They almost never survive pregnancy and
they are considered very rare by the elves- Which, by the way, makes them
unbelievably rare! ~

{\bf [The Greens]}
A political institution that is primarily High Elves
and may or MAY NOT have a beef with Kheldar.

{\bf The Sea Elves]}
The legendary race of Elves that, with
COrrellan's permission (unlike the Drow),  made an experimental change
basic nature. They swapped water where Air now is in the FAer-han.
Most Grey Elves were revolted at this and their is often conflict ..
most of the experimental subjects died- but some lived and bred true.

Kilscarana's "people" are the Sea Elves. They
are much like Grey Elves- haughty aristocratic, they believe themselves
to be superior, the "next model up" in evolution. They are tres powerful
magically and dangerous, but they are bound to the water as
Grey Elves are bound to the air... Green Elves can usually do both!!!!

{\bf [Immryl Sea]}
Where is the Southern shore of the immyrl sea relative to Marden
or Dao Shau? It is VERY North and a little tiny bit East of Marden.
It is a little North and a little West of Dao-SHau.

{\bf [Rainbow Order]
They wear rainbow robes with green hoods. (Just so they can
be inconspicuous in Marden, right? ;-)  They are a suicide cult. They have
some (perhaps mostly)   mages. When they show up, I have the impression from
what you said, that violence typically happens.  When they show, I leave.  I
know where their temple in Marden is.  I don't know if the following
is player knowledge or CB knowledge:

Morphus appears to have started this cult.

{\bf [Tev]
Most of this information is derived from Pallus the diviner
and Endir, the researcher for the theive's guild.

I remember sitting in the monastery, and Tev throwing a knife repeatedly into
a target.  Tev is wearing the rainbow robes.  My protector, a blond,
bright-eyed man who is not my father, is killed by a
black-shafted arrow with red fletching.   Tev throws a knife near me.  I
have the impression of fear and (now) anger at Tev.

See also the discussion with the street urchin.

Geshak (captain of the Dissenta ) + 50 basic Dissenta
    Minion of the WK and in direct opposition to Shifters


\printindex
\end{document}
