\documentstyle[palatino,sh]{article}
\begin{document}

\hbox{\raggedright
\vtop{
\noindent
{\bf Physical Body (PBD)}
The amount of physical damage a character can absorb. Derived from PST
and PEN.

\noindent
{\bf Physical Strength Effect   (PSE)}
    The amount of damage a character can inflict by basic use of strength.
    Derived from PST.

\noindent
{\bf Physical Fatigue (PFT)}
    The amount of energy a character can expend, either in damage or in
    work. Derived from PEN and PAG.

\noindent
{\bf Physical Awareness (PAW)}
    A measure of a chracter's connection and responses to his physical
    senses. 

\noindent
{\bf Physical Movement (PMV)}
    A measure of the character's movemnt. Derived from STR and END and
    racial modifiers.

\noindent
{\bf Accuracy (ACC)}
    A measure of the character's effectiveness with projectile or missile
    weapons. Derived from STR and DEX. Could also be called Physical
    Accuracy.

\noindent
{\bf Physical Combat Ability (PCA)}
    A measure of a character's ability to in\-flict 
	dam\-age in hand-to-hand and melee combat. Derived from 
	STR, PAG, DEX.

\noindent
{\bf Physical Defense (PDF)}
    A measure of a character's ability to dodge or evade  to avoid
	taking damage in hand-to-hand or melee combat. Derived 
	from PAG, DEX.
}

\vtop{
\noindent
{\bf Mental Body (MBD)}
    The amount of mental damage a character can absorb. Derived from MEN and MST.

\noindent
{\bf Mental Strength Effect     (MSE)}
    The amount of mental damage a character can inflict by basic use of
    mental strength. Derived from MST.

\noindent
{\bf Mental Fatigue (MFT)}
    The amount of mental energy a character can expend, either in damage
    or in work. Derived from MEN and MAG.

\noindent
{\bf Mental Awareness (MAW)}
    A Measure of the character's connection and ability to quickly correalate
    concious and subconcious clues absorbed by his senses. Derived from PSI,MAG.

\noindent
{\bf Mental Movement (MMV)}
    A measure of the characters rate of movement in the purely mental 
	realms of psionics and computer interfaces.

\noindent
{\bf Focus	(FCS)}
    A measure of the character's effectiveness with focused mental
    actions. Derived from MST and MAG. could also be called Mental
    Accuracy.

\noindent
{\bf Mental Combat Ability (MCA)}
    A measure of a character's ability to inflict damage in Mind to Mind
    combat. Derived from MST, MAG, PSI

\noindent
{\bf Mental Defense (MDF)}
    A measure of a character's ability to avoid taking damage in mental
    combat or highly stressful situations. Derived from MAG.

\noindent
{\bf General Awareness (GAW)}
    A measure of a character's connection and response to his Mental and
    physical senses. Derived from MAW and PAW.
}
}
\end{document}
